### 2020-11-02 summary/summary.tex
feat: seminar

\documentclass[11pt]{article}
\usepackage[document]{ragged2e}
\usepackage[utf8]{inputenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{tikz-qtree}
\usepackage[final]{pdfpages}
\usepackage[parfill]{parskip}
\usepackage{listings}

\newcommand\erfequiv{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily erf}}}{\equiv}}}

\begin{document}

\title{Seminar 1901 - Darstellung und Verarbeitung unsicheren Wissens mit logikbasierten Methoden}
\author{
	Heltweg, Philip
}
\maketitle

\begin{tabular}{l l}
Matrikelnummer: & 3230880\\
\\
Name, Vorname: & Heltweg, Philip\\
\\
Strasse, Nr.: & Kerpener Straße 10\\
\\
Auslandskennzeichen, PLZ, Wohnort: & D 50937 Köln\\
\\
\end{tabular}

\newpage

\section{Concepts}
\begin{itemize}
    \item belief revision, iterated belief revision, non-prioritised revision
    \begin{itemize}
        \item 1, 7, 12, 20, 21, 22, 23, 24, 34
        \item \textbf{C. Alchourrón, P. Gärdenfors, and D. Makinson. On the logic of theory change: Partial meet contrac- tion and revision functions. Journal of Symbolic Logic, 50(2):510–530, 1985.}
        \begin{itemize}
            \item "AGM postulates for belief revision"
        \end{itemize}
        \item R. Booth and T. Meyer. Admissible and restrained revision. Journal of Artificial Intelligence Research (JAIR), 26:127–151, 2006.
        \item \textbf{A. Darwiche and J. Pearl. On the logic of iterated belief revision. Artificial Intelligence, 89:1–29, 1997.}
        \begin{itemize}
            \item "reformulated the AGM postulates for belief revision to be compatible with their suggested approach to iterated revision"
        \end{itemize}
        \item A. Grove. Two modelings for theory change. Journal of Philosophical Logic, 17:157–170, 1988.
        \item S. O. Hansson, E. Ferme ́, J. Cantwell, and M. Falappa. Credibility-limited revision. Journal of Sym- bolic Logic, 66(4):1581–1596, 2001.
        \item S.O. Hansson. A survey of non-prioritized belief revision. Erkenntnis, 50(2):413–427, 1999.
        \item Y. Jin and M. Thielscher. Iterated belief revision, revised. Artificial Intelligence, 171(1):1–18, 2007.
        \item H. Katsuno and A. O. Mendelzon. Propositional knowledge base revision and minimal change. Artif. Intell., 52(3):263–294, 1991.
        \item A. Nayak, M. Pagnucco, and P. Peppas. Dynamic belief revision operators. Artificial Intelligence,
146:193–228, 2003.
    \end{itemize}
    \item agent
    \item sound and complete properties
    \begin{itemize}
        \item Wikipedia: "Informally, a soundness theorem for a deductive system expresses that all provable sentences are true. Completeness states that all true sentences are provable." -> Vollständig und Korrekt
    \end{itemize}
    \item total preorder
    \item strict preference hierarchies
    \item interval orderings
    \begin{itemize}
        \item 2, 15, 32
        \item J.F. Allen. Maintaining knowledge about temporal intervals. Communications of the ACM, 26(11):832–843, 1983.
        \begin{itemize}
            \item "such interval orders have been studied in the context of temporal reasoning"
        \end{itemize}
        \item P.C. Fishburn. Interval orders and interval graphs. Wiley, New York, 1985.
        \begin{itemize}
            \item "the question of how our work fits into the more general use of interval orderings"
        \end{itemize}
        \item \textbf{M. Öztürk, A. Tsoukia`s, and P. Vincke. Preference modelling. In Multiple Criteria Decision Analysis: State of the Art Surveys, volume 78, pages 27–71. Springer, 2005.}
        \begin{itemize}
            \item "such interval orders have been studied in the context of [...] preference modelling"
            \item "in a similar vein, there seems to be a close connection between our work and the work on preference modelling using interval orderings by Öztürk et al
        \end{itemize}
    \end{itemize}
    \item preference aggregation
    \begin{itemize}
        \item 3, 19
        \item K. Arrow. Social Choice and Individual Values. John Wiley & Sons, 1963.
        \item S.M. Glaister. Symmetry and belief revision. Erkenntnis, 49(1):21–56, 1998.
        \begin{itemize}
            \item "for more discussion on social choice-like conditions and their relevance to tpo-revision we refer the reader..."
        \end{itemize}
    \end{itemize}
\end{itemize}

\section{Ausführliche Inhaltsgliederung}
Bis zu diesem Zeitpunkt erwarten wir von Ihnen eine Kurzfassung Ihres Vortrages, die  Folgendes enthalten sollte: ausführliche Inhaltsgliederung, Angabe der Schwerpunkte, Kommentierung der von Ihnen gewählten Stoffauswahl, Zusammenfassung. Umfang: ca. 4-5 Seiten. Danach werden wir uns wieder an Sie wenden. Bitte schicken Sie uns Ihre Kurzfassung per E-Mail im PDF-Format zu.
\section{Angabe der Schwerpunkte}
\section{Kommentierung der Stoffauswahl}
\section{Zusammenfassung}

\newpage

\section{Erklärung}
Ich erkläre, dass ich die schriftliche Ausarbeitung zum Seminar selbstständig und ohne unzulässige Inanspruchnahme Dritter verfasst habe. Ich habe dabei nur die angegebenen Quellen und Hilfsmittel verwendet und die aus diesen wörtlich oder sinngemäß entnommenen Stellen als solche kenntlich gemacht. Die Versicherung selbstständiger Arbeit gilt auch für enthaltene Zeichnungen, Skizzen oder graphische Darstellungen. Die Ausarbeitung wurde bisher in gleicher oder Ähnlicher Form weder derselben noch einer anderen Prüfungsbehörde vorgelegt und auch nicht veröffentlicht. Mit der Abgabe der elektronischen Fassung der endgültigen Version der Ausarbeitung nehme ich zur Kenntnis, dass diese mit Hilfe eines Plagiatserkennungsdienstes auf enthaltene Plagiate geprüft werden kann und ausschließlich für Prüfungszwecke gespeichert wird.

\end{document}

### 2020-11-02 summary/summary.tex
feat: seminar

@@
 
+\section{Goal}
+Totale Präordnungen gelten als die Basisrepräsentation fur iterierte Revision von Wissen.
+Um auch Prinzipien für das Ändern von totalen Präordnungen zu untersuchen, schlagen Booth und Meyer vor, Intervalle zu ordnen.
+Diese grundlegende Arbeit zu dieser Idee soll aufbereitet und präsentiert werden.
+
 \section{Concepts}
 \begin{itemize}
+    \item belief, belief set
     \item belief revision, iterated belief revision, non-prioritised revision
@@
         \item A. Grove. Two modelings for theory change. Journal of Philosophical Logic, 17:157–170, 1988.
-        \item S. O. Hansson, E. Ferme ́, J. Cantwell, and M. Falappa. Credibility-limited revision. Journal of Sym- bolic Logic, 66(4):1581–1596, 2001.
+        \item S. O. Hansson, E. Fermé, J. Cantwell, and M. Falappa. Credibility-limited revision. Journal of Sym- bolic Logic, 66(4):1581–1596, 2001.
         \item S.O. Hansson. A survey of non-prioritized belief revision. Erkenntnis, 50(2):413–427, 1999.
@@
     \item agent
+    \item epistemic state of an agent
     \item sound and complete properties
@@
         \item 3, 19
-        \item K. Arrow. Social Choice and Individual Values. John Wiley & Sons, 1963.
+        \item K. Arrow. Social Choice and Individual Values. John Wiley \& Sons, 1963.
         \item S.M. Glaister. Symmetry and belief revision. Erkenntnis, 49(1):21–56, 1998.

### 2020-11-06 notes/notes.tex
feat: starting summary for seminar

--- 2020-11-02 summary/summary.tex
@@
 \section{Goal}
+\textbf{Richard Booth and Thomas Andreas Meyer. How to revise a total preorder. J. Philos. Log., 40(2):193–238, 2011.}
+Keywords: Epistemic State, Belief Revision, Preference Aggregation, Strict Preference, Social Choice Theory
+
 Totale Präordnungen gelten als die Basisrepräsentation fur iterierte Revision von Wissen.
@@
 
+\begin{itemize}
+    \item 'This paper is a combined and extended version of papers which first appeared in the proceedings of KR 2006, the 10th International Conference on Principles of Knowledge Representation and Reasoning [8], and ECSQARU 2007, the 9th European Conference on Symbolic and Quantitative Approaches to Reasoning with Uncertainty [10].'
+    \item Booth, R., Meyer, T., \& Wong, K. S. (2006). A bad day surfing is better than a good day working: How to revise a total preorder. In KR (pp. 230–238). AAAI Press.
+    \item Booth, R., \& Meyer, T. A. (2007). On the dynamics of total preorders: Revising abstract interval orders. In ECSQARU (pp. 42–53).
+\end{itemize}
+
 \section{Concepts}
@@
     \item belief, belief set
+    \begin{itemize}
+        \item set of held beliefs of an agent, 'true sentences'
+    \end{itemize}
     \item belief revision, iterated belief revision, non-prioritised revision
     \begin{itemize}
+        \item 'Das JMTS von Doyle berücksichtigt aber nicht nur explizit nichtmonotone Regeln, sondern vollzieht auch einen Wechsel des Wissens- oder Glaubenszustandes (eines maschinellen oder humanen Agenten).
+Einen solchen Wechsel bezeichnet man als Wissensrevision (belief revision).
+Heute sind die beiden Bereiche der nichtmonotonen Logiken und der Wissensrevision parallele, aber eng miteinander verwandte Fachgebiete, die sich eines großen Interesses und reger Forschungsaktivitäten erfreuen (vgl.
+die beiden Übersichtsartikel [Mak94] und [GR94], siehe auch [KI99, KI01]).
+Die Arbeit von J.
+Doyle [Doy79] leistete zu beiden einen frühen Beitrag.' - 1845 KE 3/4
+        \begin{itemize}
+            \item Makinson, D.: General patterns in nonmonotonic reasoning.
+In: Gabbay, D.M., C.H.
+Hogger und J.A.
+Robinson (Herausgeber): Handbook of Logic in Artificial Intelligence and Logic Programming, Band 3, Seiten 35–110.
+Oxford University Press, 1994.
+            \item Gardenfors, P.
+und H.
+Rott: Belief Revision.
+In: Gabbay, D.M., C.H.
+Hogger und J.A.
+Robinson (Herausgeber): Handbook of Logic in Artificial Intelligence and Logic Programming, Seiten 35–132.
+Oxford University Press, 1994.
+            \item Kern-Isberner, G.: A unifying framework for symbolic and numerical approaches to nonmonotonic reasoning and belief revision.
+Fachbereich Informatik der FernUniversität Hagen, 1999.
+Habilitationsschrift
+            \item Kern-Isberner, G.: Conditionals in nonmonotonic reasoning and belief revision. Springer, Lecture Notes in Artificial Intelligence LNAI 2087, 2001.
+            \item Doyle, J.: A Truth Maintenance System. Artificial Intelligence, 12:231–272, 1979.
+        \end{itemize}
+        \item 'Das JTMS-Verfahren so wie es hier vorgestellt wurde, kann allerdings nur angewendet werden, wenn einem TM-Netzwerk Begründungen hinzugefügt werden, nicht aber, wenn Begründungen entfernt oder modifiziert werden.
+Um diese Fälle zu behandeln, sind andere Methoden der Wissensrevision notwendig.' - 1845 KE 3/4
+        \item 'minimal change': 'Auch das DDB-Verfahren kann nur dann erfolgreich durchgeführt werden, wenn Annahmen, also nichtmonoton etablierte Knoten zurückgesetzt werden können.
+Dadurch wird eine sehr vorsichtige, möglichst geringfügige Änderung ermöglicht.
+Damit nimmt das JTMS von Doyle ein Paradigma vorweg, das auch heute noch eine zentrale Bedeutung für die Wissensrevision besitzt: Das Paradigma der minimalen Änderung (minimal change.)' - 1845 KE 3/4
         \item 1, 7, 12, 20, 21, 22, 23, 24, 34
@@
         \begin{itemize}
-            \item "AGM postulates for belief revision"
+            \item 'AGM postulates for belief revision'
+            \item theory expansion, revision and contraction with new information, revision as contraction, defining constrains (called postulates) on an operator for theory contraction on new information, operator changes currently held belief set here -> not epistemic states
         \end{itemize}
@@
             \item "reformulated the AGM postulates for belief revision to be compatible with their suggested approach to iterated revision"
+            \item works on epistemic states, not belief sets
         \end{itemize}
         \item A. Grove. Two modelings for theory change. Journal of Philosophical Logic, 17:157–170, 1988.
+        \begin{itemize}
+            \item ordered worlds/spheres approach
+        \end{itemize}
         \item S. O. Hansson, E. Fermé, J. Cantwell, and M. Falappa. Credibility-limited revision. Journal of Sym- bolic Logic, 66(4):1581–1596, 2001.
@@
     \item epistemic state of an agent
+    \item epistemic entrenchment
     \item sound and complete properties
     \begin{itemize}
-        \item Wikipedia: "Informally, a soundness theorem for a deductive system expresses that all provable sentences are true.
-Completeness states that all true sentences are provable." -> Vollständig und Korrekt
+        \item Wikipedia: 'Informally, a soundness theorem for a deductive system expresses that all provable sentences are true.
+Completeness states that all true sentences are provable.' -> Vollständig und Korrekt
     \end{itemize}
     \item total preorder
+    \begin{itemize}
+        \item Wikipedia: 'In mathematics, especially in order theory, a preorder or quasiorder is a binary relation that is reflexive and transitive.
+Preorders are more general than equivalence relations and (non-strict) partial orders, both of which are special cases of a preorder.
+An antisymmetric preorder is a partial order, and a symmetric preorder is an equivalence relation.' + total = for all a, b a <=b or b <= a
+        \item transitive, connected relation, unifying semantics booth
+        \item unifying semantics booth: preorders partition into equivalence classes
+    \end{itemize}
     \item strict preference hierarchies
@@
         \begin{itemize}
-            \item "such interval orders have been studied in the context of temporal reasoning"
+            \item 'such interval orders have been studied in the context of temporal reasoning'
         \end{itemize}
@@
         \begin{itemize}
-            \item "such interval orders have been studied in the context of [...] preference modelling"
-            \item "in a similar vein, there seems to be a close connection between our work and the work on preference modelling using interval orderings by Öztürk et al
+            \item 'such interval orders have been studied in the context of [...] preference modelling'
+            \item 'in a similar vein, there seems to be a close connection between our work and the work on preference modelling using interval orderings by Öztürk et al'
         \end{itemize}
@@
         \begin{itemize}
-            \item "for more discussion on social choice-like conditions and their relevance to tpo-revision we refer the reader..."
+            \item 'for more discussion on social choice-like conditions and their relevance to tpo-revision we refer the reader...'
         \end{itemize}
@@
 \section{Angabe der Schwerpunkte}
+Citing entry from my bibliography \cite{kutz_2013}.
 \section{Kommentierung der Stoffauswahl}
 \section{Zusammenfassung}
+
+\newpage
+
+\bibliographystyle{plain}
+\bibliography{references}
 

### 2020-11-06 notes/summary.tex
feat: starting summary for seminar

\documentclass{article}

% If you're new to LaTeX, here's some short tutorials:
% https://www.overleaf.com/learn/latex/Learn_LaTeX_in_30_minutes
% https://en.wikibooks.org/wiki/LaTeX/Basics

% Formatting
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage[titletoc,title]{appendix}

% Math
% https://www.overleaf.com/learn/latex/Mathematical_expressions
% https://en.wikibooks.org/wiki/LaTeX/Mathematics
\usepackage{amsmath,amsfonts,amssymb,mathtools}

% Images
% https://www.overleaf.com/learn/latex/Inserting_Images
% https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions
\usepackage{graphicx,float}

% Tables
% https://www.overleaf.com/learn/latex/Tables
% https://en.wikibooks.org/wiki/LaTeX/Tables

% Algorithms
% https://www.overleaf.com/learn/latex/algorithms
% https://en.wikibooks.org/wiki/LaTeX/Algorithms
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{algorithmic}

% Code syntax highlighting
% https://www.overleaf.com/learn/latex/Code_Highlighting_with_minted
\usepackage[cache=false]{minted}
\usemintedstyle{borland}

% References
% https://www.overleaf.com/learn/latex/Bibliography_management_in_LaTeX
% https://en.wikibooks.org/wiki/LaTeX/Bibliography_Management
\usepackage{biblatex}
\addbibresource{references.bib}

% Title content
\title{Seminar 1901 - Darstellung und Verarbeitung unsicheren Wissens mit logikbasierten Methoden}
\author{Philip Heltweg (3230880)}
\date{November 15, 2020}

\begin{document}

\maketitle

% Abstract
\begin{abstract}
    Add your abstract here.
\end{abstract}

% Introduction and Overview
\section{Introduction and Overview}
Add your introduction and overview here.

% Example Subsection
\subsection{Subsection Title}
This is a subsection.

% Example Subsubsection
\subsubsection{Subsubsection Title}
This is a subsubsection.

%  Theoretical Background
\section{Theoretical Background}
Add your theoretical background here. Some example text: As we learned from our textbook \cite{kutz_2013}, Fourier introduced the concept of representing a given function $f(x)$ by a trigonometric series of sines and cosines:
\begin{equation}
    f(x) = \frac{a_0}{2} + \sum_{i=1}^\infty \left(a_n\cos{nx} + b_n\sin{nx}\right) \quad x \in (-\pi,\pi].
    \label{eqn:fourierseries}
\end{equation}
You can reference numbered equations, figures, tables, algorithms, and code like this: Equation~\ref{eqn:fourierseries}, etc.

% Algorithm Implementation and Development
\section{Algorithm Implementation and Development}
Add your algorithm implementation and development here. See Algorithm~\ref{alg:example} for how to include an algorithm in your document. This is how to make an \textit{ordered} list:
\begin{enumerate}
    \item Fluffy swallowed a marble.
    \item I took Fluffy to the vet.
    \item They took an ultrasound of Fluffy's intestines.
\end{enumerate}

\begin{algorithm}
\begin{algorithmic}
    \STATE{Import data from \texttt{Testdata.mat}}
    \FOR{$j = 1:20$}
        \STATE{Extract measurement $j$ from \texttt{Undata}}
        \STATE{Do something useful}
    \ENDFOR
    \IF{$i\geq 5$} 
        \STATE{$i\gets i-1$}
    \ELSE
        \IF{$i\leq 3$}
            \STATE{$i\gets i+2$}
        \ENDIF
    \ENDIF 
\end{algorithmic}
\caption{Example Algorithm}
\label{alg:example}
\end{algorithm}

% Computational Results
\section{Computational Results}
Add your computational results here. See Table~\ref{tab:mascots} for how to include a table in your document. See Figure~\ref{fig:dubs} for how to include figures in your document.

\begin{table}
    \centering
    \begin{tabular}{rll}
    & Name & Years \\
    \hline
    1 & Frosty & 1922-1930  \\
    2 & Frosty II & 1930-1936 \\
    3 & Wasky & 1946 \\
    4 & Wasky II & 1947 \\
    5 & Ski & 1954 \\
    6 & Denali & 1958 \\
    7 & King Chinook & 1959-1968\\
    8 & Regent Denali & 1969 \\
    9 & Sundodger Denali & 1981-1992 \\
    10 & King Redoubt & 1992-1998 \\
    11 & Prince Redoubt & 1998 \\
    12 & Spirit & 1999-2008 \\
    13 & Dubs I & 2009-2018 \\
    14 & Dubs II & 2018-Present
    \end{tabular}
    \caption{UW mascots as described in \cite{washington_huskies}.}
    \label{tab:mascots}
\end{table}

% begin{figure}[tb] % t = top, b = bottom, etc.
\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{dubs.jpg}
    \caption{Here is a picture of Dubs \cite{webeck_2018}. Dubs did not swallow a marble.}
    \label{fig:dubs}
\end{figure}

% Summary and Conclusions
\section{Summary and Conclusions}
Add your summary and conclusions here.

% References
\printbibliography

% Appendices
\begin{appendices}

% MATLAB Functions
\section{MATLAB Functions}
Add your important MATLAB functions here with a brief implementation explanation. This is how to make an \textbf{unordered} list:
\begin{itemize}
    \item \texttt{y = linspace(x1,x2,n)} returns a row vector of \texttt{n} evenly spaced points between \texttt{x1} and \texttt{x2}. 
    \item \texttt{[X,Y] = meshgrid(x,y)} returns 2-D grid coordinates based on the coordinates contained in the vectors \texttt{x} and \texttt{y}. \text{X} is a matrix where each row is a copy of \texttt{x}, and \texttt{Y} is a matrix where each column is a copy of \texttt{y}. The grid represented by the coordinates \texttt{X} and \texttt{Y} has \texttt{length(y)} rows and \texttt{length(x)} columns.  
\end{itemize}

% MATLAB Codes
\section{MATLAB Code}
Add your MATLAB code here. This section will not be included in your page limit of six pages.

\begin{listing}[h]
\inputminted{matlab}{example.m}
\caption{Example code from external file.}
\label{listing:examplecode}
\end{listing}

\end{appendices}

\end{document}

### 2020-11-06 summary/summary.tex
feat: starting summary for seminar

--- 2020-11-02 summary/summary.tex
@@
 \usepackage[utf8]{inputenc}
-\usepackage[ngerman]{babel}
 \usepackage{amsmath}
-\usepackage{tikz}
-\usepackage{tikz-qtree}
-\usepackage[final]{pdfpages}
 \usepackage[parfill]{parskip}
 \usepackage{listings}
+\usepackage[acronym]{glossaries}
 
 \newcommand\erfequiv{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily erf}}}{\equiv}}}
+
+\makeglossaries
+\newglossaryentry{total preorder}
+{
+    name=total preorder,
+    description={todo}
+}
+\newglossaryentry{non-priotised revision}
+{
+    name=non-priotised revision,
+    description={revision inputs are not necessarily elements of the belief set associated to the revised preorder \cite{Booth2006}}
+}
+\newglossaryentry{iterated belief revision}
+{
+    name=iterated belief revision,
+    description={'the sequential revision of beliefs in response to a string of observations' \cite{Darwiche1997}}
+}
+\newacronym{tpos}{tpos}{Total preorders}
 
@@
 \author{
-	Heltweg, Philip
+	Heltweg, Philip (3230880) \\
+	pheltweg@gmail.com
 }
@@
 
-\begin{tabular}{l l}
-Matrikelnummer: & 3230880\\
-\\
-Name, Vorname: & Heltweg, Philip\\
-\\
-Strasse, Nr.: & Kerpener Straße 10\\
-\\
-Auslandskennzeichen, PLZ, Wohnort: & D 50937 Köln\\
-\\
-\end{tabular}
+\newpage
+
+\tableofcontents
 
@@
 
-\section{Concepts}
+\section{Research context}
 \begin{itemize}
-    \item belief revision, iterated belief revision, non-prioritised revision
+    \item Main Area: Belief change
+    \item Sub-areas according to \cite{Darwiche1997}
     \begin{itemize}
-        \item 1, 7, 12, 20, 21, 22, 23, 24, 34
-        \item \textbf{C. Alchourrón, P. Gärdenfors, and D. Makinson. On the logic of theory change: Partial meet contrac- tion and revision functions. Journal of Symbolic Logic, 50(2):510–530, 1985.}
-        \begin{itemize}
-            \item "AGM postulates for belief revision"
+        \item Belief revision ('belief changes can be characterized by a set of constraints (called postulates) on an operator $\circ$ which modifies the set $\psi$ of currently held beliefs to produce a new belief set $\psi \circ \mu$ implying the new information $\mu$', 'operator based framework')
+        \item Nonmonotonic logic ('belief change is viewed as a byproduct of extending a database containing new facts in accordance with a set of extension-construction rules called defaults') 
+        \item Probabilistic reasoning ('belief change is viewed as a byproduct of conditioning a probability function (or some qualitative abstraction thereof) on new evidence, according to bayes rule')
     \end{itemize}
-        \item R. Booth and T. Meyer. Admissible and restrained revision. Journal of Artificial Intelligence Research (JAIR), 26:127–151, 2006.
-        \item \textbf{A. Darwiche and J. Pearl. On the logic of iterated belief revision. Artificial Intelligence, 89:1–29, 1997.}
-        \begin{itemize}
-            \item "reformulated the AGM postulates for belief revision to be compatible with their suggested approach to iterated revision"
-        \end{itemize}
-        \item A. Grove. Two modelings for theory change. Journal of Philosophical Logic, 17:157–170, 1988.
-        \item S. O. Hansson, E. Ferme ́, J. Cantwell, and M. Falappa. Credibility-limited revision. Journal of Sym- bolic Logic, 66(4):1581–1596, 2001.
-        \item S.O. Hansson. A survey of non-prioritized belief revision. Erkenntnis, 50(2):413–427, 1999.
-        \item Y. Jin and M. Thielscher. Iterated belief revision, revised. Artificial Intelligence, 171(1):1–18, 2007.
-        \item H. Katsuno and A. O. Mendelzon. Propositional knowledge base revision and minimal change. Artif. Intell., 52(3):263–294, 1991.
-        \item A. Nayak, M. Pagnucco, and P. Peppas. Dynamic belief revision operators. Artificial Intelligence,
-146:193–228, 2003.
-    \end{itemize}
-    \item agent
-    \item sound and complete properties
-    \begin{itemize}
-        \item Wikipedia: "Informally, a soundness theorem for a deductive system expresses that all provable sentences are true.
-Completeness states that all true sentences are provable." -> Vollständig und Korrekt
-    \end{itemize}
-    \item total preorder
-    \item strict preference hierarchies
-    \item interval orderings
-    \begin{itemize}
-        \item 2, 15, 32
-        \item J.F. Allen. Maintaining knowledge about temporal intervals. Communications of the ACM, 26(11):832–843, 1983.
-        \begin{itemize}
-            \item "such interval orders have been studied in the context of temporal reasoning"
-        \end{itemize}
-        \item P.C. Fishburn. Interval orders and interval graphs. Wiley, New York, 1985.
-        \begin{itemize}
-            \item "the question of how our work fits into the more general use of interval orderings"
-        \end{itemize}
-        \item \textbf{M. Öztürk, A. Tsoukia`s, and P. Vincke. Preference modelling. In Multiple Criteria Decision Analysis: State of the Art Surveys, volume 78, pages 27–71. Springer, 2005.}
-        \begin{itemize}
-            \item "such interval orders have been studied in the context of [...] preference modelling"
-            \item "in a similar vein, there seems to be a close connection between our work and the work on preference modelling using interval orderings by Öztürk et al
-        \end{itemize}
-    \end{itemize}
-    \item preference aggregation
-    \begin{itemize}
-        \item 3, 19
-        \item K. Arrow. Social Choice and Individual Values. John Wiley & Sons, 1963.
-        \item S.M. Glaister. Symmetry and belief revision. Erkenntnis, 49(1):21–56, 1998.
-        \begin{itemize}
-            \item "for more discussion on social choice-like conditions and their relevance to tpo-revision we refer the reader..."
-        \end{itemize}
-    \end{itemize}
+    \item \cite{Booth2006} as work in belief revision
+    \item 'On the belief set level: \gls{non-priotised revision} in contrast to most works in iterated belief change that are given in priotised revision' \cite{Booth2006}
+    \item In the area of \gls{iterated belief revision} \cite{Booth2006}
 \end{itemize}
 
-\section{Ausführliche Inhaltsgliederung}
-Bis zu diesem Zeitpunkt erwarten wir von Ihnen eine Kurzfassung Ihres Vortrages, die  Folgendes enthalten sollte: ausführliche Inhaltsgliederung, Angabe der Schwerpunkte, Kommentierung der von Ihnen gewählten Stoffauswahl, Zusammenfassung.
-Umfang: ca.
-4-5 Seiten.
-Danach werden wir uns wieder an Sie wenden.
-Bitte schicken Sie uns Ihre Kurzfassung per E-Mail im PDF-Format zu.
-\section{Angabe der Schwerpunkte}
-\section{Kommentierung der Stoffauswahl}
-\section{Zusammenfassung}
+\section{Literature}
+\begin{itemize}
+    \item The 'AGM Paper' \cite{Alchourron1985} introduced 'AGM postulates' for belief revision.
+Works on a \textbf{belief set} of currently held beliefs and with one step revision.
+Does 'minimal change' for beliefs but not for conditional beliefs.
+    \item \cite{Darwiche1997} introduces iterated belief revision and reformulates the AGM postulates to be compatible with their approach.
+Works on 'epistemic states' of agents, not belief sets.
+Expands the operator based approach to those states.
+    \item \cite{Grove1988} introduces an ordered worlds / spheres approach instead of working on a set of held beliefs.
+    \item \cite{Booth2004} preorders as partitions into equivalence classes, ordered worlds with multiple orders $\leq$, $\preceq$, iterated belief change as outlook.
+    \item The original research paper \cite{Booth2011} which is a combined and extended version of \cite{Booth2006} and \cite{Booth2007}.
+Most papers use a one step revision operator.
+Here: Framework for multi-step revision by introducing meta info in the epistemic state for revision over a preference of worlds, then revision over that meta info structure.
+Using \gls{tpos}
+\end{itemize}
+
+\newpage
+
+\setglossarystyle{listgroup}
+\printglossaries
+
+\newpage
+
+\bibliographystyle{alpha}
+\bibliography{references}
 

### 2020-11-09 summary/summary.tex
feat: research context

@@
 \makeglossaries
+\newglossaryentry{principle of minimal change}
+{
+    name=principle of minimal change,
+    description={todo \cite{Darwiche1997}}
+}
 \newglossaryentry{total preorder}
@@
 
+\section{Presentation agenda}
+\subsection{Introduction}
+\subsubsection{Preview}
+\subsection{Research Context and definitions}
+\begin{itemize}
+    \item Introduction of the research area of belief change and major sub-areas according to \cite{Darwiche1997}: nonmonotonic logic, probabilistic reasoning and belief revision and placing of \cite{Booth2011} in the area of belief revision.
+    \item Belief revision as operator based approach that concerns itself with the definition of constrains (so called postulates) on operators that transitions between held beliefs when new information arrives \cite{Darwiche1997}.
+    \item \cite{Alchourron1985} as seminal paper for one-step belief revision on belief sets.
+Definitions of belief sets and difference between propositional beliefs and conditional beliefs.
+Adherence to the principle of minimal change for currently held beliefs only nearly no constrains on conditional beliefs.
+    \item \cite{Darwiche1997} discussion of iterated belief revision and the definition and need for epistemic states instead of belief sets for handling conditional beliefs.
+Introduction of tpos as plausibility orderings to represent conditional beliefs.
+    \item \cite{Booth2011} discusses a framework for tpo-revision that enriches an epistemic state with a framework to create a new tpo for a revision step on the basis of interval orderings between positive and negative representations of possible worlds.
+Motivation of tpo-revision as "context" as introduced in \cite{Booth2007}.
+    \item Therefor \cite{Booth2011} as work in iterated belief revision, closer placement of \cite{Booth2011} as non-priotised revision on the belief set level.
+    \item Related areas to the framework established \cite{Booth2011} with preference aggregation and relation to research in interval orderings.
+\end{itemize}
+\textbf{Section Goal:} Overview of the research area and placement of \cite{Booth2011} as work on iterated belief revision.
+Rough overview of the background for the work in \cite{Booth2011}.
+Shared understanding of: belief revision (and the difference between one-step- and iterated belief revision), belief sets and epistemic states, conditional beliefs in contrast to propositional beliefs, tpos as plausibility orderings, motivation and definition of tpo-revision as tool for iterated belief revision.
+
+\subsection{Summary}
+\subsection{Outlook}
+\subsection{Sources}
+
 \section{Research context}
@@
     \end{itemize}
-    \item \cite{Booth2006} as work in belief revision
-    \item 'On the belief set level: \gls{non-priotised revision} in contrast to most works in iterated belief change that are given in priotised revision' \cite{Booth2006}
-    \item In the area of \gls{iterated belief revision} \cite{Booth2006}
+    \item \cite{Booth2011} as work in belief revision
+    \item 'On the belief set level: \gls{non-priotised revision} in contrast to most works in iterated belief change that are given in priotised revision' \cite{Booth2011}
+    \item In the area of \gls{iterated belief revision} \cite{Booth2011}
 \end{itemize}

### 2020-11-10 summary/summary.tex
feat: more toc

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage[parfill]{parskip}
@@
     name=principle of minimal change,
+    % TODO more detail
     description={todo \cite{Darwiche1997}}
@@
     name=total preorder,
+    % TODO more detail
     description={todo}
@@
 \subsection{Introduction}
+\subsubsection{Birds eye view}
+\begin{itemize}
+% TODO more detail
+    \item Very high level view of the main idea of an ordering on a list of worlds as plausibility ordering for conditional beliefs, retrieving a belief set from it (e.g.
+using the set of sentences true in all minimal models) as a way of representing belief, relating it to defensive deduction in Poolscher default logic (???), why iterated belief change and finally the idea behind +/- worlds.
+\end{itemize}
 \subsubsection{Preview}
@@
 Adherence to the principle of minimal change for currently held beliefs only nearly no constrains on conditional beliefs.
+    % TODO grove two modellings for theory change in here as introduction for worlds?
+    % TODO build this from AGM 25 years?
     \item \cite{Darwiche1997} discussion of iterated belief revision and the definition and need for epistemic states instead of belief sets for handling conditional beliefs.
@@
 \subsection{Summary}
+% TODO add overall goal here "Sound and complete axiomatisation for revision operators" + example?
+\subsubsection{Enriched epistemic state and $\leq$-faithful tpos}
+\begin{itemize}
+    \item Notation basics.
+    \item Definition of the DP-AGM postulates and what modifications are made to them for the paper (to always be able to get a belief set from the tpo).
+Show how a belief set can be extracted from an epistemic state.
+Introduction of the notation of $\leq$ as tpo, $\ast$ as the revision operator for $\leq$ returning a new tpo $\leq^{\ast}_{\alpha}$.
+    \item Notation of the enriched epistemic state $W^{\pm}$, $\preceq$ and conditions on it as well as it's relation to $\leq$.
+Visual examples using sticks (\cite{Booth2011} and ranks \cite{Booth2006}.
+Definition of a $\leq$-faithful tpo over $W^{\pm}$.
+\end{itemize}
+\textbf{Section Goal:} Notation and introducing the concept of a $\leq$-faithful tpo over $W^{\pm}$ and how to visualise it.
+\subsubsection{tpo-revision operators: Revision of $\leq$ with $\preceq$}
+% TODO more detail
+\textbf{Section Goal:} Definition of $\ast_{\preceq}$ as example + visualisation, properties of the family of revision operators shown, Theorem 1.
+Introduction sentinential level (what is it?), properties in that view, overruling/strictly overruling, why?
+-> Disj1/2, falls into three categories depending on overruling
+\subsubsection{Strict preference}
+% TODO more detail
+% TODO is interdefinable inference relations relevant? %
+\textbf{Section Goal:} Introduction of $\lll$, $\ll$ and $<$ with example visuals.
+interdefinable inference relations for them (???).
+Limiting cases and their problems (???
+relevant?) to show that here proposed general family solves these correctly (also the issue presentes is reference to \cite{Darwiche1997}.
+Subclass $\ll$ = $\lll$, relevant?
+Improvement operators and how they relate to $\lll$, $\ll$, $<$, relevant?
+Maybe whole section of limiting cases and improvement operators as "did not talk about but related to other work here and here"
+
+\subsubsection{Strict preference hierarchies / Interval orderings}
+% TODO more detail
+\textbf{Section Goal:} Introduction of SPHs and that it can be extracted from $\preceq$, showing that the class of structures described by SPHs and $\preceq$ is equal.
+Mention of related research (\cite{allen1983maintaining} / \cite{Oeztuerk2005}).
+Definition of SPH by a tpo (theorem 3).
+Summary: SPHs and $\leq$-faithful tpo over $W^{\pm}$ as equivalent ways to describe the structure to revise a tpo, showing $\ast$ can be described with SPH only.
+Since defining a way to revise one will be equivalent to the other we can choose, choosing SPHs because it is easier to express desirable properties with it.
+
+\subsubsection{SPH revision}
+\subsubsubsection{Properties of SPH revision}
+% TODO more detail
+\textbf{Section Goal:}  Properties for admissible SPH revision in reference to \cite{Booth2006a}. Some additional properties that seem desirable and how they relate to admissible SPH revision.
+\subsubsubsection{A concrete revision operator}
+% TODO more detail
+\textbf{Section Goal:} Concrete operator explained
+
+\subsection{Relation to other areas}
+\subsubsection{Preference Aggregation and Social Choice Theory}
+% TODO more detail
+\textbf{Section Goal:}
+\subsubsection{Preference modelling using interval orderings}
+% TODO more detail
+\textbf{Section Goal:}
+
 \subsection{Outlook}
 \subsection{Sources}
-
-\section{Research context}
-\begin{itemize}
-    \item Main Area: Belief change
-    \item Sub-areas according to \cite{Darwiche1997}
-    \begin{itemize}
-        \item Belief revision ('belief changes can be characterized by a set of constraints (called postulates) on an operator $\circ$ which modifies the set $\psi$ of currently held beliefs to produce a new belief set $\psi \circ \mu$ implying the new information $\mu$', 'operator based framework')
-        \item Nonmonotonic logic ('belief change is viewed as a byproduct of extending a database containing new facts in accordance with a set of extension-construction rules called defaults') 
-        \item Probabilistic reasoning ('belief change is viewed as a byproduct of conditioning a probability function (or some qualitative abstraction thereof) on new evidence, according to bayes rule')
-    \end{itemize}
-    \item \cite{Booth2011} as work in belief revision
-    \item 'On the belief set level: \gls{non-priotised revision} in contrast to most works in iterated belief change that are given in priotised revision' \cite{Booth2011}
-    \item In the area of \gls{iterated belief revision} \cite{Booth2011}
-\end{itemize}
 
@@
 
-\newpage
-
 \bibliographystyle{alpha}

### 2020-11-11 summary/summary.tex
feat: overview mostly complete

@@
 \usepackage{amssymb}
-\usepackage[parfill]{parskip}
-\usepackage{listings}
 \usepackage[acronym]{glossaries}
-
-\newcommand\erfequiv{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily erf}}}{\equiv}}}
+\usepackage{dsfont}
 
@@
     name=principle of minimal change,
-    % TODO more detail
-    description={todo \cite{Darwiche1997}}
+    description={'The need to preserve as much of earlier beliefs as possible and to only add those beliefs that are absolutely compelled by the revision specified' \cite{Darwiche1997}}
 }
@@
     name=total preorder,
-    % TODO more detail
-    description={todo}
+    description={'A tpo is a binary relation $\leq$ which is both transitive and connected (for any x, y either $x \leq y$ or $y \leq x$).' \cite{Booth2011}}
 }
@@
 }
+\date{\today}
 \maketitle
@@
 \subsubsection{Preview}
+\textbf{Section Goal:} Motivation for the upcoming talk: Show of a complete, short example of a two step revision using the example SPH-revision operator $\circledast$ given in the paper.
+Mostly using stick visualisation.
+
 \subsection{Research Context and definitions}
 \begin{itemize}
+    % TODO build this from AGM 25 years?
     \item Introduction of the research area of belief change and major sub-areas according to \cite{Darwiche1997}: nonmonotonic logic, probabilistic reasoning and belief revision and placing of \cite{Booth2011} in the area of belief revision.
-    \item Belief revision as operator based approach that concerns itself with the definition of constrains (so called postulates) on operators that transitions between held beliefs when new information arrives \cite{Darwiche1997}.
+Belief revision as operator based approach that concerns itself with the definition of constrains (so called postulates) on operators that transitions between held beliefs when new information arrives \cite{Darwiche1997}.
     \item \cite{Alchourron1985} as seminal paper for one-step belief revision on belief sets.
@@
 Adherence to the principle of minimal change for currently held beliefs only nearly no constrains on conditional beliefs.
-    % TODO grove two modellings for theory change in here as introduction for worlds?
-    % TODO build this from AGM 25 years?
-    \item \cite{Darwiche1997} discussion of iterated belief revision and the definition and need for epistemic states instead of belief sets for handling conditional beliefs.
-Introduction of tpos as plausibility orderings to represent conditional beliefs.
+    \item \cite{Grove1988} introducing an ordered worlds / spheres approach instead of working on a set of held beliefs with \cite{Booth2004} using preorders as partitions into equivalence classes on ordered worlds with multiple orders and iterated belief change as outlook.
+    \item \cite{Darwiche1997} discussion of \gls{iterated belief revision} and the definition and need for epistemic states instead of belief sets for handling conditional beliefs.
+\Gls{total preorder}s as plausibility orderings to represent conditional beliefs.
     \item \cite{Booth2011} discusses a framework for tpo-revision that enriches an epistemic state with a framework to create a new tpo for a revision step on the basis of interval orderings between positive and negative representations of possible worlds.
 Motivation of tpo-revision as "context" as introduced in \cite{Booth2007}.
-    \item Therefor \cite{Booth2011} as work in iterated belief revision, closer placement of \cite{Booth2011} as non-priotised revision on the belief set level.
+    \item Therefor \cite{Booth2011} as work in iterated belief revision, closer placement of \cite{Booth2011} as \gls{non-priotised revision} on the belief set level.
     \item Related areas to the framework established \cite{Booth2011} with preference aggregation and relation to research in interval orderings.
@@
 \subsection{Summary}
-% TODO add overall goal here "Sound and complete axiomatisation for revision operators" + example?
+\begin{itemize}
+    \item Enriched epistemic state for tpo-revision using best-case/worst-case worldviews using using $\preceq$ without revising $\preceq$ itself (moving the problem of iterated revision one step up).
+    \item Establishing an example revision operator and a sound and complete axiomatisation for the family of revision operators considered.
+    \item Discussion of their properties from different viewpoints, especially how they relate to preference of worlds.
+    \item Introduction of SPHs $\mathds{S}$ as equivalent structure to $\preceq$ that will be easier to revise.
+    \item Definition of revision for $\mathds{S}$ and example revision operator, therefor solving the problem from the start. 
+\end{itemize}
+\textbf{Section Goal:} Very high level outline of the goal of the paper and the steps to get there.
+
 \subsubsection{Enriched epistemic state and $\leq$-faithful tpos}
@@
     \item Notation of the enriched epistemic state $W^{\pm}$, $\preceq$ and conditions on it as well as it's relation to $\leq$.
-Visual examples using sticks (\cite{Booth2011} and ranks \cite{Booth2006}.
+Visual examples using sticks (\cite{Booth2011} and ranks (and mentioning that tpos can be represented as linearly ordered set of ranks) \cite{Booth2006}.
 Definition of a $\leq$-faithful tpo over $W^{\pm}$.
@@
 \textbf{Section Goal:} Notation and introducing the concept of a $\leq$-faithful tpo over $W^{\pm}$ and how to visualise it.
+
 \subsubsection{tpo-revision operators: Revision of $\leq$ with $\preceq$}
-% TODO more detail
-\textbf{Section Goal:} Definition of $\ast_{\preceq}$ as example + visualisation, properties of the family of revision operators shown, Theorem 1.
-Introduction sentinential level (what is it?), properties in that view, overruling/strictly overruling, why?
--> Disj1/2, falls into three categories depending on overruling
+\begin{itemize}
+    \item Introduction of $\ast$ as revision operator for $\leq$ and definition of $\ast_{\preceq}$ as example with visualisation.
+    \item Properties of $\ast_{\preceq}$, their explanation and Theorem 1 as axiomatisation of the family of revision operators considered in the paper.
+    \item Explanation of sentinential view (and distinction to semantic level), definition of $\leq' \circ \beta $ and how it relates to conditional beliefs, mention of $\leq' \circ \top $ as belief set.
+Show of properties for the family of revision operators using sentinental view.
+Explanation of Disj1/Disj2 as properties that are easy to show in the sentinental view but not in the semantic formulation.
+\end{itemize}
+\textbf{Section Goal:} Definition of $\ast_{\preceq}$ as example revision operator and visualisation of it.
+Show of axiomatic definition of the family of operators in semantic and sentinential view.
+Establishing theorem 1.
+
 \subsubsection{Strict preference}
-% TODO more detail
-% TODO is interdefinable inference relations relevant? %
-\textbf{Section Goal:} Introduction of $\lll$, $\ll$ and $<$ with example visuals.
-interdefinable inference relations for them (???).
-Limiting cases and their problems (???
-relevant?) to show that here proposed general family solves these correctly (also the issue presentes is reference to \cite{Darwiche1997}.
-Subclass $\ll$ = $\lll$, relevant?
-Improvement operators and how they relate to $\lll$, $\ll$, $<$, relevant?
-Maybe whole section of limiting cases and improvement operators as "did not talk about but related to other work here and here"
+\begin{itemize}
+    \item Overruling and strict overruling in the sentinential view.
+    \item Extracting $\lll$, $\ll$ and $<$ from $\preceq$ and their interpretation as core and weakly protected preferences with visualisations as well as how they relate to overruling.
+    % TODO relevant?
+    \item Inference relations from them (is this relevant?)
+    \item Limiting cases and their counterintuitive results, Theorem 2, relation to \cite{Darwiche1997} (is this relevant?)
+    \item Improvement operators (is this relevant?)
+\end{itemize}
+\textbf{Section Goal:} Short discussion of what overruling is and introduction of $\lll$, $\ll$ and $<$ to use in the next section.
 
 \subsubsection{Strict preference hierarchies / Interval orderings}
-% TODO more detail
-\textbf{Section Goal:} Introduction of SPHs and that it can be extracted from $\preceq$, showing that the class of structures described by SPHs and $\preceq$ is equal.
-Mention of related research (\cite{allen1983maintaining} / \cite{Oeztuerk2005}).
-Definition of SPH by a tpo (theorem 3).
-Summary: SPHs and $\leq$-faithful tpo over $W^{\pm}$ as equivalent ways to describe the structure to revise a tpo, showing $\ast$ can be described with SPH only.
-Since defining a way to revise one will be equivalent to the other we can choose, choosing SPHs because it is easier to express desirable properties with it.
+\begin{itemize}
+    \item Definition of $\mathds{S}$ and SPHs, Theorem 3 and motivating the introduction as an equivalent description of the same structure as $\preceq$ that will be easier to show desirable properties for revision with it.
+Show that the revision operator $\ast$ from the start can be described using $\mathds{S}$.
+Mentioning the initial problem of moving the iterated belief revision problem 'one step up'.
+\end{itemize}
+\textbf{Section Goal:} Definition of $\mathds{S}$ and SPHs and motivation for doing so.
 
 \subsubsection{SPH revision}
-\subsubsubsection{Properties of SPH revision}
-% TODO more detail
-\textbf{Section Goal:}  Properties for admissible SPH revision in reference to \cite{Booth2006a}. Some additional properties that seem desirable and how they relate to admissible SPH revision.
-\subsubsubsection{A concrete revision operator}
-% TODO more detail
-\textbf{Section Goal:} Concrete operator explained
+\paragraph{Properties of SPH revision}
+\begin{itemize}
+    \item $\circledast$ as SPH-revision operator and fundamental properties.
+    \item Admissible according to \cite{Booth2006a}, properties for $\circledast$ to be considered admissible.
+    \item Short discussion of additional properties and if they hold for admissible SPH-revision operators.
+\end{itemize}
+\textbf{Section Goal:} Concept of a SPH-revision operator and it's properties.
+
+\paragraph{A concrete revision operator}
+\textbf{Section Goal:} Presentation of the concrete SPH-revision operator $\circledast$ shown in the paper with example. Circling back to initial preview.
 
 \subsection{Relation to other areas}
-\subsubsection{Preference Aggregation and Social Choice Theory}
+\begin{itemize}
+    % TODO more detail, see 4.1 in paper
+    \item Preference Aggregation and Social Choice Theory
     % TODO more detail
-\textbf{Section Goal:}
-\subsubsection{Preference modelling using interval orderings}
-% TODO more detail
-\textbf{Section Goal:}
+    \item Preference modelling using interval orderings
+\end{itemize}
+\textbf{Section Goal:} Short mention of how the discussed problems relate to other research areas.
 
 \subsection{Outlook}
+% TODO more detail
+
 \subsection{Sources}
+\begin{itemize}
+    \item Literature
+\end{itemize}
 
@@
 Works on a \textbf{belief set} of currently held beliefs and with one step revision.
-Does 'minimal change' for beliefs but not for conditional beliefs.
+Does adhere to the \gls{principle of minimal change} for beliefs but not for conditional beliefs.
     \item \cite{Darwiche1997} introduces iterated belief revision and reformulates the AGM postulates to be compatible with their approach.
@@
 
-\bibliographystyle{alpha}
+\typeout{}
+\nocite{*}
+\bibliographystyle{plain}
 \bibliography{references}

### 2020-11-13 summary/summary.tex
feat: final version that was sent in

@@
 \subsection{Introduction}
-\subsubsection{Birds eye view}
+\subsubsection{Agenda}
 \begin{itemize}
-% TODO more detail
-    \item Very high level view of the main idea of an ordering on a list of worlds as plausibility ordering for conditional beliefs, retrieving a belief set from it (e.g.
-using the set of sentences true in all minimal models) as a way of representing belief, relating it to defensive deduction in Poolscher default logic (???), why iterated belief change and finally the idea behind +/- worlds.
+    \item Motivation and example.
+    \item Notation and idea of preference ordering worlds with tpos and positive/negative contexts for conditional beliefs.
+    \item Introduction of tpo-revision using an operator defined from a new structure $\preceq$, moving iterated belief revision problem 'one step up' to this structure
+    \item Finding an equivalent structure to $\preceq$ in SPHs that has easier to discuss properties.
+    \item Showing how to revise SPHs (theoretically and by example) therefor solving the problem of revising from earlier.
 \end{itemize}
+
 \subsubsection{Preview}
@@
 Definitions of belief sets and difference between propositional beliefs and conditional beliefs.
-Adherence to the principle of minimal change for currently held beliefs only nearly no constrains on conditional beliefs.
-    \item \cite{Grove1988} introducing an ordered worlds / spheres approach instead of working on a set of held beliefs with \cite{Booth2004} using preorders as partitions into equivalence classes on ordered worlds with multiple orders and iterated belief change as outlook.
+Adherence to the principle of minimal change for currently held beliefs only; nearly no constrains on conditional beliefs.
+    \item \cite{Grove1988} introducing an ordered worlds / spheres approach instead of working on a set of held beliefs.
+\cite{Booth2004} understanding preorders as partitions into equivalence classes on ordered worlds (and using multiple orders).
+Iterated belief change as outlook.
     \item \cite{Darwiche1997} discussion of \gls{iterated belief revision} and the definition and need for epistemic states instead of belief sets for handling conditional beliefs.
@@
     \item \cite{Booth2011} discusses a framework for tpo-revision that enriches an epistemic state with a framework to create a new tpo for a revision step on the basis of interval orderings between positive and negative representations of possible worlds.
-Motivation of tpo-revision as "context" as introduced in \cite{Booth2007}.
+Motivation of tpo-revision as 'context' as introduced in \cite{Booth2007}.
     \item Therefor \cite{Booth2011} as work in iterated belief revision, closer placement of \cite{Booth2011} as \gls{non-priotised revision} on the belief set level.
@@
 Shared understanding of: belief revision (and the difference between one-step- and iterated belief revision), belief sets and epistemic states, conditional beliefs in contrast to propositional beliefs, tpos as plausibility orderings, motivation and definition of tpo-revision as tool for iterated belief revision.
+Section will need to be discussed with the seminar on \cite{Darwiche1997} and reduced depending on how much is shown in their presentation.
 
@@
     \item Enriched epistemic state for tpo-revision using best-case/worst-case worldviews using using $\preceq$ without revising $\preceq$ itself (moving the problem of iterated revision one step up).
-    \item Establishing an example revision operator and a sound and complete axiomatisation for the family of revision operators considered.
+    \item Establishing an example revision operator and a 'sound and complete axiomatisation for the family of revision operators considered' \cite{Booth2011}.
     \item Discussion of their properties from different viewpoints, especially how they relate to preference of worlds.
-    \item Introduction of SPHs $\mathds{S}$ as equivalent structure to $\preceq$ that will be easier to revise.
-    \item Definition of revision for $\mathds{S}$ and example revision operator, therefor solving the problem from the start. 
+    \item Introduction of SPHs $\mathds{S}$ as equivalent structure to $\preceq$ that will be easier to discuss.
+    \item Definition of revision for $\mathds{S}$ and example SPH-revision operator, therefor solving the problem from the start. 
 \end{itemize}
@@
     \item Notation of the enriched epistemic state $W^{\pm}$, $\preceq$ and conditions on it as well as it's relation to $\leq$.
-Visual examples using sticks (\cite{Booth2011} and ranks (and mentioning that tpos can be represented as linearly ordered set of ranks) \cite{Booth2006}.
+Visual examples using sticks \cite{Booth2011} and ranks (and mentioning that tpos can be represented as linearly ordered set of ranks) \cite{Booth2006}.
 Definition of a $\leq$-faithful tpo over $W^{\pm}$.
@@
     \item Introduction of $\ast$ as revision operator for $\leq$ and definition of $\ast_{\preceq}$ as example with visualisation.
-    \item Properties of $\ast_{\preceq}$, their explanation and Theorem 1 as axiomatisation of the family of revision operators considered in the paper.
+    \item Properties of $\ast_{\preceq}$, their explanation and theorem 1 as axiomatisation of the family of revision operators considered in the paper.
     \item Explanation of sentinential view (and distinction to semantic level), definition of $\leq' \circ \beta $ and how it relates to conditional beliefs, mention of $\leq' \circ \top $ as belief set.
-Show of properties for the family of revision operators using sentinental view.
-Explanation of Disj1/Disj2 as properties that are easy to show in the sentinental view but not in the semantic formulation.
+Show of properties for the family of revision operators using sentinential view.
+Explanation of Disj1/Disj2 as properties that are easy to show in the sentinential view but not in the semantic formulation.
 \end{itemize}
@@
     % TODO relevant?
-    \item Inference relations from them (is this relevant?)
-    \item Limiting cases and their counterintuitive results, Theorem 2, relation to \cite{Darwiche1997} (is this relevant?)
-    \item Improvement operators (is this relevant?)
+    \item Don't talk about: Inference relations from them (is this relevant?)
+    \item Don't talk about: Limiting cases and their counterintuitive results, theorem 2, relation to \cite{Darwiche1997} (is this relevant?)
+    \item Don't talk about: Improvement operators (is this relevant?)
 \end{itemize}
@@
 \begin{itemize}
-    \item Definition of $\mathds{S}$ and SPHs, Theorem 3 and motivating the introduction as an equivalent description of the same structure as $\preceq$ that will be easier to show desirable properties for revision with it.
-Show that the revision operator $\ast$ from the start can be described using $\mathds{S}$.
-Mentioning the initial problem of moving the iterated belief revision problem 'one step up'.
+    \item Definition of $\mathds{S}$ and SPHs, theorem 3 and motivating the introduction as an equivalent description of the same structure as $\preceq$ that will be easier to show desirable properties for and discuss.
+    \item Show that the revision operator $\ast$ from the start can be described using $\mathds{S}$. Mentioning the initial problem of moving the iterated belief revision problem 'one step up'.
 \end{itemize}
@@
     \item Short discussion of additional properties and if they hold for admissible SPH-revision operators.
+    \item Presentation of the concrete SPH-revision operator $\circledast$ shown in the paper with example.
 \end{itemize}
-\textbf{Section Goal:} Concept of a SPH-revision operator and it's properties.
-
-\paragraph{A concrete revision operator}
-\textbf{Section Goal:} Presentation of the concrete SPH-revision operator $\circledast$ shown in the paper with example. Circling back to initial preview.
+\textbf{Section Goal:} Concept of a SPH-revision operator and it's properties. Showing a concrete example and circling back to initial preview.
 
@@
     % TODO more detail, see 4.1 in paper
-    \item Preference Aggregation and Social Choice Theory
+    \item Preference aggregation and social choice theory
     % TODO more detail
@@
 % TODO more detail
+\textbf{Section Goal:} Mention of future research discussed in the paper.
 
@@
 
-\section{Literature}
+\section{Literature used so far}
 \begin{itemize}
     \item The 'AGM Paper' \cite{Alchourron1985} introduced 'AGM postulates' for belief revision.
-Works on a \textbf{belief set} of currently held beliefs and with one step revision.
+Works on a belief set of currently held beliefs and with one step revision.
 Does adhere to the \gls{principle of minimal change} for beliefs but not for conditional beliefs.
@@
 Using \gls{tpos}
+    \item \cite{Ferme2011} as overview article for the field of belief revision.
+    \item Planning to look into \cite{Allen1983} for interval orderings, \cite{Oeztuerk2005} for preference modelling and \cite{Arrow1963}, \cite{Glaister1998} for preference aggregation and social choice theory.
+    \item Planning to look into \cite{Booth2006a} for admissible revision.
+\end{itemize}
+
+\section{Questions}
+\begin{itemize}
+    \item Is it fundamentally correct that the paper (and much of the research area) are concerning themselves with defining axioms about a family of operators and looking at their properties given their definitions?
+E.g.
+the goal is not finding the operators that are given by the problem domain but defining a set of axioms that describe a family of operators the author deems reasonable?
+    \item The sentinential belief set definition of sentences true in all minimal worlds reminds me a lot of the sceptic inference in the default logic of Poole (inference of sentences true in all extensions), does that make sense?
+    \item Are there formal requirements for the written part of the seminar (for example number of words/pages)?
 \end{itemize}
@@
 \typeout{}
-\nocite{*}
 \bibliographystyle{plain}
@@
 
-\newpage
-
-\section{Erklärung}
-Ich erkläre, dass ich die schriftliche Ausarbeitung zum Seminar selbstständig und ohne unzulässige Inanspruchnahme Dritter verfasst habe.
+%\newpage
+%
+%\section{Erklärung}
+%Ich erkläre, dass ich die schriftliche Ausarbeitung zum Seminar selbstständig und ohne unzulässige Inanspruchnahme Dritter verfasst habe.
 Ich habe dabei nur die angegebenen Quellen und Hilfsmittel verwendet und die aus diesen wörtlich oder sinngemäß entnommenen Stellen als solche kenntlich gemacht.

### 2020-12-11 paper/paper.tex
feat: basic setup of seminar paper

--- 2020-11-10 summary/summary.tex
@@
-\documentclass[11pt]{article}
-\usepackage[document]{ragged2e}
+\documentclass[11pt]{scrartcl}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{amssymb}
-\usepackage[parfill]{parskip}
-\usepackage{listings}
-\usepackage[acronym]{glossaries}
-
-\newcommand\erfequiv{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily erf}}}{\equiv}}}
-
-\makeglossaries
-\newglossaryentry{principle of minimal change}
-{
-    name=principle of minimal change,
-    % TODO more detail
-    description={todo \cite{Darwiche1997}}
-}
-\newglossaryentry{total preorder}
-{
-    name=total preorder,
-    % TODO more detail
-    description={todo}
-}
-\newglossaryentry{non-priotised revision}
-{
-    name=non-priotised revision,
-    description={revision inputs are not necessarily elements of the belief set associated to the revised preorder \cite{Booth2006}}
-}
-\newglossaryentry{iterated belief revision}
-{
-    name=iterated belief revision,
-    description={'the sequential revision of beliefs in response to a string of observations' \cite{Darwiche1997}}
-}
-\newacronym{tpos}{tpos}{Total preorders}
+\usepackage{dsfont}
 
@@
 
-\title{Seminar 1901 - Darstellung und Verarbeitung unsicheren Wissens mit logikbasierten Methoden}
+% TODO better title
+\title{Report on 'How to Revise a Total Preorder' \cite{Booth2011}}
+\subtitle{Seminar 1901 - Representation and processing of uncertain knowledge with logic-based methods}
 \author{
 	Heltweg, Philip (3230880) \\
+	University of Hagen \\
 	pheltweg@gmail.com
 }
+\date{\today}
 \maketitle
+
+% TODO abstract
+\abstract{Abstract goes here}
 
@@
 
-\section{Presentation agenda}
-\subsection{Introduction}
-\subsubsection{Birds eye view}
-\begin{itemize}
-% TODO more detail
-    \item Very high level view of the main idea of an ordering on a list of worlds as plausibility ordering for conditional beliefs, retrieving a belief set from it (e.g.
-using the set of sentences true in all minimal models) as a way of representing belief, relating it to defensive deduction in Poolscher default logic (???), why iterated belief change and finally the idea behind +/- worlds.
-\end{itemize}
-\subsubsection{Preview}
-\subsection{Research Context and definitions}
+% TODO write introduction, make WAY SHORTER, inspire by kai
+\section{Introduction}
+%1.2 Ich sehe hier die Gefahr, dass das zu Ausführlich wird.
+%Keine große Diskussion von AGM, Darwiche and Pearl und so weiter.
+%Keine Beziehung zur Allen und co herstellen ;)
+%Kurz und Prägnant präsentieren, was benötgigt wird um zu Verstehen was
+%in dem Primärartikel neu ist.
+
 \begin{itemize}
     \item Introduction of the research area of belief change and major sub-areas according to \cite{Darwiche1997}: nonmonotonic logic, probabilistic reasoning and belief revision and placing of \cite{Booth2011} in the area of belief revision.
-    \item Belief revision as operator based approach that concerns itself with the definition of constrains (so called postulates) on operators that transitions between held beliefs when new information arrives \cite{Darwiche1997}.
+Belief revision as operator based approach that concerns itself with the definition of constrains (so called postulates) on operators that transitions between held beliefs when new information arrives \cite{Darwiche1997}.
     \item \cite{Alchourron1985} as seminal paper for one-step belief revision on belief sets.
 Definitions of belief sets and difference between propositional beliefs and conditional beliefs.
-Adherence to the principle of minimal change for currently held beliefs only nearly no constrains on conditional beliefs.
-    % TODO grove two modellings for theory change in here as introduction for worlds?
-    % TODO build this from AGM 25 years?
+Adherence to the principle of minimal change for currently held beliefs only; nearly no constrains on conditional beliefs.
+    \item \cite{Grove1988} introducing an ordered worlds / spheres approach instead of working on a set of held beliefs.
+\cite{Booth2004} understanding preorders as partitions into equivalence classes on ordered worlds (and using multiple orders).
+Iterated belief change as outlook.
     \item \cite{Darwiche1997} discussion of iterated belief revision and the definition and need for epistemic states instead of belief sets for handling conditional beliefs.
-Introduction of tpos as plausibility orderings to represent conditional beliefs.
+total preorders as plausibility orderings to represent conditional beliefs.
     \item \cite{Booth2011} discusses a framework for tpo-revision that enriches an epistemic state with a framework to create a new tpo for a revision step on the basis of interval orderings between positive and negative representations of possible worlds.
-Motivation of tpo-revision as "context" as introduced in \cite{Booth2007}.
+Motivation of tpo-revision as 'context' as introduced in \cite{Booth2007}.
     \item Therefor \cite{Booth2011} as work in iterated belief revision, closer placement of \cite{Booth2011} as non-priotised revision on the belief set level.
@@
 Shared understanding of: belief revision (and the difference between one-step- and iterated belief revision), belief sets and epistemic states, conditional beliefs in contrast to propositional beliefs, tpos as plausibility orderings, motivation and definition of tpo-revision as tool for iterated belief revision.
+Section will need to be discussed with the seminar on \cite{Darwiche1997} and reduced depending on how much is shown in their presentation.
 
-\subsection{Summary}
-% TODO add overall goal here "Sound and complete axiomatisation for revision operators" + example?
-\subsubsection{Enriched epistemic state and $\leq$-faithful tpos}
+see \cite{Kai2020} for inspiration
+
+% TODO write formal background
+\section{Formal background}
+\subsection{subscection for each thing, e.g. total preorder}
+\subsection{Notation}
+
+%
+%1.3.1/2 Das ist denke ich gut so.
+
+%1.3.3-1.3.4 Ich finde gut das du Dinge ausschließt.
+%Ich würde sogar vorschlagen, nur 1.3.1 und 1.3.2 auszuarbeiten und auch
+%im Vortrag zu präsentieren. Das Paper hat wirklich sehr viel Inhalt.
+%Aber die Schwerpunktsetzung sei aber dir überlassen.
+%
+%
+
+% TODO expand this into subheadings and agenda
+\section{Enriched epistemic state and $\leq$-faithful tpos}
 \begin{itemize}
@@
     \item Notation of the enriched epistemic state $W^{\pm}$, $\preceq$ and conditions on it as well as it's relation to $\leq$.
-Visual examples using sticks (\cite{Booth2011} and ranks \cite{Booth2006}.
+Visual examples using sticks \cite{Booth2011} and ranks (and mentioning that tpos can be represented as linearly ordered set of ranks) \cite{Booth2006}.
 Definition of a $\leq$-faithful tpo over $W^{\pm}$.
@@
 \textbf{Section Goal:} Notation and introducing the concept of a $\leq$-faithful tpo over $W^{\pm}$ and how to visualise it.
-\subsubsection{tpo-revision operators: Revision of $\leq$ with $\preceq$}
-% TODO more detail
-\textbf{Section Goal:} Definition of $\ast_{\preceq}$ as example + visualisation, properties of the family of revision operators shown, Theorem 1.
-Introduction sentinential level (what is it?), properties in that view, overruling/strictly overruling, why?
--> Disj1/2, falls into three categories depending on overruling
-\subsubsection{Strict preference}
-% TODO more detail
-% TODO is interdefinable inference relations relevant? %
-\textbf{Section Goal:} Introduction of $\lll$, $\ll$ and $<$ with example visuals.
-interdefinable inference relations for them (???).
-Limiting cases and their problems (???
-relevant?) to show that here proposed general family solves these correctly (also the issue presentes is reference to \cite{Darwiche1997}.
-Subclass $\ll$ = $\lll$, relevant?
-Improvement operators and how they relate to $\lll$, $\ll$, $<$, relevant?
-Maybe whole section of limiting cases and improvement operators as "did not talk about but related to other work here and here"
 
-\subsubsection{Strict preference hierarchies / Interval orderings}
-% TODO more detail
-\textbf{Section Goal:} Introduction of SPHs and that it can be extracted from $\preceq$, showing that the class of structures described by SPHs and $\preceq$ is equal.
-Mention of related research (\cite{allen1983maintaining} / \cite{Oeztuerk2005}).
-Definition of SPH by a tpo (theorem 3).
-Summary: SPHs and $\leq$-faithful tpo over $W^{\pm}$ as equivalent ways to describe the structure to revise a tpo, showing $\ast$ can be described with SPH only.
-Since defining a way to revise one will be equivalent to the other we can choose, choosing SPHs because it is easier to express desirable properties with it.
+% TODO expand this into subheadings and agenda
+\section{tpo-revision operators: Revision of $\leq$ with $\preceq$}
+\begin{itemize}
+    \item Introduction of $\ast$ as revision operator for $\leq$ and definition of $\ast_{\preceq}$ as example with visualisation.
+    \item Properties of $\ast_{\preceq}$, their explanation and theorem 1 as axiomatisation of the family of revision operators considered in the paper.
+    \item Explanation of sentinential view (and distinction to semantic level), definition of $\leq' \circ \beta $ and how it relates to conditional beliefs, mention of $\leq' \circ \top $ as belief set.
+Show of properties for the family of revision operators using sentinential view.
+Explanation of Disj1/Disj2 as properties that are easy to show in the sentinential view but not in the semantic formulation.
+\end{itemize}
+\textbf{Section Goal:} Definition of $\ast_{\preceq}$ as example revision operator and visualisation of it.
+Show of axiomatic definition of the family of operators in semantic and sentinential view.
+Establishing theorem 1.
 
-\subsubsection{SPH revision}
-\subsubsubsection{Properties of SPH revision}
-% TODO more detail
-\textbf{Section Goal:}  Properties for admissible SPH revision in reference to \cite{Booth2006a}. Some additional properties that seem desirable and how they relate to admissible SPH revision.
-\subsubsubsection{A concrete revision operator}
-% TODO more detail
-\textbf{Section Goal:} Concrete operator explained
-
-\subsection{Relation to other areas}
-\subsubsection{Preference Aggregation and Social Choice Theory}
-% TODO more detail
-\textbf{Section Goal:}
-\subsubsection{Preference modelling using interval orderings}
-% TODO more detail
-\textbf{Section Goal:}
-
-\subsection{Outlook}
-\subsection{Sources}
-
-\section{Literature}
-\begin{itemize}
-    \item The 'AGM Paper' \cite{Alchourron1985} introduced 'AGM postulates' for belief revision.
-Works on a \textbf{belief set} of currently held beliefs and with one step revision.
-Does 'minimal change' for beliefs but not for conditional beliefs.
-    \item \cite{Darwiche1997} introduces iterated belief revision and reformulates the AGM postulates to be compatible with their approach.
-Works on 'epistemic states' of agents, not belief sets.
-Expands the operator based approach to those states.
-    \item \cite{Grove1988} introduces an ordered worlds / spheres approach instead of working on a set of held beliefs.
-    \item \cite{Booth2004} preorders as partitions into equivalence classes, ordered worlds with multiple orders $\leq$, $\preceq$, iterated belief change as outlook.
-    \item The original research paper \cite{Booth2011} which is a combined and extended version of \cite{Booth2006} and \cite{Booth2007}.
-Most papers use a one step revision operator.
-Here: Framework for multi-step revision by introducing meta info in the epistemic state for revision over a preference of worlds, then revision over that meta info structure.
-Using \gls{tpos}
-\end{itemize}
+\section{Summary}
 
@@
 
-\setglossarystyle{listgroup}
-\printglossaries
-
-\bibliographystyle{alpha}
+\typeout{}
+\bibliographystyle{plain}
 \bibliography{references}
@@
 
-\section{Erklärung}
+\section*{Erklärung}
 Ich erkläre, dass ich die schriftliche Ausarbeitung zum Seminar selbstständig und ohne unzulässige Inanspruchnahme Dritter verfasst habe.

### 2020-12-15 paper/paper.tex
feat: seminar table

@@
 \section{Introduction}
+\subsection{Research context}
+A core process for an agent dealing with uncertain knowledge is updating their worldview when new information becomes available, also called belief change.
+As an agent can be human or a machine work in belief change has impact on both philosophy and artificial intelligence \cite{Ferme2011}.
+Different approaches to handling belief change have been discussed with notable approaches including nonmonotonic logic, probabilistic reasoning and belief revision \cite{Darwiche1997}.
+
+In belief revision, belief change is modelled using an operator that produces an updated set of beliefs from the state of an agent and new evidence.
+Research in this area discusses appropriate formalisations of agent state and constrains on individual or families of operators.
+Depending on if the suggested operator handles only one new evidence or multiple new evidences the approaches are called one-step or iterated belief revision.
+
+A common tool used to encode plausibility assumptions of an agent about possible worlds are total preorders (shortened as tpos) \cite{Booth2011}.
+The primary article for this report, 'How to Revise a Total Preorder' discusses how to model the change of these total preorders when new evidence becomes available.
+Being able to derive a new tpo from additional evidence is an approach to handling multiple revision steps and therefor places the article in the field of iterated belief revision.
 %1.2 Ich sehe hier die Gefahr, dass das zu Ausführlich wird.
@@
 %in dem Primärartikel neu ist.
-
-\begin{itemize}
-    \item Introduction of the research area of belief change and major sub-areas according to \cite{Darwiche1997}: nonmonotonic logic, probabilistic reasoning and belief revision and placing of \cite{Booth2011} in the area of belief revision.
+%
+%\begin{itemize}
+%    \item Introduction of the research area of belief change and major sub-areas according to \cite{Darwiche1997}: nonmonotonic logic, probabilistic reasoning and belief revision and placing of \cite{Booth2011} in the area of belief revision.
 Belief revision as operator based approach that concerns itself with the definition of constrains (so called postulates) on operators that transitions between held beliefs when new information arrives \cite{Darwiche1997}.
-    \item \cite{Alchourron1985} as seminal paper for one-step belief revision on belief sets.
+%    \item \cite{Alchourron1985} as seminal paper for one-step belief revision on belief sets.
 Definitions of belief sets and difference between propositional beliefs and conditional beliefs.
 Adherence to the principle of minimal change for currently held beliefs only; nearly no constrains on conditional beliefs.
-    \item \cite{Grove1988} introducing an ordered worlds / spheres approach instead of working on a set of held beliefs.
+%    \item \cite{Grove1988} introducing an ordered worlds / spheres approach instead of working on a set of held beliefs.
 \cite{Booth2004} understanding preorders as partitions into equivalence classes on ordered worlds (and using multiple orders).
 Iterated belief change as outlook.
-    \item \cite{Darwiche1997} discussion of iterated belief revision and the definition and need for epistemic states instead of belief sets for handling conditional beliefs.
+%    \item \cite{Darwiche1997} discussion of iterated belief revision and the definition and need for epistemic states instead of belief sets for handling conditional beliefs.
 total preorders as plausibility orderings to represent conditional beliefs.
-    \item \cite{Booth2011} discusses a framework for tpo-revision that enriches an epistemic state with a framework to create a new tpo for a revision step on the basis of interval orderings between positive and negative representations of possible worlds.
+%    \item \cite{Booth2011} discusses a framework for tpo-revision that enriches an epistemic state with a framework to create a new tpo for a revision step on the basis of interval orderings between positive and negative representations of possible worlds.
 Motivation of tpo-revision as 'context' as introduced in \cite{Booth2007}.
-    \item Therefor \cite{Booth2011} as work in iterated belief revision, closer placement of \cite{Booth2011} as non-priotised revision on the belief set level.
-    \item Related areas to the framework established \cite{Booth2011} with preference aggregation and relation to research in interval orderings.
-\end{itemize}
-\textbf{Section Goal:} Overview of the research area and placement of \cite{Booth2011} as work on iterated belief revision.
+%    \item Therefor \cite{Booth2011} as work in iterated belief revision, closer placement of \cite{Booth2011} as non-priotised revision on the belief set level.
+%    \item Related areas to the framework established \cite{Booth2011} with preference aggregation and relation to research in interval orderings.
+%\end{itemize}
+%\textbf{Section Goal:} Overview of the research area and placement of \cite{Booth2011} as work on iterated belief revision.
 Rough overview of the background for the work in \cite{Booth2011}.
 Shared understanding of: belief revision (and the difference between one-step- and iterated belief revision), belief sets and epistemic states, conditional beliefs in contrast to propositional beliefs, tpos as plausibility orderings, motivation and definition of tpo-revision as tool for iterated belief revision.
-Section will need to be discussed with the seminar on \cite{Darwiche1997} and reduced depending on how much is shown in their presentation.
-
-see \cite{Kai2020} for inspiration
+Section will need to be discussed with the seminar on \cite{Darwiche1997} and reduced depending on how much is shown in their presentation.<
+%
+%see \cite{Kai2020} for inspiration
 
@@
 \section{Formal background}
-\subsection{subscection for each thing, e.g. total preorder}
-\subsection{Notation}
 
-%
-%1.3.1/2 Das ist denke ich gut so.
+\subsection{Propositional Logic} % Aussagenlogik
+Notation follows as used in \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables, lower case greek letters for formulas in $L$ and $\top$, $\bot$ representing tautology and contradiction respectively.
+$\vdash$ as classical logical consequence, $\equiv$ classical logical equivalence.
+$Cn$ is used to denote the deductive closure of a formula or set of formulas in $L$.
 
-%1.3.3-1.3.4 Ich finde gut das du Dinge ausschließt.
-%Ich würde sogar vorschlagen, nur 1.3.1 und 1.3.2 auszuarbeiten und auch
-%im Vortrag zu präsentieren. Das Paper hat wirklich sehr viel Inhalt.
-%Aber die Schwerpunktsetzung sei aber dir überlassen.
-%
-%
+$W$ is the set of propositional worlds and given a $\alpha \in L$ the set of worlds that satisfy $\alpha$ is denoted by $[\alpha]$.
 
-% TODO expand this into subheadings and agenda
-\section{Enriched epistemic state and $\leq$-faithful tpos}
-\begin{itemize}
-    \item Notation basics.
-    \item Definition of the DP-AGM postulates and what modifications are made to them for the paper (to always be able to get a belief set from the tpo).
+For any set of worlds $S \subseteq W$ of worlds, $Th(S)$ is the set of sentences true in all worlds in $S$.
+
+\subsection{Total preorders}
+A total preorder is a binary relation $\leq$ (here over the set of propositional worlds $W$) that is total, reflexive and transitive (i.e.
+for all $x, y, z \in W$ either $x \leq y$ or $y \leq x$, $x \leq x$ and if $x \leq y$ and $y \leq z$ then $x \leq z$).
+
+The symbol $<$ is used to denote the strict part of $\leq$ while $\sim$ represents the symmetric closure of $\leq$ (i.e. $x \sim y$ iff $x \leq y$ and $y \leq x$).
+
+A helpful visualisation for tpos is used in \cite{Booth2006}.
+It uses the fact that tpos can be represented as a linearly ordered set of ranks.
+Each rank of a tpo $\leq$ is defined as the equivalence classes modulo the symetric closure of $\leq$: $[[x]]_{\sim} = \{y \vert y \sim x\}$.
+These equivalence classes are then ordered by the relation $[[x]] \leq [[y]]$ iff $x \leq y$
+
+As an example consider a set of propositional worlds $W = \{ x_{1}, x_{2}, x_{3}, x_{4}\}$ and the a tpo $\leq$ with $x_{1} < x_{2} \sim x_{4} < x_{3}$.
+The equivalent representation as a linearly ordered set of ranks is shown in \ref{tab:visualising-a-tpo-example}.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{lll}
+$R_{1}$                      & $R_{2}$                                                                   & $R_{3}$                      \\ \hline
+\multicolumn{1}{|l|}{$x_{1}$} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}$x_{2}$\\ $x_{4}$\end{tabular}} & \multicolumn{1}{l|}{$x_{3}$} \\ \hline
+\end{tabular}
+\caption{Visualising a tpo as a linearly ordered set of ranks}
+\label{tab:visualising-a-tpo-example}
+\end{table}
+
+% belief set
+% belief revision
+% conditional beliefs, evidence/new information
+
+% TODO write chapter
+\section{Epistemic states and belief sets}
+
+%why epistemic states? difference between conditional and propositional belief sets
+%To understand the requirements imposed by iterated revision we should start by
+%recalling the distinction between belief sets and epistemic states. A belief set $ characterizes the set of propositions to which an agent is committed at any given time.
+%An epistemic state contains, in addition to @, the entire information needed for coherent reasoning, including, in particular, the very strategy of belief revision which the
+%agent wishes to employ at that given time. Any such strategy encodes, and is equivalent to, a set of “conditional beliefs”, that is, beliefs that one is prepared to adopt
+%conditioned on any hypothetical evidence [ 2,3,15,16,19,20]. To fully specify behavior under successive observations, one must encode, not merely how beliefs are to be
+%revised (this is enough for the first stage only) but also how the revision strategy
+%itself is to be modified by each new evidence. This amounts, in turns, to specifying
+%which conditional beliefs are to be retained and which ones deleted with each piece of
+%evidence.
+
+%Definition of the DP-AGM postulates and what modifications are made to them for the paper (to always be able to get a belief set from the tpo).
 Show how a belief set can be extracted from an epistemic state.
 Introduction of the notation of $\leq$ as tpo, $\ast$ as the revision operator for $\leq$ returning a new tpo $\leq^{\ast}_{\alpha}$.
-    \item Notation of the enriched epistemic state $W^{\pm}$, $\preceq$ and conditions on it as well as it's relation to $\leq$.
+
+% TODO write chapter
+\section{Enriched epistemic states and $\leq$-faithful tpos}
+%\begin{itemize}
+%    \item Notation of the enriched epistemic state $W^{\pm}$, $\preceq$ and conditions on it as well as it's relation to $\leq$.
 Visual examples using sticks \cite{Booth2011} and ranks (and mentioning that tpos can be represented as linearly ordered set of ranks) \cite{Booth2006}.
 Definition of a $\leq$-faithful tpo over $W^{\pm}$.
-\end{itemize}
-\textbf{Section Goal:} Notation and introducing the concept of a $\leq$-faithful tpo over $W^{\pm}$ and how to visualise it.
+%\end{itemize}
+%\textbf{Section Goal:} Notation and introducing the concept of a $\leq$-faithful tpo over $W^{\pm}$ and how to visualise it.
 
-% TODO expand this into subheadings and agenda
-\section{tpo-revision operators: Revision of $\leq$ with $\preceq$}
-\begin{itemize}
-    \item Introduction of $\ast$ as revision operator for $\leq$ and definition of $\ast_{\preceq}$ as example with visualisation.
-    \item Properties of $\ast_{\preceq}$, their explanation and theorem 1 as axiomatisation of the family of revision operators considered in the paper.
-    \item Explanation of sentinential view (and distinction to semantic level), definition of $\leq' \circ \beta $ and how it relates to conditional beliefs, mention of $\leq' \circ \top $ as belief set.
+% TODO write chapter
+% booth: "on a semantic level, i.e., in terms of how the ordering of individual worlds x, y undergo change"
+\section{tpo-revision operators: Revising $\leq$ with $\preceq$}
+%\begin{itemize}
+%    \item Introduction of $\ast$ as revision operator for $\leq$ and definition of $\ast_{\preceq}$ as example with visualisation.
+\subsection{Example operator}
+% shortened example from paper page 232 without SPH teil, show that shortened example satisfies the properties later on.
+USE EXAMPLE from darwiche -> here to illustrate things with guy killing an alien
+%TODO this could be OWN contribution!!?
+
+% TODO write chapter
+\section{Properties of tpo-revision operators}
+%    \item Properties of $\ast_{\preceq}$, their explanation and theorem 1 as axiomatisation of the family of revision operators considered in the paper.
+
+% TODO write chapter
+\section{Sentinential view}
+%    \item Explanation of sentinential view (and distinction to semantic level), definition of $\leq' \circ \beta $ and how it relates to conditional beliefs, mention of $\leq' \circ \top $ as belief set.
 Show of properties for the family of revision operators using sentinential view.
 Explanation of Disj1/Disj2 as properties that are easy to show in the sentinential view but not in the semantic formulation.
-\end{itemize}
-\textbf{Section Goal:} Definition of $\ast_{\preceq}$ as example revision operator and visualisation of it.
+%\end{itemize}
+%\textbf{Section Goal:} Definition of $\ast_{\preceq}$ as example revision operator and visualisation of it.
 Show of axiomatic definition of the family of operators in semantic and sentinential view.

### 2020-12-19 paper/paper.tex
feat: example

@@
 \usepackage{amsmath}
+\usepackage{amsthm}
 \usepackage{amssymb}
 \usepackage{dsfont}
+
+\theoremstyle{definition}
+\newtheorem{example}{Example}[section]
 
@@
 \section{Introduction}
+
+% goal of paper: interested in function * for getting new tpo
+
+% roten faden des reports beschreiben
+
 \subsection{Research context}
@@
 
-$W$ is the set of propositional worlds and given a $\alpha \in L$ the set of worlds that satisfy $\alpha$ is denoted by $[\alpha]$.
+$W$ is the set of propositional worlds (also called propositional interpretations in classical logic \cite{Kai2020}).
+Given a $\alpha \in L$ the set of worlds that satisfy $\alpha$ is denoted by $[\alpha]$.
 
@@
 
-A helpful visualisation for tpos is used in \cite{Booth2006}.
+A helpful visualisation for tpos is shown in \cite{Booth2006}.
 It uses the fact that tpos can be represented as a linearly ordered set of ranks.
-Each rank of a tpo $\leq$ is defined as the equivalence classes modulo the symetric closure of $\leq$: $[[x]]_{\sim} = \{y \vert y \sim x\}$.
+Each rank of a tpo $\leq$ is defined as the equivalence classes modulo the symmetric closure of $\leq$: $[[x]]_{\sim} = \{y \vert y \sim x\}$.
 These equivalence classes are then ordered by the relation $[[x]] \leq [[y]]$ iff $x \leq y$
 
-As an example consider a set of propositional worlds $W = \{ x_{1}, x_{2}, x_{3}, x_{4}\}$ and the a tpo $\leq$ with $x_{1} < x_{2} \sim x_{4} < x_{3}$.
+\begin{example}
+    \label{example:example-introduction}
+    As an accompanying example consider the following situation, closely aligned to \cite{Booth2011} and \cite{Darwiche1997}:
+
+    Our agent is a judge in a murder trial.
+John and Mary are suspects.
+$p$ represents "John is the murderer", $q$ represents "Mary is the murderer" and $r$ represents "the victim is an alien".
+Possible propositional worlds will be denoted as triplets of 0s and 1s denoting $p$, $q$ and $r$ to be true or false, e.g.
+the $101$-world stands for John being the murderer and the victim being an alien.
+
+    To start the agent believes it is reasonable to assume the murderer acted alone (but are not ruling out both of the accused conspiring).
+In addition it would be extremely surprising (but not impossible) if the victim was an alien.
+Tpos are a common tool to handle preference orderings like these.
+
+    Consider the propositional worlds $W = \{ 000, 001, 010, 011, 100, 101, 110, 111\}$.
+A tpo representing the judges assumptions would be $\leq$ with $010 \sim 100 < 000 \sim 110 < 011 \sim 101 < 001 \sim 111$.
 The equivalent representation as a linearly ordered set of ranks is shown in \ref{tab:visualising-a-tpo-example}.
@@
          \centering
-\begin{tabular}{lll}
-$R_{1}$                      & $R_{2}$                                                                   & $R_{3}$                      \\ \hline
-\multicolumn{1}{|l|}{$x_{1}$} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}$x_{2}$\\ $x_{4}$\end{tabular}} & \multicolumn{1}{l|}{$x_{3}$} \\ \hline
+        \begin{tabular}{llll}
+        $R_{1}$                      & $R_{2}$                                                                   & $R_{3}$ & $R_{4}$                      \\ \hline
+        \multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}$010$\\ $100$\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}$000$\\ $110$\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}$011$\\ $101$\end{tabular}} &
+            \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}$001$\\ $111$\end{tabular}} \\ \hline
         \end{tabular}
-\caption{Visualising a tpo as a linearly ordered set of ranks}
+        \caption{Visualising a tpo as a linearly ordered set of ranks as done in \cite{Booth2006}}
         \label{tab:visualising-a-tpo-example}
     \end{table}
-
-% belief set
-% belief revision
-% conditional beliefs, evidence/new information
+\end{example}
 
 % TODO write chapter
-\section{Epistemic states and belief sets}
+\subsection{Belief sets and epistemic states}
+A belief set is the deductively closed set of propositions an agent accepts as true at any given point in time \cite{Ferme2011}.
+AGM theory \cite{Alchourron1985} defines postulates for belief sets and their contraction, revision or expansion with new evidence.
 
-%why epistemic states? difference between conditional and propositional belief sets
-%To understand the requirements imposed by iterated revision we should start by
-%recalling the distinction between belief sets and epistemic states. A belief set $ characterizes the set of propositions to which an agent is committed at any given time.
-%An epistemic state contains, in addition to @, the entire information needed for coherent reasoning, including, in particular, the very strategy of belief revision which the
-%agent wishes to employ at that given time. Any such strategy encodes, and is equivalent to, a set of “conditional beliefs”, that is, beliefs that one is prepared to adopt
-%conditioned on any hypothetical evidence [ 2,3,15,16,19,20]. To fully specify behavior under successive observations, one must encode, not merely how beliefs are to be
-%revised (this is enough for the first stage only) but also how the revision strategy
-%itself is to be modified by each new evidence. This amounts, in turns, to specifying
-%which conditional beliefs are to be retained and which ones deleted with each piece of
-%evidence.
+Darwiche and Pearl \cite{Darwiche1997} argue that working with belief sets is not expressive enough for satisfying results in iterated belief revision.
+They make the distinction between propositional beliefs (i.e.
+beliefs the agent accepts and are part of the belief set) and conditional beliefs (i.e.
+beliefs the agent is prepared to adopt with new evidence).
+
+While the AGM postulates define restrictions on revising propositional beliefs (a core one being the principle of minimal change), they place little restrictions on preserving conditional beliefs.
+In their paper Darwiche and Pearl use epistemic states, abstract entities that contain all information an agent needs for it's reasoning, especially their strategy for belief revision.
+As conditional beliefs are represented by these strategies, it is necessary to define how to modify the strategy itself when encountering multiple new information \cite{Darwiche1997}.
+
+Belief sets can be extracted from epistemic states (the belief set extracted from an epistemic state $\mathbb{E}$ is denoted as $B(\mathbb{E})$).
+
+\begin{example}
+    Continuing example \ref{example:example-introduction} it is possible to model an epistemic state $\mathbb{E}$ with the tpo $\leq_{\mathbb{E}}$.
+
+    A belief set can be extracted from it by considering the lowest ranked worlds (i.e.
+the most plausible interpretations) under $\leq_{\mathbb{E}}$.
+For notation let $min(\alpha, \leq_{\mathbb{E}})$ denote the set of minimal models for the propositional formula $\alpha$ under $\leq_{\mathbb{E}}$.
+Then $min(\top, \leq_{\mathbb{E}})$ is the belief set associated with $\mathbb{E}$.
+\end{example}
+
+%Katsuno and Mendelzon [17] propose that an epistemic state Ψ
+%should be equipped with an ordering ≤Ψ of the worlds (interpretations), where the compatibility with Bel(Ψ) is ensured by the socalled faithfulness.
+%Definition 1 (Faithful Assignment [17]) A function Ψ 
+%→≤Ψ that
+%maps each epistemic state to a total preorder on interpretations is
+%said to be a faithful assignment if and only if:
+%(FA1) if ω1 ∈ Ψ and ω2 ∈ Ψ, then ω1 Ψ ω2
+%(FA2) if ω1 ∈ Ψ and ω2 ∈  / Ψ, then ω1 <Ψ ω2
+%Intuitively, ≤Ψ orders the worlds by plausibility, such that the minimal worlds with respect to ≤Ψ are the most plausible worlds.
 
@@
 \section{Enriched epistemic states and $\leq$-faithful tpos}
+% recal table 1 with visualisation exampple
+
 %\begin{itemize}

### 2020-12-19 paper/paper.tex
feat: added actual worlds to example
feat: example more correct

@@
 
+%Consider a knowledge base (KB) represented by a set of sentences in a
+%language L. As our perception of the world described by the knowledge base
+%changes, the knowledge base must be modified. G~irdenfors [9] distinguishes
+%several kinds of modifications. If we simply acquire additional knowledge
+%about the world, and the new knowledge does not conflict with the current
+%beliefs t of the KB, we expand the KB. If, however, the new knowledge is
+%inconsistent with the old beliefs, and we want the KB to be always consistent,
+%we must resolve the conflict somehow; this operation will be called revision. A
+%* Part of this work was performed while this author was visiting the University of Toronto.
+%** This author is partially supported by the Natural Science and Engineering Research Council
+%of Canada.
+%1 We use the terms belief and knowledge interchangeably in this paper.
+%0004-3702/91/$03.50 © 1991 -- Elsevier Science Publishers B.V. All rights reserved 
+%264 H. Katsuno, A.O. Mendelzon
+%different kind of change occurs when a sentence previously believed becomes
+%questionable and has to be given up; the operation that makes this change is a
+%contraction
+
 A common tool used to encode plausibility assumptions of an agent about possible worlds are total preorders (shortened as tpos) \cite{Booth2011}.
@@
 %in dem Primärartikel neu ist.
-%
-%\begin{itemize}
-%    \item Introduction of the research area of belief change and major sub-areas according to \cite{Darwiche1997}: nonmonotonic logic, probabilistic reasoning and belief revision and placing of \cite{Booth2011} in the area of belief revision.
-Belief revision as operator based approach that concerns itself with the definition of constrains (so called postulates) on operators that transitions between held beliefs when new information arrives \cite{Darwiche1997}.
-%    \item \cite{Alchourron1985} as seminal paper for one-step belief revision on belief sets.
-Definitions of belief sets and difference between propositional beliefs and conditional beliefs.
-Adherence to the principle of minimal change for currently held beliefs only; nearly no constrains on conditional beliefs.
-%    \item \cite{Grove1988} introducing an ordered worlds / spheres approach instead of working on a set of held beliefs.
-\cite{Booth2004} understanding preorders as partitions into equivalence classes on ordered worlds (and using multiple orders).
-Iterated belief change as outlook.
-%    \item \cite{Darwiche1997} discussion of iterated belief revision and the definition and need for epistemic states instead of belief sets for handling conditional beliefs.
-total preorders as plausibility orderings to represent conditional beliefs.
-%    \item \cite{Booth2011} discusses a framework for tpo-revision that enriches an epistemic state with a framework to create a new tpo for a revision step on the basis of interval orderings between positive and negative representations of possible worlds.
-Motivation of tpo-revision as 'context' as introduced in \cite{Booth2007}.
-%    \item Therefor \cite{Booth2011} as work in iterated belief revision, closer placement of \cite{Booth2011} as non-priotised revision on the belief set level.
-%    \item Related areas to the framework established \cite{Booth2011} with preference aggregation and relation to research in interval orderings.
-%\end{itemize}
-%\textbf{Section Goal:} Overview of the research area and placement of \cite{Booth2011} as work on iterated belief revision.
-Rough overview of the background for the work in \cite{Booth2011}.
-Shared understanding of: belief revision (and the difference between one-step- and iterated belief revision), belief sets and epistemic states, conditional beliefs in contrast to propositional beliefs, tpos as plausibility orderings, motivation and definition of tpo-revision as tool for iterated belief revision.
-Section will need to be discussed with the seminar on \cite{Darwiche1997} and reduced depending on how much is shown in their presentation.<
-%
-%see \cite{Kai2020} for inspiration
 
@@
 \subsection{Propositional Logic} % Aussagenlogik
-Notation follows as used in \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables, lower case greek letters for formulas in $L$ and $\top$, $\bot$ representing tautology and contradiction respectively.
+Notation follows as used in \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables, lower case greek letters represent formulae in $L$ and $\top$, $\bot$ representing tautology and contradiction respectively.
 $\vdash$ as classical logical consequence, $\equiv$ classical logical equivalence.
-$Cn$ is used to denote the deductive closure of a formula or set of formulas in $L$.
+$Cn$ is used to denote the deductive closure of a formula or set of formulae in $L$.
 
@@
 Belief sets can be extracted from epistemic states (the belief set extracted from an epistemic state $\mathbb{E}$ is denoted as $B(\mathbb{E})$).
+When modelled with a tpo, extraction is done by considering the lowest ranked worlds (i.e.
+the most plausible interpretations) under $\leq_{\mathbb{E}}$.
+The set of propositional sentences that holds in all those worlds is assumed to be the belief set of the agent.
+For notation let $min(\alpha, \leq_{\mathbb{E}})$ denote the set of minimal models for the propositional formula $\alpha$ under $\leq_{\mathbb{E}}$.
+Then $[B(\mathbb{E})] = min(\top, \leq_{\mathbb{E}})$ is the set of worlds that are models of the belief set $B(\mathbb{E})$ associated with $\mathbb{E}$.
 
@@
 
-    A belief set can be extracted from it by considering the lowest ranked worlds (i.e.
-the most plausible interpretations) under $\leq_{\mathbb{E}}$.
-For notation let $min(\alpha, \leq_{\mathbb{E}})$ denote the set of minimal models for the propositional formula $\alpha$ under $\leq_{\mathbb{E}}$.
-Then $min(\top, \leq_{\mathbb{E}})$ is the belief set associated with $\mathbb{E}$.
+    $min(\top, \leq_{\mathbb{E}})$ is the set of worlds on the lowest rank, $\{010, 100\}$.
+A possible belief set is $B(\mathbb{E}) = \{p \vee q, \neg p \vee \neg q, \neg r\}$ as $[B(\mathbb{E})] = \{010, 100\} = min(\top, \leq_{\mathbb{E}})$.
+Intuitively this makes sense with the initial assumption that John or Mary are the suspects ($p \vee q$), have acted alone ($\neg p \vee \neg q$) and the victim is not an alien ($\neg r$).
 \end{example}
 
+% do we need to discuss this in ore detail? faithful assignment here:
 %Katsuno and Mendelzon [17] propose that an epistemic state Ψ
@@
 
+\subsection{DP-AGM postulates}
 %Definition of the DP-AGM postulates and what modifications are made to them for the paper (to always be able to get a belief set from the tpo).

### 2020-12-19 paper/paper.tex
feat: title

@@
 % TODO better title
-\title{Report on 'How to Revise a Total Preorder' \cite{Booth2011}}
-\subtitle{Seminar 1901 - Representation and processing of uncertain knowledge with logic-based methods}
+\title{A bad day of studying is better than a good day of sleeping}
+\subtitle{Report on 'How to Revise a Total Preorder' \cite{Booth2011} for seminar 1901 - Representation and processing of uncertain knowledge with logic-based methods}
 \author{

### 2020-12-23 paper/paper.tex
feat: chapter on dp-agm

@@
 Belief sets can be extracted from epistemic states (the belief set extracted from an epistemic state $\mathbb{E}$ is denoted as $B(\mathbb{E})$).
-When modelled with a tpo, extraction is done by considering the lowest ranked worlds (i.e.
+Darwiche and Pearl show that their version of revision of epistemic states can be modelled with a tpo $\leq_{\mathbb{E}}$ associated with $\mathbb{E}$.
+Extraction of $B(\mathbb{E})$ is done by considering the lowest ranked worlds (i.e.
 the most plausible interpretations) under $\leq_{\mathbb{E}}$.
@@
 \subsection{DP-AGM postulates}
-%Definition of the DP-AGM postulates and what modifications are made to them for the paper (to always be able to get a belief set from the tpo).
-Show how a belief set can be extracted from an epistemic state.
-Introduction of the notation of $\leq$ as tpo, $\ast$ as the revision operator for $\leq$ returning a new tpo $\leq^{\ast}_{\alpha}$.
+The postulates first introduced by \cite{Alchourron1985} and reformulated for iterated belief revision on epistemic states by \cite{Darwiche1997} are repeated here.
+$\mathbb{E}$ denotes an epistemic state, $B(\mathbb{E})$ it's associated belief set, $B(\mathbb{E}) + \alpha$ the expansion of $B(\mathbb{E})$ by $\alpha$ and $\ast$ being a belief change operator on epistemic states.
+
+\begin{equation*}
+\begin{aligned}
+    (\mathbb{E}\ast1) \qquad & B(\mathbb{E}\ast\alpha) = Cn(B(\mathbb{E}\ast\alpha)) \\
+    (\mathbb{E}\ast2) \qquad &  \alpha \in B(\mathbb{E}\ast\alpha) \\
+    (\mathbb{E}\ast3) \qquad & B(\mathbb{E}\ast\alpha)  \subseteq B(\mathbb{E})+\alpha \\
+    (\mathbb{E}\ast4) \qquad & \textrm{If } \alpha \notin B(\mathbb{E}) \textrm{ then } B(\mathbb{E}) + \alpha \subseteq B(\mathbb{E} \ast \alpha) \\
+    (\mathbb{E}\ast5) \qquad & \textrm{If } \mathbb{E} = \mathbb{F} \textrm{ and } \alpha \equiv \beta \textrm{ then } B(\mathbb{E} \ast \alpha) = B(\mathbb{F} \ast \beta) \\
+    (\mathbb{E}\ast6) \qquad & \bot \in B(\mathbb{E} \ast \alpha) \textrm{ iff } \vdash \neg \alpha \\
+    (\mathbb{E}\ast7) \qquad & B(\mathbb{E} \ast (\alpha \wedge \beta)) \subseteq B(\mathbb{E} \ast \alpha) + \beta \\
+    (\mathbb{E}\ast8) \qquad & \textrm{If } \neg \beta \notin B(\mathbb{E} \ast \alpha) \textrm{ then } B(\mathbb{E} \ast \alpha) + \beta \subseteq B(\mathbb{E} \ast (\alpha \wedge \beta)) \\
+\end{aligned}
+\end{equation*}
+
+To guarantee the ability to extract unique belief sets from epistemic states after a revision by $\alpha$ the Booth and Meyer \cite{Booth2011} modify these postulates by requiring consistent epistemic inputs.
+That requirement means dropping $(\mathbb{E}\ast6)$ and considering only $(\mathbb{E}\ast1)$-$(\mathbb{E}\ast5)$ and $(\mathbb{E}\ast7)$-$(\mathbb{E}\ast8)$ as DP-AGM.
+
+While DP-AGM define the most plausible worlds after a revision by $\alpha$ (as $min(\alpha, \leq_{\mathbb{E}})$), Darwiche and Pearl also define postulates that restrict the rest of the new ordering.
+Because the focus of this report is on the revision of tpos the semantic (i.e.
+in terms of how the ordering of worlds undergoes change) versions are shown here, for more details and sentential versions refer to \cite{Darwiche1997}.
+
+\begin{equation*}
+\begin{aligned}
+    (CR1) \qquad & \textrm{If } v\in [\alpha], w \in [\alpha] \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ iff } v \leq_{\mathbb{E\ast\alpha}} w\\
+    (CR2) \qquad & \textrm{If } v\in [\neg \alpha], w \in [\neg \alpha] \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ iff } v \leq_{\mathbb{E\ast\alpha}} w\\
+    (CR3) \qquad & \textrm{If } v\in [ \alpha], w \in [\neg \alpha] \textrm{ then } v <_{\mathbb{E}} w \textrm{ only if } v <_{\mathbb{E\ast\alpha}} w\\
+    (CR4) \qquad & \textrm{If } v\in [ \alpha], w \in [\neg \alpha] \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ only if } v \leq_{\mathbb{E\ast\alpha}} w\\
+\end{aligned}
+\end{equation*}
+
+$(CR1)$ and $(CR2)$ mean that the relative ordering of worlds following a revision by $\alpha$ stays the same if the worlds are either both $\alpha$ or $\neg\alpha$ worlds.
+$(CR3)$ and $(CR4)$ require that $\alpha$-worlds that are strictly/weakly more plausible than $\neg\alpha$-worlds are still strictly/weakly more plausible than them after a $\alpha$-revision.
+
+% TODO: QUESTION: do we need C1-C4 here? 
+%\begin{equation*}
+%\begin{aligned}
+%    (C1) \qquad & \textrm{If } \beta \vdash \alpha \textrm{ then } B(\mathbb{E}\ast\alpha\ast\beta)=B(\mathbb{E}\ast\beta) \\
+%    (C2) \qquad & \textrm{If } \beta \vdash \neg  \alpha \textrm{ then } B(\mathbb{E}\ast\alpha\ast\beta)=B(\mathbb{E}\ast\beta) \\
+%    (C3) \qquad & \textrm{If } \alpha \in B(\mathbb{E}\ast\beta) \textrm{ then } \alpha \in B(\mathbb{E}\ast\alpha\ast\beta) \\
+%    (C4) \qquad & \textrm{If } \neg \alpha \notin B(\mathbb{E}\ast\beta) \textrm{ then } \neg \alpha \notin B(\mathbb{E}\ast\alpha\ast\beta) \\
+%\end{aligned}
+%\end{equation*}
 
@@
 \section{Enriched epistemic states and $\leq$-faithful tpos}
+%INTRO from dpm-agm
+%For the rest of the paper we assume a fixed but arbitrary initial tpo ≤ over W
+%which we wish to revise. This tpo plays the role of the plausibility ordering over
+%worlds introduced by Darwiche and Pearl into epistemic states. < will denote
+%the strict part of ≤, and ∼ the symmetric closure of ≤ (i.e. x ∼ y iff both x ≤ y
+%and y ≤ x). We are interested in functions ∗ which, for each α ∈ L, return a
+%new ordering ≤∗
+%α, and we will refer to any such ∗ as a revision operator for ≤.
+
 % recal table 1 with visualisation exampple

### 2020-12-24 paper/paper.tex
feat: sticks image

--- 2020-12-19 paper/paper.tex
@@
 \usepackage{dsfont}
+\usepackage{enumitem}
+\usepackage{tikz}
+\usepackage{pgfplots}
 
@@
 It uses the fact that tpos can be represented as a linearly ordered set of ranks.
-Each rank of a tpo $\leq$ is defined as the equivalence classes modulo the symmetric closure of $\leq$: $[[x]]_{\sim} = \{y \vert y \sim x\}$.
+Each rank of a tpo $\leq$ is defined as the equivalence classes modulo the symmetric closure of $\leq$: $[[x]]_{\sim} = \{y \mid y \sim x\}$.
 These equivalence classes are then ordered by the relation $[[x]] \leq [[y]]$ iff $x \leq y$
@@
 \subsection{DP-AGM postulates}
-%Definition of the DP-AGM postulates and what modifications are made to them for the paper (to always be able to get a belief set from the tpo).
-Show how a belief set can be extracted from an epistemic state.
-Introduction of the notation of $\leq$ as tpo, $\ast$ as the revision operator for $\leq$ returning a new tpo $\leq^{\ast}_{\alpha}$.
+The postulates first introduced by \cite{Alchourron1985} and reformulated for iterated belief revision on epistemic states by \cite{Darwiche1997} are repeated here.
+$\mathbb{E}$ denotes an epistemic state, $B(\mathbb{E})$ it's associated belief set, $B(\mathbb{E}) + \alpha$ the expansion of $B(\mathbb{E})$ by $\alpha$ and $\ast$ being a belief change operator on epistemic states.
+
+\begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\mathbb{E}\!*\!\arabic*$)]
+    \item\label{E1} $\qquad B(\mathbb{E}\ast\alpha) = Cn(B(\mathbb{E}\ast\alpha))$
+    \item\label{E2} $\qquad \alpha \in B(\mathbb{E}\ast\alpha)$
+    \item\label{E3} $\qquad B(\mathbb{E}\ast\alpha)  \subseteq B(\mathbb{E})+\alpha$
+    \item\label{E4} $\qquad \textrm{If } \alpha \notin B(\mathbb{E}) \textrm{ then } B(\mathbb{E}) + \alpha \subseteq B(\mathbb{E} \ast \alpha)$
+    \item\label{E5} $\qquad \textrm{If } \mathbb{E} = \mathbb{F} \textrm{ and } \alpha \equiv \beta \textrm{ then } B(\mathbb{E} \ast \alpha) = B(\mathbb{F} \ast \beta)$
+    \item\label{E6} $\qquad \bot \in B(\mathbb{E} \ast \alpha) \textrm{ iff } \vdash \neg \alpha$
+    \item\label{E7} $\qquad B(\mathbb{E} \ast (\alpha \wedge \beta)) \subseteq B(\mathbb{E} \ast \alpha) + \beta$
+    \item\label{E8} $\qquad \textrm{If } \neg \beta \notin B(\mathbb{E} \ast \alpha) \textrm{ then } B(\mathbb{E} \ast \alpha) + \beta \subseteq B(\mathbb{E} \ast (\alpha \wedge \beta))$
+\end{enumerate}
+
+To guarantee the ability to extract unique belief sets from epistemic states after a revision by $\alpha$ the Booth and Meyer \cite{Booth2011} modify these postulates by requiring consistent epistemic inputs.
+That requirement means dropping \ref{E6} and considering only \ref{E1}-\ref{E5} and \ref{E7}-\ref{E8} as DP-AGM.
+
+While DP-AGM define the most plausible worlds after a revision by $\alpha$ (as $min(\alpha, \leq_{\mathbb{E}})$), Darwiche and Pearl also define postulates that restrict the rest of the new ordering.
+Because the focus of this report is on the revision of tpos the semantic (i.e.
+in terms of how the ordering of worlds undergoes change) versions are shown here, for more details and sentential versions refer to \cite{Darwiche1997}.
+
+\begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = (CR$\arabic*$)]
+    \item\label{CR1} $\qquad \textrm{If } v\in [\alpha], w \in [\alpha] \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ iff } v \leq_{\mathbb{E\ast\alpha}} w$
+    \item\label{CR2} $\qquad \textrm{If } v\in [\neg \alpha], w \in [\neg \alpha] \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ iff } v \leq_{\mathbb{E\ast\alpha}} w$
+    \item\label{CR3} $\qquad \textrm{If } v\in [ \alpha], w \in [\neg \alpha] \textrm{ then } v <_{\mathbb{E}} w \textrm{ only if } v <_{\mathbb{E\ast\alpha}} w$
+    \item\label{CR4} $\qquad \textrm{If } v\in [ \alpha], w \in [\neg \alpha] \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ only if } v \leq_{\mathbb{E\ast\alpha}} w$
+\end{enumerate}
+
+\ref{CR1} and \ref{CR2} mean that the relative ordering of worlds following a revision by $\alpha$ stays the same if the worlds are either both $\alpha$ or $\neg\alpha$ worlds.
+\ref{CR3} and \ref{CR4} require that $\alpha$-worlds that are strictly/weakly more plausible than $\neg\alpha$-worlds are still strictly/weakly more plausible than them after a $\alpha$-revision.
+
+% TODO: QUESTION: do we need C1-C4 here? 
+%\begin{equation*}
+%\begin{aligned}
+%    (C1) \qquad & \textrm{If } \beta \vdash \alpha \textrm{ then } B(\mathbb{E}\ast\alpha\ast\beta)=B(\mathbb{E}\ast\beta) \\
+%    (C2) \qquad & \textrm{If } \beta \vdash \neg  \alpha \textrm{ then } B(\mathbb{E}\ast\alpha\ast\beta)=B(\mathbb{E}\ast\beta) \\
+%    (C3) \qquad & \textrm{If } \alpha \in B(\mathbb{E}\ast\beta) \textrm{ then } \alpha \in B(\mathbb{E}\ast\alpha\ast\beta) \\
+%    (C4) \qquad & \textrm{If } \neg \alpha \notin B(\mathbb{E}\ast\beta) \textrm{ then } \neg \alpha \notin B(\mathbb{E}\ast\alpha\ast\beta) \\
+%\end{aligned}
+%\end{equation*}
 
@@
 \section{Enriched epistemic states and $\leq$-faithful tpos}
-% recal table 1 with visualisation exampple
+Based on DP-AGM and the postulates $(CR1)$-$(CR4)$ Booth and Meyer assume a fixed tpo $\leq$ over a set of worlds $W$ that acts as a plausibility ordering.
+The goal of the paper is the discussion of functions $\ast$ that return a new ordering $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
+Functions $\ast$ that can be used for iterated revision in that way are refered to as revision operators for $\leq$.
+
+Booth and Meyers \cite{Booth2011} approach is to add additional metadata to every world $w \in W$.
+This new structure is denoted as $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$.
+In this notation a world $w \in W$ is represented twice: When new evidence $\alpha$ arrives that makes $w$ more plausible (because $w \in [\alpha]$) the agent can assume it's rank as $w^{+} \in W^{\pm}$.
+In contrast if the new evidence makes $w$ less plausible ($w \notin [\alpha]$) than $w^{-} \in W^{\pm}$ is $w$'s rank.
+The pair $(w^{+}, w^{-})$ represents an abstract interval representing metadata about plausibility assumptions about $w$.
+
+For the ordering on $W^{\pm}$ Booth and Meyer suppose an additional relation $\preceq$ over $W^{\pm}$ that is added to the epistemic state of an agent.
+
+\begin{example}
+    \label{example:example-stick}
+    Recall that tpos can be equivalently thought of as a linearly ordere set of ranks (Example \ref{example:example-introduction}) and therefor a tpo over $W$ can be visualised by ordering every $w \in W$ in a table of ranks (Table \ref{tab:visualising-a-tpo-example}).
+To visualise the interval ordering introduced by $\preceq$ Booth and Meyer use a "stick" with the endpoints defined as $w^{+}$/$w^{-}$ respectively, first introduced in \cite{Booth2007}.
+
+    \begin{figure}
+        \centering
+        \begin{tikzpicture}
+            \begin{axis}[
+                  yticklabels={,,$x_{4}$,$x_{3}$,$x_{2}$,$x_{1}$},
+                  xticklabels={,,},
+                  ytick style={draw=none},
+                  xtick style={draw=none},
+                  axis line style={draw=none},
+            scatter/classes={
+                empty={mark=o,draw=black}}]
+                    \addplot[scatter,
+                        scatter src=explicit symbolic]
+                        table [meta=label] {
+                    x y label
+
+                    5 1 empty
+                    7 1 empty
+
+                    2 2 empty
+                    4 2 empty
+
+                    2 3 empty
+                    4 3 empty
+
+                    1 4 empty
+                    3 4 empty
+                    };
+            \end{axis}
+        \end{tikzpicture}
+        \label{plot:example-visualisation-scatterplot}
+            \caption{Representation of $\preceq$ over $W^{\pm}$ using sticks}
+    \end{figure}
+\end{example}
 

### 2020-12-24 paper/paper.tex
feat: better scatterplot

@@
         \centering
-        \begin{tikzpicture}
+        \begin{tikzpicture}[scale=1.2]
             \begin{axis}[
@@
                   xtick style={draw=none},
-                  axis line style={draw=none},
+                  axis line style={draw=none}
+            ]
+            \addplot[
+                scatter,
+                scatter src=explicit symbolic,
+                mark size=3,
                 scatter/classes={
-                empty={mark=o,draw=black}}]
-                    \addplot[scatter,
-                        scatter src=explicit symbolic]
-                        table [meta=label] {
-                    x y label
+                    empty={mark=o, draw=black},
+                    filled={mark=x, draw=black}
+                },
+                nodes near coords*={\Label},
+                visualization depends on={value \thisrow{label} \as \Label}
+            ]
+            table [meta=class] {
+                    x y class label
 
-                    5 1 empty
-                    7 1 empty
+                    5 1 empty $x_{4}^{+}$
+                    7 1 empty $x_{4}^{-}$
 
-                    2 2 empty
-                    4 2 empty
+                    2 2 empty $x_{3}^{+}$
+                    4 2 empty $x_{3}^{-}$
 
-                    2 3 empty
-                    4 3 empty
+                    2 3 empty $x_{2}^{+}$
+                    4 3 empty $x_{2}^{-}$
 
-                    1 4 empty
-                    3 4 empty
+                    1 4 empty $x_{1}^{+}$
+                    3 4 empty $x_{1}^{-}$
                     };

### 2020-12-24 paper/paper.tex
feat: definition 1

@@
 \newtheorem{example}{Example}[section]
+
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+\renewcommand{\thedefinition}{\arabic{definition}}
 
@@
 % TODO write chapter
-\section{Enriched epistemic states and $\leq$-faithful tpos}
+\section{Additional metadata for tpo revision}
+\subsection{Enriching epistemic states}
 Based on DP-AGM and the postulates $(CR1)$-$(CR4)$ Booth and Meyer assume a fixed tpo $\leq$ over a set of worlds $W$ that acts as a plausibility ordering.
@@
 In contrast if the new evidence makes $w$ less plausible ($w \notin [\alpha]$) than $w^{-} \in W^{\pm}$ is $w$'s rank.
-The pair $(w^{+}, w^{-})$ represents an abstract interval representing metadata about plausibility assumptions about $w$.
+In their paper \cite{Booth2011} Booth and Meyer call the pair $(w^{+}, w^{-})$ the positive/negative representation of the world $w$.
+It represents an abstract interval representing metadata about plausibility assumptions about $w$.
 
+\subsection{$\leq$-faithful tpos}
 For the ordering on $W^{\pm}$ Booth and Meyer suppose an additional relation $\preceq$ over $W^{\pm}$ that is added to the epistemic state of an agent.
@@
     \label{example:example-stick}
-    Recall that tpos can be equivalently thought of as a linearly ordere set of ranks (Example \ref{example:example-introduction}) and therefor a tpo over $W$ can be visualised by ordering every $w \in W$ in a table of ranks (Table \ref{tab:visualising-a-tpo-example}).
-To visualise the interval ordering introduced by $\preceq$ Booth and Meyer use a "stick" with the endpoints defined as $w^{+}$/$w^{-}$ respectively, first introduced in \cite{Booth2007}.
+    Recall that tpos can be equivalently thought of as a linearly ordere set of ranks (Example \ref{example:example-introduction}, page \pageref{example:example-introduction}) and therefor a tpo over $W$ can be visualised by ordering every $w \in W$ in a table of ranks (Table \ref{tab:visualising-a-tpo-example}, page \pageref{tab:visualising-a-tpo-example}).
+To visualise the interval ordering introduced by $\preceq$ Booth and Meyer use a "stick" with the endpoints defined as $w^{+}$/$w^{-}$ respectively, first introduced in \cite{Booth2007} and shown in Figure \ref{fig:example-visualisation-scatterplot}.
 
-    \begin{figure}
+    \begin{figure}[h]
         \centering
@@
 
-                    2 2 empty $x_{3}^{+}$
-                    4 2 empty $x_{3}^{-}$
+                    3 2 empty $x_{3}^{+}$
+                    5 2 empty $x_{3}^{-}$
 
@@
         \end{tikzpicture}
-        \label{plot:example-visualisation-scatterplot}
+        \label{fig:example-visualisation-scatterplot}
             \caption{Representation of $\preceq$ over $W^{\pm}$ using sticks}
     \end{figure}
+
+    In this visualisation the worlds on lower ranks (more on the left) are preferred and therefor assumed to be more plausible.
+Here for example $x_{1}^{+} \prec x_{2}^{+}$ and $x_{3}^{-} \sim x_{4}^{+}$ Note that while all sticks have the same length in this example that is not required.
 \end{example}
 
-%\begin{itemize}
-%    \item Notation of the enriched epistemic state $W^{\pm}$, $\preceq$ and conditions on it as well as it's relation to $\leq$.
-Visual examples using sticks \cite{Booth2011} and ranks (and mentioning that tpos can be represented as linearly ordered set of ranks) \cite{Booth2006}.
-Definition of a $\leq$-faithful tpo over $W^{\pm}$.
-%\end{itemize}
-%\textbf{Section Goal:} Notation and introducing the concept of a $\leq$-faithful tpo over $W^{\pm}$ and how to visualise it.
+To define the relations between $\preceq$ and $\leq$ Booth and Meyer define a list of conditions.
+
+\begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\preceq\arabic*$)]
+    \item\label{PREQ1} $\qquad \preceq \textrm{ is a tpo over } W^{\pm}$
+    \item\label{PREQ2} $\qquad x^{+} \preceq y^{+} \textrm{ iff } x \leq y$
+    \item\label{PREQ3} $\qquad x^{-} \preceq y^{-} \textrm{ iff } x \leq y$
+    \item\label{PREQ4} $\qquad x^{+} \prec x^{-}$
+\end{enumerate}
+
+The choice between positive or negative representations of two worlds should be the same as under $\leq$ (due to \ref{PREQ2}, \ref{PREQ3}).
+According to \ref{PREQ4} there has to be a difference between to ranks of a positive representation and a negative representation of the same world and given the choice between both the positive representation has to be chosen.
+
+\begin{definition}[$\leq$-faithful tpo over $W^{\pm}$ taken directly from \cite{Booth2011}]
+Let $\preceq \in W^{\pm} \times W^{\pm}$. If $\preceq$ satisfies \ref{PREQ1}-\ref{PREQ4} we say $\preceq$ is a $\leq$-faithful tpo (over $W^{\pm}$).
+\end{definition}
+
+Because of \ref{PREQ2} and \ref{PREQ3} it is sufficient to only include $\preceq$ in the epistemic state.
+The tpo $\leq$ over $W$ can be determined from $\preceq$ by restricting to only $\{ x^{+} \mid x \in W\}$ or $\{ x^{-} \mid x \in W\}$ respectively.
 

### 2020-12-25 paper/paper.tex
feat: definition of revision operators

@@
 In contrast if the new evidence makes $w$ less plausible ($w \notin [\alpha]$) than $w^{-} \in W^{\pm}$ is $w$'s rank.
-In their paper \cite{Booth2011} Booth and Meyer call the pair $(w^{+}, w^{-})$ the positive/negative representation of the world $w$.
+In their paper Booth and Meyer call the pair $(w^{+}, w^{-})$ the positive/negative representation of the world $w$.
 It represents an abstract interval representing metadata about plausibility assumptions about $w$.
@@
 The choice between positive or negative representations of two worlds should be the same as under $\leq$ (due to \ref{PREQ2}, \ref{PREQ3}).
-According to \ref{PREQ4} there has to be a difference between to ranks of a positive representation and a negative representation of the same world and given the choice between both the positive representation has to be chosen.
+According to \ref{PREQ4} there has to be a difference between two ranks of a positive representation and a negative representation of the same world and given the choice between both the positive representation has to be chosen.
 
 \begin{definition}[$\leq$-faithful tpo over $W^{\pm}$ taken directly from \cite{Booth2011}]
-Let $\preceq \in W^{\pm} \times W^{\pm}$. If $\preceq$ satisfies \ref{PREQ1}-\ref{PREQ4} we say $\preceq$ is a $\leq$-faithful tpo (over $W^{\pm}$).
+\label{definition:faithful-tpo}Let $\preceq \in W^{\pm} \times W^{\pm}$. If $\preceq$ satisfies \ref{PREQ1}-\ref{PREQ4} we say $\preceq$ is a $\leq$-faithful tpo (over $W^{\pm}$).
 \end{definition}
@@
 
+\begin{example}
+    \label{example:example-faithful-tpo}
+    Is the following tpo $\preceq$ over $W^{\pm}$ a $\leq$-faithful tpo?
+
+    \begin{figure}[h]
+        \centering
+        \begin{tikzpicture}[scale=1]
+            \begin{axis}[
+                  yticklabels={,,},
+                  xticklabels={,,},
+                  ytick style={draw=none},
+                  xtick style={draw=none},
+                  axis line style={draw=none}
+            ]
+            \addplot[
+                scatter,
+                scatter src=explicit symbolic,
+                mark size=3,
+                scatter/classes={
+                    empty={mark=o, draw=black},
+                    filled={mark=x, draw=black}
+                },
+                nodes near coords*={\Label},
+                visualization depends on={value \thisrow{label} \as \Label}
+            ]
+            table [meta=class] {
+                    x y class label
+
+                    3 1 empty $x_{3}^{+}$
+                    5 1 empty $x_{3}^{-}$
+
+                    2 2 empty $x_{2}^{+}$
+                    3 2 empty $x_{2}^{-}$
+
+                    1 3 empty $x_{1}^{+}$
+                    4 3 empty $x_{1}^{-}$
+                    };
+            \end{axis}
+        \end{tikzpicture}
+    \end{figure}
+
+    While \ref{PREQ1} and \ref{PREQ4} are satisfied, $\preceq$ is not a $\leq$-faithful tpo: Due to \ref{PREQ2} and $x_{1}^{+} \prec x_{2}^{+}$ follows $x_{1} < x_{2}$.
+That means \ref{PREQ3} can not hold as $x_{2}^{-} \prec x_{1}^{-}$ which would require $x_{2} < x_{3}$ to be true.
+
+    As demonstrated here while the "sticks" do not need to be the same size (just exist due to \ref{PREQ4}) they need to be the same size for worlds that share a rank for their corresponding representations and can not "cover" other sticks completely to continue to satisfy \ref{PREQ2} and \ref{PREQ3}.
+\end{example}
+
 % TODO write chapter
 % booth: "on a semantic level, i.e., in terms of how the ordering of individual worlds x, y undergo change"
-\section{tpo-revision operators: Revising $\leq$ with $\preceq$}
+\section{Tpo revision operators}
+Booth and Meyer \cite{Booth2011} aim to discuss tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
+To do so they define how to use the additional information from a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ to create a revision operator $\ast_{\preceq}$.
+
+\begin{definition}[Revision operator $\ast_{\preceq}$ for $\leq$ generated by $\preceq$ from \cite{Booth2011}]
+    \label{definition:revision-operator}
+    For each $\leq$-faithful tpo $\preceq$ over $W^{\pm}$, refer to $\ast_{\preceq}$ as the revision operator for $\leq$ generated by $\preceq$ defined by:
+
+    Set for any $\alpha \in L$ and $x \in W$:
+    \begin{equation*}
+        r_{\alpha}(x) = \left\{
+                    \begin{array}{ll}
+                      x^{+} \textrm{ if } x \in [\alpha]\\
+                      x^{-} \textrm{ if } x \in [\neg\alpha]
+                    \end{array}
+                  \right.
+    \end{equation*}
+
+    The revised tpo $\leq_{\alpha}^{\ast}$ is defined by setting, for each $x, y \in W$,
+
+    \begin{equation*}
+        x \leq_{\alpha}^{\ast} y \textrm{ iff } r_{\alpha}(x) \preceq r_{\alpha}(y)
+    \end{equation*}
+\end{definition}
+
+Intuitively new evidence $\alpha$ makes worlds that satisfy $\alpha$ more plausible and worlds that do not satisfy $\alpha$ less plausible.
+Therefor the agent associates worlds $w \in [\alpha]$ with their positive representation $w^{+}$ and worlds $w \in [\neg\alpha]$ with their negative representation $w^{-}$.
+
+% visual example with alien -> revise tpo
+
+% show also: new evidence that does not become part of the belief set -> non prio example, explain what it is
+\subsection{The problem of just moving things one up}
+
 %\begin{itemize}
 %    \item Introduction of $\ast$ as revision operator for $\leq$ and definition of $\ast_{\preceq}$ as example with visualisation.
+
 \subsection{Example operator}
@@
 \section{Properties of tpo-revision operators}
-%    \item Properties of $\ast_{\preceq}$, their explanation and theorem 1 as axiomatisation of the family of revision operators considered in the paper.
+%    \item Properties of $\ast_{\preceq}$, their explanation
+
+%"These
+%three rules were considered characteristic of a family of operators called
+%admissible revision operators [7]."
+% TODO: WHAT ARE ADMISSIBLE OPERATORS
+
+% THEOREM 1 as axiomatisation of the family of revision operators considered in the paper.
 
 % TODO write chapter
-\section{Sentinential view}
+\section{Sentinential view, do we even need this?}
 %    \item Explanation of sentinential view (and distinction to semantic level), definition of $\leq' \circ \beta $ and how it relates to conditional beliefs, mention of $\leq' \circ \top $ as belief set.

### 2020-12-25 paper/paper.tex
feat: more todos

@@
 
-A common tool used to encode plausibility assumptions of an agent about possible worlds are total preorders (shortened as tpos) \cite{Booth2011}.
+% TODO: discussed in \cite{Katsuno1991} correct? was mentioned in intro of Admissible and Restrained Revision
+A common tool used to encode plausibility assumptions of an agent about possible worlds are total preorders (shortened as tpos) \cite{Booth2011}, discussed in \cite{Katsuno1991}.
 The primary article for this report, 'How to Revise a Total Preorder' discusses how to model the change of these total preorders when new evidence becomes available.
@@
 AGM theory \cite{Alchourron1985} defines postulates for belief sets and their contraction, revision or expansion with new evidence.
+% TODO explain contraction, revision, expansion?
+%    As our perception of the world described by the knowledge base
+%    changes, the knowledge base must be modified. G~irdenfors [9] distinguishes
+%    several kinds of modifications. If we simply acquire additional knowledge
+%    about the world, and the new knowledge does not conflict with the current
+%    beliefs t of the KB, we expand the KB. If, however, the new knowledge is
+%    inconsistent with the old beliefs, and we want the KB to be always consistent,
+%    we must resolve the conflict somehow; this operation will be called revision. A
+%    * Part of this work was performed while this author was visiting the University of Toronto.
+%    ** This author is partially supported by the Natural Science and Engineering Research Council
+%    of Canada.
+%    1 We use the terms belief and knowledge interchangeably in this paper.
+%    0004-3702/91/$03.50 © 1991 -- Elsevier Science Publishers B.V. All rights reserved 
+%    264 H. Katsuno, A.O. Mendelzon
+%    different kind of change occurs when a sentence previously believed becomes
+%    questionable and has to be given up; the operation that makes this change is a
+%    contraction. Other kinds of operations are discussed in [14].
 
@@
 % TODO: WHAT ARE ADMISSIBLE OPERATORS
+%info here: \cite{Booth2006a}
 

### 2020-12-25 paper/paper.tex
feat: example for one step revision

@@
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\renewcommand{\thedefinition}{\arabic{definition}}
+\newtheorem{definition}{Definition}
 
@@
 
-% TODO write formal background
 \section{Formal background}
@@
 
-% TODO write chapter
 \subsection{Belief sets and epistemic states}
@@
 
-% do we need to discuss this in ore detail? faithful assignment here:
+% TODO: do we need to discuss this in ore detail? faithful assignment here:
 %Katsuno and Mendelzon [17] propose that an epistemic state Ψ
@@
 
-% TODO write chapter
 \section{Additional metadata for tpo revision}
@@
 
-                    5 1 empty $x_{4}^{+}$
-                    7 1 empty $x_{4}^{-}$
+                    3 1 empty $x_{4}^{+}$
+                    6 1 empty $x_{4}^{-}$
 
-                    3 2 empty $x_{3}^{+}$
+                    2 2 empty $x_{3}^{+}$
                     5 2 empty $x_{3}^{-}$
 
-                    2 3 empty $x_{2}^{+}$
-                    4 3 empty $x_{2}^{-}$
+                    1 3 empty $x_{2}^{+}$
+                    3 3 empty $x_{2}^{-}$
 
@@
         \end{tikzpicture}
+        \caption{Representation of $\preceq$ over $W^{\pm}$ using sticks}
         \label{fig:example-visualisation-scatterplot}
-            \caption{Representation of $\preceq$ over $W^{\pm}$ using sticks}
     \end{figure}
@@
     In this visualisation the worlds on lower ranks (more on the left) are preferred and therefor assumed to be more plausible.
-Here for example $x_{1}^{+} \prec x_{2}^{+}$ and $x_{3}^{-} \sim x_{4}^{+}$ Note that while all sticks have the same length in this example that is not required.
+Here for example $x_{1}^{+} \prec x_{3}^{+}$ and $x_{1}^{-} \sim x_{4}^{+}$ Note that while all sticks have the same length in this example that is not required.
 \end{example}
@@
 
-% visual example with alien -> revise tpo
+\begin{example}
+    \label{example:example-updated-tpo}
+    Reconsidering the tpo $\preceq$ from example \ref{example:example-stick} (page \pageref{example:example-stick}).
+When a new piece of evidence $\alpha$ has to be considered each world gets mapped to one end of the interval assigned to it depending on if it is an $\alpha$-world or not.
+In figure \ref{fig:example-updated-tpo} that mapping is indicated by the filled out dot.
+For this example $x_{1}, x_{2}$ and $x_{3}$ are $[\neg\alpha]$-worlds while $x_{4}$ is an $[\alpha]$-world.
 
+    \begin{figure}[h]
+        \centering
+        \begin{tikzpicture}[scale=1.2]
+            \begin{axis}[
+                  yticklabels={,,$x_{4}$,$x_{3}$,$x_{2}$,$x_{1}$},
+                  xticklabels={,,},
+                  ytick style={draw=none},
+                  xtick style={draw=none},
+                  axis line style={draw=none}
+            ]
+            \addplot[
+                scatter,
+                scatter src=explicit symbolic,
+                mark size=3,
+                scatter/classes={
+                    empty={mark=o, draw=black}
+                },
+                nodes near coords*={\Label},
+                visualization depends on={value \thisrow{label} \as \Label}
+            ]
+            table [meta=class] {
+                    x y class label
+
+                    3 1 filled $x_{4}^{+}$
+                    6 1 empty $x_{4}^{-}$
+
+                    2 2 empty $x_{3}^{+}$
+                    5 2 filled $x_{3}^{-}$
+
+                    1 3 empty $x_{2}^{+}$
+                    3 3 filled $x_{2}^{-}$
+
+                    1 4 empty $x_{1}^{+}$
+                    3 4 filled $x_{1}^{-}$
+                    };
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Associating worlds with their positive/negative representations}
+        \label{fig:example-updated-tpo}
+    \end{figure}
+
+    The updated tpo $\leq_{\alpha}^{\ast}$ can now be inferred from the figure as the ordering of the filled dots representing the new assignment for the respective world: $x_{1} \sim x_{2} \sim x_{4} < x_{3}$.
+\end{example}
+
+\subsection{Non priotised revision}
 % show also: new evidence that does not become part of the belief set -> non prio example, explain what it is
 \subsection{The problem of just moving things one up}
-
-%\begin{itemize}
-%    \item Introduction of $\ast$ as revision operator for $\leq$ and definition of $\ast_{\preceq}$ as example with visualisation.
-
-\subsection{Example operator}
-% shortened example from paper page 232 without SPH teil, show that shortened example satisfies the properties later on.
-USE EXAMPLE from darwiche -> here to illustrate things with guy killing an alien
-%TODO this could be OWN contribution!!?
 
@@
 % THEOREM 1 as axiomatisation of the family of revision operators considered in the paper.
+
+\subsection{Example operator}
+% shortened example from paper page 232 without SPH teil, show that shortened example satisfies the properties later on.
+USE EXAMPLE from darwiche -> here to illustrate things with guy killing an alien
+%TODO this could be OWN contribution!!?
 

### 2020-12-26 paper/paper.tex
feat: non prio revision

@@
 \subsection{DP-AGM postulates}
+\label{chapter:dp-agm-postulates}
 The postulates first introduced by \cite{Alchourron1985} and reformulated for iterated belief revision on epistemic states by \cite{Darwiche1997} are repeated here.
@@
     \label{example:example-updated-tpo}
-    Reconsidering the tpo $\preceq$ from example \ref{example:example-stick} (page \pageref{example:example-stick}).
-When a new piece of evidence $\alpha$ has to be considered each world gets mapped to one end of the interval assigned to it depending on if it is an $\alpha$-world or not.
+    Reconsider the $\leq$-faithful tpo $\preceq$ from example \ref{example:example-stick} (page \pageref{example:example-stick}).
+When a new piece of evidence $\alpha$ has to be considered each world gets mapped to one end of the interval assigned to it, depending on if it is an $\alpha$-world or not.
 In figure \ref{fig:example-updated-tpo} that mapping is indicated by the filled out dot.
@@
 
-\subsection{Non priotised revision}
-% show also: new evidence that does not become part of the belief set -> non prio example, explain what it is
-\subsection{The problem of just moving things one up}
+\subsection{Non-prioritised revision}
+
+Belief revision with the AGM postulates \cite{Alchourron1985} or the reformulation by Darwiche and Pearl \cite{Darwiche1997} always includes the new information $\alpha$ in the belief set after revision.
+This feature is explicit in \ref{E2} of DP-AGM from chapter \ref{chapter:dp-agm-postulates} (page \pageref{chapter:dp-agm-postulates}) given as $\alpha \in B(\mathbb{E}\ast\alpha)$.
+
+The operators characterised by Booth and Meyer do not require new evidence $\alpha$ to be part of the revised belief set which makes them part of non-prioritised revision \cite{Hansson1999}.
+
+An example is already given in example \ref{example:example-updated-tpo} and figure \ref{fig:example-updated-tpo}.
+The belief set extracted from the new epistemic state $\mathbb{E}$ as $[B(\mathbb{E})] = min(\top, \leq_{\alpha}^{\ast})$ includes the $[\neg\alpha]$-worlds $x_{1}$ and $x_{2}$ and therefor does not include the new evidence $\alpha$.
+
+%Although the approach described allows us to determine more than just
+%the belief set associated with an epistemic state, there is a problem with this
+%approach regarding iterated tpo-revision. While the extra structure tells us
+%how to determine a new tpo, it tells us nothing about how to determine the
+%new extra structure which is needed to guide the next revision. Clearly the
+%problem of iterated belief revision has simply re-emerged “one level up”. We
+%investigate this problem by considering some desirable properties for revising
+%the extra structure, and prove the consistency of these properties by giving a
+%concrete operator satisfying all of them.
 
 % TODO write chapter
-\section{Properties of tpo-revision operators}
+\section{Properties of Booth and Meyer tpo-revision operators}
 %    \item Properties of $\ast_{\preceq}$, their explanation
@@
 
-\subsection{Example operator}
-% shortened example from paper page 232 without SPH teil, show that shortened example satisfies the properties later on.
-USE EXAMPLE from darwiche -> here to illustrate things with guy killing an alien
-%TODO this could be OWN contribution!!?
-
 % TODO write chapter
-\section{Sentinential view, do we even need this?}
+\subsection{Sentinential view}
 %    \item Explanation of sentinential view (and distinction to semantic level), definition of $\leq' \circ \beta $ and how it relates to conditional beliefs, mention of $\leq' \circ \top $ as belief set.
@@
 
-\section{Summary}
+\section{Revising $\preceq$}
+% DO NOT DO THIS? OR mention that we only show a concrete operator and not discuss properties, see discussion
+\subsection{Example operator}
+% shortened example from paper page 232 without SPH teil, show that shortened example satisfies the properties later on.
+USE EXAMPLE from darwiche -> here to illustrate things with guy killing an alien
+%TODO this could be OWN contribution!!?
+
+% TODO write chapter
+\section{Discussion}
+\subsection{Iterating on the iterator}
+The revision operator $\ast$ based on $\preceq$ allows the revision of a tpo $\leq$ associated with an epistemic state to $\leq_{\alpha}^{\ast}$.
+To be useful in iterated belief revision the newly introduced structure $\preceq$ also needs to be revised, as Booth and Meyer put it the problem has "re-emerged 'one level up'" \cite{Booth2011}.
+In their paper Booth and Meyer discuss strict preference hierarchies (or SPHs), an equivalent structure to $\preceq$ denoted as $\$$, their properties and how to revise them.
+For more information on SPH revision see \cite{Booth2011}.
 

### 2020-12-27 paper/paper.tex
feat: properties
feat: properties of operators

@@
-\documentclass[11pt]{scrartcl}
+\documentclass[english, 12pt]{scrartcl}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{pgfplots}
+\usepackage[onehalfspacing]{setspace}
 
@@
 
+\theoremstyle{definition}
+\newtheorem{theorem}{Theorem}
+
 \begin{document}
 
-% TODO better title
+% TODO title
 \title{A bad day of studying is better than a good day of sleeping}
@@
 
-% TODO write introduction, make WAY SHORTER, inspire by kai
+% TODO introduction
 \section{Introduction}
@@
 % TODO explain contraction, revision, expansion?
+
 %    As our perception of the world described by the knowledge base
@@
 
-% TODO write chapter
-% booth: "on a semantic level, i.e., in terms of how the ordering of individual worlds x, y undergo change"
-\section{Tpo revision operators}
+\section{Booth and Meyer tpo revision operators}
 Booth and Meyer \cite{Booth2011} aim to discuss tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
@@
 
-% TODO write chapter
+% TODO write Properties of Booth and Meyer tpo-revision operators
 \section{Properties of Booth and Meyer tpo-revision operators}
-%    \item Properties of $\ast_{\preceq}$, their explanation
+While not determining a concrete operator $\ast_{\preceq}$ to revise a tpo $\leq$, definition \ref{definition:revision-operator} allows Booth and Meyer to discuss what properties any operator in that family must have \cite{Booth2011}.
 
-%"These
-%three rules were considered characteristic of a family of operators called
-%admissible revision operators [7]."
+The list of properties they consider to be a complete axiomatisation of the family of operators they consider follows:
+
+\begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\ast\arabic*$)]
+    \item\label{AST1} $\qquad \leq_{\alpha}^{\ast} \textrm{ is a tpo over } W$
+    \item\label{AST2} $\qquad\alpha \equiv \gamma \textrm{ implies } \leq_{\alpha}^{\ast}=\leq_{\gamma}^{\ast}$
+    \item\label{AST3} $\qquad \textrm{If } x, y \in [\alpha] \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
+    \item\label{AST4} $\qquad \textrm{If } x, y \in [\neg\alpha] \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
+    \item\label{AST5} $\qquad \textrm{If } x \in [\alpha], y \in [\neg\alpha] \textrm{ and } x \leq y \textrm{ then } x <_{\alpha}^{\ast} y$
+    \item\label{AST6} $\qquad \textrm{If } x \in [\alpha], y \in [\neg\alpha] \textrm{ and } y \leq_{\alpha}^{\ast} x \textrm{ then } y \leq_{\gamma}^{\ast} x$
+    \item\label{AST7} $\qquad \textrm{If } x \in [\alpha], y \in [\neg\alpha] \textrm{ and } y <_{\alpha}^{\ast} x \textrm{ then } y <_{\gamma}^{\ast} x$
+\end{enumerate}
+
+%TODO question: the text sounds like the properties are supposed by BM/they define them but they are also proved?! or does this mean proved for their approach but could be done differently?
+%We propose that if x is not more
+%preferred than y, even after receiving evidence which clearly points more to x
+%being the case than it does to y, then there can be no evi
+
+\ref{AST1} and \ref{AST2} are considered basic properties: A revision of a tpo $\leq$ over $W$ must generate another tpo over $W$ .
+In addition the operator must return the same revised tpo for semantically equivalent sentences, the so called syntax-irrelevance property.
+
+The next group of properties, \ref{AST3}-\ref{AST5} are common rules in iterated belief change.
+Booth and Meyer themselves consider them characteristic for admissible revision operators \cite{Booth2006a}.
+If revising a tpo by a sentence $\alpha$, the relative ordering of worlds that are either both $[\alpha]$- or $[\neg\alpha]$-worlds must stay the same (\ref{AST3}/\ref{AST4}).
+These properties were already part of the semantic postulates \ref{CR1} and \ref{CR2} by Darwiche and Pearl \cite{Darwiche1997} discussed in chapter \ref{chapter:dp-agm-postulates} (page \pageref{chapter:dp-agm-postulates}).
+In a similar way \ref{AST5} is a stronger requirement than the other two Darwiche and Pearl postulates \ref{CR3} and \ref{CR4}.
+It means the following: A world $x$ that is considered at least as plausible as a world $y$ before a revision by new information $\alpha$.
+If $\alpha$ makes $x$ more plausible ($x \in [\alpha]$) and $y$ less plausible ($y \in [\neg\alpha]$) then after revision $x$ should be considered strictly more plausible than $y$.
+This rule was independently proposed by Booth and Meyer \cite{Booth2006a} and Jin und Thielscher \cite{Jin2007}.
+
 % TODO: WHAT ARE ADMISSIBLE OPERATORS
@@
 
-% THEOREM 1 as axiomatisation of the family of revision operators considered in the paper.
+% TODO: pull these out? Basic postulates for tpo revision in one subsection, additional ones "supplementary rationality properties" as second section?
+These properties define tpo-revision with one input sentence which make Booth and Meyer relate them to the AGM postulates for belief set revison \cite{Alchourron1985} as basic postulates for tpo-revision \cite{Booth2011}.
 
-% TODO write chapter
+With \ref{AST6} and \ref{AST7} Booth and Meyer aim to add supplementary rationality properties to keep revision with different sentences coherent.
+These properties are largely ignored in other literature on iterated belief change \cite{Booth2011}.
+\ref{AST6} means that if, after revision by evidence $\alpha$ that makes a world $x$ more plausible than $y$, $y$ is still considered at least as plausible as $x$, then for any possible revision by evidence $\gamma$, $y$ must be at least as plausible as $x$.
+\ref{AST7} is the equivalent property for strict preference.
+
+\bigskip
+
+With these properties for $\ast$ discussed, Booth and Meyer define the family of operators they are discussing with theorem \ref{theorem:revision-operator}.
+
+% THEOREM 1 as axiomatisation of the family of revision operators considered in the paper. "It turns out that these properties provide an exact characterisation of the
+% revision operators we consider."
+
+\begin{theorem}
+\label{theorem:revision-operator}Let $\ast$ be any revision operator for $\leq$.
+Then $\ast$ is generated from some $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ iff $\ast$ satisfies \ref{AST1}-\ref{AST7}.
+\cite{Booth2011}
+\end{theorem}
+
+% TODO: do example operator for tpo <= here for each property with alien example and proof it works for each? -> OWN contrib
+
+% TODO write Sentinential view
 \subsection{Sentinential view}
+% booth: "on a semantic level, i.e., in terms of how the ordering of individual worlds x, y undergo change"
 %    \item Explanation of sentinential view (and distinction to semantic level), definition of $\leq' \circ \beta $ and how it relates to conditional beliefs, mention of $\leq' \circ \top $ as belief set.
@@
 
-% TODO write chapter
+% TODO write Discussion
 \section{Discussion}
+% TODO *6,*7 seem weird, no different "strength" of evidence?
+% TODO: discuss 6/7 being wrong? strength of evidence?=!=!, discuss 5 with it being equal when sticks - and + are same rank?! 
 \subsection{Iterating on the iterator}

### 2020-12-27 paper/paper.tex
feat: postulate of independence
fix: fixed not-filled marks in scatterplots

@@
                 scatter/classes={
-                    empty={mark=o, draw=black},
-                    filled={mark=x, draw=black}
+                    empty={mark=*, fill=white},
+                    filled={mark=*, fill=black}
                 },
@@
                 scatter/classes={
-                    empty={mark=o, draw=black}
+                    empty={mark=*, fill=white},
+                    filled={mark=*, fill=black}
                 },
@@
 If $\alpha$ makes $x$ more plausible ($x \in [\alpha]$) and $y$ less plausible ($y \in [\neg\alpha]$) then after revision $x$ should be considered strictly more plausible than $y$.
-This rule was independently proposed by Booth and Meyer \cite{Booth2006a} and Jin und Thielscher \cite{Jin2007}.
+This rule was not only proposed by Booth and Meyer \cite{Booth2006a} but also Jin und Thielscher in \cite{Jin2007} (as the postulate of independence).
 

### 2020-12-28 paper/paper.tex
fix: some writing fixes

@@
 A core process for an agent dealing with uncertain knowledge is updating their worldview when new information becomes available, also called belief change.
-As an agent can be human or a machine work in belief change has impact on both philosophy and artificial intelligence \cite{Ferme2011}.
+As an agent can be human or a machine, work in belief change has impact on both philosophy and artificial intelligence \cite{Ferme2011}.
 Different approaches to handling belief change have been discussed with notable approaches including nonmonotonic logic, probabilistic reasoning and belief revision \cite{Darwiche1997}.
@@
 In belief revision, belief change is modelled using an operator that produces an updated set of beliefs from the state of an agent and new evidence.
-Research in this area discusses appropriate formalisations of agent state and constrains on individual or families of operators.
+Research in this area discusses appropriate formalisations of agent state and constrains on individual operators or families of operators.
 Depending on if the suggested operator handles only one new evidence or multiple new evidences the approaches are called one-step or iterated belief revision.
@@
 A common tool used to encode plausibility assumptions of an agent about possible worlds are total preorders (shortened as tpos) \cite{Booth2011}, discussed in \cite{Katsuno1991}.
-The primary article for this report, 'How to Revise a Total Preorder' discusses how to model the change of these total preorders when new evidence becomes available.
+The primary article for this report, 'How to Revise a Total Preorder', researches how to model the change of these total preorders when new evidence becomes available.
 Being able to derive a new tpo from additional evidence is an approach to handling multiple revision steps and therefor places the article in the field of iterated belief revision.
@@
 For any set of worlds $S \subseteq W$ of worlds, $Th(S)$ is the set of sentences true in all worlds in $S$.
+% TODO Th(S) not needed?
 
@@
 
-A helpful visualisation for tpos is shown in \cite{Booth2006}.
+Tpos are a common tool to handle preference orderings over propositional worlds in literature about belief change \cite{Booth2011}.
+
+A helpful visualisation for tpos is described in \cite{Booth2006}.
 It uses the fact that tpos can be represented as a linearly ordered set of ranks.
@@
 
-    To start the agent believes it is reasonable to assume the murderer acted alone (but are not ruling out both of the accused conspiring).
+    To start the agent believes it is reasonable to assume the murderer acted alone (but is not ruling out both of the accused conspiring).
 In addition it would be extremely surprising (but not impossible) if the victim was an alien.
-Tpos are a common tool to handle preference orderings like these.
 
@@
 A tpo representing the judges assumptions would be $\leq$ with $010 \sim 100 < 000 \sim 110 < 011 \sim 101 < 001 \sim 111$.
-The equivalent representation as a linearly ordered set of ranks is shown in \ref{tab:visualising-a-tpo-example}.
+The equivalent representation as a linearly ordered set of ranks is shown in table \ref{tab:visualising-a-tpo-example}.
 
@@
 Belief sets can be extracted from epistemic states (the belief set extracted from an epistemic state $\mathbb{E}$ is denoted as $B(\mathbb{E})$).
-Darwiche and Pearl show that their version of revision of epistemic states can be modelled with a tpo $\leq_{\mathbb{E}}$ associated with $\mathbb{E}$.
+Darwiche and Pearl show that their version of revision of epistemic states can be modelled with a tpo $\leq_{\mathbb{E}}$, associated with $\mathbb{E}$.
 Extraction of $B(\mathbb{E})$ is done by considering the lowest ranked worlds (i.e.
@@
 
-To guarantee the ability to extract unique belief sets from epistemic states after a revision by $\alpha$ the Booth and Meyer \cite{Booth2011} modify these postulates by requiring consistent epistemic inputs.
+To guarantee the ability to extract unique belief sets from epistemic states after a revision by $\alpha$, Booth and Meyer \cite{Booth2011} modify these postulates by requiring consistent epistemic inputs.
 That requirement means dropping \ref{E6} and considering only \ref{E1}-\ref{E5} and \ref{E7}-\ref{E8} as DP-AGM.
@@
 While DP-AGM define the most plausible worlds after a revision by $\alpha$ (as $min(\alpha, \leq_{\mathbb{E}})$), Darwiche and Pearl also define postulates that restrict the rest of the new ordering.
-Because the focus of this report is on the revision of tpos the semantic (i.e.
+Because the focus of this report is on the revision of tpos, the semantic (i.e.
 in terms of how the ordering of worlds undergoes change) versions are shown here, for more details and sentential versions refer to \cite{Darwiche1997}.
@@
 
-\ref{CR1} and \ref{CR2} mean that the relative ordering of worlds following a revision by $\alpha$ stays the same if the worlds are either both $\alpha$ or $\neg\alpha$ worlds.
+\ref{CR1} and \ref{CR2} mean that the relative ordering of worlds following a revision by $\alpha$ stays the same, if the worlds are either both $\alpha$ or $\neg\alpha$ worlds.
 \ref{CR3} and \ref{CR4} require that $\alpha$-worlds that are strictly/weakly more plausible than $\neg\alpha$-worlds are still strictly/weakly more plausible than them after a $\alpha$-revision.
@@
 The goal of the paper is the discussion of functions $\ast$ that return a new ordering $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
-Functions $\ast$ that can be used for iterated revision in that way are refered to as revision operators for $\leq$.
+These functions are referred to as revision operators for $\leq$.
 
-Booth and Meyers \cite{Booth2011} approach is to add additional metadata to every world $w \in W$.
+% TODO this describes a concrete operator, not the idea. go back to more basics, w+ as positive representation, w- as negative. 
+% TODO this also is maybe wrong? "add additional metadata to world w" is not what is happening, it is an additional structure W+-
+Booth and Meyer's \cite{Booth2011} approach is to add additional metadata to every world $w \in W$.
 This new structure is denoted as $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$.
 In this notation a world $w \in W$ is represented twice: When new evidence $\alpha$ arrives that makes $w$ more plausible (because $w \in [\alpha]$) the agent can assume it's rank as $w^{+} \in W^{\pm}$.
-In contrast if the new evidence makes $w$ less plausible ($w \notin [\alpha]$) than $w^{-} \in W^{\pm}$ is $w$'s rank.
+In contrast if the new evidence makes $w$ less plausible ($w \notin [\alpha]$) then $w^{-} \in W^{\pm}$ is $w$'s rank.
 In their paper Booth and Meyer call the pair $(w^{+}, w^{-})$ the positive/negative representation of the world $w$.
-It represents an abstract interval representing metadata about plausibility assumptions about $w$.
+They are an abstract interval, representing metadata about plausibility assumptions about $w$.
 
 \subsection{$\leq$-faithful tpos}
-For the ordering on $W^{\pm}$ Booth and Meyer suppose an additional relation $\preceq$ over $W^{\pm}$ that is added to the epistemic state of an agent.
+For the ordering on $W^{\pm}$ Booth and Meyer suppose an additional relation denoted $\preceq$ over $W^{\pm}$ that is added to the epistemic state of an agent.
 
@@
     \label{example:example-stick}
-    Recall that tpos can be equivalently thought of as a linearly ordere set of ranks (Example \ref{example:example-introduction}, page \pageref{example:example-introduction}) and therefor a tpo over $W$ can be visualised by ordering every $w \in W$ in a table of ranks (Table \ref{tab:visualising-a-tpo-example}, page \pageref{tab:visualising-a-tpo-example}).
-To visualise the interval ordering introduced by $\preceq$ Booth and Meyer use a "stick" with the endpoints defined as $w^{+}$/$w^{-}$ respectively, first introduced in \cite{Booth2007} and shown in Figure \ref{fig:example-visualisation-scatterplot}.
+    Recall that tpos can be equivalently thought of as a linearly ordered set of ranks (Example \ref{example:example-introduction}, page \pageref{example:example-introduction}) and therefor a tpo over $W$ can be visualised by ordering every $w \in W$ in a table of ranks (Table \ref{tab:visualising-a-tpo-example}, page \pageref{tab:visualising-a-tpo-example}).
+To visualise the interval ordering introduced by $\preceq$, Booth and Meyer use a "stick" with the endpoints defined as $w^{+}$/$w^{-}$ respectively.
+This method was first introduced in \cite{Booth2007} and is shown in Figure \ref{fig:example-visualisation-scatterplot}.
 
@@
 
-    In this visualisation the worlds on lower ranks (more on the left) are preferred and therefor assumed to be more plausible.
+   The worlds on lower ranks (more on the left) are preferred and therefor assumed to be more plausible.
 Here for example $x_{1}^{+} \prec x_{3}^{+}$ and $x_{1}^{-} \sim x_{4}^{+}$ Note that while all sticks have the same length in this example that is not required.
@@
 
-To define the relations between $\preceq$ and $\leq$ Booth and Meyer define a list of conditions.
+To characterise the relations between $\preceq$ and $\leq$ Booth and Meyer define a list of conditions.
 
@@
 The choice between positive or negative representations of two worlds should be the same as under $\leq$ (due to \ref{PREQ2}, \ref{PREQ3}).
-According to \ref{PREQ4} there has to be a difference between two ranks of a positive representation and a negative representation of the same world and given the choice between both the positive representation has to be chosen.
+According to \ref{PREQ4} there has to be a difference between two ranks of a positive representation and a negative representation of the same world.
+Given the choice between both, the positive representation has to be chosen.
 
@@
 
-    As demonstrated here while the "sticks" do not need to be the same size (just exist due to \ref{PREQ4}) they need to be the same size for worlds that share a rank for their corresponding representations and can not "cover" other sticks completely to continue to satisfy \ref{PREQ2} and \ref{PREQ3}.
+    As demonstrated here while the "sticks" do not need to be the same size (they just must exist due to \ref{PREQ4}), they need to be the same size for worlds that share a rank for their corresponding representations.
+They can not "cover" other sticks completely to continue to satisfy \ref{PREQ2} and \ref{PREQ3}.
 \end{example}
@@
 Intuitively new evidence $\alpha$ makes worlds that satisfy $\alpha$ more plausible and worlds that do not satisfy $\alpha$ less plausible.
-Therefor the agent associates worlds $w \in [\alpha]$ with their positive representation $w^{+}$ and worlds $w \in [\neg\alpha]$ with their negative representation $w^{-}$.
+Therefor the agent associates worlds $x \in [\alpha]$ with their positive representation $x^{+}$ and worlds $x \in [\neg\alpha]$ with their negative representation $x^{-}$.
 
@@
 
-    The updated tpo $\leq_{\alpha}^{\ast}$ can now be inferred from the figure as the ordering of the filled dots representing the new assignment for the respective world: $x_{1} \sim x_{2} \sim x_{4} < x_{3}$.
+    The updated tpo $\leq_{\alpha}^{\ast}$ can now be inferred from the figure.
+It is the ordering of the filled dots, representing the new assignment for the respective world: $x_{1} \sim x_{2} \sim x_{4} < x_{3}$.
 \end{example}
@@
 Belief revision with the AGM postulates \cite{Alchourron1985} or the reformulation by Darwiche and Pearl \cite{Darwiche1997} always includes the new information $\alpha$ in the belief set after revision.
-This feature is explicit in \ref{E2} of DP-AGM from chapter \ref{chapter:dp-agm-postulates} (page \pageref{chapter:dp-agm-postulates}) given as $\alpha \in B(\mathbb{E}\ast\alpha)$.
+This feature is explicit in \ref{E2} of DP-AGM from chapter \ref{chapter:dp-agm-postulates} (page \pageref{chapter:dp-agm-postulates}), given as $\alpha \in B(\mathbb{E}\ast\alpha)$.
 
-The operators characterised by Booth and Meyer do not require new evidence $\alpha$ to be part of the revised belief set which makes them part of non-prioritised revision \cite{Hansson1999}.
+The operators characterised by Booth and Meyer do not require new evidence $\alpha$ to be part of the revised belief set, which makes them part of non-prioritised revision operators \cite{Hansson1999}.
 
-An example is already given in example \ref{example:example-updated-tpo} and figure \ref{fig:example-updated-tpo}.
+A demonstration is already provided with example \ref{example:example-updated-tpo} and figure \ref{fig:example-updated-tpo}.
 The belief set extracted from the new epistemic state $\mathbb{E}$ as $[B(\mathbb{E})] = min(\top, \leq_{\alpha}^{\ast})$ includes the $[\neg\alpha]$-worlds $x_{1}$ and $x_{2}$ and therefor does not include the new evidence $\alpha$.
@@
 
-The list of properties they consider to be a complete axiomatisation of the family of operators they consider follows:
+The list of properties they consider to be a complete axiomatisation of the family of operators they describe follows:
 
@@
 \ref{AST1} and \ref{AST2} are considered basic properties: A revision of a tpo $\leq$ over $W$ must generate another tpo over $W$ .
-In addition the operator must return the same revised tpo for semantically equivalent sentences, the so called syntax-irrelevance property.
+In addition the operator must return an equal revised tpo for semantically equivalent sentences, the so called syntax-irrelevance property.
 
@@
 Booth and Meyer themselves consider them characteristic for admissible revision operators \cite{Booth2006a}.
-If revising a tpo by a sentence $\alpha$, the relative ordering of worlds that are either both $[\alpha]$- or $[\neg\alpha]$-worlds must stay the same (\ref{AST3}/\ref{AST4}).
+If revising a tpo by a sentence $\alpha$, the relative ordering of worlds, that are either both $[\alpha]$- or $[\neg\alpha]$-worlds, must stay the same (\ref{AST3}/\ref{AST4}).
 These properties were already part of the semantic postulates \ref{CR1} and \ref{CR2} by Darwiche and Pearl \cite{Darwiche1997} discussed in chapter \ref{chapter:dp-agm-postulates} (page \pageref{chapter:dp-agm-postulates}).
+% TODO this formulation is a disaster
 In a similar way \ref{AST5} is a stronger requirement than the other two Darwiche and Pearl postulates \ref{CR3} and \ref{CR4}.
-It means the following: A world $x$ that is considered at least as plausible as a world $y$ before a revision by new information $\alpha$.
+It means the following: A world $x$ that is considered at least as plausible as a world $y$, before a revision by new information $\alpha$.
 If $\alpha$ makes $x$ more plausible ($x \in [\alpha]$) and $y$ less plausible ($y \in [\neg\alpha]$) then after revision $x$ should be considered strictly more plausible than $y$.
@@
 % TODO: pull these out? Basic postulates for tpo revision in one subsection, additional ones "supplementary rationality properties" as second section?
-These properties define tpo-revision with one input sentence which make Booth and Meyer relate them to the AGM postulates for belief set revison \cite{Alchourron1985} as basic postulates for tpo-revision \cite{Booth2011}.
+These properties define tpo-revision with one input sentence, which make Booth and Meyer relate them to the AGM postulates for belief set revison \cite{Alchourron1985} as basic postulates for tpo-revision \cite{Booth2011}.
 
@@
 
-With these properties for $\ast$ discussed, Booth and Meyer define the family of operators they are discussing with theorem \ref{theorem:revision-operator}.
+With these properties for $\ast$ defined, Booth and Meyer define the family of operators they are discussing with theorem \ref{theorem:revision-operator}.
 

### 2020-12-28 paper/paper.tex
feat: added tpo example of judge agent

@@
 % TODO title
-\title{A bad day of studying is better than a good day of sleeping}
+\title{Sticks and tpos might help me}
 \subtitle{Report on 'How to Revise a Total Preorder' \cite{Booth2011} for seminar 1901 - Representation and processing of uncertain knowledge with logic-based methods}
@@
 
+% TODO: do i need this?
+\newpage
+
+\begin{example}
+    \label{example:example-tpo-initial}
+    Continuing the courtroom demonstration introduced in \ref{example:example-introduction} of a judge deciding on a verdict on the suspects John and Mary.
+Figure \ref{fig:example-tpo-initial} shows a possible version of a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ from which the tpo $\leq$ from table \ref{tab:visualising-a-tpo-example} can be reconstructed.
+
+    \begin{figure}[h]
+            \centering
+            \begin{tikzpicture}[scale=1]
+                \begin{axis}[
+                        xticklabels={},
+                        yticklabels={},
+                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
+                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
+                        ytick style={draw=none},
+                        xtick style={draw=none},
+                        axis line style={draw=none}
+                ]
+                \addplot[
+                    scatter,
+                    scatter src=explicit symbolic,
+                    mark size=3,
+                    scatter/classes={
+                        empty={mark=*, fill=white},
+                        filled={mark=*, fill=black}
+                    },
+                    nodes near coords*={\Label},
+                    visualization depends on={value \thisrow{label} \as \Label}
+                ]
+                table [meta=class] {
+                        x y class label
+
+                        1 8 empty \empty
+                        3 8 empty
+
+                        1 7 empty 
+                        3 7 empty
+
+                        2 6 empty 
+                        4 6 empty
+
+                        2 5 empty 
+                        4 5 empty
+
+                        5 4 empty 
+                        7 4 empty
+
+                        5 3 empty 
+                        7 3 empty
+
+                        6 2 empty 
+                        8 2 empty
+
+                        6 1 empty 
+                        8 1 empty
+                        };
+                \end{axis}
+            \end{tikzpicture}
+            \caption{Representation of $\preceq$ over $W^{\pm}$ for example \ref{example:example-introduction}}
+            \label{fig:example-tpo-initial}
+    \end{figure}
+\end{example}
+
 \section{Booth and Meyer tpo revision operators}
@@
 Explanation of Disj1/Disj2 as properties that are easy to show in the sentinential view but not in the semantic formulation.
-%\end{itemize}
-%\textbf{Section Goal:} Definition of $\ast_{\preceq}$ as example revision operator and visualisation of it.
-Show of axiomatic definition of the family of operators in semantic and sentinential view.
-Establishing theorem 1.
 

### 2020-12-28 paper/paper.tex
feat: more examples

@@
     \label{example:example-introduction}
-    As an accompanying example consider the following situation, closely aligned to \cite{Booth2011} and \cite{Darwiche1997}:
+    As an accompanying example consider the following situation from a courtroom, closely aligned to \cite{Booth2011} and \cite{Darwiche1997}:
 
@@
         \centering
-        \begin{tikzpicture}[scale=1.2]
+        \begin{tikzpicture}[scale=1]
             \begin{axis}[
@@
 
-% TODO: do i need this?
 \newpage
@@
             \end{tikzpicture}
-            \caption{Representation of $\preceq$ over $W^{\pm}$ for example \ref{example:example-introduction}}
+            \caption{Representation of $\preceq$ over $W^{\pm}$ for the courtroom example \ref{example:example-introduction}}
             \label{fig:example-tpo-initial}
@@
 
+% TODO do we need this?
+\newpage
+
+\begin{example}
+    \label{example:example-tpo-revised}
+    A complex example is the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ (for the courtroom example \ref{example:example-introduction}) using the $\leq$-faithful tpo $\preceq$ introduced in example \ref{example:example-tpo-initial} and shown in figure \ref{fig:example-tpo-revised}.
+In this case the new evidence received pointed to John being the murderer so $\alpha = p$.
+
+    \begin{figure}[h]
+            \centering
+            \begin{tikzpicture}[scale=1]
+                \begin{axis}[
+                        xticklabels={},
+                        yticklabels={},
+                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
+                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
+                        ytick style={draw=none},
+                        xtick style={draw=none},
+                        axis line style={draw=none}
+                ]
+                \addplot[
+                    scatter,
+                    scatter src=explicit symbolic,
+                    mark size=3,
+                    scatter/classes={
+                        empty={mark=*, fill=white},
+                        filled={mark=*, fill=black}
+                    },
+                    nodes near coords*={\Label},
+                    visualization depends on={value \thisrow{label} \as \Label}
+                ]
+                table [meta=class] {
+                        x y class label
+
+                        1 8 empty \empty
+                        3 8 filled
+
+                        1 7 filled 
+                        3 7 empty
+
+                        2 6 empty 
+                        4 6 filled
+
+                        2 5 filled 
+                        4 5 empty
+
+                        5 4 empty 
+                        7 4 filled
+
+                        5 3 filled 
+                        7 3 empty
+
+                        6 2 empty 
+                        8 2 filled
+
+                        6 1 filled 
+                        8 1 empty
+                        };
+                \end{axis}
+            \end{tikzpicture}
+            \caption{Associating positive and negative representations of worlds for the courtroom example \ref{example:example-introduction}, after receiving evidence $\alpha=p$}
+            \label{fig:example-tpo-revised}
+    \end{figure}
+
+    For the worlds $010, 110 \in W$ in old tpo $\leq$, $010 \leq 110$ was true. To rank them with the revised tpo $\leq_{\alpha}^{\ast}$ calculate:
+
+    \begin{equation*}
+        r_{\alpha}(010) = 010^{-}, 010 \in [\neg\alpha]
+    \end{equation*}
+    \begin{equation*}
+        r_{\alpha}(110) = 110^{+}, 110 \in [\alpha]
+    \end{equation*}
+
+    and, as $r_{\alpha}(110^{+}) \prec r_{\alpha}(010^{-})$ is true, set $110 <_{\alpha}^{\ast} 010$.
+
+    Repeating for every world in $W$, the new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$.
+Unsurprisingly the belief set associated with the new epistemic state is $[B(\mathbb{E})] = min(\top, \leq_{\mathbb{E}}) = \{100\}$, "John is the murderer and the victim is not an alien".
+
+    As $\leq_{\alpha}^{\ast}$ is a representation of the conditional beliefs of the agent, it is also interesting to look at the changes for them: While the judge initially thought both suspects being the murderers ($110$) was less plausible than only Mary being the murderer ($010$), they now have updated their assumptions to think only Mary being the murderer less plausible than both conspiring.
+\end{example}
+
 \subsection{Non-prioritised revision}
@@
 
-%Although the approach described allows us to determine more than just
-%the belief set associated with an epistemic state, there is a problem with this
-%approach regarding iterated tpo-revision. While the extra structure tells us
-%how to determine a new tpo, it tells us nothing about how to determine the
-%new extra structure which is needed to guide the next revision. Clearly the
-%problem of iterated belief revision has simply re-emerged “one level up”. We
-%investigate this problem by considering some desirable properties for revising
-%the extra structure, and prove the consistency of these properties by giving a
-%concrete operator satisfying all of them.
+\begin{example}
+    \label{example:example-non-prio-revision}
+
+    Using the $\leq$-faithful tpo $\preceq$ already established for the courtroom example \ref{example:example-introduction} the revision by $\alpha = r$ ("the victim was an alien").
+is shown in figure \ref{fig:example-non-prio-revision}.
+    \begin{figure}[h]
+            \centering
+            \begin{tikzpicture}[scale=1]
+                \begin{axis}[
+                        xticklabels={},
+                        yticklabels={},
+                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
+                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
+                        ytick style={draw=none},
+                        xtick style={draw=none},
+                        axis line style={draw=none}
+                ]
+                \addplot[
+                    scatter,
+                    scatter src=explicit symbolic,
+                    mark size=3,
+                    scatter/classes={
+                        empty={mark=*, fill=white},
+                        filled={mark=*, fill=black}
+                    },
+                    nodes near coords*={\Label},
+                    visualization depends on={value \thisrow{label} \as \Label}
+                ]
+                table [meta=class] {
+                        x y class label
+
+                        1 8 empty \empty
+                        3 8 filled
+
+                        1 7 empty 
+                        3 7 filled
+
+                        2 6 empty 
+                        4 6 filled
+
+                        2 5 empty 
+                        4 5 filled
+
+                        5 4 filled 
+                        7 4 empty
+
+                        5 3 filled 
+                        7 3 empty
+
+                        6 2 filled 
+                        8 2 empty
+
+                        6 1 filled 
+                        8 1 empty
+                        };
+                \end{axis}
+            \end{tikzpicture}
+            \caption{Non-prioritised revision for $B(\mathbb{E})$}
+            \label{fig:example-non-prio-revision}
+    \end{figure}
+
+    Since the agent considered the victim being an alien very unlikely even the positive representations of worlds in $[\alpha]$ are on higher ranks (so considered less plausible) than negative representations of worlds in $[\neg\alpha]$.
+    The belief set $B(\mathbb{E})$ of the agent is unchanged even under $\leq_{\alpha}^{\ast}$, since $\{010, 100\}$ are still the most plausible worlds, and does not include $r$ "the victim is an alien".
+\end{example}
 
@@
 \subsection{Example operator}
+%Although the approach described allows us to determine more than just
+%the belief set associated with an epistemic state, there is a problem with this
+%approach regarding iterated tpo-revision. While the extra structure tells us
+%how to determine a new tpo, it tells us nothing about how to determine the
+%new extra structure which is needed to guide the next revision. Clearly the
+%problem of iterated belief revision has simply re-emerged “one level up”. We
+%investigate this problem by considering some desirable properties for revising
+%the extra structure, and prove the consistency of these properties by giving a
+%concrete operator satisfying all of them.
+
 % shortened example from paper page 232 without SPH teil, show that shortened example satisfies the properties later on.

### 2020-12-28 paper/paper.tex
feat: example for preceq revision

@@
 
+% TODO do we need this?
+\newpage
+
 \begin{example}
@@
 
+% TODO: check all \newpages if I need them or fix the figure problem
+
+% TODO do we need this?
 \newpage
@@
             \centering
-            \begin{tikzpicture}[scale=1]
+            \begin{tikzpicture}[scale=1.5]
                 \begin{axis}[
@@
 \section{Revising $\preceq$}
-% DO NOT DO THIS? OR mention that we only show a concrete operator and not discuss properties, see discussion
-\subsection{Example operator}
-%Although the approach described allows us to determine more than just
-%the belief set associated with an epistemic state, there is a problem with this
-%approach regarding iterated tpo-revision. While the extra structure tells us
-%how to determine a new tpo, it tells us nothing about how to determine the
-%new extra structure which is needed to guide the next revision. Clearly the
-%problem of iterated belief revision has simply re-emerged “one level up”. We
-%investigate this problem by considering some desirable properties for revising
-%the extra structure, and prove the consistency of these properties by giving a
-%concrete operator satisfying all of them.
 
-% shortened example from paper page 232 without SPH teil, show that shortened example satisfies the properties later on.
-USE EXAMPLE from darwiche -> here to illustrate things with guy killing an alien
-%TODO this could be OWN contribution!!?
+The operator $\ast$, based on $\preceq$, allows the revision of a tpo $\leq$ associated with an epistemic state to $\leq_{\alpha}^{\ast}$.
+To be used in iterated belief revision the newly introduced structure $\preceq$ also needs to be revised Otherwise, as Booth and Meyer put it, the problem has just "re-emerged 'one level up'" \cite{Booth2011}.
+In their paper they discuss strict preference hierarchies (or SPHs), an equivalent structure to $\preceq$ denoted as $\$$, their properties and how to revise them.
+
+This report focuses on revision of tpos itself.
+As an outlook, only the revision of a $\leq$-faithful tpo $\preceq$ using the example operator from the original paper is included.
+For a more detailed explanation of the operator, SPHs or their properties see \cite{Booth2011}.
+
+\subsection{A concrete operator}
+Booth and Meyer define their operator to revise $\preceq$ by with a function $p: W^{\pm} \mapsto \mathds{R}$ so that for all $x \in W$ the interval between it's positive and negative representation $a$ is:
+
+\begin{equation*}
+    p(x^{-}) - p(x^{+}) = a > 0
+\end{equation*}
+
+The smaller $p(x^{\epsilon})$ is, the more plausible the world is.
+The interval $(x^{+}, x^{-})$, representing a world $x \in W$ using it's representations $x^{+}, x^{-} \in W^{\pm}$, essentially becomes an interval of real numbers $(p(x^{+}), p(x^{-}))$ with length $a$.
+
+\bigskip
+
+Using $p$ a $\leq$-faithful tpo $\preceq_{p}$ satisfying \ref{PREQ1}-\ref{PREQ4} is defined by:
+
+\begin{equation*}
+    x^{\epsilon} \preceq_{p} y^{\delta} \textrm{ iff } p(x^{\epsilon}) \leq p(y^{\delta} )
+\end{equation*}
+
+\bigskip
+
+Revision of $\preceq$ becomes a two step process: First choose a function $p$ so that $\preceq_{p} = \preceq$, then revise to get a new assignment $p \ast \alpha$ that defines a new $\leq$-faithful tpo $\preceq_{p \ast \alpha}$.
+
+% TODO: probably don't need geffner ref here
+Booth and Meyer suggest an operator that keeps worlds that satisfy $\alpha$ constant and moves $\neg\alpha$-worlds "back" by $a$ (also known as L-conditionalisation in Spohn-type rankings \cite{Geffner1992}).
+They achieve this by setting $p$, for every $x^{\epsilon} \in W^{\pm}$ to:
+
+\begin{equation*}
+    (p \ast \alpha)(x^{\epsilon}) = \left\{
+                    \begin{array}{ll}
+                      p(x^{\epsilon}) \textrm{ if } x \in [\alpha]\\
+                      p(x^{\epsilon}) + a \textrm{ if } x \in [\neg\alpha]
+                    \end{array}
+                  \right.
+\end{equation*}
+
+By this definition the interval representing $\alpha$-worlds stay the same as $(p(x^{+}), p(x^{-}))$ while intervals of $\neg\alpha$-worlds become $(p(x^{-}), p(x^{-}) + a)$.
+
+% TODO put examples with alpha: r and alpha p from before here and revise them
+
+% TODO do we need this?
+\newpage
+
+\begin{example}
+    \label{example:example-preceq-revised}
+    For the courtroom example \ref{example:example-introduction} the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ for $\alpha = p$ ("John is the murderer") was already done in example \ref{example:example-tpo-revised}.
+The next step is revising $\preceq$ by $\alpha$.
+Figure \ref{fig:example-preceq-revised} shows the revised tpo $\preceq_{\alpha}$ with $\neg\alpha$-worlds moved back by $a$.
+
+    \begin{figure}[h]
+            \centering
+            \begin{tikzpicture}[scale=1.5]
+                \begin{axis}[
+                        xticklabels={},
+                        yticklabels={},
+                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
+                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
+                        ytick style={draw=none},
+                        xtick style={draw=none},
+                        axis line style={draw=none}
+                ]
+                \addplot[
+                    scatter,
+                    scatter src=explicit symbolic,
+                    mark size=3,
+                    scatter/classes={
+                        empty={mark=*, fill=white},
+                        old={mark=x, fill=white}
+                    },
+                    nodes near coords*={\Label},
+                    visualization depends on={value \thisrow{label} \as \Label}
+                ]
+                table [meta=class] {
+                        x y class label
+
+                        1 8 old \empty
+
+                        3 8 empty
+                        5 8 empty
+
+                        1 7 empty 
+                        3 7 empty
+
+                        2 6 old
+
+                        4 6 empty
+                        6 6 empty
+
+                        2 5 empty 
+                        4 5 empty
+
+                        5 4 old
+
+                        7 4 empty
+                        9 4 empty
+
+                        5 3 empty 
+                        7 3 empty
+
+                        6 2 old
+
+                        8 2 empty
+                        10 2 empty
+
+                        6 1 empty 
+                        8 1 empty
+                        };
+                \end{axis}
+            \end{tikzpicture}
+            \caption{$\preceq_{p \ast \alpha}$ for $\alpha = p$}
+            \label{fig:example-preceq-revised}
+    \end{figure}
+
+    For the first step a function $p$ is chosen so that $\preceq_{p} = \preceq$ and the intervals for all worlds $x \in W^{\pm}$ can be defined using $p$.
+
+    For example the interval representing world $010$ is $(010^{+}, 010^{-})$ and becomes $(p(010^{+}), p(010^{-})) = (0, a)$.
+Initially the world $100$ is represented by the same interval $(100^{+}, 100^{-})$ that becomes $(p(100^{+}), p(100^{-})) = (0, a)$.
+
+    \bigskip
+
+    In the second step $p$ is revised by $\alpha$ to $p \ast \alpha$ as defined above. The $\neg\alpha$-world $010$ is moved back by $a$ while the $\alpha$-world $100$ is unchanged:
+
+    \begin{equation*}
+        010 \in [\neg\alpha] \textrm{ : } (p(010^{-}), p(010^{-}) + a) = (a, 2a)
+    \end{equation*}
+
+    \begin{equation*}
+        100 \in [\alpha] \textrm{ : } (p(100^{+}), p(100^{-})) = (0, a)
+    \end{equation*}
+\end{example}
 
@@
 % TODO: discuss 6/7 being wrong? strength of evidence?=!=!, discuss 5 with it being equal when sticks - and + are same rank?! 
-\subsection{Iterating on the iterator}
-The revision operator $\ast$ based on $\preceq$ allows the revision of a tpo $\leq$ associated with an epistemic state to $\leq_{\alpha}^{\ast}$.
-To be useful in iterated belief revision the newly introduced structure $\preceq$ also needs to be revised, as Booth and Meyer put it the problem has "re-emerged 'one level up'" \cite{Booth2011}.
-In their paper Booth and Meyer discuss strict preference hierarchies (or SPHs), an equivalent structure to $\preceq$ denoted as $\$$, their properties and how to revise them.
-For more information on SPH revision see \cite{Booth2011}.
-
 \newpage

### 2020-12-29 paper/paper.tex
fix: smaller bugfixes in example and writing cleanup

@@
     \begin{equation*}
-        r_{\alpha}(010) = 010^{-}, 010 \in [\neg\alpha]
+        010 \in [\neg\alpha] \textrm{ : } r_{\alpha}(010) = 010^{-}
     \end{equation*}
     \begin{equation*}
-        r_{\alpha}(110) = 110^{+}, 110 \in [\alpha]
+        110 \in [\alpha] \textrm{ : } r_{\alpha}(110) = 110^{+}
     \end{equation*}
 
-    and, as $r_{\alpha}(110^{+}) \prec r_{\alpha}(010^{-})$ is true, set $110 <_{\alpha}^{\ast} 010$.
+    and, as $110^{+} \prec 010^{-}$ is true, set $110 <_{\alpha}^{\ast} 010$.
 
@@
 To be used in iterated belief revision the newly introduced structure $\preceq$ also needs to be revised Otherwise, as Booth and Meyer put it, the problem has just "re-emerged 'one level up'" \cite{Booth2011}.
-In their paper they discuss strict preference hierarchies (or SPHs), an equivalent structure to $\preceq$ denoted as $\$$, their properties and how to revise them.
+In their paper they discuss strict preference hierarchies (or SPHs), an equivalent structure to $\preceq$, denoted as $\$$, their properties and how to revise them.
 
 This report focuses on revision of tpos itself.
-As an outlook, only the revision of a $\leq$-faithful tpo $\preceq$ using the example operator from the original paper is included.
+As an outlook, only the revision of a $\leq$-faithful tpo $\preceq$ using the example operator from the original paper is included here.
 For a more detailed explanation of the operator, SPHs or their properties see \cite{Booth2011}.
@@
 \subsection{A concrete operator}
-Booth and Meyer define their operator to revise $\preceq$ by with a function $p: W^{\pm} \mapsto \mathds{R}$ so that for all $x \in W$ the interval between it's positive and negative representation $a$ is:
+Booth and Meyer define their operator to revise $\preceq$ with a function $p: W^{\pm} \mapsto \mathds{R}$ so that for all $x \in W$ the interval between it's positive and negative representation is a real number $a$:
 
@@
 
-Using $p$ a $\leq$-faithful tpo $\preceq_{p}$ satisfying \ref{PREQ1}-\ref{PREQ4} is defined by:
+Using $p$, a $\leq$-faithful tpo $\preceq_{p}$ satisfying \ref{PREQ1}-\ref{PREQ4} can be defined as:
 
@@
 
-Revision of $\preceq$ becomes a two step process: First choose a function $p$ so that $\preceq_{p} = \preceq$, then revise to get a new assignment $p \ast \alpha$ that defines a new $\leq$-faithful tpo $\preceq_{p \ast \alpha}$.
+Revision of $\preceq$ becomes a two step process: First choose a function $p$ so that $\preceq_{p} = \preceq$, then revise $p$ to get a new assignment $p \ast \alpha$ that defines a new $\leq$-faithful tpo $\preceq_{p \ast \alpha}$.
 
@@
 Booth and Meyer suggest an operator that keeps worlds that satisfy $\alpha$ constant and moves $\neg\alpha$-worlds "back" by $a$ (also known as L-conditionalisation in Spohn-type rankings \cite{Geffner1992}).
+They also mention other operators are possible and an area of further research.
 They achieve this by setting $p$, for every $x^{\epsilon} \in W^{\pm}$ to:

### 2020-12-29 paper/paper.tex
feat: final (?) example

@@
 
-% TODO title
-\title{Sticks and tpos might help me}
+% TODO title, "Of judges, aliens and tpos"?
+\title{Total preorder in the courtroomg}
 \subtitle{Report on 'How to Revise a Total Preorder' \cite{Booth2011} for seminar 1901 - Representation and processing of uncertain knowledge with logic-based methods}
@@
 \subsection{Non-prioritised revision}
+\label{section:non-prioritised-revision}
 
@@
 
+\begin{example}
+    \label{example:example-preceq-revised-alien}
+    For an example that demonstrates the impact the revision of $\preceq$ has on the acceptance of conditional beliefs of an agent consider again the courtroom example \ref{example:example-introduction}.
+The fact that the victim might is an alien ($r$ true) seems very unlikely, which is modelled by the gap between $[r]$-worlds and $[\neg r]$-worlds.
+
+    When evidence $\alpha = r$ arrives there seems to be little change in the epistemic state of the judge: $\leq_{\alpha}^{\ast}$ is unchanged as even considering the negative representations of $[\neg r]$-worlds they rank lower than $[r]$-worlds.
+An unchanged tpo $\leq_{\alpha}^{\ast}$ also means the believe set $B(\mathbb{E})$ stays the same and does not include $r$ (a property of non-prioritised revision as described in section \ref{section:non-prioritised-revision}).
+
+    What did change is the willingness of the agent to accept conditional beliefs about $r$ being true in light of future evidence.
+This is reflected by the revised structure $\preceq_{p \ast \alpha}$ shown in figure \ref{fig:example-preceq-revised-alien}.
+
+    \begin{figure}[h]
+            \centering
+            \begin{tikzpicture}[scale=1.5]
+                \begin{axis}[
+                        xticklabels={},
+                        yticklabels={},
+                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
+                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
+                        ytick style={draw=none},
+                        xtick style={draw=none},
+                        axis line style={draw=none}
+                ]
+                \addplot[
+                    scatter,
+                    scatter src=explicit symbolic,
+                    mark size=3,
+                    scatter/classes={
+                        empty={mark=*, fill=white},
+                        old={mark=x, fill=white}
+                    },
+                    nodes near coords*={\Label},
+                    visualization depends on={value \thisrow{label} \as \Label}
+                ]
+                table [meta=class] {
+                        x y class label
+
+                        1 8 old \empty
+
+                        3 8 empty
+                        5 8 empty
+
+                        1 7 old
+
+                        3 7 empty 
+                        5 7 empty
+
+                        2 6 old
+
+                        4 6 empty
+                        6 6 empty
+
+                        2 5 old
+
+                        4 5 empty 
+                        6 5 empty
+
+                        5 4 empty
+                        7 4 empty
+
+                        5 3 empty 
+                        7 3 empty
+
+                        6 2 empty
+                        8 2 empty
+
+                        6 1 empty 
+                        8 1 empty
+                        };
+                \end{axis}
+            \end{tikzpicture}
+            \caption{$\preceq_{p \ast \alpha}$ for $\alpha = r$}
+            \label{fig:example-preceq-revised-alien}
+    \end{figure}
+
+    % TODO tpo alpha as beta is unlucky because ast has a different meaning already, also change in figure 8 caption
+    Notice how now the gap between $[\neg r]$- and $[r]$-worlds has closed.
+After revising $\preceq_{p \ast \alpha}$ for a second piece of evidence $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$ ("the murderer was either John or Mary, not both") the new tpo $\leq_{\alpha \ast \beta}^{\ast}$ can be read from the filled dots in figure \ref{fig:example-preceq-revised-alien2}.
+
+    \begin{figure}[h]
+            \centering
+            \begin{tikzpicture}[scale=1.5]
+                \begin{axis}[
+                        xticklabels={},
+                        yticklabels={},
+                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
+                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
+                        ytick style={draw=none},
+                        xtick style={draw=none},
+                        axis line style={draw=none}
+                ]
+                \addplot[
+                    scatter,
+                    scatter src=explicit symbolic,
+                    mark size=3,
+                    scatter/classes={
+                        empty={mark=*, fill=white},
+                        filled={mark=*, fill=black},
+                        old={mark=x, fill=white}
+                    },
+                    nodes near coords*={\Label},
+                    visualization depends on={value \thisrow{label} \as \Label}
+                ]
+                table [meta=class] {
+                        x y class label
+
+                        1 8 old \empty
+
+                        3 8 filled
+                        5 8 empty
+
+                        1 7 old
+
+                        3 7 filled 
+                        5 7 empty
+
+                        2 6 old
+
+                        4 6 empty
+                        6 6 filled
+
+                        2 5 old
+
+                        4 5 empty 
+                        6 5 filled
+
+                        5 4 filled
+                        7 4 empty
+
+                        5 3 filled 
+                        7 3 empty
+
+                        6 2 empty
+                        8 2 filled
+
+                        6 1 empty 
+                        8 1 filled
+                        };
+                \end{axis}
+            \end{tikzpicture}
+            \caption{$\preceq_{p \ast \alpha \ast \beta}$ for $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$}
+            \label{fig:example-preceq-revised-alien2}
+    \end{figure}
+
+For the initial tpo $\leq$ there was no possible evidence that would change the plausibility ordering between worlds where the victim is an alien and worlds where it is not.
+That was reflected by the new tpo $\leq_{\alpha}^{\ast}$ that even with direct evidence for alien life did not change the judges plausibility orderings.
+But because of the revision of $\preceq$ to $\preceq_{p \ast \alpha}$ the evidence changed the acceptance of the judge to belief we are not alone in the universe.
+After receiving $\beta$ the judge even considers the $[r]$-worlds $\{011, 101\}$ more likely than the $[\neg r]$-worlds $\{000, 110\}$!
+
+(Luckily due to the existence of $[\beta]$-worlds $\{010, 100\}$ the belief set of the judge still does not include $r$ and rationality prevails.)
+\end{example}
+
 % TODO write Discussion
@@
 % TODO *6,*7 seem weird, no different "strength" of evidence?
+maybe revising multiple time by the same evidence should that be?
+otherwise revising multiple times by same evidence is also weird because it changes things and is not idempotent
 % TODO: discuss 6/7 being wrong? strength of evidence?=!=!, discuss 5 with it being equal when sticks - and + are same rank?! 

### 2020-12-29 paper/paper.tex
feat: reworked titles

@@
 
-\section{Booth and Meyer tpo revision operators}
+\section{Booth and Meyer tpo-revision operators}
 Booth and Meyer \cite{Booth2011} aim to discuss tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
-To do so they define how to use the additional information from a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ to create a revision operator $\ast_{\preceq}$.
+To do so they define how to use the additional information from a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ to create a revision operator $\ast_{\preceq}$ (from now on referred to as BM tpo-revision operators).
 
@@
 % TODO write Properties of Booth and Meyer tpo-revision operators
-\section{Properties of Booth and Meyer tpo-revision operators}
+\section{Properties of BM tpo-revision operators}
 While not determining a concrete operator $\ast_{\preceq}$ to revise a tpo $\leq$, definition \ref{definition:revision-operator} allows Booth and Meyer to discuss what properties any operator in that family must have \cite{Booth2011}.
@@
 
-% TODO write Sentinential view
-\subsection{Sentinential view}
+% TODO write Sentinential view, should we include this?
+%\subsection{Sentinential view}
 % booth: "on a semantic level, i.e., in terms of how the ordering of individual worlds x, y undergo change"
@@
 
-\section{Revising $\preceq$}
+\section{Iterating: $\preceq$-revision}
 

### 2020-12-29 paper/paper.tex
fix: minor text fixes

@@
 While the AGM postulates define restrictions on revising propositional beliefs (a core one being the principle of minimal change), they place little restrictions on preserving conditional beliefs.
-In their paper Darwiche and Pearl use epistemic states, abstract entities that contain all information an agent needs for it's reasoning, especially their strategy for belief revision.
+In their paper Darwiche and Pearl use epistemic states, abstract entities that contain all information an agent needs for their reasoning, especially their strategy for belief revision.
 As conditional beliefs are represented by these strategies, it is necessary to define how to modify the strategy itself when encountering multiple new information \cite{Darwiche1997}.
@@
 
-For the initial tpo $\leq$ there was no possible evidence that would change the plausibility ordering between worlds where the victim is an alien and worlds where it is not.
+For the initial tpo $\leq$ there was no possible evidence that would change the plausibility ordering between worlds where the victim is an alien and worlds where they are not.
 That was reflected by the new tpo $\leq_{\alpha}^{\ast}$ that even with direct evidence for alien life did not change the judges plausibility orderings.

### 2020-12-29 paper/paper.tex
feat: abstract

@@
 
-% TODO title, "Of judges, aliens and tpos"?
-\title{Total preorder in the courtroomg}
-\subtitle{Report on 'How to Revise a Total Preorder' \cite{Booth2011} for seminar 1901 - Representation and processing of uncertain knowledge with logic-based methods}
+% TODO title, "Total preorder in the courtroom"?
+\title{Of judges, aliens and tpos}
+\subtitle{Report on 'How to Revise a Total Preorder' \cite{Booth2011} for seminar 1901 - 'Representation and processing of uncertain knowledge with logic-based methods'}
 \author{
@@
 % TODO abstract
-\abstract{Abstract goes here}
+\abstract{Total preorders are a common tool to model plausibility orderings over worlds for agents in the research field of belief change.
+In their paper 'How to Revise a Total Preorder', Booth and Meyer present an approach to revising preorders for iterated belief revision based on assigning abstract intervals of plausibility under new evidence to worlds.
+
+This report presents part of their work in tpo-revision operators and their properties with the help of an accompanying example and additional visualisation.}
 

### 2020-12-30 paper/paper.tex
feat: introduction

@@
 
-% TODO introduction
 \section{Introduction}
 
-% goal of paper: interested in function * for getting new tpo
-
-% roten faden des reports beschreiben
+In the field of belief change total preorders (or tpos) are a common tool to model an agent's conditional beliefs.
+To support iterated belief revision it is necessary to research how these structures can be changed to adapt to an agent's changing world view.
+Booth and Meyer suggest an approach based on the idea of assigning an interval of additional metadata to the ordered, propositional worlds and iterate the tpo of an agent using that structure.
+They define and discuss properties of operators for tpo-revision and relate their approach to other fields of research.
+This report on their paper aims to present parts of their work to a wider audience with the addition of an accompanying example.
+The report's focus will be on the tpo-revision operators discussed in the paper and explicitly avoid the addition of strict preference hierarchies and relations to other research areas.
+The structure of the report will be as follows: First it will establish the context of the paper by presenting the research area of iterated belief revision and how it relates to other areas of artificial intelligence and philosophy.
+To establish a shared understanding of notation and definitions section \ref{section:formal-background} will discuss formal background and other, previous approaches to belief change.
+It will also introduce the main contribution of this report in an accompanying example demonstrating tpo-revision as described by Booth and Meyer.
+After establishing a foundation, section \ref{section:booth-and-meyer-tpo-revision-operators} and \ref{section:properties-of-bm-tpo-revision-operators} present part of the work from the original paper 'How to Revise a Total Preorder' \cite{Booth2011}.
+Section \ref{section:booth-and-meyer-tpo-revision-operators} establishes and defines functions $\ast$, used to revise tpos, a core contribution of Booth and Meyer.
+In section \ref{section:properties-of-bm-tpo-revision-operators} properties of these functions will be presented.
+To provide an outlook for the additional work done by Booth and Meyer, \ref{section:iterating-preceq-revision} shows their suggestion for a concrete operator for tpo-revision and includes several examples and novel visualisations of it being applied in the context of the accompanying example.
+Finally section \ref{section:discussion} closes the report with a summary and commentary on Booth and Meyer's approach to iterated belief revision with interval orderings.
 
@@
 \section{Formal background}
+\label{section:formal-background}
 
@@
 \section{Additional metadata for tpo revision}
+\label{section:additional-metadata-for-tpo-revision}
 \subsection{Enriching epistemic states}
@@
 \section{Booth and Meyer tpo-revision operators}
+\label{section:booth-and-meyer-tpo-revision-operators}
 Booth and Meyer \cite{Booth2011} aim to discuss tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
@@
 \section{Properties of BM tpo-revision operators}
+\label{section:properties-of-bm-tpo-revision-operators}
 While not determining a concrete operator $\ast_{\preceq}$ to revise a tpo $\leq$, definition \ref{definition:revision-operator} allows Booth and Meyer to discuss what properties any operator in that family must have \cite{Booth2011}.
@@
 \section{Iterating: $\preceq$-revision}
-
+\label{section:iterating-preceq-revision}
 The operator $\ast$, based on $\preceq$, allows the revision of a tpo $\leq$ associated with an epistemic state to $\leq_{\alpha}^{\ast}$.
@@
 By this definition the interval representing $\alpha$-worlds stay the same as $(p(x^{+}), p(x^{-}))$ while intervals of $\neg\alpha$-worlds become $(p(x^{-}), p(x^{-}) + a)$.
-
-% TODO put examples with alpha: r and alpha p from before here and revise them
-
-% TODO do we need this?
-\newpage
 
@@
 
+% TODO need this?
+\newpage
+
 \begin{example}
@@
 \section{Discussion}
+\label{section:discussion}
 % TODO *6,*7 seem weird, no different "strength" of evidence?

### 2020-12-30 paper/paper.tex
fix: fixed figures floating on random pages
feat: conclusion

@@
 \usepackage[onehalfspacing]{setspace}
+\usepackage{float}
 
@@
 
-% TODO abstract
 \abstract{Total preorders are a common tool to model plausibility orderings over worlds for agents in the research field of belief change.
@@
 In section \ref{section:properties-of-bm-tpo-revision-operators} properties of these functions will be presented.
-To provide an outlook for the additional work done by Booth and Meyer, \ref{section:iterating-preceq-revision} shows their suggestion for a concrete operator for tpo-revision and includes several examples and novel visualisations of it being applied in the context of the accompanying example.
-Finally section \ref{section:discussion} closes the report with a summary and commentary on Booth and Meyer's approach to iterated belief revision with interval orderings.
+To provide an outlook for the additional work done by Booth and Meyer, \ref{section:iterating-preceq-revision} shows their suggestion for a concrete operator for tpo-revision and includes several examples and adapted visualisations of it being applied in the context of the accompanying example.
+Finally section \ref{section:conclusion} closes the report with a summary and commentary on Booth and Meyer's approach to iterated belief revision with interval orderings.
 
@@
 Being able to derive a new tpo from additional evidence is an approach to handling multiple revision steps and therefor places the article in the field of iterated belief revision.
-%1.2 Ich sehe hier die Gefahr, dass das zu Ausführlich wird.
-%Keine große Diskussion von AGM, Darwiche and Pearl und so weiter.
-%Keine Beziehung zur Allen und co herstellen ;)
-%Kurz und Prägnant präsentieren, was benötgigt wird um zu Verstehen was
-%in dem Primärartikel neu ist.
 
@@
 
-    \begin{table}[h]
+    \begin{table}[H]
          \centering
@@
 
-    \begin{figure}[h]
+    \begin{figure}[H]
         \centering
-        \begin{tikzpicture}[scale=1]
+        \begin{tikzpicture}[scale=1.5]
             \begin{axis}[
@@
 
-% TODO do we need this?
-\newpage
-
 \begin{example}
@@
 
-% TODO: check all \newpages if I need them or fix the figure problem
-
-% TODO do we need this?
-\newpage
-
 \begin{example}
@@
 
-    \begin{figure}[h]
+    \begin{figure}[H]
             \centering
@@
 is shown in figure \ref{fig:example-non-prio-revision}.
-    \begin{figure}[h]
+    \begin{figure}[H]
             \centering
@@
 
-% TODO write Properties of Booth and Meyer tpo-revision operators
 \section{Properties of BM tpo-revision operators}
@@
 
-With these properties for $\ast$ defined, Booth and Meyer define the family of operators they are discussing with theorem \ref{theorem:revision-operator}.
-
-% THEOREM 1 as axiomatisation of the family of revision operators considered in the paper. "It turns out that these properties provide an exact characterisation of the
-% revision operators we consider."
+With these properties for $\ast$ discussed, Booth and Meyer define the family of operators they are discussing with theorem \ref{theorem:revision-operator}.
 
@@
 
-% TODO need this?
-\newpage
-
 \begin{example}
@@
 That was reflected by the new tpo $\leq_{\alpha}^{\ast}$ that even with direct evidence for alien life did not change the judges plausibility orderings.
-But because of the revision of $\preceq$ to $\preceq_{p \ast \alpha}$ the evidence changed the acceptance of the judge to belief we are not alone in the universe.
+But because of the revision of $\preceq$ to $\preceq_{p \ast \alpha}$, the evidence $\alpha$ changed the acceptance of the judge to belief we are not alone in the universe.
 After receiving $\beta$ the judge even considers the $[r]$-worlds $\{011, 101\}$ more likely than the $[\neg r]$-worlds $\{000, 110\}$!
@@
 
-% TODO write Discussion
-\section{Discussion}
-\label{section:discussion}
+% TODO write Conclusion
+\section{Conclusion}
+\label{section:conclusion}
+The featured paper 'How to Revise a Total Preorder' by Booth and Meyer \cite{Booth2011} is an expansive work on using interval orderings for belief change.
+This report focused on presenting the research context and previous work in iterated belief change as well as the concrete tpo-revision based on the additional structure of $\leq$-faithful tpos.
+A consistent example based on a trial situation (adapted from \cite{Darwiche1997} and \cite{Booth2011}) was used to accompany the discussion of the paper.
+In addition to the provided example the report also introduced an adapted visualisation for $\leq$-faithful tpo-revision based on the stick visualisation used by Booth and Meyer themselves.
+
+To make the presented content easier to follow some parts of the original paper had to be excluded.
+Booth and Meyer discuss multiple additional properties of their proposed operators as well as extreme examples.
+They also provide a different way to express the $\preceq$-structure using strict preference hierarchies and discuss how they relate to other research areas.
+For those topics as well as detailed proofs it is highly advised to read the primary paper \cite{Booth2011} itself.
+
+The idea to define an interval of plausibility for worlds depending on if evidence supports them or not does make intuitive sense.
+An angle largely missing from the paper is the discussion of the different impact and quality of new information itself.
+
+% idempotent correct?
+The proposed concrete operator for the revision of $\leq$-faithful tpos allows for multiple revisions by the same evidence $\alpha$ or semantically equivalent evidence $\beta \equiv \alpha$, consistently lowering the acceptance of $[\neg\alpha]$-worlds without presenting new evidence.
+It seems like an interesting question to ask if tpo-revision for iterated belief change should be idempotent in regards to already applied evidence.
+
+Considering quality and impact of new evidence also creates the question if \ref{AST6} and \ref{AST7} (properties of BM tpo-revision operators, page \ref{section:properties-of-bm-tpo-revision-operators}) should be weakened.
+Especially high quality evidence for a very unlikely type of world might change an agents plausibility ordering where low quality evidence that is very expected might not.
+Consider the following situation in our courtroom example \ref{example:example-introduction}: New evidence $\alpha$ arrives that fingerprints of John have been found at the place of the murder, pointing to a world $x$ with $p$ being true.
+But, because of a large body of evidence, the judge still considers a world $y$ where Mary is the murderer to be more plausible.
+This means there can be no evidence $\gamma$ that would make the agent consider the world $x$ more likely than $y$ according to \ref{AST7}:
+
+\begin{equation*}
+    \textrm{If } x \in [\alpha], y \in [\neg\alpha] \textrm{ and } y <_{\alpha}^{\ast} x \textrm{ then } y <_{\gamma}^{\ast} x
+\end{equation*}
+
+But what if evidence is submitted that if Mary is the murderer, the victim must be an alien $\gamma = q \implies r$?
+Semantically a human agent would assume all worlds in which Mary is the murderer to be highly unlikely due to how far fetched the acceptance of the victim being an alien is.
+How to solve this apparent contradiction by modelling different types and strengths of evidence could be a future area of research.
+
 % TODO *6,*7 seem weird, no different "strength" of evidence?
 maybe revising multiple time by the same evidence should that be?
-otherwise revising multiple times by same evidence is also weird because it changes things and is not idempotent
-% TODO: discuss 6/7 being wrong? strength of evidence?=!=!, discuss 5 with it being equal when sticks - and + are same rank?! 
+otherwise revising multiple times by same evidence is also weird because it changes things and is not idempotent, discuss 5 with it being equal when sticks - and + are same rank?!
 \newpage

### 2020-12-31 paper/paper.tex
feat: writing style, commas

@@
 % TODO title, "Total preorder in the courtroom"?
+% TODO: '' for quotes should be ""? Or consistent at least
+% TODO: references align: Richard Booth, sometimes R Booth
 \title{Of judges, aliens and tpos}
@@
 
-\abstract{Total preorders are a common tool to model plausibility orderings over worlds for agents in the research field of belief change.
-In their paper 'How to Revise a Total Preorder', Booth and Meyer present an approach to revising preorders for iterated belief revision based on assigning abstract intervals of plausibility under new evidence to worlds.
+\abstract{Adapting one's world view in the light of new information is a central skill of intelligent agents.
+Total preorders are a common tool to model plausibility orderings over possible worlds in the research field of belief change.
+In their paper 'How to Revise a Total Preorder', Booth and Meyer present an approach to revising preorders for iterated belief revision.
+Their operator is based on assigning abstract intervals of plausibility to worlds depending on new evidence supporting them or not.
 
@@
 
-In the field of belief change total preorders (or tpos) are a common tool to model an agent's conditional beliefs.
-To support iterated belief revision it is necessary to research how these structures can be changed to adapt to an agent's changing world view.
-Booth and Meyer suggest an approach based on the idea of assigning an interval of additional metadata to the ordered, propositional worlds and iterate the tpo of an agent using that structure.
-They define and discuss properties of operators for tpo-revision and relate their approach to other fields of research.
-This report on their paper aims to present parts of their work to a wider audience with the addition of an accompanying example.
-The report's focus will be on the tpo-revision operators discussed in the paper and explicitly avoid the addition of strict preference hierarchies and relations to other research areas.
-The structure of the report will be as follows: First it will establish the context of the paper by presenting the research area of iterated belief revision and how it relates to other areas of artificial intelligence and philosophy.
-To establish a shared understanding of notation and definitions section \ref{section:formal-background} will discuss formal background and other, previous approaches to belief change.
-It will also introduce the main contribution of this report in an accompanying example demonstrating tpo-revision as described by Booth and Meyer.
-After establishing a foundation, section \ref{section:booth-and-meyer-tpo-revision-operators} and \ref{section:properties-of-bm-tpo-revision-operators} present part of the work from the original paper 'How to Revise a Total Preorder' \cite{Booth2011}.
-Section \ref{section:booth-and-meyer-tpo-revision-operators} establishes and defines functions $\ast$, used to revise tpos, a core contribution of Booth and Meyer.
+In the field of belief change, total preorders (or tpos) are a common tool to model an agent's conditional beliefs.
+To support iterated belief revision it is necessary to research how tpos can be changed to adapt to an agent's changing world view.
+Booth and Meyer suggest an approach based on the idea of assigning an interval of additional metadata to propositional worlds and iterate the tpo of an agent using that structure.
+They define and discuss properties of operators for tpo-revision as well as relate their approach to other fields of research.
+This report on their paper aims to present parts of their work to a wider audience.
+An accompanying example is the main contribution to guide the discussion and visualise changes in the agent's state.
+The report's focus will be on the tpo-revision operators discussed in the primary paper and explicitly avoid the addition of strict preference hierarchies and relations to other research areas.
+The structure of the report will be as follows: Establish the context of the paper by presenting the research area of iterated belief revision and how it relates to other areas of artificial intelligence and philosophy.
+To create a shared understanding of notation and definitions section \ref{section:formal-background} will discuss formal background and other, previous, approaches to belief change.
+It will also introduce the main contribution of this report, an accompanying example demonstrating tpo-revision as described by Booth and Meyer.
+After building a foundation, section \ref{section:booth-and-meyer-tpo-revision-operators} and \ref{section:properties-of-bm-tpo-revision-operators} will present part of the work from the original paper 'How to Revise a Total Preorder' \cite{Booth2011}.
+Section \ref{section:booth-and-meyer-tpo-revision-operators} establishes and defines functions $\ast$, used to revise tpos.
 In section \ref{section:properties-of-bm-tpo-revision-operators} properties of these functions will be presented.
-To provide an outlook for the additional work done by Booth and Meyer, \ref{section:iterating-preceq-revision} shows their suggestion for a concrete operator for tpo-revision and includes several examples and adapted visualisations of it being applied in the context of the accompanying example.
-Finally section \ref{section:conclusion} closes the report with a summary and commentary on Booth and Meyer's approach to iterated belief revision with interval orderings.
+To provide an outlook into the additional work done by Booth and Meyer, \ref{section:iterating-preceq-revision} will show their proposal of a concrete operator for tpo-revision.
+It includes several examples and adapted visualisations of the operator being applied in the context of the accompanying example.
+Finally, section \ref{section:conclusion} closes the report with a summary and commentary on Booth and Meyer's approach to iterated belief revision with interval orderings.
 
 \subsection{Research context}
-A core process for an agent dealing with uncertain knowledge is updating their worldview when new information becomes available, also called belief change.
-As an agent can be human or a machine, work in belief change has impact on both philosophy and artificial intelligence \cite{Ferme2011}.
+A core process for an intelligent agent dealing with uncertain knowledge is updating their worldview when new information becomes available, also called belief change.
+As an agent can be human or machine, work in belief change has impact on the fields of both philosophy and artificial intelligence \cite{Ferme2011}.
 Different approaches to handling belief change have been discussed with notable approaches including nonmonotonic logic, probabilistic reasoning and belief revision \cite{Darwiche1997}.
@@
 Research in this area discusses appropriate formalisations of agent state and constrains on individual operators or families of operators.
-Depending on if the suggested operator handles only one new evidence or multiple new evidences the approaches are called one-step or iterated belief revision.
+Depending on if the suggested operator handles only one new evidence or multiple new evidences, the approaches are called one-step or iterated belief revision.
 
@@
 The primary article for this report, 'How to Revise a Total Preorder', researches how to model the change of these total preorders when new evidence becomes available.
-Being able to derive a new tpo from additional evidence is an approach to handling multiple revision steps and therefor places the article in the field of iterated belief revision.
+Being able to derive a new tpo from additional evidence is an approach to handling multiple revision steps.
+It therefor places the article in the field of iterated belief revision.
 
@@
 \subsection{Propositional Logic} % Aussagenlogik
-Notation follows as used in \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables, lower case greek letters represent formulae in $L$ and $\top$, $\bot$ representing tautology and contradiction respectively.
-$\vdash$ as classical logical consequence, $\equiv$ classical logical equivalence.
+Notation follows as used in \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables.
+Lower case greek letters represent formulae in $L$ and $\top$, $\bot$ representing tautology and contradiction respectively.
+$\vdash$ denotes classical logical consequence, $\equiv$ classical logical equivalence.
 $Cn$ is used to denote the deductive closure of a formula or set of formulae in $L$.
@@
 $W$ is the set of propositional worlds (also called propositional interpretations in classical logic \cite{Kai2020}).
-Given a $\alpha \in L$ the set of worlds that satisfy $\alpha$ is denoted by $[\alpha]$.
+Given a formula $\alpha \in L$, the set of worlds that satisfy $\alpha$ is denoted by $[\alpha]$.
 
@@
 \subsection{Total preorders}
-A total preorder is a binary relation $\leq$ (here over the set of propositional worlds $W$) that is total, reflexive and transitive (i.e.
+Tpos are a common tool to handle preference orderings over propositional worlds in literature about belief change \cite{Booth2011}.
+
+A total preorder is a binary relation $\leq$ (in this context over the set of propositional worlds $W$) that is total, reflexive and transitive (i.e.
 for all $x, y, z \in W$ either $x \leq y$ or $y \leq x$, $x \leq x$ and if $x \leq y$ and $y \leq z$ then $x \leq z$).
@@
 The symbol $<$ is used to denote the strict part of $\leq$ while $\sim$ represents the symmetric closure of $\leq$ (i.e. $x \sim y$ iff $x \leq y$ and $y \leq x$).
-
-Tpos are a common tool to handle preference orderings over propositional worlds in literature about belief change \cite{Booth2011}.
 
@@
 Each rank of a tpo $\leq$ is defined as the equivalence classes modulo the symmetric closure of $\leq$: $[[x]]_{\sim} = \{y \mid y \sim x\}$.
-These equivalence classes are then ordered by the relation $[[x]] \leq [[y]]$ iff $x \leq y$
+These equivalence classes are then ordered by the relation $[[x]] \leq [[y]]$ iff $x \leq y$.
 
@@
 $p$ represents "John is the murderer", $q$ represents "Mary is the murderer" and $r$ represents "the victim is an alien".
-Possible propositional worlds will be denoted as triplets of 0s and 1s denoting $p$, $q$ and $r$ to be true or false, e.g.
-the $101$-world stands for John being the murderer and the victim being an alien.
-
-    To start the agent believes it is reasonable to assume the murderer acted alone (but is not ruling out both of the accused conspiring).
-In addition it would be extremely surprising (but not impossible) if the victim was an alien.
+Possible propositional worlds will be denoted as triplets of 0s and 1s denoting $p$, $q$ and $r$ to be true or false.
+For example the $101$-world stands for John being the murderer and the victim being an alien.
+
+    To start the agent believes it is reasonable to assume the murderer acted alone (but is not ruling out both conspiring).
+In addition they consider it extremely unlikely, but not impossible, for the victim to be an alien.
 
@@
 A belief set is the deductively closed set of propositions an agent accepts as true at any given point in time \cite{Ferme2011}.
-AGM theory \cite{Alchourron1985} defines postulates for belief sets and their contraction, revision or expansion with new evidence.
-% TODO explain contraction, revision, expansion?
-
-%    As our perception of the world described by the knowledge base
-%    changes, the knowledge base must be modified. G~irdenfors [9] distinguishes
-%    several kinds of modifications. If we simply acquire additional knowledge
-%    about the world, and the new knowledge does not conflict with the current
-%    beliefs t of the KB, we expand the KB. If, however, the new knowledge is
-%    inconsistent with the old beliefs, and we want the KB to be always consistent,
-%    we must resolve the conflict somehow; this operation will be called revision. A
-%    * Part of this work was performed while this author was visiting the University of Toronto.
-%    ** This author is partially supported by the Natural Science and Engineering Research Council
-%    of Canada.
-%    1 We use the terms belief and knowledge interchangeably in this paper.
-%    0004-3702/91/$03.50 © 1991 -- Elsevier Science Publishers B.V. All rights reserved 
-%    264 H. Katsuno, A.O. Mendelzon
-%    different kind of change occurs when a sentence previously believed becomes
-%    questionable and has to be given up; the operation that makes this change is a
-%    contraction. Other kinds of operations are discussed in [14].
+AGM theory \cite{Alchourron1985} defines postulates for belief sets and their contraction, expansion or revision with new evidence.
+In the process of belief revision an agent keeps their set of beliefs consistent while incorporating new information, even if it is inconsistent with the current belief set \cite{Gaerdenfors1984}.
+% TODO explain contraction, revision, expansion? Gardenfors correct? read!
 
 Darwiche and Pearl \cite{Darwiche1997} argue that working with belief sets is not expressive enough for satisfying results in iterated belief revision.
-They make the distinction between propositional beliefs (i.e.
-beliefs the agent accepts and are part of the belief set) and conditional beliefs (i.e.
-beliefs the agent is prepared to adopt with new evidence).
-
-While the AGM postulates define restrictions on revising propositional beliefs (a core one being the principle of minimal change), they place little restrictions on preserving conditional beliefs.
-In their paper Darwiche and Pearl use epistemic states, abstract entities that contain all information an agent needs for their reasoning, especially their strategy for belief revision.
-As conditional beliefs are represented by these strategies, it is necessary to define how to modify the strategy itself when encountering multiple new information \cite{Darwiche1997}.
-
-Belief sets can be extracted from epistemic states (the belief set extracted from an epistemic state $\mathbb{E}$ is denoted as $B(\mathbb{E})$).
+They make the distinction between propositional beliefs (beliefs the agent accepts and are part of the belief set) and conditional beliefs as beliefs the agent is prepared to adopt with new evidence.
+
+While the AGM postulates define restrictions on revising propositional beliefs (a core one being the principle of minimal change), they don't restrict changes in conditional beliefs.
+In their paper Darwiche and Pearl argue for epistemic states, abstract entities that contain all information an agent needs for their reasoning.
+This includes especially their strategy for belief revision in addition to their belief set.
+As conditional beliefs are represented by these strategies, it is necessary to define how to modify the strategy itself when encountering new information \cite{Darwiche1997}.
+
+Belief sets can be extracted from epistemic states.
+The belief set extracted from an epistemic state $\mathbb{E}$ is denoted as $B(\mathbb{E})$.
 Darwiche and Pearl show that their version of revision of epistemic states can be modelled with a tpo $\leq_{\mathbb{E}}$, associated with $\mathbb{E}$.
-Extraction of $B(\mathbb{E})$ is done by considering the lowest ranked worlds (i.e.
+Extraction of $B(\mathbb{E})$ is achieved by considering the set of lowest ranked worlds (i.e.
 the most plausible interpretations) under $\leq_{\mathbb{E}}$.
-The set of propositional sentences that holds in all those worlds is assumed to be the belief set of the agent.
+The set of propositional sentences that holds in all those worlds is defined to be the belief set of the agent.
 For notation let $min(\alpha, \leq_{\mathbb{E}})$ denote the set of minimal models for the propositional formula $\alpha$ under $\leq_{\mathbb{E}}$.
 Then $[B(\mathbb{E})] = min(\top, \leq_{\mathbb{E}})$ is the set of worlds that are models of the belief set $B(\mathbb{E})$ associated with $\mathbb{E}$.
+The belief set of the agent with this notation is $Th([B(\mathbb{E})])$.
 
@@
 A possible belief set is $B(\mathbb{E}) = \{p \vee q, \neg p \vee \neg q, \neg r\}$ as $[B(\mathbb{E})] = \{010, 100\} = min(\top, \leq_{\mathbb{E}})$.
-Intuitively this makes sense with the initial assumption that John or Mary are the suspects ($p \vee q$), have acted alone ($\neg p \vee \neg q$) and the victim is not an alien ($\neg r$).
+Intuitively this makes sense, with the initial assumption that John or Mary are the suspects ($p \vee q$), have acted alone ($\neg p \vee \neg q$) and the victim is not an alien ($\neg r$).
 \end{example}
@@
 The postulates first introduced by \cite{Alchourron1985} and reformulated for iterated belief revision on epistemic states by \cite{Darwiche1997} are repeated here.
-$\mathbb{E}$ denotes an epistemic state, $B(\mathbb{E})$ it's associated belief set, $B(\mathbb{E}) + \alpha$ the expansion of $B(\mathbb{E})$ by $\alpha$ and $\ast$ being a belief change operator on epistemic states.
+$\mathbb{E}$ denotes an epistemic state, $B(\mathbb{E})$ it's associated belief set, $B(\mathbb{E}) + \alpha$ the expansion of $B(\mathbb{E})$ by $\alpha$.
+$\ast$ being a belief change operator on epistemic states.
 
@@
 Because the focus of this report is on the revision of tpos, the semantic (i.e.
-in terms of how the ordering of worlds undergoes change) versions are shown here, for more details and sentential versions refer to \cite{Darwiche1997}.
+in terms of how the ordering of worlds undergoes change) versions are shown here.
+For more details and sentential versions refer to \cite{Darwiche1997}.
 
@@
 
-\ref{CR1} and \ref{CR2} mean that the relative ordering of worlds following a revision by $\alpha$ stays the same, if the worlds are either both $\alpha$ or $\neg\alpha$ worlds.
+\ref{CR1} and \ref{CR2} mean that the relative ordering of worlds following a revision by $\alpha$ stays the same if the worlds are either both $\alpha$ or $\neg\alpha$ worlds.
 \ref{CR3} and \ref{CR4} require that $\alpha$-worlds that are strictly/weakly more plausible than $\neg\alpha$-worlds are still strictly/weakly more plausible than them after a $\alpha$-revision.
@@
 \subsection{Enriching epistemic states}
-Based on DP-AGM and the postulates $(CR1)$-$(CR4)$ Booth and Meyer assume a fixed tpo $\leq$ over a set of worlds $W$ that acts as a plausibility ordering.
+Based on DP-AGM and the postulates $(CR1)$-$(CR4)$, Booth and Meyer assume a fixed tpo $\leq$ over a set of worlds $W$ that acts as a plausibility ordering.
 The goal of the paper is the discussion of functions $\ast$ that return a new ordering $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
@@
 
-% TODO this describes a concrete operator, not the idea. go back to more basics, w+ as positive representation, w- as negative. 
-% TODO this also is maybe wrong? "add additional metadata to world w" is not what is happening, it is an additional structure W+-
-Booth and Meyer's \cite{Booth2011} approach is to add additional metadata to every world $w \in W$.
+Booth and Meyer's \cite{Booth2011} approach is to add an additional structure with metadata for every world $w \in W$.
 This new structure is denoted as $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$.
-In this notation a world $w \in W$ is represented twice: When new evidence $\alpha$ arrives that makes $w$ more plausible (because $w \in [\alpha]$) the agent can assume it's rank as $w^{+} \in W^{\pm}$.
-In contrast if the new evidence makes $w$ less plausible ($w \notin [\alpha]$) then $w^{-} \in W^{\pm}$ is $w$'s rank.
+In this notation a world $w \in W$ is represented twice: When new evidence $\alpha$ arrives that makes $w$ more plausible (because $w \in [\alpha]$) the agent can assume it's positive representation as $w^{+} \in W^{\pm}$.
+In contrast if the new evidence makes $w$ less plausible ($w \notin [\alpha]$) then the negative representation $w^{-} \in W^{\pm}$ is the agent's view of $w$.
 In their paper Booth and Meyer call the pair $(w^{+}, w^{-})$ the positive/negative representation of the world $w$.
@@
 \subsection{$\leq$-faithful tpos}
-For the ordering on $W^{\pm}$ Booth and Meyer suppose an additional relation denoted $\preceq$ over $W^{\pm}$ that is added to the epistemic state of an agent.
+For the ordering on $W^{\pm}$ Booth and Meyer suppose an additional relation, denoted $\preceq$ over $W^{\pm}$, that is added to the epistemic state of an agent.
 
@@
     \label{example:example-stick}
-    Recall that tpos can be equivalently thought of as a linearly ordered set of ranks (Example \ref{example:example-introduction}, page \pageref{example:example-introduction}) and therefor a tpo over $W$ can be visualised by ordering every $w \in W$ in a table of ranks (Table \ref{tab:visualising-a-tpo-example}, page \pageref{tab:visualising-a-tpo-example}).
+    Recall that tpos can be equivalently thought of as a linearly ordered set of ranks (Example \ref{example:example-introduction}, page \pageref{example:example-introduction}).
+Therefor a tpo over $W$ can be visualised by ordering every $w \in W$ in a table of ranks (table \ref{tab:visualising-a-tpo-example}).
 To visualise the interval ordering introduced by $\preceq$, Booth and Meyer use a "stick" with the endpoints defined as $w^{+}$/$w^{-}$ respectively.
@@
 
-To characterise the relations between $\preceq$ and $\leq$ Booth and Meyer define a list of conditions.
+To characterise the relations between $\preceq$ and $\leq$, Booth and Meyer define a list of conditions.
 
@@
 The choice between positive or negative representations of two worlds should be the same as under $\leq$ (due to \ref{PREQ2}, \ref{PREQ3}).
-According to \ref{PREQ4} there has to be a difference between two ranks of a positive representation and a negative representation of the same world.
-Given the choice between both, the positive representation has to be chosen.
+According to \ref{PREQ4} there has to be a difference between a positive representation and a negative representation of the same world and given the choice between both, the positive representation has to be chosen.
 
@@
 
-Because of \ref{PREQ2} and \ref{PREQ3} it is sufficient to only include $\preceq$ in the epistemic state.
+Because of \ref{PREQ2} and \ref{PREQ3}, it is sufficient to only include $\preceq$ in the epistemic state.
 The tpo $\leq$ over $W$ can be determined from $\preceq$ by restricting to only $\{ x^{+} \mid x \in W\}$ or $\{ x^{-} \mid x \in W\}$ respectively.
@@
 
-    As demonstrated here while the "sticks" do not need to be the same size (they just must exist due to \ref{PREQ4}), they need to be the same size for worlds that share a rank for their corresponding representations.
+    As demonstrated here, while the "sticks" do not need to be the same size for all worlds (they just must exist due to \ref{PREQ4}), they need to be the same size for worlds that share a rank for their corresponding representations.
 They can not "cover" other sticks completely to continue to satisfy \ref{PREQ2} and \ref{PREQ3}.
@@
     \end{figure}
+
+    Notice the "gap" between the $[r]$-worlds that include the victim being an alien.
+Even in their positive representations they are not as plausible as negative representations of $[\neg r]$-worlds.
+That fact will be discussed more in section \ref{section:non-prioritised-revision} and example \ref{example:example-non-prio-revision}.
 \end{example}
@@
 
-Intuitively new evidence $\alpha$ makes worlds that satisfy $\alpha$ more plausible and worlds that do not satisfy $\alpha$ less plausible.
+Intuitively, new evidence $\alpha$ makes worlds that satisfy $\alpha$ more plausible and worlds that do not satisfy $\alpha$ less plausible.
 Therefor the agent associates worlds $x \in [\alpha]$ with their positive representation $x^{+}$ and worlds $x \in [\neg\alpha]$ with their negative representation $x^{-}$.
@@
     Reconsider the $\leq$-faithful tpo $\preceq$ from example \ref{example:example-stick} (page \pageref{example:example-stick}).
-When a new piece of evidence $\alpha$ has to be considered each world gets mapped to one end of the interval assigned to it, depending on if it is an $\alpha$-world or not.
+When a new piece of evidence $\alpha$ has to be considered, each world gets mapped to one end of the interval assigned to it, depending on if it is an $\alpha$-world or not.
 In figure \ref{fig:example-updated-tpo} that mapping is indicated by the filled out dot.
@@
 
-    The updated tpo $\leq_{\alpha}^{\ast}$ can now be inferred from the figure.
+    The updated tpo $\leq_{\alpha}^{\ast}$ can now be inferred from figure \ref{fig:example-updated-tpo}.
 It is the ordering of the filled dots, representing the new assignment for the respective world: $x_{1} \sim x_{2} \sim x_{4} < x_{3}$.
@@
     \label{example:example-tpo-revised}
-    A complex example is the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ (for the courtroom example \ref{example:example-introduction}) using the $\leq$-faithful tpo $\preceq$ introduced in example \ref{example:example-tpo-initial} and shown in figure \ref{fig:example-tpo-revised}.
-In this case the new evidence received pointed to John being the murderer so $\alpha = p$.
+    A more complex example is the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ (for the courtroom example \ref{example:example-introduction}) using the $\leq$-faithful tpo $\preceq$, introduced in example \ref{example:example-tpo-initial} and shown in figure \ref{fig:example-tpo-revised}.
+In this case the new evidence received points to John being the murderer so $\alpha = p$.
 
@@
             \end{tikzpicture}
-            \caption{Associating positive and negative representations of worlds for the courtroom example \ref{example:example-introduction}, after receiving evidence $\alpha=p$}
+            \caption{Associating positive and negative representations of worlds after receiving evidence $\alpha=p$}
             \label{fig:example-tpo-revised}
@@
 
-    For the worlds $010, 110 \in W$ in old tpo $\leq$, $010 \leq 110$ was true. To rank them with the revised tpo $\leq_{\alpha}^{\ast}$ calculate:
+    For the worlds $010, 110 \in W$, $010 \leq 110$ was true. To rank them with the revised tpo $\leq_{\alpha}^{\ast}$ calculate:
 
@@
     Repeating for every world in $W$, the new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$.
-Unsurprisingly the belief set associated with the new epistemic state is $[B(\mathbb{E})] = min(\top, \leq_{\mathbb{E}}) = \{100\}$, "John is the murderer and the victim is not an alien".
-
-    As $\leq_{\alpha}^{\ast}$ is a representation of the conditional beliefs of the agent, it is also interesting to look at the changes for them: While the judge initially thought both suspects being the murderers ($110$) was less plausible than only Mary being the murderer ($010$), they now have updated their assumptions to think only Mary being the murderer less plausible than both conspiring.
+Unsurprisingly, the belief set associated with the new epistemic state is $[B(\mathbb{E})] = min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".
+
+    As $\leq_{\alpha}^{\ast}$ is a representation of the conditional beliefs of the agent, it is also interesting to look at the changes for them: Initially the judge thought both suspects being the murderers ($110$) was less plausible than only Mary being the murderer ($010$).
+Now they have updated their conditional beliefs to think only Mary being the murderer less plausible than both conspiring.
 \end{example}
@@
 Belief revision with the AGM postulates \cite{Alchourron1985} or the reformulation by Darwiche and Pearl \cite{Darwiche1997} always includes the new information $\alpha$ in the belief set after revision.
-This feature is explicit in \ref{E2} of DP-AGM from chapter \ref{chapter:dp-agm-postulates} (page \pageref{chapter:dp-agm-postulates}), given as $\alpha \in B(\mathbb{E}\ast\alpha)$.
+This feature is explicit in \ref{E2} of DP-AGM, given as $\alpha \in B(\mathbb{E}\ast\alpha)$.
 
@@
 A demonstration is already provided with example \ref{example:example-updated-tpo} and figure \ref{fig:example-updated-tpo}.
-The belief set extracted from the new epistemic state $\mathbb{E}$ as $[B(\mathbb{E})] = min(\top, \leq_{\alpha}^{\ast})$ includes the $[\neg\alpha]$-worlds $x_{1}$ and $x_{2}$ and therefor does not include the new evidence $\alpha$.
+The most plausible worlds in the new epistemic state $\mathbb{E}$, $min(\top, \leq_{\alpha}^{\ast})$, include the $[\neg\alpha]$-worlds $x_{1}$ and $x_{2}$.
+Therefor $Th(min(\top, \leq_{\alpha}^{\ast}))$ does not include the new evidence $\alpha$.
 
@@
 
-    Using the $\leq$-faithful tpo $\preceq$ already established for the courtroom example \ref{example:example-introduction} the revision by $\alpha = r$ ("the victim was an alien").
-is shown in figure \ref{fig:example-non-prio-revision}.
+    Using the $\leq$-faithful tpo $\preceq$ already established for the courtroom example \ref{example:example-introduction} the revision by $\alpha = r$ ("the victim was an alien") is shown in figure \ref{fig:example-non-prio-revision}.
     \begin{figure}[H]
@@
             \end{tikzpicture}
-            \caption{Non-prioritised revision for $B(\mathbb{E})$}
+            \caption{Non-prioritised revision by $\alpha = r$}
             \label{fig:example-non-prio-revision}
@@
 
-    Since the agent considered the victim being an alien very unlikely even the positive representations of worlds in $[\alpha]$ are on higher ranks (so considered less plausible) than negative representations of worlds in $[\neg\alpha]$.
-    The belief set $B(\mathbb{E})$ of the agent is unchanged even under $\leq_{\alpha}^{\ast}$, since $\{010, 100\}$ are still the most plausible worlds, and does not include $r$ "the victim is an alien".
+    Since the agent considered the victim being an alien very unlikely, even the positive representations of worlds in $[\alpha]$ are on higher ranks (so considered less plausible) than negative representations of worlds in $[\neg\alpha]$.
+    The belief set $B(\mathbb{E})$ of the agent is unchanged under $\leq_{\alpha}^{\ast}$, since $\{010, 100\}$ are still the most plausible worlds, and does not include $r$ "the victim is an alien".
 \end{example}
@@
 \label{section:properties-of-bm-tpo-revision-operators}
-While not determining a concrete operator $\ast_{\preceq}$ to revise a tpo $\leq$, definition \ref{definition:revision-operator} allows Booth and Meyer to discuss what properties any operator in that family must have \cite{Booth2011}.
+Definition \ref{definition:revision-operator} allows Booth and Meyer to discuss what properties any operator in that family must have \cite{Booth2011}.
 
@@
 Booth and Meyer themselves consider them characteristic for admissible revision operators \cite{Booth2006a}.
-If revising a tpo by a sentence $\alpha$, the relative ordering of worlds, that are either both $[\alpha]$- or $[\neg\alpha]$-worlds, must stay the same (\ref{AST3}/\ref{AST4}).
-These properties were already part of the semantic postulates \ref{CR1} and \ref{CR2} by Darwiche and Pearl \cite{Darwiche1997} discussed in chapter \ref{chapter:dp-agm-postulates} (page \pageref{chapter:dp-agm-postulates}).
-% TODO this formulation is a disaster
+If revising a tpo by a sentence $\alpha$, the relative ordering of worlds that are either both $[\alpha]$- or $[\neg\alpha]$-worlds, must stay the same (\ref{AST3}/\ref{AST4}).
+These properties were already part of the semantic postulates \ref{CR1} and \ref{CR2} by Darwiche and Pearl \cite{Darwiche1997} discussed in section \ref{chapter:dp-agm-postulates}.
 In a similar way \ref{AST5} is a stronger requirement than the other two Darwiche and Pearl postulates \ref{CR3} and \ref{CR4}.
-It means the following: A world $x$ that is considered at least as plausible as a world $y$, before a revision by new information $\alpha$.
+It means the following: A world $x$ that is considered at least as plausible as a world $y$ before a revision by new information $\alpha$.
 If $\alpha$ makes $x$ more plausible ($x \in [\alpha]$) and $y$ less plausible ($y \in [\neg\alpha]$) then after revision $x$ should be considered strictly more plausible than $y$.
@@
 % TODO: pull these out? Basic postulates for tpo revision in one subsection, additional ones "supplementary rationality properties" as second section?
-These properties define tpo-revision with one input sentence, which make Booth and Meyer relate them to the AGM postulates for belief set revison \cite{Alchourron1985} as basic postulates for tpo-revision \cite{Booth2011}.
+These properties define tpo-revision with one input sentence.
+Booth and Meyer relate them to the AGM postulates for belief set revison \cite{Alchourron1985} as basic postulates for tpo-revision \cite{Booth2011}.
 
@@
 These properties are largely ignored in other literature on iterated belief change \cite{Booth2011}.
-\ref{AST6} means that if, after revision by evidence $\alpha$ that makes a world $x$ more plausible than $y$, $y$ is still considered at least as plausible as $x$, then for any possible revision by evidence $\gamma$, $y$ must be at least as plausible as $x$.
+\ref{AST6} means that if, after revision by evidence $\alpha$, that makes a world $x$ more plausible than $y$, $y$ is still considered at least as plausible as $x$, then for any possible revision by evidence $\gamma$, $y$ must still be at least as plausible as $x$.
 \ref{AST7} is the equivalent property for strict preference.
@@
 
-% TODO: do example operator for tpo <= here for each property with alien example and proof it works for each? -> OWN contrib
-
-% TODO write Sentinential view, should we include this?
-%\subsection{Sentinential view}
-% booth: "on a semantic level, i.e., in terms of how the ordering of individual worlds x, y undergo change"
-%    \item Explanation of sentinential view (and distinction to semantic level), definition of $\leq' \circ \beta $ and how it relates to conditional beliefs, mention of $\leq' \circ \top $ as belief set.
-Show of properties for the family of revision operators using sentinential view.
-Explanation of Disj1/Disj2 as properties that are easy to show in the sentinential view but not in the semantic formulation.
-
 \section{Iterating: $\preceq$-revision}
@@
 The operator $\ast$, based on $\preceq$, allows the revision of a tpo $\leq$ associated with an epistemic state to $\leq_{\alpha}^{\ast}$.
-To be used in iterated belief revision the newly introduced structure $\preceq$ also needs to be revised Otherwise, as Booth and Meyer put it, the problem has just "re-emerged 'one level up'" \cite{Booth2011}.
-In their paper they discuss strict preference hierarchies (or SPHs), an equivalent structure to $\preceq$, denoted as $\$$, their properties and how to revise them.
+To be used in iterated belief revision the newly introduced structure $\preceq$ also needs to be revised.
+Otherwise, as Booth and Meyer put it, the problem has just "re-emerged 'one level up'" \cite{Booth2011}.
+In their paper, they discuss strict preference hierarchies (or SPHs), an equivalent structure to $\preceq$, denoted as $\$$, their properties and how to revise them.
 
@@
 \subsection{A concrete operator}
-Booth and Meyer define their operator to revise $\preceq$ with a function $p: W^{\pm} \mapsto \mathds{R}$ so that for all $x \in W$ the interval between it's positive and negative representation is a real number $a$:
+Booth and Meyer define their operator to revise $\preceq$ with a function $p: W^{\pm} \mapsto \mathds{R}$.
+For all $x \in W$ the interval between it's positive and negative representation is a real number $a$:
 
@@
 The smaller $p(x^{\epsilon})$ is, the more plausible the world is.
-The interval $(x^{+}, x^{-})$, representing a world $x \in W$ using it's representations $x^{+}, x^{-} \in W^{\pm}$, essentially becomes an interval of real numbers $(p(x^{+}), p(x^{-}))$ with length $a$.
+The interval $(x^{+}, x^{-})$, represents a world $x \in W$ using it's representations $x^{+}, x^{-} \in W^{\pm}$.
+For revision on the basis of $p$, it becomes an interval of real numbers $(p(x^{+}), p(x^{-}))$ with length $a$.
 
@@
 
-Revision of $\preceq$ becomes a two step process: First choose a function $p$ so that $\preceq_{p} = \preceq$, then revise $p$ to get a new assignment $p \ast \alpha$ that defines a new $\leq$-faithful tpo $\preceq_{p \ast \alpha}$.
+Revision of $\preceq$ becomes a two step process: First choose a function $p$ so that $\preceq_{p} = \preceq$.
+Then revise $p$ to get a new assignment $p \ast \alpha$ that defines a new $\leq$-faithful tpo $\preceq_{p \ast \alpha}$.
 
 % TODO: probably don't need geffner ref here
-Booth and Meyer suggest an operator that keeps worlds that satisfy $\alpha$ constant and moves $\neg\alpha$-worlds "back" by $a$ (also known as L-conditionalisation in Spohn-type rankings \cite{Geffner1992}).
-They also mention other operators are possible and an area of further research.
+Booth and Meyer propose an operator that keeps worlds that satisfy $\alpha$ constant and moves $\neg\alpha$-worlds "back" by $a$ (also known as L-conditionalisation in Spohn-type rankings \cite{Geffner1992}).
+Other operators are possible and an area of further research \cite{Booth2011}.
 They achieve this by setting $p$, for every $x^{\epsilon} \in W^{\pm}$ to:
@@
 Figure \ref{fig:example-preceq-revised} shows the revised tpo $\preceq_{\alpha}$ with $\neg\alpha$-worlds moved back by $a$.
+The position of their previous positive representation is displayed as x.
 
@@
 
-    For the first step a function $p$ is chosen so that $\preceq_{p} = \preceq$ and the intervals for all worlds $x \in W^{\pm}$ can be defined using $p$.
-
-    For example the interval representing world $010$ is $(010^{+}, 010^{-})$ and becomes $(p(010^{+}), p(010^{-})) = (0, a)$.
+    For the first step, a function $p$ is chosen so that $\preceq_{p} = \preceq$ and the intervals for all worlds $x \in W^{\pm}$ can be defined using $p$.
+
+    For example, the interval representing world $010$ is $(010^{+}, 010^{-})$ and becomes $(p(010^{+}), p(010^{-})) = (0, a)$.
 Initially the world $100$ is represented by the same interval $(100^{+}, 100^{-})$ that becomes $(p(100^{+}), p(100^{-})) = (0, a)$.
@@
 
-    In the second step $p$ is revised by $\alpha$ to $p \ast \alpha$ as defined above. The $\neg\alpha$-world $010$ is moved back by $a$ while the $\alpha$-world $100$ is unchanged:
+    In the second step $p$ is revised by $\alpha$ to $p \ast \alpha$. The $\neg\alpha$-world $010$ is moved back by $a$, while the $\alpha$-world $100$ is unchanged:
 
@@
     \label{example:example-preceq-revised-alien}
-    For an example that demonstrates the impact the revision of $\preceq$ has on the acceptance of conditional beliefs of an agent consider again the courtroom example \ref{example:example-introduction}.
-The fact that the victim might is an alien ($r$ true) seems very unlikely, which is modelled by the gap between $[r]$-worlds and $[\neg r]$-worlds.
-
-    When evidence $\alpha = r$ arrives there seems to be little change in the epistemic state of the judge: $\leq_{\alpha}^{\ast}$ is unchanged as even considering the negative representations of $[\neg r]$-worlds they rank lower than $[r]$-worlds.
+    For an example that demonstrates the impact the revision of $\preceq$ has on the acceptance of conditional beliefs consider again the courtroom example \ref{example:example-introduction}.
+The fact that the victim is an alien ($r$ true) seems very unlikely, which is modelled by the gap between $[r]$-worlds and $[\neg r]$-worlds.
+
+    When evidence $\alpha = r$ arrives, there seems to be little change in the epistemic state of the judge: $\leq_{\alpha}^{\ast}$ is unchanged as even considering the negative representations of $[\neg r]$-worlds they rank lower than $[r]$-worlds.
 An unchanged tpo $\leq_{\alpha}^{\ast}$ also means the believe set $B(\mathbb{E})$ stays the same and does not include $r$ (a property of non-prioritised revision as described in section \ref{section:non-prioritised-revision}).
@@
 For the initial tpo $\leq$ there was no possible evidence that would change the plausibility ordering between worlds where the victim is an alien and worlds where they are not.
-That was reflected by the new tpo $\leq_{\alpha}^{\ast}$ that even with direct evidence for alien life did not change the judges plausibility orderings.
+That was reflected by the new tpo $\leq_{\alpha}^{\ast}$ that, even with direct evidence for alien life, did not change the judges plausibility orderings.
 But because of the revision of $\preceq$ to $\preceq_{p \ast \alpha}$, the evidence $\alpha$ changed the acceptance of the judge to belief we are not alone in the universe.
-After receiving $\beta$ the judge even considers the $[r]$-worlds $\{011, 101\}$ more likely than the $[\neg r]$-worlds $\{000, 110\}$!
-
-(Luckily due to the existence of $[\beta]$-worlds $\{010, 100\}$ the belief set of the judge still does not include $r$ and rationality prevails.)
+After receiving $\beta$, the judge even considers the $[r]$-worlds $\{011, 101\}$ more likely than the $[\neg r]$-worlds $\{000, 110\}$!
+
+(Luckily, due to the existence of $[\beta]$-worlds $\{010, 100\}$, the belief set of the judge still does not include $r$ and rationality prevails.)
 \end{example}
 
-% TODO write Conclusion
 \section{Conclusion}
@@
 This report focused on presenting the research context and previous work in iterated belief change as well as the concrete tpo-revision based on the additional structure of $\leq$-faithful tpos.
-A consistent example based on a trial situation (adapted from \cite{Darwiche1997} and \cite{Booth2011}) was used to accompany the discussion of the paper.
+A consistent example including a trial situation (adapted from \cite{Darwiche1997} and \cite{Booth2011}) was used to accompany the discussion of the paper.
 In addition to the provided example the report also introduced an adapted visualisation for $\leq$-faithful tpo-revision based on the stick visualisation used by Booth and Meyer themselves.
@@
 To make the presented content easier to follow some parts of the original paper had to be excluded.
-Booth and Meyer discuss multiple additional properties of their proposed operators as well as extreme examples.
+Booth and Meyer discuss multiple additional properties of their proposed operators as well as edge cases.
 They also provide a different way to express the $\preceq$-structure using strict preference hierarchies and discuss how they relate to other research areas.
@@
 The idea to define an interval of plausibility for worlds depending on if evidence supports them or not does make intuitive sense.
-An angle largely missing from the paper is the discussion of the different impact and quality of new information itself.
-
-% idempotent correct?
-The proposed concrete operator for the revision of $\leq$-faithful tpos allows for multiple revisions by the same evidence $\alpha$ or semantically equivalent evidence $\beta \equiv \alpha$, consistently lowering the acceptance of $[\neg\alpha]$-worlds without presenting new evidence.
-It seems like an interesting question to ask if tpo-revision for iterated belief change should be idempotent in regards to already applied evidence.
-
-Considering quality and impact of new evidence also creates the question if \ref{AST6} and \ref{AST7} (properties of BM tpo-revision operators, page \ref{section:properties-of-bm-tpo-revision-operators}) should be weakened.
-Especially high quality evidence for a very unlikely type of world might change an agents plausibility ordering where low quality evidence that is very expected might not.
-Consider the following situation in our courtroom example \ref{example:example-introduction}: New evidence $\alpha$ arrives that fingerprints of John have been found at the place of the murder, pointing to a world $x$ with $p$ being true.
-But, because of a large body of evidence, the judge still considers a world $y$ where Mary is the murderer to be more plausible.
+An view largely missing from the paper is the discussion of the different impact and quality of new information itself.
+
+% TODO: question, idempotent correct?
+The proposed, concrete operator for the revision of $\leq$-faithful tpos allows for multiple revisions by the same evidence $\alpha$ or semantically equivalent evidence $\beta \equiv \alpha$.
+Those would consistently lower the acceptance of $[\neg\alpha]$-worlds without presenting new evidence.
+It seems like an interesting question to ask, if tpo-revision for iterated belief change could be idempotent in regards to already known information.
+
+% TODO: this critique example seems very weak
+Considering quality and impact of new evidence also creates the question if \ref{AST6} and \ref{AST7} (properties of BM tpo-revision operators, section \ref{section:properties-of-bm-tpo-revision-operators}) should be weakened.
+Especially high quality evidence for a very unlikely type of world might change an agents plausibility ordering, while low quality evidence that is very expected might not.
+Consider the following situation in our courtroom example \ref{example:example-introduction}: New evidence $\alpha$ arrives that fingerprints of John have been found at the place of the murder.
+$\alpha$  makes a world $x$, with $p$ being true, more likely.
+But, because of a large body of evidence, the judge still considers a world $y$, where Mary is the murderer, to be more plausible.
 This means there can be no evidence $\gamma$ that would make the agent consider the world $x$ more likely than $y$ according to \ref{AST7}:
@@
 
-But what if evidence is submitted that if Mary is the murderer, the victim must be an alien $\gamma = q \implies r$?
+But what if evidence is submitted that, if Mary is the murderer, the victim must be an alien $\gamma = q \implies r$?
 Semantically a human agent would assume all worlds in which Mary is the murderer to be highly unlikely due to how far fetched the acceptance of the victim being an alien is.
@@
 
-% TODO *6,*7 seem weird, no different "strength" of evidence?
-maybe revising multiple time by the same evidence should that be?
-otherwise revising multiple times by same evidence is also weird because it changes things and is not idempotent, discuss 5 with it being equal when sticks - and + are same rank?!
 \newpage

### 2021-01-12 paper/1901_3230880_philip_heltweg.tex
improvement: caro feedback

--- 2020-12-31 paper/paper.tex
@@
 \theoremstyle{definition}
-\newtheorem{example}{Example}[section]
+\newtheorem{example}{Example}
 
@@
 
-% TODO title, "Total preorder in the courtroom"?
+\begin{titlepage}
+\pagenumbering{gobble}
+  {\centering
+  \vskip 30 pt
+  \LARGE Synopsis of 'How to Revise a Total Preorder' \cite{Booth2011} for seminar 1901 - 'Representation and processing of uncertain knowledge with logic-based methods' \par
+  \vskip 1.5em
+  \large Philip Heltweg, matriculation number 3230880 \par
+  \vskip 1.5em}
+
+  Ich erkläre, dass ich die schriftliche Ausarbeitung zum Seminar selbstständig und ohne unzulässige Inanspruchnahme Dritter verfasst habe.
+Ich habe dabei nur die angegebenen Quellen und Hilfsmittel verwendet und die aus diesen wörtlich oder sinngemäß entnommenen Stellen als solche kenntlich gemacht.
+Die Versicherung selbstständiger Arbeit gilt auch für enthaltene Zeichnungen, Skizzen oder graphische Darstellungen.
+Die Ausarbeitung wurde bisher in gleicher oder Ähnlicher Form weder derselben noch einer anderen Prüfungsbehörde vorgelegt und auch nicht veröffentlicht.
+Mit der Abgabe der elektronischen Fassung der endgültigen Version der Ausarbeitung nehme ich zur Kenntnis, dass diese mit Hilfe eines Plagiatserkennungsdienstes auf enthaltene Plagiate geprüft werden kann und ausschließlich für Prüfungszwecke gespeichert wird.
+\end{titlepage}
+\pagenumbering{arabic}
+
 % TODO: '' for quotes should be ""? Or consistent at least
 % TODO: references align: Richard Booth, sometimes R Booth
-\title{Of judges, aliens and tpos}
-\subtitle{Report on 'How to Revise a Total Preorder' \cite{Booth2011} for seminar 1901 - 'Representation and processing of uncertain knowledge with logic-based methods'}
+\title{Of judges, aliens and total preorders}
 \author{
-	Heltweg, Philip (3230880) \\
+	Heltweg, Philip \\
 	University of Hagen \\
@@
 
-This report presents part of their work in tpo-revision operators and their properties with the help of an accompanying example and additional visualisation.}
+This synopsis presents part of their work in tpo-revision operators and their properties with the help of an accompanying example and additional visualisation.}
 
@@
 
+% TODO: consider not having a table of contents
 \tableofcontents
@@
 \section{Introduction}
-
-In the field of belief change, total preorders (or tpos) are a common tool to model an agent's conditional beliefs.
-To support iterated belief revision it is necessary to research how tpos can be changed to adapt to an agent's changing world view.
-Booth and Meyer suggest an approach based on the idea of assigning an interval of additional metadata to propositional worlds and iterate the tpo of an agent using that structure.
-They define and discuss properties of operators for tpo-revision as well as relate their approach to other fields of research.
-This report on their paper aims to present parts of their work to a wider audience.
-An accompanying example is the main contribution to guide the discussion and visualise changes in the agent's state.
-The report's focus will be on the tpo-revision operators discussed in the primary paper and explicitly avoid the addition of strict preference hierarchies and relations to other research areas.
-The structure of the report will be as follows: Establish the context of the paper by presenting the research area of iterated belief revision and how it relates to other areas of artificial intelligence and philosophy.
-To create a shared understanding of notation and definitions section \ref{section:formal-background} will discuss formal background and other, previous, approaches to belief change.
-It will also introduce the main contribution of this report, an accompanying example demonstrating tpo-revision as described by Booth and Meyer.
-After building a foundation, section \ref{section:booth-and-meyer-tpo-revision-operators} and \ref{section:properties-of-bm-tpo-revision-operators} will present part of the work from the original paper 'How to Revise a Total Preorder' \cite{Booth2011}.
-Section \ref{section:booth-and-meyer-tpo-revision-operators} establishes and defines functions $\ast$, used to revise tpos.
-In section \ref{section:properties-of-bm-tpo-revision-operators} properties of these functions will be presented.
-To provide an outlook into the additional work done by Booth and Meyer, \ref{section:iterating-preceq-revision} will show their proposal of a concrete operator for tpo-revision.
-It includes several examples and adapted visualisations of the operator being applied in the context of the accompanying example.
-Finally, section \ref{section:conclusion} closes the report with a summary and commentary on Booth and Meyer's approach to iterated belief revision with interval orderings.
-
-\subsection{Research context}
 A core process for an intelligent agent dealing with uncertain knowledge is updating their worldview when new information becomes available, also called belief change.
@@
 % TODO: discussed in \cite{Katsuno1991} correct? was mentioned in intro of Admissible and Restrained Revision
-A common tool used to encode plausibility assumptions of an agent about possible worlds are total preorders (shortened as tpos) \cite{Booth2011}, discussed in \cite{Katsuno1991}.
-The primary article for this report, 'How to Revise a Total Preorder', researches how to model the change of these total preorders when new evidence becomes available.
+A common tool used to encode plausibility assumptions of an agent about possible worlds are total preorders (tpos) \cite{Booth2011}, discussed in \cite{Katsuno1991}.
+'How to Revise a Total Preorder', discusses how to model the change of these total preorders when new evidence becomes available.
 Being able to derive a new tpo from additional evidence is an approach to handling multiple revision steps.
-It therefor places the article in the field of iterated belief revision.
+It places the article in the field of iterated belief revision.
+
+To support iterated belief revision it is necessary to research how tpos can be changed to adapt to an agent's changing world view.
+Booth and Meyer suggest an approach based on the idea of assigning an interval of additional metadata to propositional worlds and iterate the tpo of an agent using that structure.
+They define and discuss properties of operators for tpo-revision as well as relate their approach to other fields of research.
+This synopsis presents parts of their work to a wider audience.
+An accompanying example will guide the discussion and visualise changes in the agent's state.
+The focus will be on the tpo-revision operators discussed in the primary paper and explicitly avoid the addition of strict preference hierarchies and relations to other research areas.
+
+The structure of the synopsis will be as follows: Establish the context of the paper by presenting the research area of iterated belief revision and how it relates to other areas of artificial intelligence and philosophy.
+To create a shared understanding of notation and definitions section \ref{section:formal-background} will discuss formal background and other, previous, approaches to belief change.
+It will also introduce the main contribution of this synopsis, an accompanying example demonstrating tpo-revision as described by Booth and Meyer.
+After building a foundation, section \ref{section:booth-and-meyer-tpo-revision-operators} and \ref{section:properties-of-bm-tpo-revision-operators} will present part of the work from the original paper 'How to Revise a Total Preorder' \cite{Booth2011}.
+Section \ref{section:booth-and-meyer-tpo-revision-operators} establishes and defines functions $\ast$, used to revise tpos.
+In section \ref{section:properties-of-bm-tpo-revision-operators} properties of these functions will be presented.
+To provide an outlook into the additional work done by Booth and Meyer, \ref{section:iterating-preceq-revision} will show their proposal of a concrete operator for tpo-revision.
+It includes several examples and adapted visualisations of the operator being applied in the context of the accompanying example.
+Finally, section \ref{section:conclusion} closes the synopsis with a summary and commentary on Booth and Meyer's approach to iterated belief revision with interval orderings.
 
@@
 \subsection{Propositional Logic} % Aussagenlogik
-Notation follows as used in \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables.
+The following notation is used to align with \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables.
 Lower case greek letters represent formulae in $L$ and $\top$, $\bot$ representing tautology and contradiction respectively.
@@
         \end{tabular}
-        \caption{Visualising a tpo as a linearly ordered set of ranks as done in \cite{Booth2006}}
+        \caption{Visualising a tpo as a linearly ordered set of ranks, as done in \cite{Booth2006}}.
         \label{tab:visualising-a-tpo-example}
@@
 \subsection{Belief sets and epistemic states}
+% TODO explain contraction, revision, expansion? Gardenfors correct? read!
 A belief set is the deductively closed set of propositions an agent accepts as true at any given point in time \cite{Ferme2011}.
-AGM theory \cite{Alchourron1985} defines postulates for belief sets and their contraction, expansion or revision with new evidence.
+Alchourrón, Gärdenfors, and Makinson (AGM theory, \cite{Alchourron1985}) define postulates for belief sets and their contraction, expansion or revision with new evidence.
 In the process of belief revision an agent keeps their set of beliefs consistent while incorporating new information, even if it is inconsistent with the current belief set \cite{Gaerdenfors1984}.
-% TODO explain contraction, revision, expansion? Gardenfors correct? read!
-
 Darwiche and Pearl \cite{Darwiche1997} argue that working with belief sets is not expressive enough for satisfying results in iterated belief revision.
@@
 While the AGM postulates define restrictions on revising propositional beliefs (a core one being the principle of minimal change), they don't restrict changes in conditional beliefs.
-In their paper Darwiche and Pearl argue for epistemic states, abstract entities that contain all information an agent needs for their reasoning.
+In their paper, Darwiche and Pearl argue for epistemic states, abstract entities that contain all information an agent needs for their reasoning.
 This includes especially their strategy for belief revision in addition to their belief set.
@@
 
-\subsection{DP-AGM postulates}
+\subsection{Belief revision postulates}
 \label{chapter:dp-agm-postulates}
-The postulates first introduced by \cite{Alchourron1985} and reformulated for iterated belief revision on epistemic states by \cite{Darwiche1997} are repeated here.
+The postulates first introduced by \cite{Alchourron1985} and reformulated for iterated belief revision on epistemic states by \cite{Darwiche1997} follow.
 $\mathbb{E}$ denotes an epistemic state, $B(\mathbb{E})$ it's associated belief set, $B(\mathbb{E}) + \alpha$ the expansion of $B(\mathbb{E})$ by $\alpha$.
@@
 
-To guarantee the ability to extract unique belief sets from epistemic states after a revision by $\alpha$, Booth and Meyer \cite{Booth2011} modify these postulates by requiring consistent epistemic inputs.
-That requirement means dropping \ref{E6} and considering only \ref{E1}-\ref{E5} and \ref{E7}-\ref{E8} as DP-AGM.
+To guarantee the ability to extract unique belief sets from epistemic states after a revision by $\alpha$, Booth and Meyer \cite{Booth2011} require consistent epistemic inputs.
+That means dropping \ref{E6} and considering only \ref{E1}-\ref{E5} and \ref{E7}-\ref{E8} for their belief revision postulates, named DP-AGM.
 
 While DP-AGM define the most plausible worlds after a revision by $\alpha$ (as $min(\alpha, \leq_{\mathbb{E}})$), Darwiche and Pearl also define postulates that restrict the rest of the new ordering.
-Because the focus of this report is on the revision of tpos, the semantic (i.e.
+As this synopsis focusses on the revision of tpos, the semantic (i.e.
 in terms of how the ordering of worlds undergoes change) versions are shown here.
@@
 
+% TODO: we probably need to make clearer that this is where the paper starts, caro thought it should be in 2.x
 \section{Additional metadata for tpo revision}
@@
 Based on DP-AGM and the postulates $(CR1)$-$(CR4)$, Booth and Meyer assume a fixed tpo $\leq$ over a set of worlds $W$ that acts as a plausibility ordering.
-The goal of the paper is the discussion of functions $\ast$ that return a new ordering $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
+The goal of their paper is the discussion of functions $\ast$ that return a new ordering $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
 These functions are referred to as revision operators for $\leq$.
@@
 This new structure is denoted as $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$.
-In this notation a world $w \in W$ is represented twice: When new evidence $\alpha$ arrives that makes $w$ more plausible (because $w \in [\alpha]$) the agent can assume it's positive representation as $w^{+} \in W^{\pm}$.
-In contrast if the new evidence makes $w$ less plausible ($w \notin [\alpha]$) then the negative representation $w^{-} \in W^{\pm}$ is the agent's view of $w$.
-In their paper Booth and Meyer call the pair $(w^{+}, w^{-})$ the positive/negative representation of the world $w$.
+In this notation a world $w \in W$ is represented twice: When new evidence $\alpha$ arrives that makes $w$ more plausible (because $w \in [\alpha]$), the agent can assume it's positive representation as $w^{+} \in W^{\pm}$.
+In contrast, if the new evidence makes $w$ less plausible ($w \notin [\alpha]$), then the negative representation $w^{-} \in W^{\pm}$ is the agent's view of $w$.
+Booth and Meyer call the pair $(w^{+}, w^{-})$ the positive/negative representation of the world $w$.
 They are an abstract interval, representing metadata about plausibility assumptions about $w$.
@@
     \label{example:example-stick}
-    Recall that tpos can be equivalently thought of as a linearly ordered set of ranks (Example \ref{example:example-introduction}, page \pageref{example:example-introduction}).
-Therefor a tpo over $W$ can be visualised by ordering every $w \in W$ in a table of ranks (table \ref{tab:visualising-a-tpo-example}).
+    Recall that tpos can be equivalently thought of as a linearly ordered set of ranks (Example \ref{example:example-introduction}).
+A tpo over $W$ can be visualised by ordering every $w \in W$ in a table of ranks (table \ref{tab:visualising-a-tpo-example}).
 To visualise the interval ordering introduced by $\preceq$, Booth and Meyer use a "stick" with the endpoints defined as $w^{+}$/$w^{-}$ respectively.
@@
 
-   The worlds on lower ranks (more on the left) are preferred and therefor assumed to be more plausible.
-Here for example $x_{1}^{+} \prec x_{3}^{+}$ and $x_{1}^{-} \sim x_{4}^{+}$ Note that while all sticks have the same length in this example that is not required.
+   The worlds on lower ranks (more on the left) are preferred and assumed to be more plausible.
+Here for example $x_{1}^{+} \prec x_{3}^{+}$ and $x_{1}^{-} \sim x_{4}^{+}$ Note that, while all sticks have the same length in this example, that is not required.
 \end{example}
@@
 \begin{definition}[$\leq$-faithful tpo over $W^{\pm}$ taken directly from \cite{Booth2011}]
-\label{definition:faithful-tpo}Let $\preceq \in W^{\pm} \times W^{\pm}$. If $\preceq$ satisfies \ref{PREQ1}-\ref{PREQ4} we say $\preceq$ is a $\leq$-faithful tpo (over $W^{\pm}$).
+\label{definition:faithful-tpo}Let $\preceq \in W^{\pm} \times W^{\pm}$. If $\preceq$ satisfies \ref{PREQ1}-\ref{PREQ4}, we say $\preceq$ is a $\leq$-faithful tpo (over $W^{\pm}$).
 \end{definition}
@@
 Because of \ref{PREQ2} and \ref{PREQ3}, it is sufficient to only include $\preceq$ in the epistemic state.
-The tpo $\leq$ over $W$ can be determined from $\preceq$ by restricting to only $\{ x^{+} \mid x \in W\}$ or $\{ x^{-} \mid x \in W\}$ respectively.
+The tpo $\leq$ over $W$ can be determined from $\preceq$ by restricting to only $\{ x^{+} \mid x \in W\}$ or $\{ x^{-} \mid x \in W\}$, respectively.
 
@@
 
-    While \ref{PREQ1} and \ref{PREQ4} are satisfied, $\preceq$ is not a $\leq$-faithful tpo: Due to \ref{PREQ2} and $x_{1}^{+} \prec x_{2}^{+}$ follows $x_{1} < x_{2}$.
+    \ref{PREQ1} and \ref{PREQ4} are satisfied but $\preceq$ is not a $\leq$-faithful tpo: From \ref{PREQ2} and $x_{1}^{+} \prec x_{2}^{+}$ follows $x_{1} < x_{2}$.
 That means \ref{PREQ3} can not hold as $x_{2}^{-} \prec x_{1}^{-}$ which would require $x_{2} < x_{3}$ to be true.
 
-    As demonstrated here, while the "sticks" do not need to be the same size for all worlds (they just must exist due to \ref{PREQ4}), they need to be the same size for worlds that share a rank for their corresponding representations.
+    As demonstrated here, the "sticks" do not need to be the same size for all worlds (they just must exist due to \ref{PREQ4}).
+They need to be the same size for worlds that share a rank for their corresponding representations.
 They can not "cover" other sticks completely to continue to satisfy \ref{PREQ2} and \ref{PREQ3}.
@@
 \label{section:booth-and-meyer-tpo-revision-operators}
-Booth and Meyer \cite{Booth2011} aim to discuss tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
+Booth and Meyer \cite{Booth2011} discuss tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
 To do so they define how to use the additional information from a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ to create a revision operator $\ast_{\preceq}$ (from now on referred to as BM tpo-revision operators).
@@
 Intuitively, new evidence $\alpha$ makes worlds that satisfy $\alpha$ more plausible and worlds that do not satisfy $\alpha$ less plausible.
-Therefor the agent associates worlds $x \in [\alpha]$ with their positive representation $x^{+}$ and worlds $x \in [\neg\alpha]$ with their negative representation $x^{-}$.
+The agent associates worlds $x \in [\alpha]$ with their positive representation $x^{+}$ and worlds $x \in [\neg\alpha]$ with their negative representation $x^{-}$.
 
@@
     \label{example:example-updated-tpo}
-    Reconsider the $\leq$-faithful tpo $\preceq$ from example \ref{example:example-stick} (page \pageref{example:example-stick}).
+    Reconsider the $\leq$-faithful tpo $\preceq$ from example \ref{example:example-stick}.
 When a new piece of evidence $\alpha$ has to be considered, each world gets mapped to one end of the interval assigned to it, depending on if it is an $\alpha$-world or not.
@@
 The most plausible worlds in the new epistemic state $\mathbb{E}$, $min(\top, \leq_{\alpha}^{\ast})$, include the $[\neg\alpha]$-worlds $x_{1}$ and $x_{2}$.
-Therefor $Th(min(\top, \leq_{\alpha}^{\ast}))$ does not include the new evidence $\alpha$.
+$Th(min(\top, \leq_{\alpha}^{\ast}))$ does not include the new evidence $\alpha$.
 
@@
 %info here: \cite{Booth2006a}
+% see also http://ceur-ws.org/Vol-2445/paper_2.pdf
 
@@
 These properties define tpo-revision with one input sentence.
-Booth and Meyer relate them to the AGM postulates for belief set revison \cite{Alchourron1985} as basic postulates for tpo-revision \cite{Booth2011}.
+Booth and Meyer relate them to the AGM postulates for belief set revision \cite{Alchourron1985} as basic postulates for tpo-revision \cite{Booth2011}.
 
@@
 Otherwise, as Booth and Meyer put it, the problem has just "re-emerged 'one level up'" \cite{Booth2011}.
-In their paper, they discuss strict preference hierarchies (or SPHs), an equivalent structure to $\preceq$, denoted as $\$$, their properties and how to revise them.
-
-This report focuses on revision of tpos itself.
-As an outlook, only the revision of a $\leq$-faithful tpo $\preceq$ using the example operator from the original paper is included here.
-For a more detailed explanation of the operator, SPHs or their properties see \cite{Booth2011}.
+They discuss strict preference hierarchies (SPHs), an equivalent structure to $\preceq$, denoted as $\$$, their properties and how to revise them.
+
+To focus on the revision of tpos itself, only the revision of a $\leq$-faithful tpo $\preceq$ using the example operator from the original paper is included here.
+For a more detailed explanation of the operator, SPHs or their properties refer to \cite{Booth2011}.
 
@@
 The smaller $p(x^{\epsilon})$ is, the more plausible the world is.
-The interval $(x^{+}, x^{-})$, represents a world $x \in W$ using it's representations $x^{+}, x^{-} \in W^{\pm}$.
+The interval $(x^{+}, x^{-})$, represents a world $x \in W$ using the representations $x^{+}, x^{-} \in W^{\pm}$.
 For revision on the basis of $p$, it becomes an interval of real numbers $(p(x^{+}), p(x^{-}))$ with length $a$.
@@
 
-By this definition the interval representing $\alpha$-worlds stay the same as $(p(x^{+}), p(x^{-}))$ while intervals of $\neg\alpha$-worlds become $(p(x^{-}), p(x^{-}) + a)$.
+By this definition, the interval representing $\alpha$-worlds stay the same as $(p(x^{+}), p(x^{-}))$ while intervals of $\neg\alpha$-worlds become $(p(x^{-}), p(x^{-}) + a)$.
 
@@
 
-    For the first step, a function $p$ is chosen so that $\preceq_{p} = \preceq$ and the intervals for all worlds $x \in W^{\pm}$ can be defined using $p$.
+    As first step, a function $p$ is chosen so that $\preceq_{p} = \preceq$ and the intervals for all worlds $x \in W^{\pm}$ can be defined using $p$.
 
@@
     \label{example:example-preceq-revised-alien}
-    For an example that demonstrates the impact the revision of $\preceq$ has on the acceptance of conditional beliefs consider again the courtroom example \ref{example:example-introduction}.
+    For an example that demonstrates the impact the revision of $\preceq$ has on the acceptance of conditional beliefs, consider again the courtroom example \ref{example:example-introduction}.
 The fact that the victim is an alien ($r$ true) seems very unlikely, which is modelled by the gap between $[r]$-worlds and $[\neg r]$-worlds.
 
-    When evidence $\alpha = r$ arrives, there seems to be little change in the epistemic state of the judge: $\leq_{\alpha}^{\ast}$ is unchanged as even considering the negative representations of $[\neg r]$-worlds they rank lower than $[r]$-worlds.
-An unchanged tpo $\leq_{\alpha}^{\ast}$ also means the believe set $B(\mathbb{E})$ stays the same and does not include $r$ (a property of non-prioritised revision as described in section \ref{section:non-prioritised-revision}).
+    When evidence $\alpha = r$ arrives, there seems to be little change in the epistemic state of the judge: $\leq_{\alpha}^{\ast}$ is unchanged, as even considering the negative representations of $[\neg r]$-worlds, they rank lower than $[r]$-worlds.
+An unchanged tpo $\leq_{\alpha}^{\ast}$ also means the believe set $B(\mathbb{E})$ stays the same and does not include $r$ (a property of non-prioritised revision as described in \ref{section:non-prioritised-revision}).
 
@@
     % TODO tpo alpha as beta is unlucky because ast has a different meaning already, also change in figure 8 caption
-    Notice how now the gap between $[\neg r]$- and $[r]$-worlds has closed.
+    Notice how the gap between $[\neg r]$- and $[r]$-worlds has closed.
 After revising $\preceq_{p \ast \alpha}$ for a second piece of evidence $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$ ("the murderer was either John or Mary, not both") the new tpo $\leq_{\alpha \ast \beta}^{\ast}$ can be read from the filled dots in figure \ref{fig:example-preceq-revised-alien2}.
@@
 For the initial tpo $\leq$ there was no possible evidence that would change the plausibility ordering between worlds where the victim is an alien and worlds where they are not.
-That was reflected by the new tpo $\leq_{\alpha}^{\ast}$ that, even with direct evidence for alien life, did not change the judges plausibility orderings.
+That was reflected by the new tpo $\leq_{\alpha}^{\ast}$ that, even after direct evidence for alien life, did not change the judges plausibility orderings.
 But because of the revision of $\preceq$ to $\preceq_{p \ast \alpha}$, the evidence $\alpha$ changed the acceptance of the judge to belief we are not alone in the universe.
@@
 
-\section{Conclusion}
+\section{Final remarks}
 \label{section:conclusion}
-The featured paper 'How to Revise a Total Preorder' by Booth and Meyer \cite{Booth2011} is an expansive work on using interval orderings for belief change.
-This report focused on presenting the research context and previous work in iterated belief change as well as the concrete tpo-revision based on the additional structure of $\leq$-faithful tpos.
+The featured paper 'How to Revise a Total Preorder' by Booth and Meyer \cite{Booth2011} is a work on using interval orderings for belief change.
+This synopsis focused on presenting the research context and previous work in iterated belief change as well as the concrete tpo-revision based on the additional structure of $\leq$-faithful tpos.
 A consistent example including a trial situation (adapted from \cite{Darwiche1997} and \cite{Booth2011}) was used to accompany the discussion of the paper.
-In addition to the provided example the report also introduced an adapted visualisation for $\leq$-faithful tpo-revision based on the stick visualisation used by Booth and Meyer themselves.
+In addition to the provided example the synopsis also introduced an adapted visualisation for $\leq$-faithful tpo-revision based on the stick visualisation used by Booth and Meyer themselves.
 
@@
 
-\newpage
-
-\section*{Erklärung}
-Ich erkläre, dass ich die schriftliche Ausarbeitung zum Seminar selbstständig und ohne unzulässige Inanspruchnahme Dritter verfasst habe.
-Ich habe dabei nur die angegebenen Quellen und Hilfsmittel verwendet und die aus diesen wörtlich oder sinngemäß entnommenen Stellen als solche kenntlich gemacht.
-Die Versicherung selbstständiger Arbeit gilt auch für enthaltene Zeichnungen, Skizzen oder graphische Darstellungen.
-Die Ausarbeitung wurde bisher in gleicher oder Ähnlicher Form weder derselben noch einer anderen Prüfungsbehörde vorgelegt und auch nicht veröffentlicht.
-Mit der Abgabe der elektronischen Fassung der endgültigen Version der Ausarbeitung nehme ich zur Kenntnis, dass diese mit Hilfe eines Plagiatserkennungsdienstes auf enthaltene Plagiate geprüft werden kann und ausschließlich für Prüfungszwecke gespeichert wird.
-
 \end{document}

### 2021-01-12 paper/1901_3230880_philip_heltweg.tex
improvement: second round of feedback

@@
 A common tool used to encode plausibility assumptions of an agent about possible worlds are total preorders (tpos) \cite{Booth2011}, discussed in \cite{Katsuno1991}.
-'How to Revise a Total Preorder', discusses how to model the change of these total preorders when new evidence becomes available.
+In 'How to Revise a Total Preorder', Booth and Meyer describe how to model the change of these total preorders when new evidence becomes available.
 Being able to derive a new tpo from additional evidence is an approach to handling multiple revision steps.
-It places the article in the field of iterated belief revision.
+It therefore places the article in the field of iterated belief revision.
 
@@
 They define and discuss properties of operators for tpo-revision as well as relate their approach to other fields of research.
-This synopsis presents parts of their work to a wider audience.
+This synopsis presents parts of their work to a broader audience.
 An accompanying example will guide the discussion and visualise changes in the agent's state.
@@
 \subsection{Propositional Logic} % Aussagenlogik
-The following notation is used to align with \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables.
+The following notation will be used, as proposed by \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables.
 Lower case greek letters represent formulae in $L$ and $\top$, $\bot$ representing tautology and contradiction respectively.
@@
 \label{chapter:dp-agm-postulates}
-The postulates first introduced by \cite{Alchourron1985} and reformulated for iterated belief revision on epistemic states by \cite{Darwiche1997} follow.
+The postulates first introduced by \cite{Alchourron1985} and reformulated for iterated belief revision on epistemic states by \cite{Darwiche1997} which are further used in this text are presented here.
 $\mathbb{E}$ denotes an epistemic state, $B(\mathbb{E})$ it's associated belief set, $B(\mathbb{E}) + \alpha$ the expansion of $B(\mathbb{E})$ by $\alpha$.
@@
 While DP-AGM define the most plausible worlds after a revision by $\alpha$ (as $min(\alpha, \leq_{\mathbb{E}})$), Darwiche and Pearl also define postulates that restrict the rest of the new ordering.
-As this synopsis focusses on the revision of tpos, the semantic (i.e.
+Since this synopsis only focused on the revision of tpos, the semantic (i.e.
 in terms of how the ordering of worlds undergoes change) versions are shown here.
@@
     Recall that tpos can be equivalently thought of as a linearly ordered set of ranks (Example \ref{example:example-introduction}).
-A tpo over $W$ can be visualised by ordering every $w \in W$ in a table of ranks (table \ref{tab:visualising-a-tpo-example}).
+Therefore a tpo over $W$ can be visualised by ordering every $w \in W$ in a table of ranks (table \ref{tab:visualising-a-tpo-example}).
 To visualise the interval ordering introduced by $\preceq$, Booth and Meyer use a "stick" with the endpoints defined as $w^{+}$/$w^{-}$ respectively.
@@
    The worlds on lower ranks (more on the left) are preferred and assumed to be more plausible.
-Here for example $x_{1}^{+} \prec x_{3}^{+}$ and $x_{1}^{-} \sim x_{4}^{+}$ Note that, while all sticks have the same length in this example, that is not required.
+Here for example $x_{1}^{+} \prec x_{3}^{+}$ and $x_{1}^{-} \sim x_{4}^{+}$ Note that, even though all sticks have the same length in this example, that is not required.
 \end{example}
@@
 
-    \ref{PREQ1} and \ref{PREQ4} are satisfied but $\preceq$ is not a $\leq$-faithful tpo: From \ref{PREQ2} and $x_{1}^{+} \prec x_{2}^{+}$ follows $x_{1} < x_{2}$.
+    Even though \ref{PREQ1} and \ref{PREQ4} are satisfied, $\preceq$ is not a $\leq$-faithful tpo: From \ref{PREQ2} and $x_{1}^{+} \prec x_{2}^{+}$ follows $x_{1} < x_{2}$.
 That means \ref{PREQ3} can not hold as $x_{2}^{-} \prec x_{1}^{-}$ which would require $x_{2} < x_{3}$ to be true.
 
-    As demonstrated here, the "sticks" do not need to be the same size for all worlds (they just must exist due to \ref{PREQ4}).
-They need to be the same size for worlds that share a rank for their corresponding representations.
-They can not "cover" other sticks completely to continue to satisfy \ref{PREQ2} and \ref{PREQ3}.
+    As demonstrated here, even though the "sticks" do not need to be the same size for all worlds (they just must exist due to \ref{PREQ4}), they need to be the same size for worlds that share a rank for their corresponding representations.
+They can not overlap other sticks completely to continue to satisfy \ref{PREQ2} and \ref{PREQ3}.
 \end{example}
@@
 \label{section:booth-and-meyer-tpo-revision-operators}
-Booth and Meyer \cite{Booth2011} discuss tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
+Booth and Meyer \cite{Booth2011} discussed tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
 To do so they define how to use the additional information from a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ to create a revision operator $\ast_{\preceq}$ (from now on referred to as BM tpo-revision operators).
@@
 Intuitively, new evidence $\alpha$ makes worlds that satisfy $\alpha$ more plausible and worlds that do not satisfy $\alpha$ less plausible.
-The agent associates worlds $x \in [\alpha]$ with their positive representation $x^{+}$ and worlds $x \in [\neg\alpha]$ with their negative representation $x^{-}$.
+Therefore the agent associates worlds $x \in [\alpha]$ with their positive representation $x^{+}$ and worlds $x \in [\neg\alpha]$ with their negative representation $x^{-}$.
 
@@
 The most plausible worlds in the new epistemic state $\mathbb{E}$, $min(\top, \leq_{\alpha}^{\ast})$, include the $[\neg\alpha]$-worlds $x_{1}$ and $x_{2}$.
-$Th(min(\top, \leq_{\alpha}^{\ast}))$ does not include the new evidence $\alpha$.
+Therefore $Th(min(\top, \leq_{\alpha}^{\ast}))$ does not include the new evidence $\alpha$.
 
@@
 If $\alpha$ makes $x$ more plausible ($x \in [\alpha]$) and $y$ less plausible ($y \in [\neg\alpha]$) then after revision $x$ should be considered strictly more plausible than $y$.
-This rule was not only proposed by Booth and Meyer \cite{Booth2006a} but also Jin und Thielscher in \cite{Jin2007} (as the postulate of independence).
+This rule was not only proposed by Booth and Meyer \cite{Booth2006a} but also by Jin und Thielscher in \cite{Jin2007} (as the postulate of independence).
 
@@
 Otherwise, as Booth and Meyer put it, the problem has just "re-emerged 'one level up'" \cite{Booth2011}.
-They discuss strict preference hierarchies (SPHs), an equivalent structure to $\preceq$, denoted as $\$$, their properties and how to revise them.
-
-To focus on the revision of tpos itself, only the revision of a $\leq$-faithful tpo $\preceq$ using the example operator from the original paper is included here.
+In their study, they discuss strict preference hierarchies (SPHs), an equivalent structure to $\preceq$, denoted as $\$$, their properties and how to revise them.
+
+Since this synopsis focuses on the revision of tpos itself, only the revision of a $\leq$-faithful tpo $\preceq$ using the example operator from the original paper is included here.
 For a more detailed explanation of the operator, SPHs or their properties refer to \cite{Booth2011}.
@@
 The smaller $p(x^{\epsilon})$ is, the more plausible the world is.
-The interval $(x^{+}, x^{-})$, represents a world $x \in W$ using the representations $x^{+}, x^{-} \in W^{\pm}$.
+The interval $(x^{+}, x^{-})$, represents a world $x \in W$ using its representations $x^{+}, x^{-} \in W^{\pm}$.
 For revision on the basis of $p$, it becomes an interval of real numbers $(p(x^{+}), p(x^{-}))$ with length $a$.
@@
 
-By this definition, the interval representing $\alpha$-worlds stay the same as $(p(x^{+}), p(x^{-}))$ while intervals of $\neg\alpha$-worlds become $(p(x^{-}), p(x^{-}) + a)$.
+By this definition, the interval representing $\alpha$-worlds stays the same as $(p(x^{+}), p(x^{-}))$ while intervals of $\neg\alpha$-worlds become $(p(x^{-}), p(x^{-}) + a)$.
 
@@
     When evidence $\alpha = r$ arrives, there seems to be little change in the epistemic state of the judge: $\leq_{\alpha}^{\ast}$ is unchanged, as even considering the negative representations of $[\neg r]$-worlds, they rank lower than $[r]$-worlds.
-An unchanged tpo $\leq_{\alpha}^{\ast}$ also means the believe set $B(\mathbb{E})$ stays the same and does not include $r$ (a property of non-prioritised revision as described in \ref{section:non-prioritised-revision}).
+An unchanged tpo $\leq_{\alpha}^{\ast}$ also means the believe set $B(\mathbb{E})$ stays the same and does not include $r$ (a property of non-prioritised revision as described in item \ref{section:non-prioritised-revision}).
 
@@
     % TODO tpo alpha as beta is unlucky because ast has a different meaning already, also change in figure 8 caption
-    Notice how the gap between $[\neg r]$- and $[r]$-worlds has closed.
+    Notice how the gap between $[\neg r]$- and $[r]$-worlds has now closed.
 After revising $\preceq_{p \ast \alpha}$ for a second piece of evidence $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$ ("the murderer was either John or Mary, not both") the new tpo $\leq_{\alpha \ast \beta}^{\ast}$ can be read from the filled dots in figure \ref{fig:example-preceq-revised-alien2}.
@@
 \label{section:conclusion}
-The featured paper 'How to Revise a Total Preorder' by Booth and Meyer \cite{Booth2011} is a work on using interval orderings for belief change.
+The featured paper 'How to Revise a Total Preorder' by Booth and Meyer \cite{Booth2011} is a comprehensive work on using interval orderings for belief change.
 This synopsis focused on presenting the research context and previous work in iterated belief change as well as the concrete tpo-revision based on the additional structure of $\leq$-faithful tpos.
@@
 % TODO: this critique example seems very weak
-Considering quality and impact of new evidence also creates the question if \ref{AST6} and \ref{AST7} (properties of BM tpo-revision operators, section \ref{section:properties-of-bm-tpo-revision-operators}) should be weakened.
+Considering the quality and impact of new evidence also creates the question if \ref{AST6} and \ref{AST7} (properties of BM tpo-revision operators, section \ref{section:properties-of-bm-tpo-revision-operators}) should be weakened.
 Especially high quality evidence for a very unlikely type of world might change an agents plausibility ordering, while low quality evidence that is very expected might not.
@@
 Semantically a human agent would assume all worlds in which Mary is the murderer to be highly unlikely due to how far fetched the acceptance of the victim being an alien is.
-How to solve this apparent contradiction by modelling different types and strengths of evidence could be a future area of research.
+Further research is required to solve this apparent contradiction by modelling different types and strengths of evidence.
 

### 2021-01-12 paper/1901_3230880_philip_heltweg.tex
fix: fixed todolist

@@
   \vskip 30 pt
-  \LARGE Synopsis of 'How to Revise a Total Preorder' \cite{Booth2011} for seminar 1901 - 'Representation and processing of uncertain knowledge with logic-based methods' \par
+  \LARGE Synopsis of "How to Revise a Total Preorder" \cite{Booth2011} for seminar 1901 - "Representation and processing of uncertain knowledge with logic-based methods" \par
   \vskip 1.5em
@@
 
-% TODO: '' for quotes should be ""? Or consistent at least
-% TODO: references align: Richard Booth, sometimes R Booth
 \title{Of judges, aliens and total preorders}
@@
 Total preorders are a common tool to model plausibility orderings over possible worlds in the research field of belief change.
-In their paper 'How to Revise a Total Preorder', Booth and Meyer present an approach to revising preorders for iterated belief revision.
+In their paper "How to Revise a Total Preorder", Booth and Meyer present an approach to revising preorders for iterated belief revision.
 Their operator is based on assigning abstract intervals of plausibility to worlds depending on new evidence supporting them or not.
@@
 
-% TODO: consider not having a table of contents
+% TODO: QUESTION: consider not having a table of contents
 \tableofcontents
@@
 A common tool used to encode plausibility assumptions of an agent about possible worlds are total preorders (tpos) \cite{Booth2011}, discussed in \cite{Katsuno1991}.
-In 'How to Revise a Total Preorder', Booth and Meyer describe how to model the change of these total preorders when new evidence becomes available.
+In "How to Revise a Total Preorder", Booth and Meyer describe how to model the change of these total preorders when new evidence becomes available.
 Being able to derive a new tpo from additional evidence is an approach to handling multiple revision steps.
@@
 It will also introduce the main contribution of this synopsis, an accompanying example demonstrating tpo-revision as described by Booth and Meyer.
-After building a foundation, section \ref{section:booth-and-meyer-tpo-revision-operators} and \ref{section:properties-of-bm-tpo-revision-operators} will present part of the work from the original paper 'How to Revise a Total Preorder' \cite{Booth2011}.
+After building a foundation, section \ref{section:booth-and-meyer-tpo-revision-operators} and \ref{section:properties-of-bm-tpo-revision-operators} will present part of the work from the original paper "How to Revise a Total Preorder" \cite{Booth2011}.
 Section \ref{section:booth-and-meyer-tpo-revision-operators} establishes and defines functions $\ast$, used to revise tpos.
@@
 For any set of worlds $S \subseteq W$ of worlds, $Th(S)$ is the set of sentences true in all worlds in $S$.
-% TODO Th(S) not needed?
 
@@
 \subsection{Belief sets and epistemic states}
-% TODO explain contraction, revision, expansion? Gardenfors correct? read!
+% TODO QUESTION: explain contraction, revision, expansion?
+% TODO: Gardenfors correct? read!
 A belief set is the deductively closed set of propositions an agent accepts as true at any given point in time \cite{Ferme2011}.
@@
 
-% TODO: do we need to discuss this in ore detail? faithful assignment here:
+% TODO QUESTION: do we need to discuss this in ore detail? faithful assignment here:
 %Katsuno and Mendelzon [17] propose that an epistemic state Ψ
@@
 
-% TODO: we probably need to make clearer that this is where the paper starts, caro thought it should be in 2.x
+% TODO QUESTION: we probably need to make clearer that this is where the paper starts, caro thought it should be in 2.x
 \section{Additional metadata for tpo revision}
-\label{section:additional-metadata-for-tpo-revision}
 \subsection{Enriching epistemic states}
@@
 
-%TODO question: the text sounds like the properties are supposed by BM/they define them but they are also proved?! or does this mean proved for their approach but could be done differently?
+%TODO QUESTION: the text sounds like the properties are supposed by BM/they define them but they are also proved?! or does this mean proved for their approach but could be done differently?
 %We propose that if x is not more
@@
 
-% TODO: pull these out? Basic postulates for tpo revision in one subsection, additional ones "supplementary rationality properties" as second section?
 These properties define tpo-revision with one input sentence.
@@
 \label{section:conclusion}
-The featured paper 'How to Revise a Total Preorder' by Booth and Meyer \cite{Booth2011} is a comprehensive work on using interval orderings for belief change.
+The featured paper "How to Revise a Total Preorder" by Booth and Meyer \cite{Booth2011} is a comprehensive work on using interval orderings for belief change.
 This synopsis focused on presenting the research context and previous work in iterated belief change as well as the concrete tpo-revision based on the additional structure of $\leq$-faithful tpos.
@@
 The idea to define an interval of plausibility for worlds depending on if evidence supports them or not does make intuitive sense.
-An view largely missing from the paper is the discussion of the different impact and quality of new information itself.
-
-% TODO: question, idempotent correct?
+A view largely missing from the paper is the discussion of the different impact and quality of new information itself.
+
+% TODO: QUESTION, idempotent correct?
 The proposed, concrete operator for the revision of $\leq$-faithful tpos allows for multiple revisions by the same evidence $\alpha$ or semantically equivalent evidence $\beta \equiv \alpha$.
@@
 
-% TODO: this critique example seems very weak
+% TODO QUESTION: this critique example seems very weak
 Considering the quality and impact of new evidence also creates the question if \ref{AST6} and \ref{AST7} (properties of BM tpo-revision operators, section \ref{section:properties-of-bm-tpo-revision-operators}) should be weakened.

### 2021-01-29 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: beamer setup

%%
% Please see https://bitbucket.org/rivanvx/beamer/wiki/Home for obtaining beamer.
%%
\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}

\usefonttheme{professionalfonts}
\usetheme{Madrid}
\usecolortheme{orchid}

\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents[currentsection]
  \end{frame}
}

\begin{document}
\title{Of judges, aliens and total preorders}
\author[Heltweg, Philip]{Heltweg, Philip\\pheltweg@gmail.com}
\institute{University of Hagen}
\date{\today}

\frame{\titlepage}

\begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents
\end{frame}

\section{Example}

\begin{frame}
    \frametitle{Sample frame title}
    This is a text in the first frame. This is a text in the first frame. This is a text in the first frame.
\end{frame}

\begin{frame}
\frametitle{Sample frame title}

In this slide, some important text will be
\alert{highlighted} because it's important.
Please, don't abuse it.

\begin{block}{Remark}
Sample text
\end{block}

\begin{alertblock}{Important theorem}
Sample text in red box
\end{alertblock}

\begin{examples}
Sample text in green box. The title of the block is ``Examples".
\end{examples}
\end{frame}

\section{More examples}

\begin{frame}
\frametitle{Two-column slide}

\begin{columns}

\column{0.5\textwidth}
This is a text in first column.
$$E=mc^2$$
\begin{itemize}
\item First item
\item Second item
\end{itemize}

\column{0.5\textwidth}
This text will be in the second column
and on a second tought this is a nice looking
layout in some cases.
\end{columns}
\end{frame}

\end{document}

### 2021-02-01 paper/1901_3230880_philip_heltweg.tex
feat: beamer setup
fix: added advisor feedback

@@
 \usepackage{float}
+\usepackage{stmaryrd}
 
@@
 \newtheorem{theorem}{Theorem}
+
+\newcommand{\modelsOf}[1]{\llbracket #1 \rrbracket}
 
@@
 Research in this area discusses appropriate formalisations of agent state and constrains on individual operators or families of operators.
-Depending on if the suggested operator handles only one new evidence or multiple new evidences, the approaches are called one-step or iterated belief revision.
+Depending on if the suggested operator handles only one new evidence or consecutive evidence, the approaches are called one-step or iterated belief revision.
 
@@
 Lower case greek letters represent formulae in $L$ and $\top$, $\bot$ representing tautology and contradiction respectively.
-$\vdash$ denotes classical logical consequence, $\equiv$ classical logical equivalence.
+$\models$ denotes classical logical consequence, $\equiv$ classical logical equivalence.
 $Cn$ is used to denote the deductive closure of a formula or set of formulae in $L$.
@@
 $W$ is the set of propositional worlds (also called propositional interpretations in classical logic \cite{Kai2020}).
-Given a formula $\alpha \in L$, the set of worlds that satisfy $\alpha$ is denoted by $[\alpha]$.
+Given a formula $\alpha \in L$, the set of worlds that satisfy $\alpha$ is denoted by $\modelsOf{\alpha}$.
 
@@
 For notation let $min(\alpha, \leq_{\mathbb{E}})$ denote the set of minimal models for the propositional formula $\alpha$ under $\leq_{\mathbb{E}}$.
-Then $[B(\mathbb{E})] = min(\top, \leq_{\mathbb{E}})$ is the set of worlds that are models of the belief set $B(\mathbb{E})$ associated with $\mathbb{E}$.
-The belief set of the agent with this notation is $Th([B(\mathbb{E})])$.
+Then $\modelsOf{B(\mathbb{E})} = min(\top, \leq_{\mathbb{E}})$ is the set of worlds that are models of the belief set $B(\mathbb{E})$ associated with $\mathbb{E}$.
+The belief set of the agent with this notation is $Th(\modelsOf{B(\mathbb{E})})$.
 
@@
     $min(\top, \leq_{\mathbb{E}})$ is the set of worlds on the lowest rank, $\{010, 100\}$.
-A possible belief set is $B(\mathbb{E}) = \{p \vee q, \neg p \vee \neg q, \neg r\}$ as $[B(\mathbb{E})] = \{010, 100\} = min(\top, \leq_{\mathbb{E}})$.
+A possible belief set is $B(\mathbb{E}) = \{p \vee q, \neg p \vee \neg q, \neg r\}$ as $\modelsOf{B(\mathbb{E})} = \{010, 100\} = min(\top, \leq_{\mathbb{E}})$.
 Intuitively this makes sense, with the initial assumption that John or Mary are the suspects ($p \vee q$), have acted alone ($\neg p \vee \neg q$) and the victim is not an alien ($\neg r$).
@@
 \label{chapter:dp-agm-postulates}
-The postulates first introduced by \cite{Alchourron1985} and reformulated for iterated belief revision on epistemic states by \cite{Darwiche1997} which are further used in this text are presented here.
+A well established set of Postulates for revision are the AGM postulates \cite{Alchourron1985}.
+In this text, a reformulation for epistemic states by Darwiche and Pearl \cite{Darwiche1997} is used, presented in the following.
 $\mathbb{E}$ denotes an epistemic state, $B(\mathbb{E})$ it's associated belief set, $B(\mathbb{E}) + \alpha$ the expansion of $B(\mathbb{E})$ by $\alpha$.
@@
     \item\label{E5} $\qquad \textrm{If } \mathbb{E} = \mathbb{F} \textrm{ and } \alpha \equiv \beta \textrm{ then } B(\mathbb{E} \ast \alpha) = B(\mathbb{F} \ast \beta)$
-    \item\label{E6} $\qquad \bot \in B(\mathbb{E} \ast \alpha) \textrm{ iff } \vdash \neg \alpha$
+    \item\label{E6} $\qquad \bot \in B(\mathbb{E} \ast \alpha) \textrm{ iff } \models \neg \alpha$
     \item\label{E7} $\qquad B(\mathbb{E} \ast (\alpha \wedge \beta)) \subseteq B(\mathbb{E} \ast \alpha) + \beta$
@@
 \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = (CR$\arabic*$)]
-    \item\label{CR1} $\qquad \textrm{If } v\in [\alpha], w \in [\alpha] \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ iff } v \leq_{\mathbb{E\ast\alpha}} w$
-    \item\label{CR2} $\qquad \textrm{If } v\in [\neg \alpha], w \in [\neg \alpha] \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ iff } v \leq_{\mathbb{E\ast\alpha}} w$
-    \item\label{CR3} $\qquad \textrm{If } v\in [ \alpha], w \in [\neg \alpha] \textrm{ then } v <_{\mathbb{E}} w \textrm{ only if } v <_{\mathbb{E\ast\alpha}} w$
-    \item\label{CR4} $\qquad \textrm{If } v\in [ \alpha], w \in [\neg \alpha] \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ only if } v \leq_{\mathbb{E\ast\alpha}} w$
+    \item\label{CR1} $\qquad \textrm{If } v\in \modelsOf{\alpha}, w \in \modelsOf{\alpha} \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ iff } v \leq_{\mathbb{E\ast\alpha}} w$
+    \item\label{CR2} $\qquad \textrm{If } v\in \modelsOf{\neg\alpha}, w \in \modelsOf{\neg\alpha} \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ iff } v \leq_{\mathbb{E\ast\alpha}} w$
+    \item\label{CR3} $\qquad \textrm{If } v\in \modelsOf{\alpha}, w \in \modelsOf{\neg\alpha} \textrm{ then } v <_{\mathbb{E}} w \textrm{ only if } v <_{\mathbb{E\ast\alpha}} w$
+    \item\label{CR4} $\qquad \textrm{If } v\in \modelsOf{\alpha}, w \in \modelsOf{\neg\alpha} \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ only if } v \leq_{\mathbb{E\ast\alpha}} w$
 \end{enumerate}
 
-\ref{CR1} and \ref{CR2} mean that the relative ordering of worlds following a revision by $\alpha$ stays the same if the worlds are either both $\alpha$ or $\neg\alpha$ worlds.
-\ref{CR3} and \ref{CR4} require that $\alpha$-worlds that are strictly/weakly more plausible than $\neg\alpha$-worlds are still strictly/weakly more plausible than them after a $\alpha$-revision.
-
-% TODO: QUESTION: do we need C1-C4 here? 
-%\begin{equation*}
-%\begin{aligned}
-%    (C1) \qquad & \textrm{If } \beta \vdash \alpha \textrm{ then } B(\mathbb{E}\ast\alpha\ast\beta)=B(\mathbb{E}\ast\beta) \\
-%    (C2) \qquad & \textrm{If } \beta \vdash \neg  \alpha \textrm{ then } B(\mathbb{E}\ast\alpha\ast\beta)=B(\mathbb{E}\ast\beta) \\
-%    (C3) \qquad & \textrm{If } \alpha \in B(\mathbb{E}\ast\beta) \textrm{ then } \alpha \in B(\mathbb{E}\ast\alpha\ast\beta) \\
-%    (C4) \qquad & \textrm{If } \neg \alpha \notin B(\mathbb{E}\ast\beta) \textrm{ then } \neg \alpha \notin B(\mathbb{E}\ast\alpha\ast\beta) \\
-%\end{aligned}
-%\end{equation*}
+\ref{CR1} and \ref{CR2} mean that the relative ordering of worlds following a revision by $\alpha$ stays the same if the worlds are either both $\alpha$- or $\neg\alpha$- worlds.
+\ref{CR3} and \ref{CR4} require that $\alpha$-worlds that are strictly/weakly more plausible than $\neg\alpha$-worlds are still strictly/weakly more plausible than them after an $\alpha$-revision.
 
@@
 This new structure is denoted as $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$.
-In this notation a world $w \in W$ is represented twice: When new evidence $\alpha$ arrives that makes $w$ more plausible (because $w \in [\alpha]$), the agent can assume it's positive representation as $w^{+} \in W^{\pm}$.
-In contrast, if the new evidence makes $w$ less plausible ($w \notin [\alpha]$), then the negative representation $w^{-} \in W^{\pm}$ is the agent's view of $w$.
+In this notation a world $w \in W$ is represented twice: When new evidence $\alpha$ arrives that makes $w$ more plausible (because $w \in \modelsOf{\alpha}$), the agent can assume it's positive representation as $w^{+} \in W^{\pm}$.
+In contrast, if the new evidence makes $w$ less plausible ($w \notin \modelsOf{\alpha}$), then the negative representation $w^{-} \in W^{\pm}$ is the agent's view of $w$.
 Booth and Meyer call the pair $(w^{+}, w^{-})$ the positive/negative representation of the world $w$.
@@
 \begin{example}
-    \label{example:example-stick}
+    \label{example:example-intervals}
     Recall that tpos can be equivalently thought of as a linearly ordered set of ranks (Example \ref{example:example-introduction}).
-Therefore a tpo over $W$ can be visualised by ordering every $w \in W$ in a table of ranks (table \ref{tab:visualising-a-tpo-example}).
-To visualise the interval ordering introduced by $\preceq$, Booth and Meyer use a "stick" with the endpoints defined as $w^{+}$/$w^{-}$ respectively.
-This method was first introduced in \cite{Booth2007} and is shown in Figure \ref{fig:example-visualisation-scatterplot}.
+Therefore a tpo over $W$ can be visualised by displaying every $w \in W$ in a table that has one column for every rank (like in Table \ref{tab:visualising-a-tpo-example}).
+To visualise the interval ordering introduced by $\preceq$, Booth and Meyer use an interval with the endpoints defined as $w^{+}$/$w^{-}$ respectively.
+This type of visualisation was first introduced in a previous paper by Booth and Meyer themselves \cite{Booth2007} and is shown in Figure \ref{fig:example-visualisation-scatterplot}.
 
@@
         \end{tikzpicture}
-        \caption{Representation of $\preceq$ over $W^{\pm}$ using sticks}
+        \caption{Representation of $\preceq$ over $W^{\pm}$ using intervals}
         \label{fig:example-visualisation-scatterplot}
@@
    The worlds on lower ranks (more on the left) are preferred and assumed to be more plausible.
-Here for example $x_{1}^{+} \prec x_{3}^{+}$ and $x_{1}^{-} \sim x_{4}^{+}$ Note that, even though all sticks have the same length in this example, that is not required.
+Here for example $x_{1}^{+} \prec x_{3}^{+}$ and $x_{1}^{-} \sim x_{4}^{+}$ Note that, even though all intervals have the same length in this example, that is not required.
 \end{example}
@@
 
-\begin{definition}[$\leq$-faithful tpo over $W^{\pm}$ taken directly from \cite{Booth2011}]
-\label{definition:faithful-tpo}Let $\preceq \in W^{\pm} \times W^{\pm}$. If $\preceq$ satisfies \ref{PREQ1}-\ref{PREQ4}, we say $\preceq$ is a $\leq$-faithful tpo (over $W^{\pm}$).
+\begin{definition}[$\leq$-faithful tpo over $W^{\pm}$ \cite{Booth2011}]
+\label{definition:faithful-tpo}Let $\preceq \subseteq W^{\pm} \times W^{\pm}$. If $\preceq$ satisfies \ref{PREQ1}-\ref{PREQ4}, we say $\preceq$ is a $\leq$-faithful tpo (over $W^{\pm}$).
 \end{definition}
@@
     \label{example:example-faithful-tpo}
-    Is the following tpo $\preceq$ over $W^{\pm}$ a $\leq$-faithful tpo?
+    Consider the following tpo $\preceq$ over $W^{\pm}$.
 
@@
 
-    Even though \ref{PREQ1} and \ref{PREQ4} are satisfied, $\preceq$ is not a $\leq$-faithful tpo: From \ref{PREQ2} and $x_{1}^{+} \prec x_{2}^{+}$ follows $x_{1} < x_{2}$.
+    $\preceq$ is not a $\leq$-faithful tpo: Even though \ref{PREQ1} and \ref{PREQ4} are satisfied, $\preceq$ is not a $\leq$-faithful tpo: From \ref{PREQ2} and $x_{1}^{+} \prec x_{2}^{+}$ follows $x_{1} < x_{2}$.
 That means \ref{PREQ3} can not hold as $x_{2}^{-} \prec x_{1}^{-}$ which would require $x_{2} < x_{3}$ to be true.
 
-    As demonstrated here, even though the "sticks" do not need to be the same size for all worlds (they just must exist due to \ref{PREQ4}), they need to be the same size for worlds that share a rank for their corresponding representations.
-They can not overlap other sticks completely to continue to satisfy \ref{PREQ2} and \ref{PREQ3}.
+    As demonstrated here, even though the intervals do not need to be the same size for all worlds (they just must exist due to \ref{PREQ4}), they need to be the same size for worlds that share a rank for their corresponding representations.
+They can not overlap other intervals completely to continue to satisfy \ref{PREQ2} and \ref{PREQ3}.
 \end{example}
@@
     \label{example:example-tpo-initial}
-    Continuing the courtroom demonstration introduced in \ref{example:example-introduction} of a judge deciding on a verdict on the suspects John and Mary.
+    Continuing the courtroom demonstration introduced in Example \ref{example:example-introduction} of a judge deciding on a verdict on the suspects John and Mary.
 Figure \ref{fig:example-tpo-initial} shows a possible version of a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ from which the tpo $\leq$ from table \ref{tab:visualising-a-tpo-example} can be reconstructed.
@@
 
-    Notice the "gap" between the $[r]$-worlds that include the victim being an alien.
-Even in their positive representations they are not as plausible as negative representations of $[\neg r]$-worlds.
+    Notice the "gap" between the $\modelsOf{r}$-worlds that include the victim being an alien.
+Even in their positive representations they are not as plausible as negative representations of $\modelsOf{\neg r}$-worlds.
 That fact will be discussed more in section \ref{section:non-prioritised-revision} and example \ref{example:example-non-prio-revision}.
@@
 Booth and Meyer \cite{Booth2011} discussed tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
-To do so they define how to use the additional information from a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ to create a revision operator $\ast_{\preceq}$ (from now on referred to as BM tpo-revision operators).
-
-\begin{definition}[Revision operator $\ast_{\preceq}$ for $\leq$ generated by $\preceq$ from \cite{Booth2011}]
+They define how to use the additional information from a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ to create a revision operator $\ast_{\preceq}$ (from now on referred to as BM tpo-revision operators).
+
+\begin{definition}[Revision operator $\ast_{\preceq}$ for $\leq$ generated by $\preceq$ \cite{Booth2011}]
     \label{definition:revision-operator}
@@
                     \begin{array}{ll}
-                      x^{+} \textrm{ if } x \in [\alpha]\\
-                      x^{-} \textrm{ if } x \in [\neg\alpha]
+                      x^{+} \textrm{ if } x \in \modelsOf{\alpha}\\
+                      x^{-} \textrm{ if } x \in \modelsOf{\neg\alpha}
                     \end{array}
@@
 Intuitively, new evidence $\alpha$ makes worlds that satisfy $\alpha$ more plausible and worlds that do not satisfy $\alpha$ less plausible.
-Therefore the agent associates worlds $x \in [\alpha]$ with their positive representation $x^{+}$ and worlds $x \in [\neg\alpha]$ with their negative representation $x^{-}$.
+Therefore the agent associates worlds $x \in \modelsOf{\alpha}$ with their positive representation $x^{+}$ and worlds $x \in \modelsOf{\neg\alpha}$ with their negative representation $x^{-}$.
 
@@
     \label{example:example-updated-tpo}
-    Reconsider the $\leq$-faithful tpo $\preceq$ from example \ref{example:example-stick}.
+    Reconsider the $\leq$-faithful tpo $\preceq$ from example \ref{example:example-intervals}.
 When a new piece of evidence $\alpha$ has to be considered, each world gets mapped to one end of the interval assigned to it, depending on if it is an $\alpha$-world or not.
 In figure \ref{fig:example-updated-tpo} that mapping is indicated by the filled out dot.
-For this example $x_{1}, x_{2}$ and $x_{3}$ are $[\neg\alpha]$-worlds while $x_{4}$ is an $[\alpha]$-world.
+For this example $x_{1}, x_{2}$ and $x_{3}$ are $\modelsOf{\neg\alpha}$-worlds while $x_{4}$ is an $\modelsOf{\alpha}$-world.
 
@@
     \label{example:example-tpo-revised}
-    A more complex example is the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ (for the courtroom example \ref{example:example-introduction}) using the $\leq$-faithful tpo $\preceq$, introduced in example \ref{example:example-tpo-initial} and shown in figure \ref{fig:example-tpo-revised}.
+    A more complex example is the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ (for the courtroom Example \ref{example:example-introduction}) using the $\leq$-faithful tpo $\preceq$, introduced in Example \ref{example:example-tpo-initial} and shown in Figure \ref{fig:example-tpo-revised}.
 In this case the new evidence received points to John being the murderer so $\alpha = p$.
@@
     \begin{equation*}
-        010 \in [\neg\alpha] \textrm{ : } r_{\alpha}(010) = 010^{-}
+        010 \in \modelsOf{\neg\alpha} \textrm{ : } r_{\alpha}(010) = 010^{-}
     \end{equation*}
     \begin{equation*}
-        110 \in [\alpha] \textrm{ : } r_{\alpha}(110) = 110^{+}
+        110 \in \modelsOf{\alpha} \textrm{ : } r_{\alpha}(110) = 110^{+}
     \end{equation*}
@@
     Repeating for every world in $W$, the new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$.
-Unsurprisingly, the belief set associated with the new epistemic state is $[B(\mathbb{E})] = min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".
+Unsurprisingly, the belief set associated with the new epistemic state is $\modelsOf{B(\mathbb{E})} = min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".
 
@@
 
-A demonstration is already provided with example \ref{example:example-updated-tpo} and figure \ref{fig:example-updated-tpo}.
-The most plausible worlds in the new epistemic state $\mathbb{E}$, $min(\top, \leq_{\alpha}^{\ast})$, include the $[\neg\alpha]$-worlds $x_{1}$ and $x_{2}$.
+A demonstration is already provided with Example \ref{example:example-updated-tpo} and Figure \ref{fig:example-updated-tpo}.
+The most plausible worlds in the new epistemic state $\mathbb{E}$, $min(\top, \leq_{\alpha}^{\ast})$, include the $\modelsOf{\neg\alpha}$-worlds $x_{1}$ and $x_{2}$.
 Therefore $Th(min(\top, \leq_{\alpha}^{\ast}))$ does not include the new evidence $\alpha$.
@@
 
-    Since the agent considered the victim being an alien very unlikely, even the positive representations of worlds in $[\alpha]$ are on higher ranks (so considered less plausible) than negative representations of worlds in $[\neg\alpha]$.
+    Since the agent considered the victim being an alien very unlikely, even the positive representations of worlds in $\modelsOf{\alpha}$ are on higher ranks (so considered less plausible) than negative representations of worlds in $\modelsOf{\neg\alpha}$.
     The belief set $B(\mathbb{E})$ of the agent is unchanged under $\leq_{\alpha}^{\ast}$, since $\{010, 100\}$ are still the most plausible worlds, and does not include $r$ "the victim is an alien".
@@
     \item\label{AST2} $\qquad\alpha \equiv \gamma \textrm{ implies } \leq_{\alpha}^{\ast}=\leq_{\gamma}^{\ast}$
-    \item\label{AST3} $\qquad \textrm{If } x, y \in [\alpha] \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
-    \item\label{AST4} $\qquad \textrm{If } x, y \in [\neg\alpha] \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
-    \item\label{AST5} $\qquad \textrm{If } x \in [\alpha], y \in [\neg\alpha] \textrm{ and } x \leq y \textrm{ then } x <_{\alpha}^{\ast} y$
-    \item\label{AST6} $\qquad \textrm{If } x \in [\alpha], y \in [\neg\alpha] \textrm{ and } y \leq_{\alpha}^{\ast} x \textrm{ then } y \leq_{\gamma}^{\ast} x$
-    \item\label{AST7} $\qquad \textrm{If } x \in [\alpha], y \in [\neg\alpha] \textrm{ and } y <_{\alpha}^{\ast} x \textrm{ then } y <_{\gamma}^{\ast} x$
+    \item\label{AST3} $\qquad \textrm{If } x, y \in \modelsOf{\alpha} \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
+    \item\label{AST4} $\qquad \textrm{If } x, y \in \modelsOf{\neg\alpha} \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
+    \item\label{AST5} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } x \leq y \textrm{ then } x <_{\alpha}^{\ast} y$
+    \item\label{AST6} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } y \leq_{\alpha}^{\ast} x \textrm{ then } y \leq_{\gamma}^{\ast} x$
+    \item\label{AST7} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } y <_{\alpha}^{\ast} x \textrm{ then } y <_{\gamma}^{\ast} x$
 \end{enumerate}
@@
 
-\ref{AST1} and \ref{AST2} are considered basic properties: A revision of a tpo $\leq$ over $W$ must generate another tpo over $W$ .
+\ref{AST1} and \ref{AST2} are considered basic properties: A revision of a tpo $\leq$ over $W$ must generate another tpo over $W$.
 In addition the operator must return an equal revised tpo for semantically equivalent sentences, the so called syntax-irrelevance property.
@@
 Booth and Meyer themselves consider them characteristic for admissible revision operators \cite{Booth2006a}.
-If revising a tpo by a sentence $\alpha$, the relative ordering of worlds that are either both $[\alpha]$- or $[\neg\alpha]$-worlds, must stay the same (\ref{AST3}/\ref{AST4}).
+If revising a tpo by a sentence $\alpha$, the relative ordering of worlds that are either both $\modelsOf{\alpha}$- or $\modelsOf{\neg\alpha}$-worlds, must stay the same (\ref{AST3}/\ref{AST4}).
 These properties were already part of the semantic postulates \ref{CR1} and \ref{CR2} by Darwiche and Pearl \cite{Darwiche1997} discussed in section \ref{chapter:dp-agm-postulates}.
@@
 It means the following: A world $x$ that is considered at least as plausible as a world $y$ before a revision by new information $\alpha$.
-If $\alpha$ makes $x$ more plausible ($x \in [\alpha]$) and $y$ less plausible ($y \in [\neg\alpha]$) then after revision $x$ should be considered strictly more plausible than $y$.
+If $\alpha$ makes $x$ more plausible ($x \in \modelsOf{\alpha}$) and $y$ less plausible ($y \in \modelsOf{\neg\alpha}$) then after revision $x$ should be considered strictly more plausible than $y$.
 This rule was not only proposed by Booth and Meyer \cite{Booth2006a} but also by Jin und Thielscher in \cite{Jin2007} (as the postulate of independence).
@@
 % see also http://ceur-ws.org/Vol-2445/paper_2.pdf
+% see also: Whiwap: Checking Iterative Belief Changes
 
@@
                     \begin{array}{ll}
-                      p(x^{\epsilon}) \textrm{ if } x \in [\alpha]\\
-                      p(x^{\epsilon}) + a \textrm{ if } x \in [\neg\alpha]
+                      p(x^{\epsilon}) \textrm{ if } x \in \modelsOf{\alpha}\\
+                      p(x^{\epsilon}) + a \textrm{ if } x \in \modelsOf{\neg\alpha}
                     \end{array}
@@
     \begin{equation*}
-        010 \in [\neg\alpha] \textrm{ : } (p(010^{-}), p(010^{-}) + a) = (a, 2a)
+        010 \in \modelsOf{\neg\alpha} \textrm{ : } (p(010^{-}), p(010^{-}) + a) = (a, 2a)
     \end{equation*}
@@
     \begin{equation*}
-        100 \in [\alpha] \textrm{ : } (p(100^{+}), p(100^{-})) = (0, a)
+        100 \in \modelsOf{\alpha} \textrm{ : } (p(100^{+}), p(100^{-})) = (0, a)
     \end{equation*}
@@
     For an example that demonstrates the impact the revision of $\preceq$ has on the acceptance of conditional beliefs, consider again the courtroom example \ref{example:example-introduction}.
-The fact that the victim is an alien ($r$ true) seems very unlikely, which is modelled by the gap between $[r]$-worlds and $[\neg r]$-worlds.
-
-    When evidence $\alpha = r$ arrives, there seems to be little change in the epistemic state of the judge: $\leq_{\alpha}^{\ast}$ is unchanged, as even considering the negative representations of $[\neg r]$-worlds, they rank lower than $[r]$-worlds.
+The fact that the victim is an alien ($r=\textrm{true}$) seems very unlikely, which is modelled by the gap between $\modelsOf{r}$-worlds and $\modelsOf{\neg r}$-worlds.
+
+    When evidence $\alpha = r$ arrives, there seems to be little change in the epistemic state of the judge: $\leq_{\alpha}^{\ast}$ is unchanged, as even considering the negative representations of $\modelsOf{\neg r}$-worlds, they rank lower than $\modelsOf{r}$-worlds.
 An unchanged tpo $\leq_{\alpha}^{\ast}$ also means the believe set $B(\mathbb{E})$ stays the same and does not include $r$ (a property of non-prioritised revision as described in item \ref{section:non-prioritised-revision}).
@@
     What did change is the willingness of the agent to accept conditional beliefs about $r$ being true in light of future evidence.
-This is reflected by the revised structure $\preceq_{p \ast \alpha}$ shown in figure \ref{fig:example-preceq-revised-alien}.
+This is reflected by the revised structure $\preceq_{p \ast \alpha}$ shown in figure \ref{fig:example-preceq-revised-alien2}.
 
@@
     % TODO tpo alpha as beta is unlucky because ast has a different meaning already, also change in figure 8 caption
-    Notice how the gap between $[\neg r]$- and $[r]$-worlds has now closed.
+    Notice how the gap between $\modelsOf{\neg r}$- and $\modelsOf{r}$-worlds has now closed.
 After revising $\preceq_{p \ast \alpha}$ for a second piece of evidence $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$ ("the murderer was either John or Mary, not both") the new tpo $\leq_{\alpha \ast \beta}^{\ast}$ can be read from the filled dots in figure \ref{fig:example-preceq-revised-alien2}.
@@
 But because of the revision of $\preceq$ to $\preceq_{p \ast \alpha}$, the evidence $\alpha$ changed the acceptance of the judge to belief we are not alone in the universe.
-After receiving $\beta$, the judge even considers the $[r]$-worlds $\{011, 101\}$ more likely than the $[\neg r]$-worlds $\{000, 110\}$!
-
-(Luckily, due to the existence of $[\beta]$-worlds $\{010, 100\}$, the belief set of the judge still does not include $r$ and rationality prevails.)
+After receiving $\beta$, the judge even considers the $\modelsOf{r}$-worlds $\{011, 101\}$ more likely than the $\modelsOf{\neg r}$-worlds $\{000, 110\}$!
+
+(Luckily, due to the existence of $\modelsOf{\beta}$-worlds $\{010, 100\}$, the belief set of the judge still does not include $r$ and rationality prevails.)
 \end{example}
@@
 A consistent example including a trial situation (adapted from \cite{Darwiche1997} and \cite{Booth2011}) was used to accompany the discussion of the paper.
-In addition to the provided example the synopsis also introduced an adapted visualisation for $\leq$-faithful tpo-revision based on the stick visualisation used by Booth and Meyer themselves.
+In addition to the provided example the synopsis also introduced an adapted visualisation for $\leq$-faithful tpo-revision based on the interval visualisation used by Booth and Meyer themselves.
 
@@
 
-% TODO: QUESTION, idempotent correct?
-The proposed, concrete operator for the revision of $\leq$-faithful tpos allows for multiple revisions by the same evidence $\alpha$ or semantically equivalent evidence $\beta \equiv \alpha$.
-Those would consistently lower the acceptance of $[\neg\alpha]$-worlds without presenting new evidence.
+The proposed, concrete operator for the revision of $\leq$-faithful tpos allows for consecutive revisions by the same evidence $\alpha$ or semantically equivalent evidence $\beta \equiv \alpha$.
+Those would consistently lower the acceptance of $\modelsOf{\neg\alpha}$-worlds without presenting new evidence.
 It seems like an interesting question to ask, if tpo-revision for iterated belief change could be idempotent in regards to already known information.
@@
 \begin{equation*}
-    \textrm{If } x \in [\alpha], y \in [\neg\alpha] \textrm{ and } y <_{\alpha}^{\ast} x \textrm{ then } y <_{\gamma}^{\ast} x
+    \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } y <_{\alpha}^{\ast} x \textrm{ then } y <_{\gamma}^{\ast} x
 \end{equation*}

### 2021-02-01 paper/1901_3230880_philip_heltweg.tex
fix: more feedback

@@
 
-% TODO: QUESTION: consider not having a table of contents
 \tableofcontents
@@
 
+% TODO: put text here
+
 \subsection{Propositional Logic} % Aussagenlogik
@@
 \subsection{Belief sets and epistemic states}
-% TODO QUESTION: explain contraction, revision, expansion?
+\label{chapter:belief-sets-and-epistemic-states}
+% TODO: explain contraction, revision, expansion
+% ANSWER: Ich würdes es ganz kurz erläutern im Text. Im Vortrag vielleicht nicht umbedingt.
+
 % TODO: Gardenfors correct? read!
@@
 % TODO QUESTION: do we need to discuss this in ore detail? faithful assignment here:
+
+% ANSWER: Das ist eine gute Frage. So wie ich das Paper von Booth und Meyer im
+% Kopf habe werden dort die Ordnung mit epistemischen Zuständen
+% gleichgesetzt (was Darwiche und Pearl ja nicht machen). Von daher halte
+% ich das für ok es nicht im aller formalen Ausführlichkeit zu machen.
+% Aber man könnte es im einen Satz erwähnen.
+
 %Katsuno and Mendelzon [17] propose that an epistemic state Ψ
@@
 
-While DP-AGM define the most plausible worlds after a revision by $\alpha$ (as $min(\alpha, \leq_{\mathbb{E}})$), Darwiche and Pearl also define postulates that restrict the rest of the new ordering.
+The DP-AGM postulates put restrictions how the belief set of an agent changes after revision of new evidence $\alpha$.
+As outlined before belief sets can be extracted from epistemic states by taking the set of formulae true in all most plausible worlds after revision by $\alpha$, defined as $\modelsOf{B(\mathbb{E}\ast\alpha)} = min(\alpha, \leq_{\mathbb{E}})$.
+
+Darwiche and Pearl also define postulates that restrict how the rest of the new ordering changes.
+This extends the constrains to not only the changes in the currently held belief of an agent (the belief set), but also to the conditional beliefs it is prepared to accept depending on future evidence.
 Since this synopsis only focused on the revision of tpos, the semantic (i.e.
 in terms of how the ordering of worlds undergoes change) versions are shown here.
-For more details and sentential versions refer to \cite{Darwiche1997}.
+For more details and sentential versions refer to Darwiche and Pearl \cite{Darwiche1997}.
 
@@
 
-% TODO QUESTION: we probably need to make clearer that this is where the paper starts, caro thought it should be in 2.x
 \section{Additional metadata for tpo revision}
+% TODO: Text, put in that paper by booth and meyer starts here basically
 \subsection{Enriching epistemic states}
@@
 Since this synopsis focuses on the revision of tpos itself, only the revision of a $\leq$-faithful tpo $\preceq$ using the example operator from the original paper is included here.
-For a more detailed explanation of the operator, SPHs or their properties refer to \cite{Booth2011}.
+For a more detailed explanation of the operator, SPHs or their properties refer to Booth and Meyer \cite{Booth2011}.
 
@@
 
-% TODO QUESTION: this critique example seems very weak
+% TODO: this critique example seems very weak
 Considering the quality and impact of new evidence also creates the question if \ref{AST6} and \ref{AST7} (properties of BM tpo-revision operators, section \ref{section:properties-of-bm-tpo-revision-operators}) should be weakened.

### 2021-02-01 paper/1901_3230880_philip_heltweg.tex
fix: more feedback by advisor

@@
 \label{section:formal-background}
-
-% TODO: put text here
-
-\subsection{Propositional Logic} % Aussagenlogik
-The following notation will be used, as proposed by \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables.
+The following notation will be used, largely aligned to Booth and Meyer \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables.
 Lower case greek letters represent formulae in $L$ and $\top$, $\bot$ representing tautology and contradiction respectively.
@@
 \section{Additional metadata for tpo revision}
-% TODO: Text, put in that paper by booth and meyer starts here basically
+After discussing notation and previous research, the following chapters present an excerpt of the new work done by Booth and Meyer in \cite{Booth2011}.
+To support their approach to tpo revision, Booth and Meyer propose adding additional metadata to epistemic states.
+
 \subsection{Enriching epistemic states}

### 2021-02-02 paper/1901_3230880_philip_heltweg.tex
fix: fixed lower case in examples, tables and figures

@@
 A tpo representing the judges assumptions would be $\leq$ with $010 \sim 100 < 000 \sim 110 < 011 \sim 101 < 001 \sim 111$.
-The equivalent representation as a linearly ordered set of ranks is shown in table \ref{tab:visualising-a-tpo-example}.
+The equivalent representation as a linearly ordered set of ranks is shown in Table \ref{tab:visualising-a-tpo-example}.
 
@@
 \begin{example}
-    Continuing example \ref{example:example-introduction} it is possible to model an epistemic state $\mathbb{E}$ with the tpo $\leq_{\mathbb{E}}$.
+    Continuing Example \ref{example:example-introduction} it is possible to model an epistemic state $\mathbb{E}$ with the tpo $\leq_{\mathbb{E}}$.
 
@@
     Continuing the courtroom demonstration introduced in Example \ref{example:example-introduction} of a judge deciding on a verdict on the suspects John and Mary.
-Figure \ref{fig:example-tpo-initial} shows a possible version of a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ from which the tpo $\leq$ from table \ref{tab:visualising-a-tpo-example} can be reconstructed.
+Figure \ref{fig:example-tpo-initial} shows a possible version of a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ from which the tpo $\leq$ from Table \ref{tab:visualising-a-tpo-example} can be reconstructed.
 
@@
 Even in their positive representations they are not as plausible as negative representations of $\modelsOf{\neg r}$-worlds.
-That fact will be discussed more in section \ref{section:non-prioritised-revision} and example \ref{example:example-non-prio-revision}.
+That fact will be discussed more in section \ref{section:non-prioritised-revision} and Example \ref{example:example-non-prio-revision}.
 \end{example}
@@
     \label{example:example-updated-tpo}
-    Reconsider the $\leq$-faithful tpo $\preceq$ from example \ref{example:example-intervals}.
+    Reconsider the $\leq$-faithful tpo $\preceq$ from Example \ref{example:example-intervals}.
 When a new piece of evidence $\alpha$ has to be considered, each world gets mapped to one end of the interval assigned to it, depending on if it is an $\alpha$-world or not.
-In figure \ref{fig:example-updated-tpo} that mapping is indicated by the filled out dot.
+In Figure \ref{fig:example-updated-tpo} that mapping is indicated by the filled out dot.
 For this example $x_{1}, x_{2}$ and $x_{3}$ are $\modelsOf{\neg\alpha}$-worlds while $x_{4}$ is an $\modelsOf{\alpha}$-world.
@@
 
-    The updated tpo $\leq_{\alpha}^{\ast}$ can now be inferred from figure \ref{fig:example-updated-tpo}.
+    The updated tpo $\leq_{\alpha}^{\ast}$ can now be inferred from Figure \ref{fig:example-updated-tpo}.
 It is the ordering of the filled dots, representing the new assignment for the respective world: $x_{1} \sim x_{2} \sim x_{4} < x_{3}$.
@@
 
-    Using the $\leq$-faithful tpo $\preceq$ already established for the courtroom example \ref{example:example-introduction} the revision by $\alpha = r$ ("the victim was an alien") is shown in figure \ref{fig:example-non-prio-revision}.
+    Using the $\leq$-faithful tpo $\preceq$ already established for the courtroom Example \ref{example:example-introduction} the revision by $\alpha = r$ ("the victim was an alien") is shown in Figure \ref{fig:example-non-prio-revision}.
     \begin{figure}[H]
@@
     \label{example:example-preceq-revised}
-    For the courtroom example \ref{example:example-introduction} the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ for $\alpha = p$ ("John is the murderer") was already done in example \ref{example:example-tpo-revised}.
+    For the courtroom Example \ref{example:example-introduction} the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ for $\alpha = p$ ("John is the murderer") was already done in Example \ref{example:example-tpo-revised}.
 The next step is revising $\preceq$ by $\alpha$.
@@
     \label{example:example-preceq-revised-alien}
-    For an example that demonstrates the impact the revision of $\preceq$ has on the acceptance of conditional beliefs, consider again the courtroom example \ref{example:example-introduction}.
+    For an example that demonstrates the impact the revision of $\preceq$ has on the acceptance of conditional beliefs, consider again the courtroom Example \ref{example:example-introduction}.
 The fact that the victim is an alien ($r=\textrm{true}$) seems very unlikely, which is modelled by the gap between $\modelsOf{r}$-worlds and $\modelsOf{\neg r}$-worlds.
@@
     What did change is the willingness of the agent to accept conditional beliefs about $r$ being true in light of future evidence.
-This is reflected by the revised structure $\preceq_{p \ast \alpha}$ shown in figure \ref{fig:example-preceq-revised-alien2}.
+This is reflected by the revised structure $\preceq_{p \ast \alpha}$ shown in Figure \ref{fig:example-preceq-revised-alien2}.
 
@@
     Notice how the gap between $\modelsOf{\neg r}$- and $\modelsOf{r}$-worlds has now closed.
-After revising $\preceq_{p \ast \alpha}$ for a second piece of evidence $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$ ("the murderer was either John or Mary, not both") the new tpo $\leq_{\alpha \ast \beta}^{\ast}$ can be read from the filled dots in figure \ref{fig:example-preceq-revised-alien2}.
+After revising $\preceq_{p \ast \alpha}$ for a second piece of evidence $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$ ("the murderer was either John or Mary, not both") the new tpo $\leq_{\alpha \ast \beta}^{\ast}$ can be read from the filled dots in Figure \ref{fig:example-preceq-revised-alien2}.
 
@@
 Especially high quality evidence for a very unlikely type of world might change an agents plausibility ordering, while low quality evidence that is very expected might not.
-Consider the following situation in our courtroom example \ref{example:example-introduction}: New evidence $\alpha$ arrives that fingerprints of John have been found at the place of the murder.
+Consider the following situation in our courtroom Example \ref{example:example-introduction}: New evidence $\alpha$ arrives that fingerprints of John have been found at the place of the murder.
 $\alpha$  makes a world $x$, with $p$ being true, more likely.

### 2021-02-02 paper/1901_3230880_philip_heltweg.tex
feat: explained belief set expansion, contraction and revision

@@
 
-%Consider a knowledge base (KB) represented by a set of sentences in a
-%language L. As our perception of the world described by the knowledge base
-%changes, the knowledge base must be modified. G~irdenfors [9] distinguishes
-%several kinds of modifications. If we simply acquire additional knowledge
-%about the world, and the new knowledge does not conflict with the current
-%beliefs t of the KB, we expand the KB. If, however, the new knowledge is
-%inconsistent with the old beliefs, and we want the KB to be always consistent,
-%we must resolve the conflict somehow; this operation will be called revision. A
-%* Part of this work was performed while this author was visiting the University of Toronto.
-%** This author is partially supported by the Natural Science and Engineering Research Council
-%of Canada.
-%1 We use the terms belief and knowledge interchangeably in this paper.
-%0004-3702/91/$03.50 © 1991 -- Elsevier Science Publishers B.V. All rights reserved 
-%264 H. Katsuno, A.O. Mendelzon
-%different kind of change occurs when a sentence previously believed becomes
-%questionable and has to be given up; the operation that makes this change is a
-%contraction
-
 % TODO: discussed in \cite{Katsuno1991} correct? was mentioned in intro of Admissible and Restrained Revision
@@
 % ANSWER: Ich würdes es ganz kurz erläutern im Text. Im Vortrag vielleicht nicht umbedingt.
-
 % TODO: Gardenfors correct? read!
 A belief set is the deductively closed set of propositions an agent accepts as true at any given point in time \cite{Ferme2011}.
-Alchourrón, Gärdenfors, and Makinson (AGM theory, \cite{Alchourron1985}) define postulates for belief sets and their contraction, expansion or revision with new evidence.
-In the process of belief revision an agent keeps their set of beliefs consistent while incorporating new information, even if it is inconsistent with the current belief set \cite{Gaerdenfors1984}.
+Alchourrón, Gärdenfors, and Makinson (AGM theory, \cite{Alchourron1985}) define postulates for belief sets and their expansion, contraction or revision with new evidence.
+Belief set expansion is the process of incorporating a new piece of evidence that is not inconsistent with currently held beliefs while contraction refers to giving up a belief that has become questionable.
+The process of belief revision refers to keeping an agent's set of beliefs consistent while incorporating new information that is inconsistent with the current belief set \cite{Katsuno1991, Gaerdenfors1984}.
 Darwiche and Pearl \cite{Darwiche1997} argue that working with belief sets is not expressive enough for satisfying results in iterated belief revision.

### 2021-02-02 paper/1901_3230880_philip_heltweg.tex
docs: removed todos

@@
 \label{chapter:belief-sets-and-epistemic-states}
-% TODO: explain contraction, revision, expansion
-% ANSWER: Ich würdes es ganz kurz erläutern im Text. Im Vortrag vielleicht nicht umbedingt.
-% TODO: Gardenfors correct? read!
 A belief set is the deductively closed set of propositions an agent accepts as true at any given point in time \cite{Ferme2011}.

### 2021-02-02 paper/1901_3230880_philip_heltweg.tex
feat: removed l conditionalisation reference, added info about admissible revision

@@
 
-% TODO: discussed in \cite{Katsuno1991} correct? was mentioned in intro of Admissible and Restrained Revision
-A common tool used to encode plausibility assumptions of an agent about possible worlds are total preorders (tpos) \cite{Booth2011}, discussed in \cite{Katsuno1991}.
+A common tool used to encode plausibility assumptions of an agent about possible worlds are total preorders (tpos) \cite{Booth2011}, also discussed in \cite{Katsuno1991}.
 In "How to Revise a Total Preorder", Booth and Meyer describe how to model the change of these total preorders when new evidence becomes available.
@@
 The next group of properties, \ref{AST3}-\ref{AST5} are common rules in iterated belief change.
-Booth and Meyer themselves consider them characteristic for admissible revision operators \cite{Booth2006a}.
+Booth and Meyer themselves consider them characteristic for admissible revision operators, a class of operators that requires new evidence to not be ignored completely \cite{Booth2006a}.
+This is in contrast to revision strategies like natural revision by Boutilier \cite{Boutilier1996} that minimise change in conditional beliefs.
 If revising a tpo by a sentence $\alpha$, the relative ordering of worlds that are either both $\modelsOf{\alpha}$- or $\modelsOf{\neg\alpha}$-worlds, must stay the same (\ref{AST3}/\ref{AST4}).
@@
 
-% TODO: WHAT ARE ADMISSIBLE OPERATORS
-%info here: \cite{Booth2006a}
-% see also http://ceur-ws.org/Vol-2445/paper_2.pdf
-% see also: Whiwap: Checking Iterative Belief Changes
-
 These properties define tpo-revision with one input sentence.
@@
 
-% TODO: probably don't need geffner ref here
-Booth and Meyer propose an operator that keeps worlds that satisfy $\alpha$ constant and moves $\neg\alpha$-worlds "back" by $a$ (also known as L-conditionalisation in Spohn-type rankings \cite{Geffner1992}).
+Booth and Meyer propose an operator that keeps worlds that satisfy $\alpha$ constant and moves $\neg\alpha$-worlds "back" by $a$.
 Other operators are possible and an area of further research \cite{Booth2011}.

### 2021-02-02 paper/1901_3230880_philip_heltweg.tex
feat: explained faithful assignment and refered to katsuno and mendelzon for details

@@
 
+Darwiche and Pearl show that their version of belief revision on epistemic states can be modelled with a tpo $\leq_{\mathbb{E}}$, associated with $\mathbb{E}$.
+The mapping of a belief state $\mathbb{E}$ to a tpo $\leq_{\mathbb{E}}$, that maintains the belief set, is is called a faithful assignment.
+As Booth and Meyer describe an additional structure, from which a tpo $\leq_{\mathbb{E}}$ can be determined, faithful assignment is mentioned here only for completeness.
+For more information refer to Katsuno and Mendelzon \cite{Katsuno1991}.
+
 Belief sets can be extracted from epistemic states.
 The belief set extracted from an epistemic state $\mathbb{E}$ is denoted as $B(\mathbb{E})$.
-Darwiche and Pearl show that their version of revision of epistemic states can be modelled with a tpo $\leq_{\mathbb{E}}$, associated with $\mathbb{E}$.
 Extraction of $B(\mathbb{E})$ is achieved by considering the set of lowest ranked worlds (i.e.
@@
 
-% TODO QUESTION: do we need to discuss this in ore detail? faithful assignment here:
-
-% ANSWER: Das ist eine gute Frage. So wie ich das Paper von Booth und Meyer im
-% Kopf habe werden dort die Ordnung mit epistemischen Zuständen
-% gleichgesetzt (was Darwiche und Pearl ja nicht machen). Von daher halte
-% ich das für ok es nicht im aller formalen Ausführlichkeit zu machen.
-% Aber man könnte es im einen Satz erwähnen.
-
-%Katsuno and Mendelzon [17] propose that an epistemic state Ψ
-%should be equipped with an ordering ≤Ψ of the worlds (interpretations), where the compatibility with Bel(Ψ) is ensured by the socalled faithfulness.
-%Definition 1 (Faithful Assignment [17]) A function Ψ 
-%→≤Ψ that
-%maps each epistemic state to a total preorder on interpretations is
-%said to be a faithful assignment if and only if:
-%(FA1) if ω1 ∈ Ψ and ω2 ∈ Ψ, then ω1 Ψ ω2
-%(FA2) if ω1 ∈ Ψ and ω2 ∈  / Ψ, then ω1 <Ψ ω2
-%Intuitively, ≤Ψ orders the worlds by plausibility, such that the minimal worlds with respect to ≤Ψ are the most plausible worlds.
-
 \subsection{Belief revision postulates}
 \label{chapter:dp-agm-postulates}
-A well established set of Postulates for revision are the AGM postulates \cite{Alchourron1985}.
+A well established set of postulates for revision are the AGM postulates \cite{Alchourron1985}.
 In this text, a reformulation for epistemic states by Darwiche and Pearl \cite{Darwiche1997} is used, presented in the following.
@@
 
-%TODO QUESTION: the text sounds like the properties are supposed by BM/they define them but they are also proved?! or does this mean proved for their approach but could be done differently?
-%We propose that if x is not more
-%preferred than y, even after receiving evidence which clearly points more to x
-%being the case than it does to y, then there can be no evi
-
 \ref{AST1} and \ref{AST2} are considered basic properties: A revision of a tpo $\leq$ over $W$ must generate another tpo over $W$.
@@
 
-    % TODO tpo alpha as beta is unlucky because ast has a different meaning already, also change in figure 8 caption
+    % TODO tpo alpha ast beta is unlucky because ast has a different meaning already, also change in figure 8 caption
     Notice how the gap between $\modelsOf{\neg r}$- and $\modelsOf{r}$-worlds has now closed.

### 2021-02-08 paper/1901_3230880_philip_heltweg.tex
feat: rewritten discussion example

@@
 Darwiche and Pearl show that their version of belief revision on epistemic states can be modelled with a tpo $\leq_{\mathbb{E}}$, associated with $\mathbb{E}$.
-The mapping of a belief state $\mathbb{E}$ to a tpo $\leq_{\mathbb{E}}$, that maintains the belief set, is is called a faithful assignment.
+A mapping of a belief state $\mathbb{E}$ to a tpo $\leq_{\mathbb{E}}$, that maintains the belief set, is is called a faithful assignment.
 As Booth and Meyer describe an additional structure, from which a tpo $\leq_{\mathbb{E}}$ can be determined, faithful assignment is mentioned here only for completeness.
@@
 
-    % TODO tpo alpha ast beta is unlucky because ast has a different meaning already, also change in figure 8 caption
     Notice how the gap between $\modelsOf{\neg r}$- and $\modelsOf{r}$-worlds has now closed.
@@
 Especially high quality evidence for a very unlikely type of world might change an agents plausibility ordering, while low quality evidence that is very expected might not.
-Consider the following situation in our courtroom Example \ref{example:example-introduction}: New evidence $\alpha$ arrives that fingerprints of John have been found at the place of the murder.
-$\alpha$  makes a world $x$, with $p$ being true, more likely.
-But, because of a large body of evidence, the judge still considers a world $y$, where Mary is the murderer, to be more plausible.
+Consider the following situation in a world described by the set of propositional variables $\{x_1, x_2, x_3, y\}$: New evidence $\alpha = x_1$ arrives that  makes a world $x$, with $x_1$ being true, more likely.
+But, because $\alpha$ is just one piece of fairly unspecific evidence among many, the agent still considers a world $y$ to be more plausible.
 This means there can be no evidence $\gamma$ that would make the agent consider the world $x$ more likely than $y$ according to \ref{AST7}:
@@
 
-But what if evidence is submitted that, if Mary is the murderer, the victim must be an alien $\gamma = q \implies r$?
-Semantically a human agent would assume all worlds in which Mary is the murderer to be highly unlikely due to how far fetched the acceptance of the victim being an alien is.
-Further research is required to solve this apparent contradiction by modelling different types and strengths of evidence.
+But what if evidence is submitted, for example $\gamma = x_1 \wedge x_2 \wedge x_3$?
+Because $\gamma$ is more specific ($|\modelsOf{\gamma}| <  |\modelsOf{\alpha}|$) a human might consider it semantically stronger in favour of the worlds in $\modelsOf{\gamma}$.
+Because all worlds in $\modelsOf{\gamma}$ are also in $\modelsOf{\alpha}$, and the agent has already established no evidence can change their mind due to \ref{AST7}, even this very specific evidence can not change the relative ordering of worlds.
+Different operators might weaken \ref{AST6} and \ref{AST7} to solve this apparent contradiction by modelling different strengths of evidence.
 

### 2021-02-10 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: explained belief set expansion, contraction and revision
feat: explained faithful assignment and refered to katsuno and mendelzon for details
feat: beamer notes setup
feat: few slides

@@
-%%
-% Please see https://bitbucket.org/rivanvx/beamer/wiki/Home for obtaining beamer.
-%%
+% TODO: explain contraction, revision, expansion
+% ANSWER: Ich würdes es ganz kurz erläutern im Text. Im Vortrag vielleicht nicht umbedingt.
+
+% TODO QUESTION: do we need to discuss this in ore detail? faithful assignment here:
+
+% ANSWER: Das ist eine gute Frage. So wie ich das Paper von Booth und Meyer im
+% Kopf habe werden dort die Ordnung mit epistemischen Zuständen
+% gleichgesetzt (was Darwiche und Pearl ja nicht machen). Von daher halte
+% ich das für ok es nicht im aller formalen Ausführlichkeit zu machen.
+% Aber man könnte es im einen Satz erwähnen.
+
 \documentclass[11pt]{beamer}
 \usepackage[utf8]{inputenc}
+\usepackage{pgfpages}
+\usepackage{enumitem}
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{amssymb}
+\usepackage{dsfont}
+\usepackage{tikz}
+\usepackage{pgfplots}
+\usepackage{float}
+\usepackage{stmaryrd}
+
+\newcommand{\modelsOf}[1]{\llbracket #1 \rrbracket}
 
@@
 \usecolortheme{orchid}
+
+% Notes
+% Talk using pympress: brew install pympress
+% Talk command: pympress -t 40 -n right ~/Documents/master/1901/presentation/1901_3230880_philip_heltweg_presentation.pdf
+\setbeameroption{show notes on second screen=right} % Both
+% Coloring note-pages
+\setbeamertemplate{note page}{\pagecolor{yellow!15}\insertnote\vfill\insertframenumber}
+\setbeamertemplate{note page}{
+	\pagecolor{yellow!15}
+	\medskip
+	SLIDE: \insertframenumber\\
+	TITLE: \insertframetitle,
+
+	\insertnote
+
+}
 
@@
 
-\begin{frame}
-    \frametitle{Table of Contents}
+\begin{frame}{Table of Contents}
     \tableofcontents
+
+    \note{
+        \begin{itemize}
+            \item Foo
+            \item Bar
+        \end{itemize}
+    }
 \end{frame}
 
-\section{Example}
+\section{Introduction}
 
-\begin{frame}
-    \frametitle{Sample frame title}
+\begin{frame}{Motivation}
+    How should a judge change their worldview when presented with new information?  
+    \note{
+        \begin{itemize}
+            \item Example question to motivate
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Courtroom example \footnote{inspired by \cite{Booth2011}, \cite{Darwiche1997}}}
+    \begin{itemize}
+        \item The agent is a judge in a murder trial, "John" and "Mary" are suspects
+        \item $\Sigma = \{ p, q, r\}$
+        \begin{itemize}
+            \item p = "John is the murderer"
+            \item q = "Mary is the murderer"
+            \item r = "The victim is an alien"
+        \end{itemize}
+        \item  $I_{\Sigma} = W = \{ 000, 001, 010, 011, 100, 101, 110, 111\}$ 
+    \end{itemize} 
+    \note{
+        \begin{itemize}
+            \item NOTE
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Research Context}
+    \note{
+        \begin{itemize}
+            \item Research context with areas according to darwiche
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Different types of belief}
+    \note{
+        \begin{itemize}
+            \item belief sets (AGM) vs conditional beliefs (Darwiche and Pearl) vs iterating on conditional beliefs (Booth and Meyer)
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Paper goal}
+    \note{
+        \begin{itemize}
+            \item present paper goal as defining postulates for a family of operators, functions $\ast$ for iterating on belief change revision operators
+            \item explain the concept of defining postulates for a family of operators and research in these postulates to have something to talk about, explain there are different operators and different postulates.
+this is not finding "the true one" but defining families and discussing pro/contra
+        \end{itemize}
+    }
+\end{frame}
+
+\section{Formal Background}
+
+\begin{frame}{Total preorders}
+    \begin{itemize}
+        \item Common tool to handle preference orderings over propositional worlds \cite{Booth2011}
+        \item binary relation $\leq$, total, reflexive, transitive
+        \item  $<$ strict, $\sim$ symmetric closure
+    \end{itemize}
+    \note{
+        \begin{itemize}
+            \item total (for all $x, y \in W$ either $x \leq y$ or $y \leq x$)
+            \item reflexive ($x \leq x$ for all $x \in W$)
+            \item transitive (if $x \leq y$ and $y \leq z$ then $x \leq z$)
+            \item  $<$ strict part of $\leq$
+            \item $\sim$ symmetric closure of $\leq$ (i.e. $x \sim y$ iff $x \leq y$ and $y \leq x$)
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Preorder example}
+    \begin{itemize}
+        \item Judge beliefs
+        \begin{itemize}
+            \item Murderer probably acted alone but possible that they conspired
+            \item Unlikely, but not impossible, for the victim to be an alien
+        \end{itemize} 
+        \item $\leq$ over $W$: $010 \sim 100 < 000 \sim 110 < 011 \sim 101 < 001 \sim 111$
+    \end{itemize}
+    \note{
+        \begin{itemize}
+            \item NOTE
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Preorder visualisation}
+    \begin{table}[H]
+         \centering
+        \begin{tabular}{llll}
+        $R_{1}$                      & $R_{2}$                                                                   & $R_{3}$ & $R_{4}$                      \\ \hline
+        \multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}$010$\\ $100$\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}$000$\\ $110$\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}$011$\\ $101$\end{tabular}} &
+            \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}$001$\\ $111$\end{tabular}} \\ \hline
+        \end{tabular}
+        \caption{Visualising a tpo as a linearly ordered set of ranks, as done in \cite{Booth2006}}.
+        \label{tab:visualising-a-tpo-example}
+    \end{table}
+    \note{
+        \begin{itemize}
+            \item It uses the fact that tpos can be represented as a linearly ordered set of ranks.
+Each rank of a tpo $\leq$ is defined as the equivalence classes modulo the symmetric closure of $\leq$: $[[x]]_{\sim} = \{y \mid y \sim x\}$.
+These equivalence classes are then ordered by the relation $[[x]] \leq [[y]]$ iff $x \leq y$.
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Belief Sets}
+    \note{
+        \begin{itemize}
+            \item 
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Epistemic States}
+    \note{
+        \begin{itemize}
+            \item how to extract belief sets from epistemic states
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Belief Set Revision Postulates\footnote{AGM postulates \cite{Alchourron1985}, reformulated for epistemic states by Darwiche and Pearl \cite{Darwiche1997}}}
+    \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\mathbb{E}\!*\!\arabic*$)]
+        \item\label{E1} $\qquad B(\mathbb{E}\ast\alpha) = Cn(B(\mathbb{E}\ast\alpha))$
+        \item\label{E2} $\qquad \alpha \in B(\mathbb{E}\ast\alpha)$
+        \item\label{E3} $\qquad B(\mathbb{E}\ast\alpha)  \subseteq B(\mathbb{E})+\alpha$
+        \item\label{E4} $\qquad \textrm{If } \alpha \notin B(\mathbb{E}) \textrm{ then } B(\mathbb{E}) + \alpha \subseteq B(\mathbb{E} \ast \alpha)$
+        \item\label{E5} $\qquad \textrm{If } \mathbb{E} = \mathbb{F} \textrm{ and } \alpha \equiv \beta \textrm{ then } B(\mathbb{E} \ast \alpha) = B(\mathbb{F} \ast \beta)$
+        \item\label{E6} $\qquad \bot \in B(\mathbb{E} \ast \alpha) \textrm{ iff } \models \neg \alpha$
+        \item\label{E7} $\qquad B(\mathbb{E} \ast (\alpha \wedge \beta)) \subseteq B(\mathbb{E} \ast \alpha) + \beta$
+        \item\label{E8} $\qquad \textrm{If } \neg \beta \notin B(\mathbb{E} \ast \alpha) \textrm{ then } B(\mathbb{E} \ast \alpha) + \beta \subseteq B(\mathbb{E} \ast (\alpha \wedge \beta))$
+    \end{enumerate}
+
+    \note{
+        \begin{itemize}
+            \item 
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Conditional Belief Revision Postulates\footnote{by Darwiche and Pearl \cite{Darwiche1997}}}
+    \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = (CR$\arabic*$)]
+        \item\label{CR1} $\qquad \textrm{If } v\in \modelsOf{\alpha}, w \in \modelsOf{\alpha} \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ iff } v \leq_{\mathbb{E\ast\alpha}} w$
+        \item\label{CR2} $\qquad \textrm{If } v\in \modelsOf{\neg\alpha}, w \in \modelsOf{\neg\alpha} \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ iff } v \leq_{\mathbb{E\ast\alpha}} w$
+        \item\label{CR3} $\qquad \textrm{If } v\in \modelsOf{\alpha}, w \in \modelsOf{\neg\alpha} \textrm{ then } v <_{\mathbb{E}} w \textrm{ only if } v <_{\mathbb{E\ast\alpha}} w$
+        \item\label{CR4} $\qquad \textrm{If } v\in \modelsOf{\alpha}, w \in \modelsOf{\neg\alpha} \textrm{ then } v \leq_{\mathbb{E}} w \textrm{ only if } v \leq_{\mathbb{E\ast\alpha}} w$
+    \end{enumerate}
+    \note{
+        \begin{itemize}
+            \item 
+        \end{itemize}
+    }
+\end{frame}
+
+\section{Additional metadata for tpo revision}
+\section{Booth and Meyer tpo-revision operators}
+\section{Iterating: $\preceq$-revision}
+\section{Final remarks}
+
+\begin{frame}{References}
+    \typeout{}
+    \bibliographystyle{plain}
+    \bibliography{references}
+\end{frame}
+
+\begin{frame}{Sample frame title}
     This is a text in the first frame. This is a text in the first frame. This is a text in the first frame.

### 2021-02-12 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: slides structure

@@
 \usecolortheme{orchid}
+
+\setbeamertemplate{caption}[numbered]
+\setbeamertemplate{theorems}[numbered]
+
+% TODO theorems/definitions etc should be numbered
+
+% TODO itemize dots seem to be lost
 
@@
 \section{Additional metadata for tpo revision}
+
+\begin{frame}{Enriching Epistemic States}
+    \note{
+        \begin{itemize}
+            \item W+-
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{$\leq$-faithful tpo}
+    \begin{definition}[$\leq$-faithful tpo over $W^{\pm}$ \cite{Booth2011}]
+        \label{definition:faithful-tpo}Let $\preceq \subseteq W^{\pm} \times W^{\pm}$. If $\preceq$ satisfies \ref{PREQ1}-\ref{PREQ4}, we say $\preceq$ is a $\leq$-faithful tpo (over $W^{\pm}$).
+    \end{definition}
+    \note{
+        \begin{itemize}
+            \item characteristics + definition
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}[fragile]{$\leq$-faithful tpo visualisation}
+    \begin{figure}[H]
+        \centering
+        \begin{tikzpicture}[scale=1]
+            \begin{axis}[
+                  yticklabels={,,$x_{4}$,$x_{3}$,$x_{2}$,$x_{1}$},
+                  xticklabels={,,},
+                  ytick style={draw=none},
+                  xtick style={draw=none},
+                  axis line style={draw=none}
+            ]
+            \addplot[
+                scatter,
+                scatter src=explicit symbolic,
+                mark size=3,
+                scatter/classes={
+                    empty={mark=*, fill=white},
+                    filled={mark=*, fill=black}
+                },
+                nodes near coords*={\Label},
+                visualization depends on={value \thisrow{label} \as \Label}
+            ]
+            table [meta=class] {
+                    x y class label
+
+                    3 1 empty $x_{4}^{+}$
+                    6 1 empty $x_{4}^{-}$
+
+                    2 2 empty $x_{3}^{+}$
+                    5 2 empty $x_{3}^{-}$
+
+                    1 3 empty $x_{2}^{+}$
+                    3 3 empty $x_{2}^{-}$
+
+                    1 4 empty $x_{1}^{+}$
+                    3 4 empty $x_{1}^{-}$
+            };
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Representation of $\preceq$ over $W^{\pm}$ using intervals}
+        \label{fig:example-visualisation-scatterplot}
+    \end{figure}
+
+    \note{
+        \begin{itemize}
+            \item example with sticks
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Courtroom example: $\leq$-faithful tpo}
+    \note{
+        \begin{itemize}
+            \item example for courtroom
+        \end{itemize}
+    }
+\end{frame}
+
 \section{Booth and Meyer tpo-revision operators}
+
+\begin{frame}{BM tpo-revision operator}
+    \note{
+        \begin{itemize}
+            \item definition
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Courtroom example: Revision}
+    \note{
+        \begin{itemize}
+            \item example 7, math
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Courtroom example: Revision Visualised}
+    \note{
+        \begin{itemize}
+            \item example 7, figure 4
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{BACKUP: non-prioritised revision}
+    \note{
+        \begin{itemize}
+            \item example 7, figure 4
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Properties of BM Revision Operators}
+    \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\ast\arabic*$)]
+        \item\label{AST1} $\qquad \leq_{\alpha}^{\ast} \textrm{ is a tpo over } W$
+        \item\label{AST2} $\qquad\alpha \equiv \gamma \textrm{ implies } \leq_{\alpha}^{\ast}=\leq_{\gamma}^{\ast}$
+        \item\label{AST3} $\qquad \textrm{If } x, y \in \modelsOf{\alpha} \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
+        \item\label{AST4} $\qquad \textrm{If } x, y \in \modelsOf{\neg\alpha} \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
+        \item\label{AST5} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } x \leq y \textrm{ then } x <_{\alpha}^{\ast} y$
+        \item\label{AST6} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } y \leq_{\alpha}^{\ast} x \textrm{ then } y \leq_{\gamma}^{\ast} x$
+        \item\label{AST7} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } y <_{\alpha}^{\ast} x \textrm{ then } y <_{\gamma}^{\ast} x$
+    \end{enumerate}
+
+    \note{
+        \begin{itemize}
+            \item properties
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Family of BM Revision Operators}
+    \begin{theorem}
+        \label{theorem:revision-operator}Let $\ast$ be any revision operator for $\leq$.
+Then $\ast$ is generated from some $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ iff $\ast$ satisfies \ref{AST1}-\ref{AST7}.
+\cite{Booth2011}
+    \end{theorem}
+
+    \note{
+        \begin{itemize}
+            \item theorem 1
+        \end{itemize}
+    }
+\end{frame}
+
 \section{Iterating: $\preceq$-revision}
+
+\begin{frame}{A concrete operator}
+    \note{
+        \begin{itemize}
+            \item math for operator
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Courtroom Example: A concrete operator}
+    \note{
+        \begin{itemize}
+            \item math for example with operator
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Courtroom Example: Visualised}
+    \note{
+        \begin{itemize}
+            \item figure 6
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Courtroom Example: Conditional beliefs 1}
+    \note{
+        \begin{itemize}
+            \item figure 7
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Courtroom Example: Conditional beliefs 2}
+    \note{
+        \begin{itemize}
+            \item figure 8
+        \end{itemize}
+    }
+\end{frame}
+
 \section{Final remarks}

### 2021-02-12 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: some more slides + brought back itemize dots

@@
 \usepackage{pgfpages}
-\usepackage{enumitem}
 \usepackage{amsmath}
@@
 
+\usepackage{enumitem}
+\setitemize{label=\usebeamerfont*{itemize item}
+  \usebeamercolor[fg]{itemize item}
+  \usebeamertemplate{itemize item}}
+
 \newcommand{\modelsOf}[1]{\llbracket #1 \rrbracket}
@@
 \setbeamertemplate{theorems}[numbered]
-
-% TODO theorems/definitions etc should be numbered
-
-% TODO itemize dots seem to be lost
 
@@
 \begin{frame}{Enriching Epistemic States}
+    \begin{itemize}
+        \item $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$
+        \item $w \in \modelsOf{\alpha}$ / $w \in \modelsOf{\neg\alpha}$
+        \item $(w^{+}, w^{-})$
+    \end{itemize}
     \note{
@@
 
-\begin{frame}{Courtroom example: $\leq$-faithful tpo}
+\begin{frame}[fragile]{Courtroom example: $\leq$-faithful tpo}
+   \begin{figure}[H]
+            \centering
+            \begin{tikzpicture}[scale=1]
+                \begin{axis}[
+                        xticklabels={},
+                        yticklabels={},
+                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
+                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
+                        ytick style={draw=none},
+                        xtick style={draw=none},
+                        axis line style={draw=none}
+                ]
+                \addplot[
+                    scatter,
+                    scatter src=explicit symbolic,
+                    mark size=3,
+                    scatter/classes={
+                        empty={mark=*, fill=white},
+                        filled={mark=*, fill=black}
+                    },
+                    nodes near coords*={\Label},
+                    visualization depends on={value \thisrow{label} \as \Label}
+                ]
+                table [meta=class] {
+                        x y class label
+
+                        1 8 empty \empty
+                        3 8 empty
+
+                        1 7 empty 
+                        3 7 empty
+
+                        2 6 empty 
+                        4 6 empty
+
+                        2 5 empty 
+                        4 5 empty
+
+                        5 4 empty 
+                        7 4 empty
+
+                        5 3 empty 
+                        7 3 empty
+
+                        6 2 empty 
+                        8 2 empty
+
+                        6 1 empty 
+                        8 1 empty
+                        };
+                \end{axis}
+            \end{tikzpicture}
+            \caption{Representation of $\preceq$ over $W^{\pm}$ for the courtroom example \ref{example:example-introduction}}
+            \label{fig:example-tpo-initial}
+    \end{figure}
+
     \note{
@@
 \begin{frame}{BM tpo-revision operator}
+    \begin{definition}[Revision operator $\ast_{\preceq}$ for $\leq$ generated by $\preceq$ \cite{Booth2011}]
+        \label{definition:revision-operator}
+        For each $\leq$-faithful tpo $\preceq$ over $W^{\pm}$, refer to $\ast_{\preceq}$ as the revision operator for $\leq$ generated by $\preceq$ defined by:
+
+        Set for any $\alpha \in L$ and $x \in W$:
+        \begin{equation*}
+            r_{\alpha}(x) = \left\{
+                        \begin{array}{ll}
+                          x^{+} \textrm{ if } x \in \modelsOf{\alpha}\\
+                          x^{-} \textrm{ if } x \in \modelsOf{\neg\alpha}
+                        \end{array}
+                      \right.
+        \end{equation*}
+
+        The revised tpo $\leq_{\alpha}^{\ast}$ is defined by setting, for each $x, y \in W$,
+
+        \begin{equation*}
+            x \leq_{\alpha}^{\ast} y \textrm{ iff } r_{\alpha}(x) \preceq r_{\alpha}(y)
+        \end{equation*}
+    \end{definition}
+
     \note{
@@
             \item definition
+        \end{itemize}
+    }\include{figures/example-visualisation-scatterplot}
+\end{frame}
+
+\begin{frame}[fragile]{Courtroom example: Revision Visualised}
+
+    \begin{figure}[H]
+            \centering
+            \begin{tikzpicture}[scale=1]
+                \begin{axis}[
+                        xticklabels={},
+                        yticklabels={},
+                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
+                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
+                        ytick style={draw=none},
+                        xtick style={draw=none},
+                        axis line style={draw=none}
+                ]
+                \addplot[
+                    scatter,
+                    scatter src=explicit symbolic,
+                    mark size=3,
+                    scatter/classes={
+                        empty={mark=*, fill=white},
+                        filled={mark=*, fill=black}
+                    },
+                    nodes near coords*={\Label},
+                    visualization depends on={value \thisrow{label} \as \Label}
+                ]
+                table [meta=class] {
+                        x y class label
+
+                        1 8 empty \empty
+                        3 8 filled
+
+                        1 7 filled 
+                        3 7 empty
+
+                        2 6 empty 
+                        4 6 filled
+
+                        2 5 filled 
+                        4 5 empty
+
+                        5 4 empty 
+                        7 4 filled
+
+                        5 3 filled 
+                        7 3 empty
+
+                        6 2 empty 
+                        8 2 filled
+
+                        6 1 filled 
+                        8 1 empty
+                        };
+                \end{axis}
+            \end{tikzpicture}
+            \caption{Associating positive and negative representations of worlds after receiving evidence $\alpha=p$}
+            \label{fig:example-tpo-revised}
+    \end{figure}
+
+    \note{
+        \begin{itemize}
+            \item example 7, figure 4
         \end{itemize}
@@
 \begin{frame}{Courtroom example: Revision}
+
+    \begin{itemize}
+        \item for $010, 110 \in W$, $010 \leq 110$ before, revise by $\alpha = p$
+    \end{itemize}
+
+    \begin{equation*}
+        010 \in \modelsOf{\neg\alpha} \textrm{ : } r_{\alpha}(010) = 010^{-}
+    \end{equation*}
+    \begin{equation*}
+        110 \in \modelsOf{\alpha} \textrm{ : } r_{\alpha}(110) = 110^{+}
+    \end{equation*}
+
+    \begin{itemize}
+        \item $110^{+} \prec 010^{-}$ is true, set $110 <_{\alpha}^{\ast} 010$
+        \item new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$
+        \item $\modelsOf{B(\mathbb{E})} = min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".
+        \item $\leq_{\alpha}^{\ast}$ as representation of the conditional beliefs
+        \begin{itemize}
+            \item before $010 \leq 110$: "Both suspects being the murderer is less plausible than Mary being the murderer"
+            \item now $110 <_{\alpha}^{\ast} 010$: "Only Mary being the murderer less plausible than both conspiring".
+        \end{itemize}
+    \end{itemize}
+
     \note{
@@
             \item example 7, math
-        \end{itemize}
-    }
-\end{frame}
-
-\begin{frame}{Courtroom example: Revision Visualised}
-    \note{
-        \begin{itemize}
-            \item example 7, figure 4
         \end{itemize}

### 2021-02-15 paper/1901_3230880_philip_heltweg.tex
fix: minor spelling correction
fix: various small writing fixes, commas, figure numbering

@@
 In their paper "How to Revise a Total Preorder", Booth and Meyer present an approach to revising preorders for iterated belief revision.
-Their operator is based on assigning abstract intervals of plausibility to worlds depending on new evidence supporting them or not.
+Their operator is based on assigning abstract intervals of plausibility to worlds, depending on new evidence supporting them or not.
 
@@
 As an agent can be human or machine, work in belief change has impact on the fields of both philosophy and artificial intelligence \cite{Ferme2011}.
-Different approaches to handling belief change have been discussed with notable approaches including nonmonotonic logic, probabilistic reasoning and belief revision \cite{Darwiche1997}.
+Different approaches to handling belief change have been discussed, with notable approaches including nonmonotonic logic, probabilistic reasoning and belief revision \cite{Darwiche1997}.
 
@@
 In "How to Revise a Total Preorder", Booth and Meyer describe how to model the change of these total preorders when new evidence becomes available.
-Being able to derive a new tpo from additional evidence is an approach to handling multiple revision steps.
+Being able to derive a new tpo from additional evidence is a way to handle consecutive revision steps.
 It therefore places the article in the field of iterated belief revision.
@@
 The structure of the synopsis will be as follows: Establish the context of the paper by presenting the research area of iterated belief revision and how it relates to other areas of artificial intelligence and philosophy.
-To create a shared understanding of notation and definitions section \ref{section:formal-background} will discuss formal background and other, previous, approaches to belief change.
-It will also introduce the main contribution of this synopsis, an accompanying example demonstrating tpo-revision as described by Booth and Meyer.
-After building a foundation, section \ref{section:booth-and-meyer-tpo-revision-operators} and \ref{section:properties-of-bm-tpo-revision-operators} will present part of the work from the original paper "How to Revise a Total Preorder" \cite{Booth2011}.
+To create a shared understanding of notation and definitions section \ref{section:formal-background} discusses formal background and other, previous, approaches to belief change.
+It also introduces the main contribution of this synopsis, an accompanying example demonstrating tpo-revision as described by Booth and Meyer.
+After building this foundation, section \ref{section:booth-and-meyer-tpo-revision-operators} and \ref{section:properties-of-bm-tpo-revision-operators} present selected parts of the work from the original paper "How to Revise a Total Preorder" \cite{Booth2011}.
 Section \ref{section:booth-and-meyer-tpo-revision-operators} establishes and defines functions $\ast$, used to revise tpos.
-In section \ref{section:properties-of-bm-tpo-revision-operators} properties of these functions will be presented.
-To provide an outlook into the additional work done by Booth and Meyer, \ref{section:iterating-preceq-revision} will show their proposal of a concrete operator for tpo-revision.
+In section \ref{section:properties-of-bm-tpo-revision-operators} properties of these functions are presented.
+To provide an outlook into the additional work done by Booth and Meyer, section \ref{section:iterating-preceq-revision} will show their proposal of a concrete operator for tpo-revision.
 It includes several examples and adapted visualisations of the operator being applied in the context of the accompanying example.
@@
 
-For any set of worlds $S \subseteq W$ of worlds, $Th(S)$ is the set of sentences true in all worlds in $S$.
+For any set of worlds $S \subseteq W$, $Th(S)$ is the set of sentences true in all worlds in $S$.
 
@@
 A total preorder is a binary relation $\leq$ (in this context over the set of propositional worlds $W$) that is total, reflexive and transitive (i.e.
-for all $x, y, z \in W$ either $x \leq y$ or $y \leq x$, $x \leq x$ and if $x \leq y$ and $y \leq z$ then $x \leq z$).
+for all $x, y, z \in W$: either $x \leq y$ or $y \leq x$, $x \leq x$ and if $x \leq y$ and $y \leq z$, then $x \leq z$).
 
@@
 Alchourrón, Gärdenfors, and Makinson (AGM theory, \cite{Alchourron1985}) define postulates for belief sets and their expansion, contraction or revision with new evidence.
-Belief set expansion is the process of incorporating a new piece of evidence that is not inconsistent with currently held beliefs while contraction refers to giving up a belief that has become questionable.
-The process of belief revision refers to keeping an agent's set of beliefs consistent while incorporating new information that is inconsistent with the current belief set \cite{Katsuno1991, Gaerdenfors1984}.
+Belief set expansion is the process of incorporating a new piece of evidence that is not inconsistent with currently held beliefs.
+Contraction refers to giving up a belief that has become questionable.
+The process of belief revision refers to keeping an agent's set of beliefs consistent, while incorporating new information that can be inconsistent with the current belief set \cite{Katsuno1991, Gaerdenfors1984}.
+% TODO: mention this addition in email
+
 Darwiche and Pearl \cite{Darwiche1997} argue that working with belief sets is not expressive enough for satisfying results in iterated belief revision.
@@
 
-Darwiche and Pearl show that their version of belief revision on epistemic states can be modelled with a tpo $\leq_{\mathbb{E}}$, associated with $\mathbb{E}$.
+Darwiche and Pearl show that their version of belief revision can be modelled with a tpo $\leq_{\mathbb{E}}$, associated with an epistemic state $\mathbb{E}$.
 A mapping of a belief state $\mathbb{E}$ to a tpo $\leq_{\mathbb{E}}$, that maintains the belief set, is is called a faithful assignment.
@@
 
-To guarantee the ability to extract unique belief sets from epistemic states after a revision by $\alpha$, Booth and Meyer \cite{Booth2011} require consistent epistemic inputs.
+To guarantee the ability to extract unique belief sets from epistemic states after a revision by $\alpha$, Booth and Meyer require consistent epistemic inputs \cite{Booth2011}.
 That means dropping \ref{E6} and considering only \ref{E1}-\ref{E5} and \ref{E7}-\ref{E8} for their belief revision postulates, named DP-AGM.
 
-The DP-AGM postulates put restrictions how the belief set of an agent changes after revision of new evidence $\alpha$.
-As outlined before belief sets can be extracted from epistemic states by taking the set of formulae true in all most plausible worlds after revision by $\alpha$, defined as $\modelsOf{B(\mathbb{E}\ast\alpha)} = min(\alpha, \leq_{\mathbb{E}})$.
+The DP-AGM postulates put restrictions on how the belief set of an agent changes after revision with new evidence $\alpha$.
+As outlined before, belief sets can be extracted from epistemic states by taking the set of formulae true in all most plausible worlds after revision by $\alpha$.
 
@@
 \section{Additional metadata for tpo revision}
-After discussing notation and previous research, the following chapters present an excerpt of the new work done by Booth and Meyer in \cite{Booth2011}.
+After discussing notation and previous research, the following sections present an excerpt of the new work done by Booth and Meyer in \cite{Booth2011}.
 To support their approach to tpo revision, Booth and Meyer propose adding additional metadata to epistemic states.
@@
 In this notation a world $w \in W$ is represented twice: When new evidence $\alpha$ arrives that makes $w$ more plausible (because $w \in \modelsOf{\alpha}$), the agent can assume it's positive representation as $w^{+} \in W^{\pm}$.
-In contrast, if the new evidence makes $w$ less plausible ($w \notin \modelsOf{\alpha}$), then the negative representation $w^{-} \in W^{\pm}$ is the agent's view of $w$.
+In contrast, if the new evidence makes $w$ less plausible ($w \in \modelsOf{\neg\alpha}$), then the negative representation $w^{-} \in W^{\pm}$ is the agent's view of $w$.
 Booth and Meyer call the pair $(w^{+}, w^{-})$ the positive/negative representation of the world $w$.
-They are an abstract interval, representing metadata about plausibility assumptions about $w$.
+They are an abstract interval, representing metadata about plausibility assumptions for $w$.
 
 \subsection{$\leq$-faithful tpos}
-For the ordering on $W^{\pm}$ Booth and Meyer suppose an additional relation, denoted $\preceq$ over $W^{\pm}$, that is added to the epistemic state of an agent.
+For the ordering on $W^{\pm}$, Booth and Meyer suppose an additional relation, denoted $\preceq$ over $W^{\pm}$, that is added to the epistemic state of an agent.
 
@@
 Therefore a tpo over $W$ can be visualised by displaying every $w \in W$ in a table that has one column for every rank (like in Table \ref{tab:visualising-a-tpo-example}).
-To visualise the interval ordering introduced by $\preceq$, Booth and Meyer use an interval with the endpoints defined as $w^{+}$/$w^{-}$ respectively.
+To visualise the ordering introduced by $\preceq$, Booth and Meyer use an interval with the endpoints defined as $w^{+}$/$w^{-}$ respectively.
 This type of visualisation was first introduced in a previous paper by Booth and Meyer themselves \cite{Booth2007} and is shown in Figure \ref{fig:example-visualisation-scatterplot}.
@@
    The worlds on lower ranks (more on the left) are preferred and assumed to be more plausible.
-Here for example $x_{1}^{+} \prec x_{3}^{+}$ and $x_{1}^{-} \sim x_{4}^{+}$ Note that, even though all intervals have the same length in this example, that is not required.
+Here for example $x_{1}^{+} \prec x_{3}^{+}$ and $x_{1}^{-} \sim x_{4}^{+}$.
+Note, even though all intervals have the same length in this example, that is not required.
 \end{example}
@@
 
-The choice between positive or negative representations of two worlds should be the same as under $\leq$ (due to \ref{PREQ2}, \ref{PREQ3}).
-According to \ref{PREQ4} there has to be a difference between a positive representation and a negative representation of the same world and given the choice between both, the positive representation has to be chosen.
+The choice between positive or negative representations of two worlds should be the same as under $\leq$ (due to \ref{PREQ2} and \ref{PREQ3}).
+According to \ref{PREQ4} there has to be a difference between a positive representation and a negative representation of the same world.
+Given the choice between both, the positive representation has to be chosen.
 
@@
         \end{tikzpicture}
+        \caption{A tpo $\preceq$ over $W^{\pm}$}
+        \label{fig:example-not-tpo}
     \end{figure}
 
-    $\preceq$ is not a $\leq$-faithful tpo: Even though \ref{PREQ1} and \ref{PREQ4} are satisfied, $\preceq$ is not a $\leq$-faithful tpo: From \ref{PREQ2} and $x_{1}^{+} \prec x_{2}^{+}$ follows $x_{1} < x_{2}$.
+    Even though \ref{PREQ1} and \ref{PREQ4} are satisfied, $\preceq$ is not a $\leq$-faithful tpo: From \ref{PREQ2} and $x_{1}^{+} \prec x_{2}^{+}$ follows $x_{1} < x_{2}$.
 That means \ref{PREQ3} can not hold as $x_{2}^{-} \prec x_{1}^{-}$ which would require $x_{2} < x_{3}$ to be true.
@@
 
+% TODO: check if figures are on the right pages with their text
+
 \begin{example}
     \label{example:example-tpo-initial}
-    Continuing the courtroom demonstration introduced in Example \ref{example:example-introduction} of a judge deciding on a verdict on the suspects John and Mary.
+    Continuing the courtroom demonstration, introduced in Example \ref{example:example-introduction} of a judge deciding on a verdict on the suspects John and Mary.
 Figure \ref{fig:example-tpo-initial} shows a possible version of a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ from which the tpo $\leq$ from Table \ref{tab:visualising-a-tpo-example} can be reconstructed.
@@
             \end{tikzpicture}
-            \caption{Representation of $\preceq$ over $W^{\pm}$ for the courtroom example \ref{example:example-introduction}}
+            \caption{Representation of $\preceq$ over $W^{\pm}$ for the courtroom Example \ref{example:example-introduction}}
             \label{fig:example-tpo-initial}
@@
 \label{section:booth-and-meyer-tpo-revision-operators}
-Booth and Meyer \cite{Booth2011} discussed tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$.
+Booth and Meyer discuss tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$ \cite{Booth2011}.
 They define how to use the additional information from a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ to create a revision operator $\ast_{\preceq}$ (from now on referred to as BM tpo-revision operators).
@@
     \label{example:example-tpo-revised}
-    A more complex example is the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ (for the courtroom Example \ref{example:example-introduction}) using the $\leq$-faithful tpo $\preceq$, introduced in Example \ref{example:example-tpo-initial} and shown in Figure \ref{fig:example-tpo-revised}.
+    A more complex example is the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ (for the courtroom Example \ref{example:example-introduction}), using the $\leq$-faithful tpo $\preceq$, introduced in Example \ref{example:example-tpo-initial} and shown in Figure \ref{fig:example-tpo-revised}.
 In this case the new evidence received points to John being the murderer so $\alpha = p$.
@@
 
-    For the worlds $010, 110 \in W$, $010 \leq 110$ was true. To rank them with the revised tpo $\leq_{\alpha}^{\ast}$ calculate:
+    For the worlds $010, 110 \in W$, $010 < 110$ was true. To rank them with the revised tpo $\leq_{\alpha}^{\ast}$ calculate:
 
@@
     Repeating for every world in $W$, the new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$.
-Unsurprisingly, the belief set associated with the new epistemic state is $\modelsOf{B(\mathbb{E})} = min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".
-
-    As $\leq_{\alpha}^{\ast}$ is a representation of the conditional beliefs of the agent, it is also interesting to look at the changes for them: Initially the judge thought both suspects being the murderers ($110$) was less plausible than only Mary being the murderer ($010$).
+Unsurprisingly, the belief set associated with the new epistemic state is $Th(min(\top, \leq_{\mathbb{E}})) = Th(\{100\})$: "John is the only murderer and the victim is not an alien".
+
+    As $\leq_{\alpha}^{\ast}$ is a representation of the conditional beliefs of the agent, it is also interesting to look at how they changed: Initially the judge thought both suspects being the murderers ($110$) was less plausible than only Mary being the murderer ($010$).
 Now they have updated their conditional beliefs to think only Mary being the murderer less plausible than both conspiring.
@@
 
-    Since the agent considered the victim being an alien very unlikely, even the positive representations of worlds in $\modelsOf{\alpha}$ are on higher ranks (so considered less plausible) than negative representations of worlds in $\modelsOf{\neg\alpha}$.
+    Because the agent considered the victim being an alien very unlikely, even the positive representations of worlds in $\modelsOf{\alpha}$ are on higher ranks (so considered less plausible) than negative representations of worlds in $\modelsOf{\neg\alpha}$.
     The belief set $B(\mathbb{E})$ of the agent is unchanged under $\leq_{\alpha}^{\ast}$, since $\{010, 100\}$ are still the most plausible worlds, and does not include $r$ "the victim is an alien".
@@
 This is in contrast to revision strategies like natural revision by Boutilier \cite{Boutilier1996} that minimise change in conditional beliefs.
+% TODO: mention this addition in email
+
+% TODO: question marks in references/figures etc!
+
 If revising a tpo by a sentence $\alpha$, the relative ordering of worlds that are either both $\modelsOf{\alpha}$- or $\modelsOf{\neg\alpha}$-worlds, must stay the same (\ref{AST3}/\ref{AST4}).
 These properties were already part of the semantic postulates \ref{CR1} and \ref{CR2} by Darwiche and Pearl \cite{Darwiche1997} discussed in section \ref{chapter:dp-agm-postulates}.
+
 In a similar way \ref{AST5} is a stronger requirement than the other two Darwiche and Pearl postulates \ref{CR3} and \ref{CR4}.
-It means the following: A world $x$ that is considered at least as plausible as a world $y$ before a revision by new information $\alpha$.
-If $\alpha$ makes $x$ more plausible ($x \in \modelsOf{\alpha}$) and $y$ less plausible ($y \in \modelsOf{\neg\alpha}$) then after revision $x$ should be considered strictly more plausible than $y$.
-This rule was not only proposed by Booth and Meyer \cite{Booth2006a} but also by Jin und Thielscher in \cite{Jin2007} (as the postulate of independence).
+It means the following: When a world $x$ is considered at least as plausible as a world $y$ before a revision by new information $\alpha$: If $\alpha$ makes $x$ more plausible ($x \in \modelsOf{\alpha}$) and $y$ less plausible ($y \in \modelsOf{\neg\alpha}$), then after revision by $\alpha$, $x$ should be considered strictly more plausible than $y$.
+This property was not only proposed by Booth and Meyer \cite{Booth2006a} but also by Jin und Thielscher in \cite{Jin2007} (as the postulate of independence).
 
@@
 These properties are largely ignored in other literature on iterated belief change \cite{Booth2011}.
-\ref{AST6} means that if, after revision by evidence $\alpha$, that makes a world $x$ more plausible than $y$, $y$ is still considered at least as plausible as $x$, then for any possible revision by evidence $\gamma$, $y$ must still be at least as plausible as $x$.
+\ref{AST6} means that if, after revision by evidence $\alpha$ that makes a world $x$ more plausible than $y$, $y$ is still considered at least as plausible as $x$, then for revision by any possible evidence $\gamma$, $y$ must still be at least as plausible as $x$.
 \ref{AST7} is the equivalent property for strict preference.
@@
 
-With these properties for $\ast$ discussed, Booth and Meyer define the family of operators they are discussing with theorem \ref{theorem:revision-operator}.
+With these properties for $\ast$ outlined, Booth and Meyer define the family of operators they are discussing with Theorem \ref{theorem:revision-operator}.
 
@@
 Otherwise, as Booth and Meyer put it, the problem has just "re-emerged 'one level up'" \cite{Booth2011}.
-In their study, they discuss strict preference hierarchies (SPHs), an equivalent structure to $\preceq$, denoted as $\$$, their properties and how to revise them.
+In their paper, they discuss strict preference hierarchies (SPHs), an equivalent structure to $\preceq$, their properties and how to revise them.
 
@@
 The smaller $p(x^{\epsilon})$ is, the more plausible the world is.
-The interval $(x^{+}, x^{-})$, represents a world $x \in W$ using its representations $x^{+}, x^{-} \in W^{\pm}$.
+The interval $(x^{+}, x^{-})$ represents a world $x \in W$ using its representations $x^{+}, x^{-} \in W^{\pm}$.
 For revision on the basis of $p$, it becomes an interval of real numbers $(p(x^{+}), p(x^{-}))$ with length $a$.
@@
 Other operators are possible and an area of further research \cite{Booth2011}.
-They achieve this by setting $p$, for every $x^{\epsilon} \in W^{\pm}$ to:
+They achieve this by setting $p$, for every $x^{\epsilon} \in W^{\pm}$, to:
 
@@
 Figure \ref{fig:example-preceq-revised} shows the revised tpo $\preceq_{\alpha}$ with $\neg\alpha$-worlds moved back by $a$.
-The position of their previous positive representation is displayed as x.
+The position of their previous positive representation is displayed as a cross.
 
@@
 
-    In the second step $p$ is revised by $\alpha$ to $p \ast \alpha$. The $\neg\alpha$-world $010$ is moved back by $a$, while the $\alpha$-world $100$ is unchanged:
+    In the second step, $p$ is revised by $\alpha$ to $p \ast \alpha$. The $\neg\alpha$-world $010$ is moved back by $a$, while the $\alpha$-world $100$ is unchanged:
 
@@
     For an example that demonstrates the impact the revision of $\preceq$ has on the acceptance of conditional beliefs, consider again the courtroom Example \ref{example:example-introduction}.
-The fact that the victim is an alien ($r=\textrm{true}$) seems very unlikely, which is modelled by the gap between $\modelsOf{r}$-worlds and $\modelsOf{\neg r}$-worlds.
+The fact that the victim is an alien ($r=\textrm{true}$) seems very unlikely, which is modelled by the gap between $\modelsOf{r}$-worlds and $\modelsOf{\neg r}$-worlds as mentioned in Example \ref{example:example-tpo-initial}.
 
@@
     What did change is the willingness of the agent to accept conditional beliefs about $r$ being true in light of future evidence.
-This is reflected by the revised structure $\preceq_{p \ast \alpha}$ shown in Figure \ref{fig:example-preceq-revised-alien2}.
+This is reflected by the revised structure $\preceq_{p \ast \alpha}$ shown in Figure \ref{fig:example-preceq-revised-alien}.
 
@@
     Notice how the gap between $\modelsOf{\neg r}$- and $\modelsOf{r}$-worlds has now closed.
-After revising $\preceq_{p \ast \alpha}$ for a second piece of evidence $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$ ("the murderer was either John or Mary, not both") the new tpo $\leq_{\alpha \ast \beta}^{\ast}$ can be read from the filled dots in Figure \ref{fig:example-preceq-revised-alien2}.
+After revising $\preceq_{p \ast \alpha}$ for a second piece of evidence $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$ ("the murderer was either John or Mary, not both"), the new tpo $\leq_{\alpha \ast \beta}^{\ast}$ can be read from the filled dots in Figure \ref{fig:example-preceq-revised-alien2}.
 
@@
 The featured paper "How to Revise a Total Preorder" by Booth and Meyer \cite{Booth2011} is a comprehensive work on using interval orderings for belief change.
-This synopsis focused on presenting the research context and previous work in iterated belief change as well as the concrete tpo-revision based on the additional structure of $\leq$-faithful tpos.
+This synopsis focused on presenting the research context and previous work in iterated belief change, as well as the concrete tpo-revision based on the additional structure of $\leq$-faithful tpos.
 A consistent example including a trial situation (adapted from \cite{Darwiche1997} and \cite{Booth2011}) was used to accompany the discussion of the paper.
@@
 The idea to define an interval of plausibility for worlds depending on if evidence supports them or not does make intuitive sense.
-A view largely missing from the paper is the discussion of the different impact and quality of new information itself.
 
@@
 Especially high quality evidence for a very unlikely type of world might change an agents plausibility ordering, while low quality evidence that is very expected might not.
-Consider the following situation in a world described by the set of propositional variables $\{x_1, x_2, x_3, y\}$: New evidence $\alpha = x_1$ arrives that  makes a world $x$, with $x_1$ being true, more likely.
+Consider the following situation in a world described by the set of propositional variables $\{x_1, x_2, x_3, y_1\}$: New evidence $\alpha = x_1$ arrives that  makes a world $x$, with $x_1$ being true, more likely.
 But, because $\alpha$ is just one piece of fairly unspecific evidence among many, the agent still considers a world $y$ to be more plausible.

### 2021-02-15 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: some more slides

@@
 \begin{frame}{A concrete operator}
+    \begin{itemize}
+        \item $p: W^{\pm} \mapsto \mathds{R}$
+        \item $p(x^{-}) - p(x^{+}) = a > 0$
+        \item $x^{\epsilon} \preceq_{p} y^{\delta} \textrm{ iff } p(x^{\epsilon}) \leq p(y^{\delta})$
+        \item Set $p$, for every $x^{\epsilon} \in W^{\pm}$, to:
+    \end{itemize}
+
+    \begin{equation*}
+        (p \ast \alpha)(x^{\epsilon}) = \left\{
+                        \begin{array}{ll}
+                          p(x^{\epsilon}) \textrm{ if } x \in \modelsOf{\alpha}\\
+                          p(x^{\epsilon}) + a \textrm{ if } x \in \modelsOf{\neg\alpha}
+                        \end{array}
+                      \right.
+    \end{equation*}
+
     \note{
@@
 \begin{frame}{Courtroom Example: A concrete operator}
+    \begin{itemize}
+        \item Choose initial $p$ so that $\preceq_{p} = \preceq$
+        \begin{itemize}
+            \item $010 \textrm{ : } (p(010^{+}), p(010^{-})) = (0, a)$.
+            \item $100 \textrm{ : } (p(100^{+}), p(100^{-})) = (0, a)$.
+        \end{itemize}
+        \item Revise $p$ by $\alpha$ to $p \ast \alpha$
+        \begin{itemize}
+            \item $010 \in \modelsOf{\neg\alpha} \textrm{ : } (p(010^{-}), p(010^{-}) + a) = (a, 2a)$
+            \item $100 \in \modelsOf{\alpha} \textrm{ : } (p(100^{+}), p(100^{-})) = (0, a)$
+        \end{itemize}
+            \end{itemize}
+
     \note{
@@
 
-\begin{frame}{Courtroom Example: Visualised}
-    \note{
-        \begin{itemize}
-            \item figure 6
-        \end{itemize}
-    }
-\end{frame}
+\begin{frame}[fragile]{Courtroom Example: Visualised}
+    \begin{figure}[H]
+            \centering
+            \begin{tikzpicture}[scale=1]
+                \begin{axis}[
+                        xticklabels={},
+                        yticklabels={},
+                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
+                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
+                        ytick style={draw=none},
+                        xtick style={draw=none},
+                        axis line style={draw=none}
+                ]
+                \addplot[
+                    scatter,
+                    scatter src=explicit symbolic,
+                    mark size=3,
+                    scatter/classes={
+                        empty={mark=*, fill=white},
+                        old={mark=x, fill=white}
+                    },
+                    nodes near coords*={\Label},
+                    visualization depends on={value \thisrow{label} \as \Label}
+                ]
+                table [meta=class] {
+                        x y class label
 
-\begin{frame}{Courtroom Example: Conditional beliefs 1}
+                        1 8 old \empty
+
+                        3 8 empty
+                        5 8 empty
+
+                        1 7 empty 
+                        3 7 empty
+
+                        2 6 old
+
+                        4 6 empty
+                        6 6 empty
+
+                        2 5 empty 
+                        4 5 empty
+
+                        5 4 old
+
+                        7 4 empty
+                        9 4 empty
+
+                        5 3 empty 
+                        7 3 empty
+
+                        6 2 old
+
+                        8 2 empty
+                        10 2 empty
+
+                        6 1 empty 
+                        8 1 empty
+                        };
+                \end{axis}
+            \end{tikzpicture}
+            \caption{$\preceq_{p \ast \alpha}$ for $\alpha = p$}
+            \label{fig:example-preceq-revised}
+    \end{figure}
+
     \note{
@@
 
-\begin{frame}{Courtroom Example: Conditional beliefs 2}
+\begin{frame}[fragile]{Courtroom Example: Conditional beliefs 1}
+    \begin{figure}[H]
+            \centering
+            \begin{tikzpicture}[scale=1]
+                \begin{axis}[
+                        xticklabels={},
+                        yticklabels={},
+                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
+                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
+                        ytick style={draw=none},
+                        xtick style={draw=none},
+                        axis line style={draw=none}
+                ]
+                \addplot[
+                    scatter,
+                    scatter src=explicit symbolic,
+                    mark size=3,
+                    scatter/classes={
+                        empty={mark=*, fill=white},
+                        old={mark=x, fill=white}
+                    },
+                    nodes near coords*={\Label},
+                    visualization depends on={value \thisrow{label} \as \Label}
+                ]
+                table [meta=class] {
+                        x y class label
+
+                        1 8 old \empty
+
+                        3 8 empty
+                        5 8 empty
+
+                        1 7 old
+
+                        3 7 empty 
+                        5 7 empty
+
+                        2 6 old
+
+                        4 6 empty
+                        6 6 empty
+
+                        2 5 old
+
+                        4 5 empty 
+                        6 5 empty
+
+                        5 4 empty
+                        7 4 empty
+
+                        5 3 empty 
+                        7 3 empty
+
+                        6 2 empty
+                        8 2 empty
+
+                        6 1 empty 
+                        8 1 empty
+                        };
+                \end{axis}
+            \end{tikzpicture}
+            \caption{$\preceq_{p \ast \alpha}$ for $\alpha = r$}
+            \label{fig:example-preceq-revised-alien}
+    \end{figure}
+
     \note{
@@
 
-\section{Final remarks}
+\begin{frame}[fragile]{Courtroom Example: Conditional beliefs 2}
+    \begin{figure}[H]
+            \centering
+            \begin{tikzpicture}[scale=1]
+                \begin{axis}[
+                        xticklabels={},
+                        yticklabels={},
+                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
+                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
+                        ytick style={draw=none},
+                        xtick style={draw=none},
+                        axis line style={draw=none}
+                ]
+                \addplot[
+                    scatter,
+                    scatter src=explicit symbolic,
+                    mark size=3,
+                    scatter/classes={
+                        empty={mark=*, fill=white},
+                        filled={mark=*, fill=black},
+                        old={mark=x, fill=white}
+                    },
+                    nodes near coords*={\Label},
+                    visualization depends on={value \thisrow{label} \as \Label}
+                ]
+                table [meta=class] {
+                        x y class label
+
+                        1 8 old \empty
+
+                        3 8 filled
+                        5 8 empty
+
+                        1 7 old
+
+                        3 7 filled 
+                        5 7 empty
+
+                        2 6 old
+
+                        4 6 empty
+                        6 6 filled
+
+                        2 5 old
+
+                        4 5 empty 
+                        6 5 filled
+
+                        5 4 filled
+                        7 4 empty
+
+                        5 3 filled 
+                        7 3 empty
+
+                        6 2 empty
+                        8 2 filled
+
+                        6 1 empty 
+                        8 1 filled
+                        };
+                \end{axis}
+            \end{tikzpicture}
+            \caption{$\preceq_{p \ast \alpha \ast \beta}$ for $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$}
+            \label{fig:example-preceq-revised-alien2}
+    \end{figure}
+
+    \note{
+        \begin{itemize}
+            \item figure 9
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{}
+  \centering \Huge
+  Thank You
+\end{frame}
 
@@
 
-\begin{frame}{Sample frame title}
-    This is a text in the first frame. This is a text in the first frame. This is a text in the first frame.
-\end{frame}
-
-\begin{frame}
-\frametitle{Sample frame title}
-
-In this slide, some important text will be
-\alert{highlighted} because it's important.
-Please, don't abuse it.
-
-\begin{block}{Remark}
-Sample text
-\end{block}
-
-\begin{alertblock}{Important theorem}
-Sample text in red box
-\end{alertblock}
-
-\begin{examples}
-Sample text in green box. The title of the block is ``Examples".
-\end{examples}
-\end{frame}
-
-\section{More examples}
-
-\begin{frame}
-\frametitle{Two-column slide}
-
-\begin{columns}
-
-\column{0.5\textwidth}
-This is a text in first column.
-$$E=mc^2$$
-\begin{itemize}
-\item First item
-\item Second item
-\end{itemize}
-
-\column{0.5\textwidth}
-This text will be in the second column
-and on a second tought this is a nice looking
-layout in some cases.
-\end{columns}
-\end{frame}
-
 \end{document}

### 2021-02-16 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: more slides

@@
 \begin{frame}{Research Context}
+    \begin{itemize}
+        \item Philosophy and artificial intelligence \cite{Ferme2011}
+        \item Belief change \cite{Darwiche1997}
+            \begin{itemize}
+                \item Nonmonotonic logic
+                \item Probabilistic reasoning
+                \item Belief revision
+            \end{itemize}
+        \item One-step vs. iterated belief revision
+    \end{itemize}
+
     \note{
         \begin{itemize}
-            \item Research context with areas according to darwiche
+            \item Belief change, adapting one's world view under imperfect information
+            \item Agent can be human or machine -> major areas philosophy and AI
+            \item Different approaches, nonmonotonic logic known from beierle courses (truth maintenance systems, default logic like reiter or pool), probabilistic reasoning (also known from beierle course 1845),
+            \item Belief revision: operator based. Define and discuss operators that transition agent state from one to the next for new evidence
+            \item One step vs iterated depending on how many consecutive new information it handels
+            \item Booth and Meyer: iterated belief revision
         \end{itemize}
@@
 \begin{frame}{Different types of belief}
+    \begin{itemize}
+        \item Belief set \cite{Alchourron1985}
+        \item Conditional beliefs \cite{Darwiche1997}
+        \item Change of conditional beliefs \cite{Booth2011}
+    \end{itemize}
+
     \note{
         \begin{itemize}
-            \item belief sets (AGM) vs conditional beliefs (Darwiche and Pearl) vs iterating on conditional beliefs (Booth and Meyer)
+            \item Belief sets as what an agent currently accepts as true (AGM theory: How is a belief set defined and how does the belief set change with new evidence?)
+            \item Conditional beliefs as what an agent is prepared to accept as true depending on future evidence?
+(Darwiche and Pearl: In addition to how does the belief set change, what is the "strategy" for future belief set change?
+How do conditional beliefs change?)
+            \item Booth and Meyer: Change of conditional beliefs: If conditional beliefs are the strategy to change belief sets with future evidence, how can we change conditional beliefs with new evidence?
         \end{itemize}
@@
 
-\begin{frame}{Paper goal}
+\begin{frame}{Goal}
+    \begin{itemize}
+        \item "conditional belief" revision operators
+        \item axiomatisation of a family of operators by defining properties
+        \item discuss properties and edge cases
+    \end{itemize}
+
     \note{
         \begin{itemize}
-            \item present paper goal as defining postulates for a family of operators, functions $\ast$ for iterating on belief change revision operators
-            \item explain the concept of defining postulates for a family of operators and research in these postulates to have something to talk about, explain there are different operators and different postulates.
-this is not finding "the true one" but defining families and discussing pro/contra
+            \item paper goal/focus of this talk revision operators for conditional belief structure (not mention tpo yet)
+            \item postulates for operators to restrict them, define a family of operators (axiomatisation) by doing that
+            \item properties are not "correct" but has to be done to reasonably talk about those operators and narrow down possibilities, compare to other properties/edge cases to branch out
         \end{itemize}
@@
 \begin{frame}{Belief Sets}
+    \begin{itemize}
+        \item Set of propositions the agent accepts as true at any point in time \cite{Ferme2011}
+        \item Deductively closed
+        \item Possible for example: $Cn(\{ p \vee q, \neg(p \wedge q), \neg r \})$
+    \end{itemize}
+    % TODO: Cn here good?
+
     \note{
@@
 \begin{frame}{Epistemic States}
+    \begin{itemize}
+        \item abstract entity $\mathbb{E}$ that contain all information an agent need for their reasoning \cite{Darwiche1997}
+        \item commonly used: tpo $\leq_{\mathbb{E}}$
+        \item belief sets $B(\mathbb{E})$ can be extracted from epistemic states as all sentences true in the most plausible worlds
+            \begin{itemize}
+                \item set of minimal worlds in which $\alpha$ is true: $min(\alpha, \leq_{\mathbb{E}})$, set of most plausible worlds:  $min(\top, \leq_{\mathbb{E}})$
+                \item Set of worlds that are models of the belief set of the agent $\modelsOf{B(\mathbb{E})} = min(\top, \leq_{\mathbb{E}})$
+                \item All sentences true in those worlds: $Th(\modelsOf{B(\mathbb{E})})$
+            \end{itemize}
+    \end{itemize}
+
     \note{
         \begin{itemize}
-            \item how to extract belief sets from epistemic states
+            \item "commonly used" does not mean has to be used, abstract
         \end{itemize}
@@
             \item example 7, math
-        \end{itemize}
-    }
-\end{frame}
-
-\begin{frame}{BACKUP: non-prioritised revision}
-    \note{
-        \begin{itemize}
-            \item example 7, figure 4
         \end{itemize}
@@
 
-\begin{frame}{References}
+\begin{frame}[allowframebreaks=0.9]{References}
     \typeout{}

### 2021-02-23 paper/1901_3230880_philip_heltweg.tex
fix: fixed wrong belief set definition
improvement: various small typos and endless comma fixes

@@
 
+% TODO: check if figures are on the right pages with their text
+% TODO: question marks in references/figures etc!
+% TODO: critique example very weak?
+
 \begin{document}
@@
 As an agent can be human or machine, work in belief change has impact on the fields of both philosophy and artificial intelligence \cite{Ferme2011}.
-Different approaches to handling belief change have been discussed, with notable approaches including nonmonotonic logic, probabilistic reasoning and belief revision \cite{Darwiche1997}.
+Different solutions to handling belief change have been discussed, with notable approaches including nonmonotonic logic, probabilistic reasoning and belief revision \cite{Darwiche1997}.
 
@@
 The structure of the synopsis will be as follows: Establish the context of the paper by presenting the research area of iterated belief revision and how it relates to other areas of artificial intelligence and philosophy.
-To create a shared understanding of notation and definitions section \ref{section:formal-background} discusses formal background and other, previous, approaches to belief change.
-It also introduces the main contribution of this synopsis, an accompanying example demonstrating tpo-revision as described by Booth and Meyer.
+To create a shared understanding of notation and definitions section \ref{section:formal-background} discusses formal background and other previous approaches to belief change.
+It also introduces the main contribution of this synopsis, the use of an accompanying example demonstrating tpo-revision as described by Booth and Meyer.
 After building this foundation, section \ref{section:booth-and-meyer-tpo-revision-operators} and \ref{section:properties-of-bm-tpo-revision-operators} present selected parts of the work from the original paper "How to Revise a Total Preorder" \cite{Booth2011}.
 Section \ref{section:booth-and-meyer-tpo-revision-operators} establishes and defines functions $\ast$, used to revise tpos.
-In section \ref{section:properties-of-bm-tpo-revision-operators} properties of these functions are presented.
+Properties of these functions are presented in section \ref{section:properties-of-bm-tpo-revision-operators}.
 To provide an outlook into the additional work done by Booth and Meyer, section \ref{section:iterating-preceq-revision} will show their proposal of a concrete operator for tpo-revision.
@@
 The following notation will be used, largely aligned to Booth and Meyer \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables.
-Lower case greek letters represent formulae in $L$ and $\top$, $\bot$ representing tautology and contradiction respectively.
-$\models$ denotes classical logical consequence, $\equiv$ classical logical equivalence.
-$Cn$ is used to denote the deductive closure of a formula or set of formulae in $L$.
+Lower case greek letters represent formulae in $L$, and $\top$ and $\bot$ represent tautology and contradiction respectively.
+$\models$ denotes classical logical consequence, $\equiv$ classical logical equivalence, and $Cn$ is used to denote the deductive closure of a formula or set of formulae in $L$.
 
@@
     \label{example:example-introduction}
-    As an accompanying example consider the following situation from a courtroom, closely aligned to \cite{Booth2011} and \cite{Darwiche1997}:
+    As an accompanying example, consider the following situation from a courtroom, closely aligned to \cite{Booth2011} and \cite{Darwiche1997}:
 
@@
 The process of belief revision refers to keeping an agent's set of beliefs consistent, while incorporating new information that can be inconsistent with the current belief set \cite{Katsuno1991, Gaerdenfors1984}.
-% TODO: mention this addition in email
 
@@
 Darwiche and Pearl show that their version of belief revision can be modelled with a tpo $\leq_{\mathbb{E}}$, associated with an epistemic state $\mathbb{E}$.
-A mapping of a belief state $\mathbb{E}$ to a tpo $\leq_{\mathbb{E}}$, that maintains the belief set, is is called a faithful assignment.
-As Booth and Meyer describe an additional structure, from which a tpo $\leq_{\mathbb{E}}$ can be determined, faithful assignment is mentioned here only for completeness.
-For more information refer to Katsuno and Mendelzon \cite{Katsuno1991}.
+A mapping of a belief state $\mathbb{E}$ to a tpo $\leq_{\mathbb{E}}$ that maintains the belief set is called a faithful assignment.
+As Booth and Meyer describe an additional structure from which a tpo $\leq_{\mathbb{E}}$ can be determined faithful assignment is mentioned here only for completeness.
+For more information, refer to Katsuno and Mendelzon \cite{Katsuno1991}.
 
@@
 The set of propositional sentences that holds in all those worlds is defined to be the belief set of the agent.
-For notation let $min(\alpha, \leq_{\mathbb{E}})$ denote the set of minimal models for the propositional formula $\alpha$ under $\leq_{\mathbb{E}}$.
+For notation, let $min(\alpha, \leq_{\mathbb{E}})$ denote the set of minimal models for the propositional formula $\alpha$ under $\leq_{\mathbb{E}}$.
 Then $\modelsOf{B(\mathbb{E})} = min(\top, \leq_{\mathbb{E}})$ is the set of worlds that are models of the belief set $B(\mathbb{E})$ associated with $\mathbb{E}$.
-The belief set of the agent with this notation is $Th(\modelsOf{B(\mathbb{E})})$.
+The belief set of the agent with this notation is $Th(min(\top, \leq_{\mathbb{E}}))$.
 
 \begin{example}
-    Continuing Example \ref{example:example-introduction} it is possible to model an epistemic state $\mathbb{E}$ with the tpo $\leq_{\mathbb{E}}$.
+    Continuing Example \ref{example:example-introduction}, it is possible to model an epistemic state $\mathbb{E}$ with the tpo $\leq_{\mathbb{E}}$.
 
@@
 In this text, a reformulation for epistemic states by Darwiche and Pearl \cite{Darwiche1997} is used, presented in the following.
-$\mathbb{E}$ denotes an epistemic state, $B(\mathbb{E})$ it's associated belief set, $B(\mathbb{E}) + \alpha$ the expansion of $B(\mathbb{E})$ by $\alpha$.
-$\ast$ being a belief change operator on epistemic states.
+$\mathbb{E}$ denotes an epistemic state, $B(\mathbb{E})$ its associated belief set and $B(\mathbb{E}) + \alpha$ is the expansion of $B(\mathbb{E})$ by $\alpha$, with $\ast$ being a belief change operator on epistemic states.
 
@@
 in terms of how the ordering of worlds undergoes change) versions are shown here.
-For more details and sentential versions refer to Darwiche and Pearl \cite{Darwiche1997}.
+For more details and sentential versions, refer to Darwiche and Pearl \cite{Darwiche1997}.
 
@@
 After discussing notation and previous research, the following sections present an excerpt of the new work done by Booth and Meyer in \cite{Booth2011}.
-To support their approach to tpo revision, Booth and Meyer propose adding additional metadata to epistemic states.
+To support their approach to tpo revision, Booth and Meyer propose inserting additional metadata in epistemic states.
 
@@
 
-Booth and Meyer's \cite{Booth2011} approach is to add an additional structure with metadata for every world $w \in W$.
+Booth and Meyer's \cite{Booth2011} approach is to include an additional structure with metadata for every world $w \in W$.
 This new structure is denoted as $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$.
-In this notation a world $w \in W$ is represented twice: When new evidence $\alpha$ arrives that makes $w$ more plausible (because $w \in \modelsOf{\alpha}$), the agent can assume it's positive representation as $w^{+} \in W^{\pm}$.
+In this notation, a world $w \in W$ is represented twice: When new evidence $\alpha$ arrives that makes $w$ more plausible (because $w \in \modelsOf{\alpha}$), the agent can assume its positive representation as $w^{+} \in W^{\pm}$.
 In contrast, if the new evidence makes $w$ less plausible ($w \in \modelsOf{\neg\alpha}$), then the negative representation $w^{-} \in W^{\pm}$ is the agent's view of $w$.
@@
     Recall that tpos can be equivalently thought of as a linearly ordered set of ranks (Example \ref{example:example-introduction}).
-Therefore a tpo over $W$ can be visualised by displaying every $w \in W$ in a table that has one column for every rank (like in Table \ref{tab:visualising-a-tpo-example}).
+Therefore, a tpo over $W$ can be visualised by displaying every $w \in W$ in a table that has one column for every rank (like in Table \ref{tab:visualising-a-tpo-example}).
 To visualise the ordering introduced by $\preceq$, Booth and Meyer use an interval with the endpoints defined as $w^{+}$/$w^{-}$ respectively.
@@
 The choice between positive or negative representations of two worlds should be the same as under $\leq$ (due to \ref{PREQ2} and \ref{PREQ3}).
-According to \ref{PREQ4} there has to be a difference between a positive representation and a negative representation of the same world.
+According to \ref{PREQ4}, there has to be a difference between a positive representation and a negative representation of the same world.
 Given the choice between both, the positive representation has to be chosen.
@@
 Because of \ref{PREQ2} and \ref{PREQ3}, it is sufficient to only include $\preceq$ in the epistemic state.
-The tpo $\leq$ over $W$ can be determined from $\preceq$ by restricting to only $\{ x^{+} \mid x \in W\}$ or $\{ x^{-} \mid x \in W\}$, respectively.
+The tpo $\leq$ over $W$ can be determined from $\preceq$ by restricting it to only $\{ x^{+} \mid x \in W\}$ or $\{ x^{-} \mid x \in W\}$, respectively.
 
@@
 
-    Even though \ref{PREQ1} and \ref{PREQ4} are satisfied, $\preceq$ is not a $\leq$-faithful tpo: From \ref{PREQ2} and $x_{1}^{+} \prec x_{2}^{+}$ follows $x_{1} < x_{2}$.
+    Even though \ref{PREQ1} and \ref{PREQ4} are satisfied, $\preceq$ is not a $\leq$-faithful tpo: From \ref{PREQ2} and $x_{1}^{+} \prec x_{2}^{+}$, follows $x_{1} < x_{2}$.
 That means \ref{PREQ3} can not hold as $x_{2}^{-} \prec x_{1}^{-}$ which would require $x_{2} < x_{3}$ to be true.
@@
 
-% TODO: check if figures are on the right pages with their text
-
 \begin{example}
     \label{example:example-tpo-initial}
-    Continuing the courtroom demonstration, introduced in Example \ref{example:example-introduction} of a judge deciding on a verdict on the suspects John and Mary.
-Figure \ref{fig:example-tpo-initial} shows a possible version of a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ from which the tpo $\leq$ from Table \ref{tab:visualising-a-tpo-example} can be reconstructed.
+    Continuing the courtroom demonstration, introduced in Example \ref{example:example-introduction}, of a judge deciding on a verdict on the suspects John and Mary, Figure \ref{fig:example-tpo-initial} shows a possible version of a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ from which the tpo $\leq$ from Table \ref{tab:visualising-a-tpo-example} can be reconstructed.
 
@@
 
+% TODO make sure this is on one page?
 \begin{definition}[Revision operator $\ast_{\preceq}$ for $\leq$ generated by $\preceq$ \cite{Booth2011}]
     \label{definition:revision-operator}
-    For each $\leq$-faithful tpo $\preceq$ over $W^{\pm}$, refer to $\ast_{\preceq}$ as the revision operator for $\leq$ generated by $\preceq$ defined by:
+    For each $\leq$-faithful tpo $\preceq$ over $W^{\pm}$, refer to $\ast_{\preceq}$ as the revision operator for $\leq$ generated by $\preceq$, defined by:
 
@@
 Intuitively, new evidence $\alpha$ makes worlds that satisfy $\alpha$ more plausible and worlds that do not satisfy $\alpha$ less plausible.
-Therefore the agent associates worlds $x \in \modelsOf{\alpha}$ with their positive representation $x^{+}$ and worlds $x \in \modelsOf{\neg\alpha}$ with their negative representation $x^{-}$.
+Therefore, the agent associates worlds $x \in \modelsOf{\alpha}$ with their positive representation $x^{+}$ and worlds $x \in \modelsOf{\neg\alpha}$ with their negative representation $x^{-}$.
 
@@
 When a new piece of evidence $\alpha$ has to be considered, each world gets mapped to one end of the interval assigned to it, depending on if it is an $\alpha$-world or not.
-In Figure \ref{fig:example-updated-tpo} that mapping is indicated by the filled out dot.
-For this example $x_{1}, x_{2}$ and $x_{3}$ are $\modelsOf{\neg\alpha}$-worlds while $x_{4}$ is an $\modelsOf{\alpha}$-world.
+In Figure \ref{fig:example-updated-tpo}, that mapping is indicated by the filled out dot.
+For this example, $x_{1}, x_{2}$ and $x_{3}$ are $\modelsOf{\neg\alpha}$-worlds, while $x_{4}$ is an $\modelsOf{\alpha}$-world.
 
@@
     \label{example:example-tpo-revised}
-    A more complex example is the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ (for the courtroom Example \ref{example:example-introduction}), using the $\leq$-faithful tpo $\preceq$, introduced in Example \ref{example:example-tpo-initial} and shown in Figure \ref{fig:example-tpo-revised}.
-In this case the new evidence received points to John being the murderer so $\alpha = p$.
+    A more complex example is the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ (of the courtroom Example \ref{example:example-introduction}), using the $\leq$-faithful tpo $\preceq$ introduced in Example \ref{example:example-tpo-initial} and shown in Figure \ref{fig:example-tpo-revised}.
+In this case, the new evidence received points to John being the murderer so $\alpha = p$.
 
@@
 
-    For the worlds $010, 110 \in W$, $010 < 110$ was true. To rank them with the revised tpo $\leq_{\alpha}^{\ast}$ calculate:
+    For the worlds $010, 110 \in W$, $010 < 110$ was true. To rank them with the revised tpo $\leq_{\alpha}^{\ast}$, calculate:
 
@@
 The most plausible worlds in the new epistemic state $\mathbb{E}$, $min(\top, \leq_{\alpha}^{\ast})$, include the $\modelsOf{\neg\alpha}$-worlds $x_{1}$ and $x_{2}$.
-Therefore $Th(min(\top, \leq_{\alpha}^{\ast}))$ does not include the new evidence $\alpha$.
+Therefore, $Th(min(\top, \leq_{\alpha}^{\ast}))$ does not include the new evidence $\alpha$.
 
@@
 
-The list of properties they consider to be a complete axiomatisation of the family of operators they describe follows:
+The list of properties they consider to be a complete axiomatisation of the family of operators they describe is presented below:
 
@@
 \ref{AST1} and \ref{AST2} are considered basic properties: A revision of a tpo $\leq$ over $W$ must generate another tpo over $W$.
-In addition the operator must return an equal revised tpo for semantically equivalent sentences, the so called syntax-irrelevance property.
+In addition, the operator must return an equal revised tpo for semantically equivalent sentences, the so called syntax-irrelevance property.
 
@@
 Booth and Meyer themselves consider them characteristic for admissible revision operators, a class of operators that requires new evidence to not be ignored completely \cite{Booth2006a}.
-This is in contrast to revision strategies like natural revision by Boutilier \cite{Boutilier1996} that minimise change in conditional beliefs.
-% TODO: mention this addition in email
-
-% TODO: question marks in references/figures etc!
+This is in contrast to revision strategies like natural revision by Boutilier \cite{Boutilier1996}, which minimises change in conditional beliefs.
 
 If revising a tpo by a sentence $\alpha$, the relative ordering of worlds that are either both $\modelsOf{\alpha}$- or $\modelsOf{\neg\alpha}$-worlds, must stay the same (\ref{AST3}/\ref{AST4}).
-These properties were already part of the semantic postulates \ref{CR1} and \ref{CR2} by Darwiche and Pearl \cite{Darwiche1997} discussed in section \ref{chapter:dp-agm-postulates}.
-
-In a similar way \ref{AST5} is a stronger requirement than the other two Darwiche and Pearl postulates \ref{CR3} and \ref{CR4}.
-It means the following: When a world $x$ is considered at least as plausible as a world $y$ before a revision by new information $\alpha$: If $\alpha$ makes $x$ more plausible ($x \in \modelsOf{\alpha}$) and $y$ less plausible ($y \in \modelsOf{\neg\alpha}$), then after revision by $\alpha$, $x$ should be considered strictly more plausible than $y$.
-This property was not only proposed by Booth and Meyer \cite{Booth2006a} but also by Jin und Thielscher in \cite{Jin2007} (as the postulate of independence).
+These properties were already part of the semantic postulates \ref{CR1} and \ref{CR2}, by Darwiche and Pearl \cite{Darwiche1997}, discussed in section \ref{chapter:dp-agm-postulates}.
+
+In a similar way, \ref{AST5} is a stronger requirement than the other two Darwiche and Pearl postulates \ref{CR3} and \ref{CR4}.
+It means the following: When a world $x$ is considered at least as plausible as a world $y$ before a revision by new information $\alpha$, if $\alpha$ makes $x$ more plausible ($x \in \modelsOf{\alpha}$) and $y$ less plausible ($y \in \modelsOf{\neg\alpha}$), then after revision by $\alpha$, $x$ should be considered strictly more plausible than $y$.
+This property was not only proposed by Booth and Meyer \cite{Booth2006a}, but also by Jin und Thielscher in \cite{Jin2007} (as the postulate of independence).
 
@@
 
-With \ref{AST6} and \ref{AST7} Booth and Meyer aim to add supplementary rationality properties to keep revision with different sentences coherent.
+With \ref{AST6} and \ref{AST7}, Booth and Meyer aim to add supplementary rationality properties to keep revision with different sentences coherent.
 These properties are largely ignored in other literature on iterated belief change \cite{Booth2011}.
@@
 The operator $\ast$, based on $\preceq$, allows the revision of a tpo $\leq$ associated with an epistemic state to $\leq_{\alpha}^{\ast}$.
-To be used in iterated belief revision the newly introduced structure $\preceq$ also needs to be revised.
+To be used in iterated belief revision, the newly introduced structure $\preceq$ also needs to be revised.
 Otherwise, as Booth and Meyer put it, the problem has just "re-emerged 'one level up'" \cite{Booth2011}.
@@
 Since this synopsis focuses on the revision of tpos itself, only the revision of a $\leq$-faithful tpo $\preceq$ using the example operator from the original paper is included here.
-For a more detailed explanation of the operator, SPHs or their properties refer to Booth and Meyer \cite{Booth2011}.
+For a more detailed explanation of the operator, SPHs or their properties, refer to Booth and Meyer \cite{Booth2011}.
 
@@
 Booth and Meyer define their operator to revise $\preceq$ with a function $p: W^{\pm} \mapsto \mathds{R}$.
-For all $x \in W$ the interval between it's positive and negative representation is a real number $a$:
+For all $x \in W$ the interval between its positive and negative representation is a real number $a$:
 
@@
 
-Revision of $\preceq$ becomes a two step process: First choose a function $p$ so that $\preceq_{p} = \preceq$.
-Then revise $p$ to get a new assignment $p \ast \alpha$ that defines a new $\leq$-faithful tpo $\preceq_{p \ast \alpha}$.
+Revision of $\preceq$ becomes a two step process: First, choose a function $p$ so that $\preceq_{p} = \preceq$; Then revise $p$ to get a new assignment $p \ast \alpha$ that defines a new $\leq$-faithful tpo $\preceq_{p \ast \alpha}$.
 
@@
 Other operators are possible and an area of further research \cite{Booth2011}.
-They achieve this by setting $p$, for every $x^{\epsilon} \in W^{\pm}$, to:
+They achieve this by setting $p$, for every $x^{\epsilon} \in W^{\pm}$, as:
 
@@
 
-By this definition, the interval representing $\alpha$-worlds stays the same as $(p(x^{+}), p(x^{-}))$ while intervals of $\neg\alpha$-worlds become $(p(x^{-}), p(x^{-}) + a)$.
+By this definition, the interval representing $\alpha$-worlds stays the same as $(p(x^{+}), p(x^{-}))$, while intervals of $\neg\alpha$-worlds become $(p(x^{-}), p(x^{-}) + a)$.
 
@@
     \label{example:example-preceq-revised}
-    For the courtroom Example \ref{example:example-introduction} the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ for $\alpha = p$ ("John is the murderer") was already done in Example \ref{example:example-tpo-revised}.
+    For the courtroom Example \ref{example:example-introduction}, the revision of $\leq$ to $\leq_{\alpha}^{\ast}$ for $\alpha = p$ ("John is the murderer") was already done in Example \ref{example:example-tpo-revised}.
 The next step is revising $\preceq$ by $\alpha$.
@@
     For example, the interval representing world $010$ is $(010^{+}, 010^{-})$ and becomes $(p(010^{+}), p(010^{-})) = (0, a)$.
-Initially the world $100$ is represented by the same interval $(100^{+}, 100^{-})$ that becomes $(p(100^{+}), p(100^{-})) = (0, a)$.
+Initially, the world $100$ is represented by the same interval $(100^{+}, 100^{-})$, which now becomes $(p(100^{+}), p(100^{-})) = (0, a)$.
 
@@
     \label{example:example-preceq-revised-alien}
-    For an example that demonstrates the impact the revision of $\preceq$ has on the acceptance of conditional beliefs, consider again the courtroom Example \ref{example:example-introduction}.
-The fact that the victim is an alien ($r=\textrm{true}$) seems very unlikely, which is modelled by the gap between $\modelsOf{r}$-worlds and $\modelsOf{\neg r}$-worlds as mentioned in Example \ref{example:example-tpo-initial}.
-
-    When evidence $\alpha = r$ arrives, there seems to be little change in the epistemic state of the judge: $\leq_{\alpha}^{\ast}$ is unchanged, as even considering the negative representations of $\modelsOf{\neg r}$-worlds, they rank lower than $\modelsOf{r}$-worlds.
-An unchanged tpo $\leq_{\alpha}^{\ast}$ also means the believe set $B(\mathbb{E})$ stays the same and does not include $r$ (a property of non-prioritised revision as described in item \ref{section:non-prioritised-revision}).
-
+    For an example that demonstrates the impact that the revision of $\preceq$ has on the acceptance of conditional beliefs, consider again the courtroom Example \ref{example:example-introduction}.
+The fact that the victim is an alien ($r=\textrm{true}$) seems very unlikely, which is modelled by the gap between $\modelsOf{r}$-worlds and $\modelsOf{\neg r}$-worlds mentioned in Example \ref{example:example-tpo-initial}.
+
+    When evidence $\alpha = r$ arrives, there seems to be little change in the epistemic state of the judge: $\leq_{\alpha}^{\ast}$ is unchanged, as, even considering the negative representations of $\modelsOf{\neg r}$-worlds, they rank lower than $\modelsOf{r}$-worlds.
+An unchanged tpo $\leq_{\alpha}^{\ast}$ also means the believe set $B(\mathbb{E})$ stays the same and does not include $r$ (a property of non-prioritised revision, as described in item \ref{section:non-prioritised-revision}).
 What did change is the willingness of the agent to accept conditional beliefs about $r$ being true in light of future evidence.
@@
 A consistent example including a trial situation (adapted from \cite{Darwiche1997} and \cite{Booth2011}) was used to accompany the discussion of the paper.
-In addition to the provided example the synopsis also introduced an adapted visualisation for $\leq$-faithful tpo-revision based on the interval visualisation used by Booth and Meyer themselves.
-
-To make the presented content easier to follow some parts of the original paper had to be excluded.
-Booth and Meyer discuss multiple additional properties of their proposed operators as well as edge cases.
-They also provide a different way to express the $\preceq$-structure using strict preference hierarchies and discuss how they relate to other research areas.
-For those topics as well as detailed proofs it is highly advised to read the primary paper \cite{Booth2011} itself.
+In addition to the provided example, the synopsis also introduced an adapted visualisation for $\leq$-faithful tpo-revision based on the interval visualisation used by Booth and Meyer themselves.
+
+To make the presented content easier to follow, some parts of the original paper had to be excluded.
+Booth and Meyer discuss multiple additional properties of their proposed operators, as well as edge cases.
+They also provide a different way to express the $\preceq$-structure using strict preference hierarchies, and discuss how they relate to other research areas.
+For those topics, as well as detailed proofs, it is highly advised to read the primary paper \cite{Booth2011} itself.
 
 The idea to define an interval of plausibility for worlds depending on if evidence supports them or not does make intuitive sense.
-
-The proposed, concrete operator for the revision of $\leq$-faithful tpos allows for consecutive revisions by the same evidence $\alpha$ or semantically equivalent evidence $\beta \equiv \alpha$.
+The proposed concrete operator for the revision of $\leq$-faithful tpos allows consecutive revisions by the same evidence $\alpha$ or semantically equivalent evidence $\beta \equiv \alpha$.
 Those would consistently lower the acceptance of $\modelsOf{\neg\alpha}$-worlds without presenting new evidence.
-It seems like an interesting question to ask, if tpo-revision for iterated belief change could be idempotent in regards to already known information.
-
-% TODO: this critique example seems very weak
-Considering the quality and impact of new evidence also creates the question if \ref{AST6} and \ref{AST7} (properties of BM tpo-revision operators, section \ref{section:properties-of-bm-tpo-revision-operators}) should be weakened.
-Especially high quality evidence for a very unlikely type of world might change an agents plausibility ordering, while low quality evidence that is very expected might not.
+It seems like an interesting question to ask if tpo-revision for iterated belief change could be idempotent in regards to already known information.
+
+Considering the quality and impact of new evidence also raises the question if \ref{AST6} and \ref{AST7} (properties of BM tpo-revision operators, section \ref{section:properties-of-bm-tpo-revision-operators}) should be weakened.
+Especially high quality evidence for a very unlikely type of world might change an agent's plausibility ordering, while low quality evidence that is very expected might not.
 Consider the following situation in a world described by the set of propositional variables $\{x_1, x_2, x_3, y_1\}$: New evidence $\alpha = x_1$ arrives that  makes a world $x$, with $x_1$ being true, more likely.
@@
 
-But what if evidence is submitted, for example $\gamma = x_1 \wedge x_2 \wedge x_3$?
-Because $\gamma$ is more specific ($|\modelsOf{\gamma}| <  |\modelsOf{\alpha}|$) a human might consider it semantically stronger in favour of the worlds in $\modelsOf{\gamma}$.
+But what if very specific evidence $\gamma$ is submitted, for example $\gamma = x_1 \wedge x_2 \wedge x_3$?
+Because $\gamma$ holds in less worlds ($|\modelsOf{\gamma}| <  |\modelsOf{\alpha}|$) a human might consider it semantically stronger in favour of the worlds in $\modelsOf{\gamma}$.
 Because all worlds in $\modelsOf{\gamma}$ are also in $\modelsOf{\alpha}$, and the agent has already established no evidence can change their mind due to \ref{AST7}, even this very specific evidence can not change the relative ordering of worlds.

### 2021-02-24 presentation/1901_3230880_philip_heltweg_presentation.tex
fix: small bugfixes
added gitignore for generated files from vscode

@@
 	\insertnote
-
 }
@@
         \begin{itemize}
-            \item Example question to motivate
+            \item Beispiel Frage zur Motivation
+            \item Unvollständige Information: Kein gesichertes Wissen sondern Glauben und Annahmen aus Zeugenaussagen/Indizien
+            \item Inkonsistente Information: Zeugen können lügen, Indizien falsch sein, Informationen können mit dem aktuellen Glauben inkonsistent sein
+            \item Keine reine richtig/falsch Frage. Soll neuer Information immer geglaubt werden? Wie sollen Konflikte gelöst werden?
         \end{itemize}
@@
 
-\begin{frame}{Courtroom example \footnote{inspired by \cite{Booth2011}, \cite{Darwiche1997}}}
+\begin{frame}{Courtroom example \footnote{inspired by Booth and Meyer \cite{Booth2011} and Darwiche and Pearl \cite{Darwiche1997}}}
     \begin{itemize}
@@
         \end{itemize}
-        \item  $I_{\Sigma} = W = \{ 000, 001, 010, 011, 100, 101, 110, 111\}$ 
+        \item  $Int({\Sigma}) = W = \{ 000, 001, 010, 011, 100, 101, 110, 111\}$ 
     \end{itemize} 
@@
         \end{itemize}
-    }\include{figures/example-visualisation-scatterplot}
+    }
 \end{frame}

### 2021-02-24 paper/1901_3230880_philip_heltweg.tex
fix: writing error

@@
 This synopsis presents parts of their work to a broader audience.
-An accompanying example will guide the discussion and visualise changes in the agent's state.
+An accompanying example will guide the discussion and visualize changes in the agent's state.
 The focus will be on the tpo-revision operators discussed in the primary paper and explicitly avoid the addition of strict preference hierarchies and relations to other research areas.
@@
         \end{tabular}
-        \caption{Visualising a tpo as a linearly ordered set of ranks, as done in \cite{Booth2006}}.
+        \caption{Visualizing a tpo as a linearly ordered set of ranks, as done in \cite{Booth2006}}.
         \label{tab:visualising-a-tpo-example}
@@
     Recall that tpos can be equivalently thought of as a linearly ordered set of ranks (Example \ref{example:example-introduction}).
-Therefore, a tpo over $W$ can be visualised by displaying every $w \in W$ in a table that has one column for every rank (like in Table \ref{tab:visualising-a-tpo-example}).
-To visualise the ordering introduced by $\preceq$, Booth and Meyer use an interval with the endpoints defined as $w^{+}$/$w^{-}$ respectively.
+Therefore, a tpo over $W$ can be visualized by displaying every $w \in W$ in a table that has one column for every rank (like in Table \ref{tab:visualising-a-tpo-example}).
+To visualize the ordering introduced by $\preceq$, Booth and Meyer use an interval with the endpoints defined as $w^{+}$/$w^{-}$ respectively.
 This type of visualisation was first introduced in a previous paper by Booth and Meyer themselves \cite{Booth2007} and is shown in Figure \ref{fig:example-visualisation-scatterplot}.

### 2021-02-27 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: more notes

@@
-% TODO: explain contraction, revision, expansion
-% ANSWER: Ich würdes es ganz kurz erläutern im Text. Im Vortrag vielleicht nicht umbedingt.
-
-% TODO QUESTION: do we need to discuss this in ore detail? faithful assignment here:
-
-% ANSWER: Das ist eine gute Frage. So wie ich das Paper von Booth und Meyer im
-% Kopf habe werden dort die Ordnung mit epistemischen Zuständen
-% gleichgesetzt (was Darwiche und Pearl ja nicht machen). Von daher halte
-% ich das für ok es nicht im aller formalen Ausführlichkeit zu machen.
-% Aber man könnte es im einen Satz erwähnen.
-
 \documentclass[11pt]{beamer}
@@
 \usepackage{enumitem}
+
+% TODO QUESTION: do we need to discuss this in ore detail? faithful assignment here:
+
+% ANSWER: Das ist eine gute Frage. So wie ich das Paper von Booth und Meyer im
+% Kopf habe werden dort die Ordnung mit epistemischen Zuständen
+% gleichgesetzt (was Darwiche und Pearl ja nicht machen). Von daher halte
+% ich das für ok es nicht im aller formalen Ausführlichkeit zu machen.
+% Aber man könnte es im einen Satz erwähnen
+
+% Representation theorem
+% In mathematics, a representation theorem is a theorem that states that every abstract structure with certain properties is isomorphic to another (abstract or concrete) structure.
+% In mathematics, an isomorphism is a structure-preserving mapping between two structures of the same type that can be reversed by an inverse mapping.
+
+% Operationalization
+% In research design, especially in psychology, social sciences, life sciences and physics, operationalization or operationalisation is a process of defining the measurement of a phenomenon that is not directly measurable, though its existence is inferred by other phenomena.
+% In a broader sense, it defines the extension of a concept—describing what is and is not an instance of that concept.
+
+\pgfplotsset{compat=1.17}
+
 \setitemize{label=\usebeamerfont*{itemize item}
@@
 \institute{University of Hagen}
-\date{\today}
+\date{March 13th, 2021}
 
@@
         \begin{itemize}
-            \item Foo
-            \item Bar
+            \item Einführung mit Motivation, Forschungskontext und Beispiel
+            \item Hintergrund: Festlegen Notation, was sind TPOs überhaupt, vorherige Arbeit von Alchouron et al, Darwiche und Pearl
+            \item Metadata: Wie bauen Booth und Meyer auf der vorherigen Arbeit auf, Erklärung des Ansatzes zur TPO revision
+            \item BM operators: Wie benutzen BM die vorher besprochenen Metadaten für belief revision, Definition von Eigenschaften ihrer Operatoren
+            \item Iteration: Ausblick, wenn wir tpos mit der neuen Struktur anpassen können müssen wir auch die neue Struktur anpassen, ansonsten kann man nicht mehrere neue Informationen einpflegen.
+Hier haben BM sehr viel mehr geschrieben als hier vorgestellt aber ein konkreter Operator wird hier vorgestellt.
         \end{itemize}
@@
 \section{Introduction}
+\note{
+    \begin{itemize}
+        \item Jetzt: Verstehen der Forschungsfrage, Einordnung des Papiers in einen Forschungskontext und Aufsetzen des begleitenden Beispiels ohne Formalisierung
+    \end{itemize}
+}
 
@@
         \begin{itemize}
-            \item Beispiel Frage zur Motivation
+            \item Beispiel Frage zur Motivation, wird unser Beispiel sein. Wir haben zwei Verdächtige und diverse Beweise und Indizien, wie bilden wir uns ein Bild über die Welt?
             \item Unvollständige Information: Kein gesichertes Wissen sondern Glauben und Annahmen aus Zeugenaussagen/Indizien
             \item Inkonsistente Information: Zeugen können lügen, Indizien falsch sein, Informationen können mit dem aktuellen Glauben inkonsistent sein
-            \item Keine reine richtig/falsch Frage. Soll neuer Information immer geglaubt werden? Wie sollen Konflikte gelöst werden?
-        \end{itemize}
-    }
-\end{frame}
-
-\begin{frame}{Courtroom example \footnote{inspired by Booth and Meyer \cite{Booth2011} and Darwiche and Pearl \cite{Darwiche1997}}}
-    \begin{itemize}
-        \item The agent is a judge in a murder trial, "John" and "Mary" are suspects
-        \item $\Sigma = \{ p, q, r\}$
-        \begin{itemize}
-            \item p = "John is the murderer"
-            \item q = "Mary is the murderer"
-            \item r = "The victim is an alien"
-        \end{itemize}
-        \item  $Int({\Sigma}) = W = \{ 000, 001, 010, 011, 100, 101, 110, 111\}$ 
-    \end{itemize} 
-    \note{
-        \begin{itemize}
-            \item NOTE
+            \item Keine reine richtig/falsch Frage.
+Soll neuer Information immer geglaubt werden?
+Wie sollen Konflikte gelöst werden?
+Wie kann man abbilden, dass der Richter mit Indizien für einen Sachverhalt immer mehr bereit ist an diesen Sachverhalt zu glauben?
         \end{itemize}
@@
 
-\begin{frame}{Goal}
+\begin{frame}{Research question}
     \begin{itemize}
@@
         \item axiomatisation of a family of operators by defining properties
-        \item discuss properties and edge cases
+        \item discuss properties and define concrete example
     \end{itemize}
@@
         \begin{itemize}
+            \item Conditional beliefs/Conditional belief revision: Indizien für Sachverhalt = Sachverhalt nicht direkt glauben aber bei mehr Indizien immer mehr daran glauben/immer mehr bereit sein es zu akzeptieren.
             \item paper goal/focus of this talk revision operators for conditional belief structure (not mention tpo yet)
@@
 \section{Formal Background}
+\note{
+    \begin{itemize}
+        \item Vorher: Verstehen der Forschungsfrage, Einordnung des Papiers in einen Forschungskontext und Aufsetzen des begleitenden Beispiels
+        \item Jetzt: Formalisierung des Beispiels, Etablieren was eine total preorder ist.
+        \item Jetzt: Einführung von Formalisierungen zu Glaubensmengen/Annahmen und wie preorders dort benutzt werden
+        \item Jetzt: Postulate um Änderungen dieser Glaubensmengen/Annahmen mit neuen Informationen einzuschränken
+    \end{itemize}
+}
+
+\begin{frame}{Courtroom example \footnote{inspired by \cite{Booth2011} and \cite{Darwiche1997}}}
+    \begin{itemize}
+        \item The agent is a judge in a murder trial, "John" and "Mary" are suspects, the victim might be an alien
+        \item $\Sigma = \{ p, q, r\}$
+              \begin{itemize}
+                  \item p = "John is the murderer"
+                  \item q = "Mary is the murderer"
+                  \item r = "The victim is an alien"
+              \end{itemize}
+        \item  $Int({\Sigma}) = W = \{ 000, 001, 010, 011, 100, 101, 110, 111\}$
+    \end{itemize}
+
+    \note{
+        \begin{itemize}
+            \item Konsistentes Beispiel in der Präsentation, gut aufpassen
+            \item Beispiel inspiriert aus der Literatur
+            \item Aussagenlogik, Aussagenvariablen p, q, r
+            \item "Mögliche Welt" als aussagenlogische Interpretationen/Belegungen, damit 2 hoch 3 = 8 mögliche Alternativen hier
+            \item Kodierung der Welt als Tupel von Wahrheitswerten (0 = false, 1 = true)
+            \item Beispiel für 1-2 Welten durchgehen: 010 = Mary ist Mörderin, Opfer ist kein Alien, 111 = John und Mary sind die Mörder, haben ein Alien getötet
+        \end{itemize}
+    }
+\end{frame}
 
@@
         \end{tabular}
-        \caption{Visualising a tpo as a linearly ordered set of ranks, as done in \cite{Booth2006}}.
+        \caption{Visualizing a tpo as a linearly ordered set of ranks, as done in \cite{booth2006bad}}.
         \label{tab:visualising-a-tpo-example}
@@
         \begin{itemize}
-            \item 
+            \item Belief sets als aktuell akzeptierte Sätze eines Agenten
+            \item Gegensatz zu conditional beliefs: Sätze im Belief set werden als war angenommen.
+            \item Betrachtungsgegenstand von AGM-Theorie \cite{Alchourron1985} die Postulate definiert haben um Belief set revision einzuschränken, rationale revision, wir sprechen das allerdings später an weil wir die neu formulierten Postulates von \cite{Darwiche1997} nutzen
         \end{itemize}
@@
                   \item Set of worlds that are models of the belief set of the agent $\modelsOf{B(\mathbb{E})} = min(\top, \leq_{\mathbb{E}})$
-                \item All sentences true in those worlds: $Th(\modelsOf{B(\mathbb{E})})$
+                  \item All sentences true in those worlds: $Th(min(\top, \leq_{\mathbb{E}}))$
               \end{itemize}
@@
         \begin{itemize}
+            \item Darwiche and Pearl argumentieren das Belief sets nicht ausreichend sind.
+Die Postulate von AGM definieren nur wie sich belief sets ändern (principle of least change) aber conditional beliefs können sich ändern wie sie wollen.
+Epistemic states enthalten die Strategie des Agenten wie er seinen Glauben ändert, damit auch die conditional beliefs.
             \item "commonly used" does not mean has to be used, abstract
@@
         \begin{itemize}
-            \item 
+            \item $\mathbb{E}$ als epistemischer status, $B(\mathbb{E})$ belief set des status, $B(\mathbb{E}) + \alpha$ ist die expansion $B(\mathbb{E})$ mit $\alpha$ ($\alpha$ hinzufügen.
+$CN(B(\mathbb{E}) \cup \alpha)$), $\ast$ being a belief change operator on epistemic states
+            \item Postulates
+                  \begin{itemize}
+                      \item 1: deduktiv abgeschlossen
+                      \item 2: neue information ist immer teil des belief sets nach revision.
+Das muss nicht so sein, für BM tpo revision operatoren die wir hier betrachten gilt dies z.b.
+nicht.
+Wird "non-priotized revision" genannt
+                      \item 3: % TODO
+                      \item 4:
+                      \item 5: Syntax irrelevanz für information mit der revision betrieben wird.
+Epistemische zustände müssen gleich sein hier, im AGM original muss nur das belief set der zustände gleich sein.
+Also ist E5 schwächer als das Original von AGM.
+                      \item 6: Das belief set enthält elementaren widerspruch nach revision mit inkonsistenten informationen (alpha wärend not alpha eine tautologie ist).
+BM bestehen auf konsistente Eingaben damit sie immer ein belief set aus dem epistemischen status ableiten können.
+Daher nehmen sie E6 nicht an und nur E1-5, E7-8 als "DP-AGM"
+                      \item 7: % TODO
+                      \item 8: % TODO
+                  \end{itemize}
         \end{itemize}
@@
         \begin{itemize}
-            \item 
+            \item Zusätzliche postulate von DP um conditional belief revision einzuschränken
+            \item Semantische version aka wie sich die Ordnung der Welten ändert mit v,w in W
+            \item CR1/2: Relative Ordnung der alpha/not alpha welten bleibt gleich bei alpha/not alpha revision
+            \item CR3 wenn eine alpha welt strikt bevorzugt wurde vor einer not alpha welt dann muss das auch nach einer revision mit alpha gelten
+            \item CR4 wie CR3 nur für "weak preference"
         \end{itemize}
@@
 \section{Additional metadata for tpo revision}
+\note{
+    \begin{itemize}
+        \item Vorher: Formalisierung des Beispiels/Glaubensmengen/Epistemischen Zuständen, Etablieren was eine total preorder ist, Postulate für Revision von Glaubensmengen und Annahmen
+        \item Jetzt: BM wollen revision von tpos besprechen und führen dafür neue Metadaten und Strukturen im epistemischen Zustand ein, wir stellen diese nun vor bevor wir im nächsten Schritt die Änderung selbst besprechen
+        \item Jetzt: Einführung einer intuitiven Visualisierung der neuen Struktur die wir im weiteren Verlauf nutzen
+    \end{itemize}
+}
 
@@
     \begin{itemize}
-        \item $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$
-        \item $w \in \modelsOf{\alpha}$ / $w \in \modelsOf{\neg\alpha}$
-        \item $(w^{+}, w^{-})$
+        \item Additional structure of plausibility of worlds under new evidence $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$
+        \item Worlds are either supported by evidence or not $w \in \modelsOf{\alpha}$ / $w \in \modelsOf{\neg\alpha}$
+        \item Interval representing a world $(w^{+}, w^{-})$
     \end{itemize}
@@
 \begin{frame}{$\leq$-faithful tpo}
+    \begin{itemize}
+        \item original tpo $\leq$ was an order over $W$
+        \item additional structure $\preceq$ over new $W^{\pm}$
+    \end{itemize}
+
+    \note{
+        \begin{itemize}
+            \item what is it
+            \item say that the original tpo can be reconstructed from it
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{$\leq$-faithful tpo - definition}
+    \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\preceq\arabic*$)]
+        \item\label{PREQ1} $\qquad \preceq \textrm{ is a tpo over } W^{\pm}$
+        \item\label{PREQ2} $\qquad x^{+} \preceq y^{+} \textrm{ iff } x \leq y$
+        \item\label{PREQ3} $\qquad x^{-} \preceq y^{-} \textrm{ iff } x \leq y$
+        \item\label{PREQ4} $\qquad x^{+} \prec x^{-}$
+    \end{enumerate}
+
     \begin{definition}[$\leq$-faithful tpo over $W^{\pm}$ \cite{Booth2011}]
@@
             \item characteristics + definition
+            \item original tpo can be reconstructed from this
         \end{itemize}
@@
         \end{tikzpicture}
-            \caption{Representation of $\preceq$ over $W^{\pm}$ for the courtroom example \ref{example:example-introduction}}
+        \caption{Representation of $\preceq$ over $W^{\pm}$ for the courtroom example}
         \label{fig:example-tpo-initial}
@@
 \section{Booth and Meyer tpo-revision operators}
+\note{
+    \begin{itemize}
+        \item Vorher: Neue Metadaten/Strukturen im epistemischen Zustand und Visualisierung
+        \item Jetzt: Nutzen dieser neuen Strukturen für tpo revision, Postulates für BM revision operatoren und Definition der Familie von BM revisons operatoren
+        \item Jetzt: Abstrakte tpo revision am Beispiel
+    \end{itemize}
+}
 
@@
             \begin{array}{ll}
-                          x^{+} \textrm{ if } x \in \modelsOf{\alpha}\\
+                x^{+} \textrm{ if } x \in \modelsOf{\alpha} \\
                 x^{-} \textrm{ if } x \in \modelsOf{\neg\alpha}
@@
 
-\section{Iterating: $\preceq$-revision}
+\section{Iterating: \texorpdfstring{$\preceq$}{tpo}-revision}
+\note{
+    \begin{itemize}
+        \item Vorher: BM revisions operatoren definition, Revision der tpo am Beispiel
+        \item Jetzt: Revision der neuen Struktur $\preceq$, ansonsten Problem mehrmaliger Revision nur "hochgeschoben"
+        \item Jetzt: Ein möglicher konkreter Beispieloperator + Visualisierung
+    \end{itemize}
+}
 
@@
         \begin{array}{ll}
-                          p(x^{\epsilon}) \textrm{ if } x \in \modelsOf{\alpha}\\
+            p(x^{\epsilon}) \textrm{ if } x \in \modelsOf{\alpha} \\
             p(x^{\epsilon}) + a \textrm{ if } x \in \modelsOf{\neg\alpha}
@@
 \end{frame}
+\note{
+    \begin{itemize}
+        \item Vorher: Revision der neuen Struktur $\preceq$, ein möglicher konkreter Beispieloperator + Visualisierung
+        \item Jetzt: Fragen? Diskussion
+    \end{itemize}
+}
 
@@
     \typeout{}
-    \bibliographystyle{plain}
+    \bibliographystyle{apalike}
     \bibliography{references}

### 2021-02-27 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: removed reference to belief set
feat: some more text

@@
     \begin{itemize}
-        \item Additional structure of plausibility of worlds under new evidence $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$
+        \item Additional structure $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$
+        \item "A bad day surfing is better than a good day working" \cite{booth2006bad}
         \item Worlds are either supported by evidence or not $w \in \modelsOf{\alpha}$ / $w \in \modelsOf{\neg\alpha}$
@@
         \begin{itemize}
-            \item W+-
+            \item Additional structure of plausibility of worlds under new evidence  W+-
+            \item "A bad day surfing is better than a good day working" als idee das eine Welt sogar unter evidenz die sie nicht supported mehr plausibel bleiben kann, e.g.
+aliens tendenziell nicht so einfach zu glauben
         \end{itemize}
@@
         \item original tpo $\leq$ was an order over $W$
-        \item additional structure $\preceq$ over new $W^{\pm}$
+        \item $\preceq$ over new $W^{\pm}$
     \end{itemize}
@@
         \item new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$
-        \item $\modelsOf{B(\mathbb{E})} = min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".
+        \item $min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".
         \item $\leq_{\alpha}^{\ast}$ as representation of the conditional beliefs
@@
         \item Jetzt: Ein möglicher konkreter Beispieloperator + Visualisierung
+        \item Jetzt: Wie die Revision von Annahmen funktioniert für mehr als einen Input
     \end{itemize}
@@
 
-\begin{frame}{A concrete operator}
+\begin{frame}{A concrete operator: Setup}
     \begin{itemize}
-        \item $p: W^{\pm} \mapsto \mathds{R}$
-        \item $p(x^{-}) - p(x^{+}) = a > 0$
-        \item $x^{\epsilon} \preceq_{p} y^{\delta} \textrm{ iff } p(x^{\epsilon}) \leq p(y^{\delta})$
-        \item Set $p$, for every $x^{\epsilon} \in W^{\pm}$, to:
+        \item Function p mapping worlds to real numbers: $p: W^{\pm} \mapsto \mathds{R}$
+        \item Interval representing a world: $(p(x^{+}), p(x^{-}))$
+        \item Distance between representations: $p(x^{-}) - p(x^{+}) = a > 0$
+        \item Define a tpo from $p$: $x^{\epsilon} \preceq_{p} y^{\delta} \textrm{ iff } p(x^{\epsilon}) \leq p(y^{\delta})$
+    \end{itemize}
+
+    \note{
+        \begin{itemize}
+            \item math for operator
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{A concrete operator: Iteration}
+    \begin{itemize}
+        \item Choose initial $p$ so that $\preceq_{p} = \preceq$
+        \item Revise $p$ by $\alpha$ to $p \ast \alpha$, for every $x^{\epsilon} \in W^{\pm}$:
     \end{itemize}
@@
     \end{equation*}
+
+    \begin{itemize}
+        \item Define a revised tpo $\preceq_{p \ast \alpha}$ from $p \ast \alpha$: $x^{\epsilon} \preceq_{p \ast \alpha} y^{\delta} \textrm{ iff } (p \ast \alpha)(x^{\epsilon}) \leq (p \ast \alpha)(y^{\delta})$
+    \end{itemize}
 
@@
             \item figure 7
+            \item maybe put the figure 5 from paper (original revision of <=) before this
+            \item maybe put slides for complete example in here going from tpo to revision once, to revision twice
         \end{itemize}

### 2021-02-27 paper/1901_3230880_philip_heltweg.tex
feat: added author names and changed figure 9 title

@@
 Die Versicherung selbstständiger Arbeit gilt auch für enthaltene Zeichnungen, Skizzen oder graphische Darstellungen.
-Die Ausarbeitung wurde bisher in gleicher oder Ähnlicher Form weder derselben noch einer anderen Prüfungsbehörde vorgelegt und auch nicht veröffentlicht.
+Die Ausarbeitung wurde bisher in gleicher oder ähnlicher Form weder derselben noch einer anderen Prüfungsbehörde vorgelegt und auch nicht veröffentlicht.
 Mit der Abgabe der elektronischen Fassung der endgültigen Version der Ausarbeitung nehme ich zur Kenntnis, dass diese mit Hilfe eines Plagiatserkennungsdienstes auf enthaltene Plagiate geprüft werden kann und ausschließlich für Prüfungszwecke gespeichert wird.
@@
     \label{example:example-introduction}
-    As an accompanying example, consider the following situation from a courtroom, closely aligned to \cite{Booth2011} and \cite{Darwiche1997}:
+    As an accompanying example, consider the following situation from a courtroom, closely aligned to Booth and Meyer \cite{Booth2011}, as well as to Darwiche and Pearl \cite{Darwiche1997}:
 
@@
 
-% TODO make sure this is on one page?
 \begin{definition}[Revision operator $\ast_{\preceq}$ for $\leq$ generated by $\preceq$ \cite{Booth2011}]
@@
             \end{tikzpicture}
-            \caption{$\preceq_{p \ast \alpha \ast \beta}$ for $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$}
+            \caption{$\leq_{\alpha \ast \beta}^{\ast}$ for $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$}
             \label{fig:example-preceq-revised-alien2}

### 2021-03-06 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: split up a slide with a lot of text
feat: not sure
feat: notes

@@
-\documentclass[11pt]{beamer}
+\documentclass[12pt, notheorems]{beamer}
+%\documentclass[12pt, notheorems, handout]{beamer}
 \usepackage[utf8]{inputenc}
@@
 
+% Unique numbering scheme for definitions and theorems with the "notheorems" options on loading beamer
+% see https://tex.stackexchange.com/questions/82415/beamer-different-numbering-for-theorems-examples-definition-and-lemma
+\makeatletter
+    \ifbeamer@countsect
+      \newtheorem{theorem}{\translate{Theorem}}[section]
+    \else
+      \newtheorem{theorem}{\translate{Theorem}}
+    \fi
+    \newtheorem{corollary}{\translate{Corollary}}
+    \newtheorem{fact}{\translate{Fact}}
+    \newtheorem{lemma}{\translate{Lemma}}
+    \newtheorem{problem}{\translate{Problem}}
+    \newtheorem{solution}{\translate{Solution}}
+
+    \theoremstyle{definition}
+    \newtheorem{definition}{\translate{Definition}}
+    \newtheorem{definitions}{\translate{Definitions}}
+
+    \theoremstyle{example}
+    \newtheorem{example}{\translate{Example}}
+    \newtheorem{examples}{\translate{Examples}}
+
+    % Compatibility
+    \newtheorem{Beispiel}{Beispiel}
+    \newtheorem{Beispiele}{Beispiele}
+    \theoremstyle{plain}
+    \newtheorem{Loesung}{L\"osung}
+    \newtheorem{Satz}{Satz}
+    \newtheorem{Folgerung}{Folgerung}
+    \newtheorem{Fakt}{Fakt}
+    \newenvironment{Beweis}{\begin{proof}[Beweis.]}{\end{proof}}
+    \newenvironment{Lemma}{\begin{lemma}}{\end{lemma}}
+    \newenvironment{Proof}{\begin{proof}}{\end{proof}}
+    \newenvironment{Theorem}{\begin{theorem}}{\end{theorem}}
+    \newenvironment{Problem}{\begin{problem}}{\end{problem}}
+    \newenvironment{Corollary}{\begin{corollary}}{\end{corollary}}
+    \newenvironment{Example}{\begin{example}}{\end{example}}
+    \newenvironment{Examples}{\begin{examples}}{\end{examples}}
+    \newenvironment{Definition}{\begin{definition}}{\end{definition}}
+\makeatother
+
 % Notes
 % Talk using pympress: brew install pympress
-% Talk command: pympress -t 40 -n right ~/Documents/master/1901/presentation/1901_3230880_philip_heltweg_presentation.pdf
+% Talk command: pympress -t 40 -n right ~/Documents/master/master-seminar/presentation/1901_3230880_philip_heltweg_presentation.pdf
 \setbeameroption{show notes on second screen=right} % Both
+
 % Coloring note-pages
@@
 \frame{\titlepage}
+\note{
+    \begin{itemize}
+        \item Folien sind nummeriert unten rechts, bei Fragen am besten Nummer aufschreiben
+    \end{itemize}
+}
 
@@
 
-\begin{frame}{Courtroom example: Revision}
+\begin{frame}{Courtroom example: Revision 1}
 
@@
         \item new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$
+    \end{itemize}
+
+    \note{
+        \begin{itemize}
+            \item example 7, math
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Courtroom example: Revision 2}
+    \begin{itemize}
+        \item new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$
         \item $min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".
@@
 
-\begin{frame}{Properties of BM Revision Operators}
+\begin{frame}{Properties of BM Revision Operators: Basic properties}
     \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\ast\arabic*$)]
@@
         \item\label{AST2} $\qquad\alpha \equiv \gamma \textrm{ implies } \leq_{\alpha}^{\ast}=\leq_{\gamma}^{\ast}$
+    \end{enumerate}
+
+    \note{
+        \begin{itemize}
+            \item \ref{AST1} and \ref{AST2} are considered basic properties: A revision of a tpo $\leq$ over $W$ must generate another tpo over $W$.
+In addition, the operator must return an equal revised tpo for semantically equivalent sentences, the so called syntax-irrelevance property.
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Properties of BM Revision Operators: Common rules in iterated belief change}
+    \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\ast\arabic*$)]
+        \setcounter{enumi}{2}
         \item\label{AST3} $\qquad \textrm{If } x, y \in \modelsOf{\alpha} \textrm{ then } x \leq_{\alpha}^{\ast} y \textrm{ iff } x \leq y$
@@
         \item\label{AST5} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } x \leq y \textrm{ then } x <_{\alpha}^{\ast} y$
+    \end{enumerate}
+
+    \note{
+        \begin{itemize}
+            \item The next group of properties, \ref{AST3}-\ref{AST5} are common rules in iterated belief change.
+Booth and Meyer themselves consider them characteristic for admissible revision operators, a class of operators that requires new evidence to not be ignored completely \cite{Booth2006a}.
+This is in contrast to revision strategies like natural revision by Boutilier \cite{Boutilier1996}, which minimises change in conditional beliefs.
+            \item If revising a tpo by a sentence $\alpha$, the relative ordering of worlds that are either both $\modelsOf{\alpha}$- or $\modelsOf{\neg\alpha}$-worlds, must stay the same (\ref{AST3}/\ref{AST4}).
+These properties were already part of the semantic postulates \ref{CR1} and \ref{CR2}, by Darwiche and Pearl \cite{Darwiche1997}, discussed in section \ref{chapter:dp-agm-postulates}.
+            \item In a similar way, \ref{AST5} is a stronger requirement than the other two Darwiche and Pearl postulates \ref{CR3} and \ref{CR4}.
+It means the following: When a world $x$ is considered at least as plausible as a world $y$ before a revision by new information $\alpha$, if $\alpha$ makes $x$ more plausible ($x \in \modelsOf{\alpha}$) and $y$ less plausible ($y \in \modelsOf{\neg\alpha}$), then after revision by $\alpha$, $x$ should be considered strictly more plausible than $y$.
+This property was not only proposed by Booth and Meyer \cite{Booth2006a}, but also by Jin und Thielscher in \cite{Jin2007} (as the postulate of independence).
+            \item These properties define tpo-revision with one input sentence.
+Booth and Meyer relate them to the AGM postulates for belief set revision \cite{Alchourron1985} as basic postulates for tpo-revision \cite{Booth2011}.
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Properties of BM Revision Operators: Supplementary rationality properties }
+    \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\ast\arabic*$)]
+        \setcounter{enumi}{5}
         \item\label{AST6} $\qquad \textrm{If } x \in \modelsOf{\alpha}, y \in \modelsOf{\neg\alpha} \textrm{ and } y \leq_{\alpha}^{\ast} x \textrm{ then } y \leq_{\gamma}^{\ast} x$
@@
         \begin{itemize}
-            \item properties
+            \item With \ref{AST6} and \ref{AST7}, Booth and Meyer aim to add supplementary rationality properties to keep revision with different sentences coherent.
+These properties are largely ignored in other literature on iterated belief change \cite{Booth2011}.
+\ref{AST6} means that if, after revision by evidence $\alpha$ that makes a world $x$ more plausible than $y$, $y$ is still considered at least as plausible as $x$, then for revision by any possible evidence $\gamma$, $y$ must still be at least as plausible as $x$.
+\ref{AST7} is the equivalent property for strict preference.
         \end{itemize}
@@
 
+\begin{frame}[fragile]{Non-priotized revision}
+    \begin{figure}[H]
+        \centering
+        \begin{tikzpicture}[scale=1]
+            \begin{axis}[
+                    xticklabels={},
+                    yticklabels={},
+                    extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
+                    extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
+                    ytick style={draw=none},
+                    xtick style={draw=none},
+                    axis line style={draw=none}
+                ]
+                \addplot[
+                    scatter,
+                    scatter src=explicit symbolic,
+                    mark size=3,
+                    scatter/classes={
+                            empty={mark=*, fill=white},
+                            filled={mark=*, fill=black}
+                        },
+                    nodes near coords*={\Label},
+                    visualization depends on={value \thisrow{label} \as \Label}
+                ]
+                table [meta=class] {
+                        x y class label
+
+                        1 8 empty \empty
+                        3 8 filled
+
+                        1 7 empty
+                        3 7 filled
+
+                        2 6 empty
+                        4 6 filled
+
+                        2 5 empty
+                        4 5 filled
+
+                        5 4 filled
+                        7 4 empty
+
+                        5 3 filled
+                        7 3 empty
+
+                        6 2 filled
+                        8 2 empty
+
+                        6 1 filled
+                        8 1 empty
+                    };
+            \end{axis}
+        \end{tikzpicture}
+        \caption{Non-prioritised revision by $\alpha = r$}
+        \label{fig:example-non-prio-revision}
+    \end{figure}
+
+    \note{
+        \begin{itemize}
+            \item Es gibt postulate die erfordern, dass neuen Informationen immer geglaubt wird und sie in das belief set aufgenommen werden, e.g. \ref{E2} als $\alpha \in B(\mathbb{E}\ast\alpha)$
+            \item BM revision operatoren sind "non priotized revision", d.h. neue informationen müssen nicht teil des belief sets werden wie hier gezeigt
+            \item aber auch erinnerung: admissible revision von BM erfordert (\ref{AST3} - \ref{AST5}), dass neue informationen nicht ignoriert werden, hier r verändert die conditional beliefs
+            \item das im gegensatz zu natural revision by boutilier welches minimal change für conditional beliefs fordert
+        \end{itemize}
+    }
+\end{frame}
+
 \section{Iterating: \texorpdfstring{$\preceq$}{tpo}-revision}
@@
 
-\begin{frame}{A concrete operator: Setup}
+\begin{frame}{A concrete operator \footnote{as shown in \cite{Booth2011}}: Setup}
     \begin{itemize}

### 2021-03-08 notes/example.m
feat: removed old notes

@@ -1,17 +1,0 @@
-clear all; close all; clc;
-load Testdata
-
-L = 15; % spatial domain
-n = 64; % Fourier modes
-x2 = linspace(-L,L,n+1); x = x2(1:n); y = x; z = x;
-k = (2*pi/(2*L))*[0:(n/2-1) -n/2:-1]; ks = fftshift(k);
-
-[X,Y,Z] = meshgrid(x,y,z);
-[Kx,Ky,Kz] = meshgrid(ks,ks,ks);
-
-for j = 1:20
-    Un = reshape(Undata(j,:),n,n,n);
-    close all, isosurface(X,Y,Z,abs(Un),0.4)
-    axis([-20 20 -20 20 -20 20]), grid on, drawnow
-    pause(1)
-end

### 2021-03-08 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: more notes in presentation, agm postulates

@@
         \begin{itemize}
-            \item NOTE
+            \item Erklärung TPO, ein Mörderer und kein Alien gleich plausibel, dann kein/beide, dann jeweils mit Alien
         \end{itemize}
@@
 \begin{frame}{Preorder visualisation}
+
+    \begin{itemize}
+        \item $[[x]]_{\sim} = \{y \mid y \sim x\}$
+        \item $[[x]] \leq [[y]]$ iff $x \leq y$
+    \end{itemize}
+
     \begin{table}[H]
@@
     \end{table}
-    \note{
-        \begin{itemize}
-            \item It uses the fact that tpos can be represented as a linearly ordered set of ranks.
-Each rank of a tpo $\leq$ is defined as the equivalence classes modulo the symmetric closure of $\leq$: $[[x]]_{\sim} = \{y \mid y \sim x\}$.
-These equivalence classes are then ordered by the relation $[[x]] \leq [[y]]$ iff $x \leq y$.
+
+    \note{
+        \begin{itemize}
+            \item TPOs können visualisiert werden als geordnete Liste von Rängen auf denen die Welten sind
+            \item Die Ränge enthalten jeweils Welten mit gleicher Plausibilität
+            \item Mathematisch ausgedrückt sind sie die Äquivalenzklassen zur Symmetrie (teilt die Welten in disjunkte Teilmengen ein)
         \end{itemize}
@@
         \item abstract entity $\mathbb{E}$ that contain all information an agent need for their reasoning \cite{Darwiche1997}
-        \item commonly used: tpo $\leq_{\mathbb{E}}$
+        \item strategy for reasoning can be modeled as tpo $\leq_{\mathbb{E}}$ over worlds
         \item belief sets $B(\mathbb{E})$ can be extracted from epistemic states as all sentences true in the most plausible worlds
@@
 Epistemic states enthalten die Strategie des Agenten wie er seinen Glauben ändert, damit auch die conditional beliefs.
-            \item "commonly used" does not mean has to be used, abstract
+            \item ("commonly used" does not mean has to be used, abstract) - BM nehmen es aber an in ihrem paper
         \end{itemize}
@@
         \item\label{E3} $\qquad B(\mathbb{E}\ast\alpha)  \subseteq B(\mathbb{E})+\alpha$
-        \item\label{E4} $\qquad \textrm{If } \alpha \notin B(\mathbb{E}) \textrm{ then } B(\mathbb{E}) + \alpha \subseteq B(\mathbb{E} \ast \alpha)$
+        \item\label{E4} $\qquad \textrm{If } \neg \alpha \notin B(\mathbb{E}) \textrm{ then } B(\mathbb{E}) + \alpha \subseteq B(\mathbb{E} \ast \alpha)$
         \item\label{E5} $\qquad \textrm{If } \mathbb{E} = \mathbb{F} \textrm{ and } \alpha \equiv \beta \textrm{ then } B(\mathbb{E} \ast \alpha) = B(\mathbb{F} \ast \beta)$
@@
                   \begin{itemize}
-                      \item 1: deduktiv abgeschlossen
-                      \item 2: neue information ist immer teil des belief sets nach revision.
+                      \item 1: "Closure": deduktiv abgeschlossen, ist ein belief set
+                      \item 2: "Success": neue information ist immer teil des belief sets nach revision.
 Das muss nicht so sein, für BM tpo revision operatoren die wir hier betrachten gilt dies z.b.
@@
 Wird "non-priotized revision" genannt
-                      \item 3: % TODO
-                      \item 4:
+                      \item 3 und 4: "Inclusion" und "Vacuity": zusammen, wenn neues belief ist konsistent mit dem vorherigen belief set dann gibt es keinen grund beliefs zu entfernen.
+das neue belief set wird vorheriges belief set + alpha + was aus alpha und belief set folgt sein, minimal change wenn alpha konsistent mit belief set
                       \item 5: Syntax irrelevanz für information mit der revision betrieben wird.
@@
 Also ist E5 schwächer als das Original von AGM.
-                      \item 6: Das belief set enthält elementaren widerspruch nach revision mit inkonsistenten informationen (alpha wärend not alpha eine tautologie ist).
+                      \item 6: Das belief set enthält elementaren widerspruch NUR nach revision mit inkonsistenten informationen, konsistenz "at all costs" (alpha wärend not alpha eine tautologie ist).
 BM bestehen auf konsistente Eingaben damit sie immer ein belief set aus dem epistemischen status ableiten können.
 Daher nehmen sie E6 nicht an und nur E1-5, E7-8 als "DP-AGM"
-                      \item 7: % TODO
-                      \item 8: % TODO
+                      \item 7 und 8: Wenn ein belief set nach revision mit alpha konsistent ist mit beta dann kann kann man das belief set von alpha und beta durch expansion mit beta erreichen (revision nicht nötig), wieder minimal change
                   \end{itemize}
@@
 \ref{AST7} is the equivalent property for strict preference.
+                  %\item so far each of our rules mention onlyonerevision input sentenceα(modulo logical equivalence).
+Byanalogy  with the AGM postulates  forbelief setrevision ,  we might consider them as the set ofbasicpostulates  for  tpo-revision.
+One  thing  largely  missing  from  the  literature  on  iterated  belief  change  is  aserious study ofsupplementaryrationality properties which bestow a certain amount of coherence on theresults of revising bydifferentsentences.
+The last couple of properties do this.
         \end{itemize}

### 2021-03-08 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: notes up until operator properties

@@
         \begin{itemize}
-            \item what is it
-            \item say that the original tpo can be reconstructed from it
+            \item zusätzlich zu der neuen Repräsentation von Welten eine neue Ordnung über diese Intervalle
         \end{itemize}
@@
         \begin{itemize}
-            \item characteristics + definition
-            \item original tpo can be reconstructed from this
+            \item 1. basic, preceq ist eine tpo über die neue intervall Struktur
+            \item 2/3 faithful zur orginalen tpo, positive representation precqe iff es auch so in der originalen tpo ist
+            \item das bedeutet die originale tpo kann von der faithful tpo rekonstruiert werden (einfach nur auf + oder - einschränken und alte tpo ablesen)
+            \item daher muss man nur neue tpo und W+- speichern im epistemischen Zustand
+            \item 4 bedeutet es muss einen unterschied geben zwischen den representation, interval kann nicht länge 0 haben
         \end{itemize}
@@
         \begin{itemize}
-            \item example with sticks
+            \item beispielvisualisierung, x1+- hier zusätzlich dran geschrieben zur einführung, wird nachher weggelassen
+            \item zeilen sind die welten, spalten kann man sich als Ränge in der TPO vorstellen
+            \item je weiter links desto plausibler
+            \item Interval zwischen + und - ergibt sich aus proposition 4 vorher, muss nicht gleich sein aber größer als 0
         \end{itemize}
@@
         \begin{itemize}
-            \item example for courtroom
+            \item Visualisierung für unser Beispiel
+            \item Erinnerung an die vier Äquivalenzklassen von vorher: 1 Mörderer, kein/zwei Mörderer und beides jeweils mit Alien
+            \item Anmerken: Überlappung zwischen den positiven/negativen Repräsentationen im nicht Alien Fall und Abstand zwischen Alien und nicht Alien, gehen wir nachher noch drauf ein aber hätte man vorher nur mit W nicht modellieren können, Unterschiedlich unwahrscheinliche Welten
         \end{itemize}
@@
         \begin{itemize}
-            \item definition
+            \item Definition eines BM revisions operators
+            \item Funktion * von tpo und satz alpha aus L zu neuer tpo auf W, basierend auf unserer extra struktur auf W+-
+            \item Damit operator basierte belief revision, konditionale glauben (strategie) in form der tpo und glaubensset weil man es aus der tpo extrahieren kann
+            \item Prinzip einfach: Für jeden satz alpha und welt x, setze x auf ihre positive representation x+ in w+ wenn x ein model von alpha ist und auf ihre negative representation x- wenn sie kein model von alpha ist
+            \item Die neue TPO ergibt sich dann aus der Ordnung auf den jeweiligen postiven/negativen representationen
         \end{itemize}
@@
         \begin{itemize}
-            \item example 7, figure 4
+            \item Hier beispiel von vorher mit alpha gleich p "John ist der Mörderer"
+            \item r subskript alpha von x ist hier jeweils als schwarzer Punkt markiert
+            \item Für Welten die Modelle von alpha sind (wie 100 oder 110) wird ihre positive representation gewählt
+            \item Für Welten die keine Modelle sind (wie 010 "Mary ist die Mörderin") die negative representation
+            \item Anmerkung: Welten die keine Modelle sind können trotzdem noch plausibler sein, siehe 010 und 101.
+            \item Es macht intuitiv Sinn: Ein Richter würde eher annehmen, dass Mary die Mörderin ist obwohl es Indizien für John gibt als zu akzeptieren, dass das Opfer ein Alien ist
+            \item Das wird noch kommen als "non-priotized revision"
         \end{itemize}
@@
         \begin{itemize}
-            \item example 7, math
+            \item Gleiches Beispiel, Mathe statt grafisch
+            \item Hier für 010 "Mary ist die Mörderin" und 110 "Mary und John sind die Mörder"
+            \item Vorher: Zwei Mörderer sind unwahrscheinlich, daher ist nur Mary ist die Mörderin plausibler
+            \item Evidenz für p "John ist der Mörder"
+            \item 010 "Mary ist die Mörderin" ist kein Model also wird ihr die negative Representation 010- zugewiesen
+            \item 110 "Mary und John sind die Mörder" ist ein Model also wird ihr die positive Representation 110+ zugewiesen
+            \item Da die positive Representation 110+ für "Mary und John sind die Mörderer" plausibler ist als die negative Representation von 010- Mary ist die Mörderin ist nach der Evidenz 110 (beide sind Mörderer) plausibler
+            \item neue TPO nachdem man diesen Prozess für alle Welten macht
         \end{itemize}
@@
         \begin{itemize}
-            \item example 7, math
+            \item Das belief set hat sich geändert: Das belief set der neuen tpo ist nun alle sätze die wahr sind in der plausibelsten welt: "John ist der mörderer und das opfer ist kein alien"
+            \item Macht intuitiv Sinn
+            \item Auch die conditional beliefs des agenten haben sich geändert mit der TPO: Vorher beide Mörderer nicht so plausibel wie nur Mary, jetzt beide Mörderer plausibler als nur Mary (weil wir ja evidenz haben das zumindest John ein Mörderer ist)
+            \item Macht intuitiv auch Sinn
         \end{itemize}

### 2021-03-08 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: all the notes

@@
 \begin{frame}{Courtroom example \footnote{inspired by \cite{Booth2011} and \cite{Darwiche1997}}}
+    \label{slide:example-setup}
     \begin{itemize}
@@
 \begin{frame}{Preorder visualisation}
-
+    \label{slide:vis-ranks}
     \begin{itemize}
@@
 \begin{frame}{Belief Set Revision Postulates\footnote{AGM postulates \cite{Alchourron1985}, reformulated for epistemic states by Darwiche and Pearl \cite{Darwiche1997}}}
+    \label{slide:e1-8}
     \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\mathbb{E}\!*\!\arabic*$)]
@@
         \begin{itemize}
+            \tiny
             \item $\mathbb{E}$ als epistemischer status, $B(\mathbb{E})$ belief set des status, $B(\mathbb{E}) + \alpha$ ist die expansion $B(\mathbb{E})$ mit $\alpha$ ($\alpha$ hinzufügen.
 $CN(B(\mathbb{E}) \cup \alpha)$), $\ast$ being a belief change operator on epistemic states
-            \item Postulates
-                  \begin{itemize}
             \item 1: "Closure": deduktiv abgeschlossen, ist ein belief set
@@
         \end{itemize}
-        \end{itemize}
     }
@@
 \begin{frame}{Conditional Belief Revision Postulates\footnote{by Darwiche and Pearl \cite{Darwiche1997}}}
+    \label{slide:cr1-4}
     \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = (CR$\arabic*$)]
@@
 \begin{frame}{$\leq$-faithful tpo - definition}
+    \label{slide:faithful-tpo}
     \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\preceq\arabic*$)]
@@
 \begin{frame}{BM tpo-revision operator}
+    \label{slide:bm-revision-operator}
     \begin{definition}[Revision operator $\ast_{\preceq}$ for $\leq$ generated by $\preceq$ \cite{Booth2011}]
@@
             \item Funktion * von tpo und satz alpha aus L zu neuer tpo auf W, basierend auf unserer extra struktur auf W+-
-            \item Damit operator basierte belief revision, konditionale glauben (strategie) in form der tpo und glaubensset weil man es aus der tpo extrahieren kann
+            \item Syntax: neue tpo als tpo subscript alpha, generiert mit superskript *
+            \item Damit operatorbasierte belief revision, konditionale glauben (strategie) in form der tpo und glaubensset weil man es aus der tpo extrahieren kann
             \item Prinzip einfach: Für jeden satz alpha und welt x, setze x auf ihre positive representation x+ in w+ wenn x ein model von alpha ist und auf ihre negative representation x- wenn sie kein model von alpha ist
@@
     \note{
+        \footnotesize
         \begin{itemize}
@@
 \begin{frame}{Properties of BM Revision Operators: Basic properties}
+    \label{slide:ast1-7}
     \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\ast\arabic*$)]
@@
         \begin{itemize}
-            \item \ref{AST1} and \ref{AST2} are considered basic properties: A revision of a tpo $\leq$ over $W$ must generate another tpo over $W$.
-In addition, the operator must return an equal revised tpo for semantically equivalent sentences, the so called syntax-irrelevance property.
+            \item Was sind Eigenschaften von BM revisions operatoren?
+Diese Eigenschaften sind gruppiert, ich werde sie durchgehen und am Ende werden sie die Familie von operatoren kategorisieren/einschränken über die BM reden
+            \item \ref{AST1} und \ref{AST2} sind basis Eigenschaften
+            \item Eine revision einer tpo über W muss wieder eine tpo über W sein
+            \item Für semantisch äquivalente Sätze muss der operator die gleiche neue tpo erzeugen, so genannte syntax irrelevance property
         \end{itemize}
@@
     \note{
-        \begin{itemize}
-            \item The next group of properties, \ref{AST3}-\ref{AST5} are common rules in iterated belief change.
-Booth and Meyer themselves consider them characteristic for admissible revision operators, a class of operators that requires new evidence to not be ignored completely \cite{Booth2006a}.
-This is in contrast to revision strategies like natural revision by Boutilier \cite{Boutilier1996}, which minimises change in conditional beliefs.
-            \item If revising a tpo by a sentence $\alpha$, the relative ordering of worlds that are either both $\modelsOf{\alpha}$- or $\modelsOf{\neg\alpha}$-worlds, must stay the same (\ref{AST3}/\ref{AST4}).
-These properties were already part of the semantic postulates \ref{CR1} and \ref{CR2}, by Darwiche and Pearl \cite{Darwiche1997}, discussed in section \ref{chapter:dp-agm-postulates}.
-            \item In a similar way, \ref{AST5} is a stronger requirement than the other two Darwiche and Pearl postulates \ref{CR3} and \ref{CR4}.
-It means the following: When a world $x$ is considered at least as plausible as a world $y$ before a revision by new information $\alpha$, if $\alpha$ makes $x$ more plausible ($x \in \modelsOf{\alpha}$) and $y$ less plausible ($y \in \modelsOf{\neg\alpha}$), then after revision by $\alpha$, $x$ should be considered strictly more plausible than $y$.
-This property was not only proposed by Booth and Meyer \cite{Booth2006a}, but also by Jin und Thielscher in \cite{Jin2007} (as the postulate of independence).
-            \item These properties define tpo-revision with one input sentence.
-Booth and Meyer relate them to the AGM postulates for belief set revision \cite{Alchourron1985} as basic postulates for tpo-revision \cite{Booth2011}.
+        \footnotesize
+        \begin{itemize}
+            \item 3-5 regeln für iterated belief change mit einem input alpha
+            \item BM vergleichen sie mit den AGM postulaten, AGM postulate für revision von belief sets, postulate 1-5 für revision von tpos
+            \item charakteristisch für "admissible revision operators" die eingaben nicht ignorieren, selbst wenn es nicht zu Änderungen am belief set führt (siehe 5)
+            \item (im gegensatz zu e.g. natural revision von boutilier die Änderungen in conditional beliefs minimiert)
+            \item 3 und 4: die relative Ordnung für Welten die entweder beide Modelle für die Eingabe sind oder nicht muss gleich bleiben (schon gegeben in conditional belief revision postulates CR1/CR2 von Darwiche and pearl)
+            \item 5: wenn eine welt x mindestens so plausibel ist wie eine Welt y soll x nach einer Eingabe für die x ein model ist und y nicht strikt plausibler sein (ähnlich wie CR3/4 von DP aber strenger)
         \end{itemize}
@@
         \begin{itemize}
-            \item With \ref{AST6} and \ref{AST7}, Booth and Meyer aim to add supplementary rationality properties to keep revision with different sentences coherent.
-These properties are largely ignored in other literature on iterated belief change \cite{Booth2011}.
-\ref{AST6} means that if, after revision by evidence $\alpha$ that makes a world $x$ more plausible than $y$, $y$ is still considered at least as plausible as $x$, then for revision by any possible evidence $\gamma$, $y$ must still be at least as plausible as $x$.
-\ref{AST7} is the equivalent property for strict preference.
-                  %\item so far each of our rules mention onlyonerevision input sentenceα(modulo logical equivalence).
-Byanalogy  with the AGM postulates  forbelief setrevision ,  we might consider them as the set ofbasicpostulates  for  tpo-revision.
-One  thing  largely  missing  from  the  literature  on  iterated  belief  change  is  aserious study ofsupplementaryrationality properties which bestow a certain amount of coherence on theresults of revising bydifferentsentences.
-The last couple of properties do this.
+            \item vorher nur eine eingabe, diese zusätzlichen postulate um revision mit unterschiedlichen eingaben stimmig zu halten
+            \item 6: wenn nach einer revision mit alpha die welt y mindestens so plausibel ist wie x obwohl x ein model für alpha ist und y nicht, dann ist y für jede eingabe gamme mindestens so plausibel wie x
+            \item 7: gleich, nur für die strikt plausiblere version
         \end{itemize}
@@
 \begin{frame}{Family of BM Revision Operators}
+    \label{slide:theorem1}
     \begin{theorem}
@@
         \begin{itemize}
-            \item theorem 1
+            \item theorem 1 als definition der funktionen/revisionsoperatoren für eine tpo die BM diskutieren/vorschlagen
+            \item erinnern an faithful tpo, W+-, 1-7
         \end{itemize}
@@
     \note{
+        \footnotesize
         \begin{itemize}
             \item Es gibt postulate die erfordern, dass neuen Informationen immer geglaubt wird und sie in das belief set aufgenommen werden, e.g. \ref{E2} als $\alpha \in B(\mathbb{E}\ast\alpha)$
-            \item BM revision operatoren sind "non priotized revision", d.h. neue informationen müssen nicht teil des belief sets werden wie hier gezeigt
-            \item aber auch erinnerung: admissible revision von BM erfordert (\ref{AST3} - \ref{AST5}), dass neue informationen nicht ignoriert werden, hier r verändert die conditional beliefs
-            \item das im gegensatz zu natural revision by boutilier welches minimal change für conditional beliefs fordert
+            \item hier im Beispiel revision mit p "das Opfer ist ein Alien", modelle/nicht modelle jeweils mit positiver/negativer representation identifizieren (schwarzer punkt), neue tpo ablesen.
+hier trotz evidenz "das opfer ist ein alien", min worlds 010, 100 aka teil des belief sets ist "das opfer ist KEIN alien"
+            \item BM revision operatoren sind "non priotized revision", d.h. neue informationen müssen nicht teil des belief sets werden
+            \item aber auch erinnerung: admissible revision von BM erfordert (\ref{AST3} - \ref{AST5}), dass neue informationen nicht ignoriert werden, hier r verändert die conditional beliefs.
+das im gegensatz zu natural revision by boutilier welches minimal change für conditional beliefs fordert
+            \item Wann glaubt der Richter denn an aliens? Welche zusätzlichen beweise braucht er und wie iterieren wir ein weiteres mal jetzt? I am glad you asked!
         \end{itemize}
@@
         \item Function p mapping worlds to real numbers: $p: W^{\pm} \mapsto \mathds{R}$
-        \item Interval representing a world: $(p(x^{+}), p(x^{-}))$
+        \item Interval representing a world $x$: $(p(x^{+}), p(x^{-}))$
         \item Distance between representations: $p(x^{-}) - p(x^{+}) = a > 0$
@@
         \begin{itemize}
-            \item math for operator
+            \item explizit nur ein beispiel, nicht der einzige mögliche operator
+            \item definiert über eine funktion p die welten aus w+- echten zahlen zuweist (je kleiner desto plausibler)
+            \item damit wird ein interval für eine welt x aus W zu einem intervall von echten zahlen
+            \item aufgrund der faithful tpo definition (slide 20) postulat 4 ist x+ < x-, daher distanz a des intervals > 0
+            \item jetzt kann man mit p eine tpo definieren indem man welten in der tpo nach ihrer zahl in p anordnet
         \end{itemize}
@@
         \begin{itemize}
-            \item math for operator
+            \item revision der übergeordneten tpo ist jetzt ein zwei schritt prozess:
+            \item 1. schritt: mit der funktion p kann man eine tpo definieren, wähle p so das die damit definierte tpo = unserer übergeordneten tpo auf w+- ist
+            \item 2.
+schritt: p mit alpha zu p alpha ändern indem man alle welten die ein model von alpha sind unverändert lässt und alle anderen um a "zurückschiebt" (x+ wird zur gleichen zahl wie x- da um a zurückgeschoben und x- zu x- + a)
+            \item von der neuen funktion p alpha kann man jetzt eine neue übergeordnete tpo ablesen
         \end{itemize}
@@
     \begin{itemize}
+        \item $\preceq_{p \ast \alpha}$ for $\alpha = p$
         \item Choose initial $p$ so that $\preceq_{p} = \preceq$
@@
         \begin{itemize}
-            \item math for example with operator
+            \item hier an unserem beispiel für alpha "John ist der mörderer"
+            \item initial hat der richter keine präferenz welcher verdächtige der mörder ist, die welten 010 und 100 sind am plausibelsten (am weitesten links) und haben das gleiche interval.
+hier mit p zu 0 im positiven fall und a im negativen fall abgebildet.
+            \item nachdem wir p zu p alpha verändern sind die intervalle:
+            \item für das nicht model 010 vom START p(010+) + a = p(010-) zum ENDE p(010-) + a, also (a, 2a) "um a zurück geschoben"
+            \item für das model 100 unverändert als (0, a)
+            \item das kann man nun für alle welten machen und die neue übergeordnete tpo von p ableiten
         \end{itemize}
@@
         \begin{itemize}
-            \item figure 7
-            \item maybe put the figure 5 from paper (original revision of <=) before this
-            \item maybe put slides for complete example in here going from tpo to revision once, to revision twice
+            \item hier visualisiert revision der übergeordneten tpo auf w+- mit alpha = p = John ist der mörderer
+            \item intervalle der welten in der tpo p sternchen alpha dargestellt wie vorher
+            \item alte positive repräsentationen vor der revision von nicht modellen markiert als x
+            \item alle nicht modelle von p um a zurück geschoben, alle modelle bleiben gleich
+            \item damit neue tpo ablesbar, minimale welt 100, neues belief set "John ist der mörderer" wie vorher und intuitiv
+            \item was hat sich jetzt geändert? die konditionalen annahmen, was der agent bereit ist zu akzeptieren mit neuen beweisen
         \end{itemize}
@@
         \begin{itemize}
-            \item figure 8
+            \item hier, revision mit alpha = r = "Das opfer war ein alien"
+            \item wie vorher besprochen, trotz der evidenz ist "das opfer ist ein alien" nicht teil der minimalen welten und damit nicht teil des belief sets (non priotized revision)
+            \item aber die konditionalen annahmen haben sich jetzt verändert, der abstand zwischen den alien welten und nicht alien welten ist weg
         \end{itemize}
@@
         \begin{itemize}
-            \item figure 9
+            \item jetzt revision mit beta "der mörder hat alleine gehandelt" nachdem wir vorher mit alpha "das opfer war ein alien" revision betrieben haben
+            \item jetzt sind die welten mit dem opfer als alien und einem einzeltäter plausibler als die welten ohne alien aber ohne mörder/mit zwei mördern!
+            \item hätten wir direkt mit beta revision betrieben wäre das nicht passiert, iterated belief revision am werk
+            \item allerdings hier: die welten mit einem einzeltäter und ohne alien (010 und 100) sind immernoch die minimalen welten und damit ist r "das opfer ist ein alien" nicht teil des belief sets
         \end{itemize}
@@
         \item Jetzt: Fragen? Diskussion
+        \item Example setup: \pageref{slide:example-setup} - 1
+        \item Visualisierung ranks: \pageref{slide:vis-ranks} -1
+        \item E1-8: \pageref{slide:e1-8} -1
+        \item CR1-4: \pageref{slide:cr1-4} -1
+        \item faithful-tpo: \pageref{slide:faithful-tpo} -1
+        \item bm-revision-operator: \pageref{slide:bm-revision-operator} -1
+        \item ast1-7: \pageref{slide:ast1-7} -1
+        \item theorem1: \pageref{slide:theorem1} -1
     \end{itemize}

### 2021-03-09 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: few changes from live test

@@
     \begin{itemize}
+        \item Paper "How to Revise a Total Preorder" von booth and meyer
         \item Folien sind nummeriert unten rechts, bei Fragen am besten Nummer aufschreiben
@@
             \item Beispiel Frage zur Motivation, wird unser Beispiel sein. Wir haben zwei Verdächtige und diverse Beweise und Indizien, wie bilden wir uns ein Bild über die Welt?
+            \item Iterierte Information: Immer wieder neue Informationen nacheinander mit der wir unseren GLauben immer wieder anpassen müssen.
             \item Unvollständige Information: Kein gesichertes Wissen sondern Glauben und Annahmen aus Zeugenaussagen/Indizien
@@
         \begin{itemize}
-            \item Belief change, adapting one's world view under imperfect information
-            \item Agent can be human or machine -> major areas philosophy and AI
-            \item Different approaches, nonmonotonic logic known from beierle courses (truth maintenance systems, default logic like reiter or pool), probabilistic reasoning (also known from beierle course 1845),
-            \item Belief revision: operator based. Define and discuss operators that transition agent state from one to the next for new evidence
-            \item One step vs iterated depending on how many consecutive new information it handels
+            \item Belief change, Glaubens änderung, Veränderung der Weltansicht mit neuen, unsicheren informationen
+            \item Agent kann mensch oder maschine sein, phylosophie oder KI
+            \item Unterschiedliche Lösungsansätze, nichtmonotone logik bekannt aus lehrstuhl kursen (truth maintenance systems, default logic wie reiter), probabilistisches denken (auch in Lehrstuhl kursen),
+            \item Belief revision: operator basiert. Operatoren die einen Agentenstatus in einen neuen überführen mit neuen infromationen: definieren und Eigenschaften diskutieren
+            \item One step vs iterated depending: Je nachdem ob man eine neue information betrachtet oder eine Reihe von neuen informationen
             \item Booth and Meyer: iterated belief revision
@@
         \begin{itemize}
-            \item Belief sets as what an agent currently accepts as true (AGM theory: How is a belief set defined and how does the belief set change with new evidence?)
-            \item Conditional beliefs as what an agent is prepared to accept as true depending on future evidence?
-(Darwiche and Pearl: In addition to how does the belief set change, what is the "strategy" for future belief set change?
-How do conditional beliefs change?)
-            \item Booth and Meyer: Change of conditional beliefs: If conditional beliefs are the strategy to change belief sets with future evidence, how can we change conditional beliefs with new evidence?
+            \item Glaubensmengen sind was ein agent aktuell als wahr akzeptiert (AGM theory: Wie ist eine glaubensmenge definiert und wie kann sie sich mit neuen informationen ändern?)
+            \item Konditionale annahmen sind was ein agent bereit ist zu akzeptieren mit neuen informationen?
+(Darwiche and Pearl: Was ist die "strategie" für zukünftige glaubensmengen änderungen?
+Wie ändern sich konditionale glauben?)
+            \item Booth and Meyer: Änderung in konditionalen glauben: Wenn konditionale glauben die strategie der änderung ist, wie können wir unsere strategie ändern?
         \end{itemize}
@@
         \begin{itemize}
-            \item Conditional beliefs/Conditional belief revision: Indizien für Sachverhalt = Sachverhalt nicht direkt glauben aber bei mehr Indizien immer mehr daran glauben/immer mehr bereit sein es zu akzeptieren.
-            \item paper goal/focus of this talk revision operators for conditional belief structure (not mention tpo yet)
-            \item postulates for operators to restrict them, define a family of operators (axiomatisation) by doing that
-            \item properties are not "correct" but has to be done to reasonably talk about those operators and narrow down possibilities, compare to other properties/edge cases to branch out
+            \item Konditionaler Glauben Ändern: Indizien für Sachverhalt = Sachverhalt nicht direkt glauben aber bei mehr Indizien immer mehr daran glauben/immer mehr bereit sein es zu akzeptieren.
+            \item Ziel des Papiers: Revisionsoperatoren besprechen für die änderung von konditionalen glauben
+            \item Wie? über die definition von postulaten die diese operatoren einschränken und damit eine familie von operatoren definieren über die wir reden können
+            \item postulate sind nicht zwingend, nur zur einschränkung damit wir über diese operatoren reden können
         \end{itemize}
@@
         \item  $Int({\Sigma}) = W = \{ 000, 001, 010, 011, 100, 101, 110, 111\}$
+        \item $Mod(p) = \modelsOf{p} = \{ 100, 101, 110, 111\}$, $100 \in \modelsOf{p}$
     \end{itemize}
@@
             \item Beispiel inspiriert aus der Literatur
-            \item Aussagenlogik, Aussagenvariablen p, q, r
+            \item Aussagenlogik, Aussagenlogische Signatur mit Aussagenvariablen p, q, r
             \item "Mögliche Welt" als aussagenlogische Interpretationen/Belegungen, damit 2 hoch 3 = 8 mögliche Alternativen hier
             \item Kodierung der Welt als Tupel von Wahrheitswerten (0 = false, 1 = true)
-            \item Beispiel für 1-2 Welten durchgehen: 010 = Mary ist Mörderin, Opfer ist kein Alien, 111 = John und Mary sind die Mörder, haben ein Alien getötet
+            \item models of syntax, modelle von p
+            \item Beispiele für 1-2 Welten durchgehen: 010 = Mary ist Mörderin, Opfer ist kein Alien, 111 = John und Mary sind die Mörder, haben ein Alien getötet
         \end{itemize}
@@
         \begin{itemize}
+            \item übliches werkzeug um präferenzen von möglichen welten zu modellieren
             \item total (for all $x, y \in W$ either $x \leq y$ or $y \leq x$)
@@
             \item  $<$ strict part of $\leq$
-            \item $\sim$ symmetric closure of $\leq$ (i.e. $x \sim y$ iff $x \leq y$ and $y \leq x$)
+            \item $\sim$ (tilde) symmetrische relation auf of $\leq$ (i.e. $x \sim y$ iff $x \leq y$ and $y \leq x$)
         \end{itemize}
@@
         \begin{itemize}
-            \item Erklärung TPO, ein Mörderer und kein Alien gleich plausibel, dann kein/beide, dann jeweils mit Alien
+            \item Beispiel TPO anhand des richters der denkt einer der angeklagten ist wahrscheinlich der mörderer und hat alleine gehandelt. sehr unwahrscheinliche aber möglich, opfer ist ein alien.
+            \item ein Mörderer und kein Alien gleich plausibel, dann kein/beide, dann jeweils mit Alien
         \end{itemize}
@@
         \begin{itemize}
-            \item Belief sets als aktuell akzeptierte Sätze eines Agenten
-            \item Gegensatz zu conditional beliefs: Sätze im Belief set werden als war angenommen.
+            \item Belief sets als aktuell als wahr akzeptierte Sätze eines Agenten
+            \item deduktiv abgeschlossen
+            \item Gegensatz zu konditionalen glauben: Sätze im Belief set werden als war angenommen.
             \item Betrachtungsgegenstand von AGM-Theorie \cite{Alchourron1985} die Postulate definiert haben um Belief set revision einzuschränken, rationale revision, wir sprechen das allerdings später an weil wir die neu formulierten Postulates von \cite{Darwiche1997} nutzen
@@
     \end{itemize}
-
+    % TODO very complex, make shorter?
     \note{
@@
         \begin{itemize}
-            \item Gleiches Beispiel, Mathe statt grafisch
-            \item Hier für 010 "Mary ist die Mörderin" und 110 "Mary und John sind die Mörder"
+            \item Hier für 010 "Nur Mary ist die Mörderin" und 110 "Mary und John sind die Mörder"
             \item Vorher: Zwei Mörderer sind unwahrscheinlich, daher ist nur Mary ist die Mörderin plausibler
-            \item Evidenz für p "John ist der Mörder"
-            \item 010 "Mary ist die Mörderin" ist kein Model also wird ihr die negative Representation 010- zugewiesen
+            \item Evidenz für p "Nur John ist der Mörder"
+            \item 010 "Nur Mary ist die Mörderin" ist kein Model also wird ihr die negative Representation 010- zugewiesen
             \item 110 "Mary und John sind die Mörder" ist ein Model also wird ihr die positive Representation 110+ zugewiesen
-            \item Da die positive Representation 110+ für "Mary und John sind die Mörderer" plausibler ist als die negative Representation von 010- Mary ist die Mörderin ist nach der Evidenz 110 (beide sind Mörderer) plausibler
+            \item zurückgehen zur grafik und zeigen
+            \item Da die positive Representation 110+ für "Mary und John sind die Mörderer" plausibler ist als die negative Representation von 010- Nur  Mary ist die Mörderin ist nach der Evidenz 110 (beide sind Mörderer) plausibler
             \item neue TPO nachdem man diesen Prozess für alle Welten macht
@@
               \begin{itemize}
-                  \item before $010 \leq 110$: "Both suspects being the murderer is less plausible than Mary being the murderer"
+                  \item before $010 \leq 110$: "Both suspects being the murderer is less plausible than only Mary being the murderer"
                   \item now $110 <_{\alpha}^{\ast} 010$: "Only Mary being the murderer less plausible than both conspiring".
@@
             \item 3-5 regeln für iterated belief change mit einem input alpha
+            \item 3 und 4: die relative Ordnung für Welten die entweder beide Modelle für die Eingabe sind oder nicht muss gleich bleiben (schon gegeben in conditional belief revision postulates CR1/CR2 von Darwiche and pearl)
+            \item 5: wenn eine welt x mindestens so plausibel ist wie eine Welt y soll x nach einer Eingabe für die x ein model ist und y nicht strikt plausibler sein (ähnlich wie CR3/4 von DP aber strenger)
             \item BM vergleichen sie mit den AGM postulaten, AGM postulate für revision von belief sets, postulate 1-5 für revision von tpos
@@
             \item (im gegensatz zu e.g. natural revision von boutilier die Änderungen in conditional beliefs minimiert)
-            \item 3 und 4: die relative Ordnung für Welten die entweder beide Modelle für die Eingabe sind oder nicht muss gleich bleiben (schon gegeben in conditional belief revision postulates CR1/CR2 von Darwiche and pearl)
-            \item 5: wenn eine welt x mindestens so plausibel ist wie eine Welt y soll x nach einer Eingabe für die x ein model ist und y nicht strikt plausibler sein (ähnlich wie CR3/4 von DP aber strenger)
         \end{itemize}
@@
             \item aber die konditionalen annahmen haben sich jetzt verändert, der abstand zwischen den alien welten und nicht alien welten ist weg
+            \item 1. tpo revision, 1. neue tpo ablesbar
         \end{itemize}
@@
             \item hätten wir direkt mit beta revision betrieben wäre das nicht passiert, iterated belief revision am werk
+            \item 2. tpo revision, 2. tpo
             \item allerdings hier: die welten mit einem einzeltäter und ohne alien (010 und 100) sind immernoch die minimalen welten und damit ist r "das opfer ist ein alien" nicht teil des belief sets

### 2021-03-09 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: small changes to slides and notes

@@
         \item $Mod(p) = \modelsOf{p} = \{ 100, 101, 110, 111\}$, $100 \in \modelsOf{p}$
-    \end{itemize}
-
-    \note{
-        \begin{itemize}
-            \item Konsistentes Beispiel in der Präsentation, gut aufpassen
+        \item Lower case greek letters often used for propositional sentences $\alpha$
+    \end{itemize}
+
+    \note{
+        \footnotesize
+        \begin{itemize}
+            \item Konsistentes Beispiel in der Präsentation, der Agent ist ein Richter in einem Mörderprozess vor Gericht, John und Marry sind verdächtige und das Opfer könnte ein alien sein
             \item Beispiel inspiriert aus der Literatur
@@
             \item models of syntax, modelle von p
+            \item Aussagenlogische formeln als griechische buchstaben
             \item Beispiele für 1-2 Welten durchgehen: 010 = Mary ist Mörderin, Opfer ist kein Alien, 111 = John und Mary sind die Mörder, haben ein Alien getötet
@@
         \item strategy for reasoning can be modeled as tpo $\leq_{\mathbb{E}}$ over worlds
-        \item belief sets $B(\mathbb{E})$ can be extracted from epistemic states as all sentences true in the most plausible worlds
+        \item belief sets $B(\mathbb{E})$ can be extracted from epistemic states
               \begin{itemize}
                   \item set of minimal worlds in which $\alpha$ is true: $min(\alpha, \leq_{\mathbb{E}})$, set of most plausible worlds:  $min(\top, \leq_{\mathbb{E}})$
-                  \item Set of worlds that are models of the belief set of the agent $\modelsOf{B(\mathbb{E})} = min(\top, \leq_{\mathbb{E}})$
+                  \item Set of most plausible worlds $min(\top, \leq_{\mathbb{E}})$
                   \item All sentences true in those worlds: $Th(min(\top, \leq_{\mathbb{E}}))$
@@
             \item Darwiche and Pearl argumentieren das Belief sets nicht ausreichend sind.
-Die Postulate von AGM definieren nur wie sich belief sets ändern (principle of least change) aber conditional beliefs können sich ändern wie sie wollen.
-Epistemic states enthalten die Strategie des Agenten wie er seinen Glauben ändert, damit auch die conditional beliefs.
+            \item Die Postulate von AGM definieren nur wie sich belief sets ändern (prinzip of least change/geringste änderung) aber conditional beliefs können sich ändern wie sie wollen.
+            \item Epistemic states enthalten die Strategie des Agenten wie er seinen Glauben ändert, damit auch die conditional beliefs.
             \item ("commonly used" does not mean has to be used, abstract) - BM nehmen es aber an in ihrem paper
@@
         \begin{itemize}
-            \item Additional structure of plausibility of worlds under new evidence  W+-
+            \item zusätzliche struktur um plausibilität von welten in W nach neuer information zu modelieren
             \item "A bad day surfing is better than a good day working" als idee das eine Welt sogar unter evidenz die sie nicht supported mehr plausibel bleiben kann, e.g.
@@
             \item Definition eines BM revisions operators
-            \item Funktion * von tpo und satz alpha aus L zu neuer tpo auf W, basierend auf unserer extra struktur auf W+-
+            \item Funktion * von tpo und satz $\alpha$ aus L zu neuer tpo auf W, basierend auf unserer extra struktur auf W+-
             \item Syntax: neue tpo als tpo subscript alpha, generiert mit superskript *
             \item Damit operatorbasierte belief revision, konditionale glauben (strategie) in form der tpo und glaubensset weil man es aus der tpo extrahieren kann
-            \item Prinzip einfach: Für jeden satz alpha und welt x, setze x auf ihre positive representation x+ in w+ wenn x ein model von alpha ist und auf ihre negative representation x- wenn sie kein model von alpha ist
-            \item Die neue TPO ergibt sich dann aus der Ordnung auf den jeweiligen postiven/negativen representationen
+            \item Prinzip einfach: Für jeden satz alpha und welt x, ASSOZIIERE x mit ihrer positive representation x+ in w+ wenn x ein model von alpha ist und auf ihre negative representation x- wenn sie kein model von alpha ist
+            \item Die neue TPO ergibt sich dann aus der Ordnung auf den jeweiligen positiven/negativen representationen
         \end{itemize}
@@
         \item new tpo $\leq_{\alpha}^{\ast}$ is: $100 <_{\alpha}^{\ast} 110 <_{\alpha}^{\ast} 010 <_{\alpha}^{\ast} 000 <_{\alpha}^{\ast} 101 <_{\alpha}^{\ast} 111 <_{\alpha}^{\ast} 011 <_{\alpha}^{\ast} 001$
-        \item $min(\top, \leq_{\mathbb{E}}) = \{100\}$: "John is the murderer and the victim is not an alien".
+        \item $min(\top, \leq_{\alpha}^{\ast} ) = \{100\}$: "John is the murderer and the victim is not an alien".
         \item $\leq_{\alpha}^{\ast}$ as representation of the conditional beliefs
               \begin{itemize}
-                  \item before $010 \leq 110$: "Both suspects being the murderer is less plausible than only Mary being the murderer"
+                  \item before $010 < 110$: "Both suspects being the murderer is less plausible than only Mary being the murderer"
                   \item now $110 <_{\alpha}^{\ast} 010$: "Only Mary being the murderer less plausible than both conspiring".

### 2021-03-10 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: updated notes first chapter

@@
             \item Einführung mit Motivation, Forschungskontext und Beispiel
-            \item Hintergrund: Festlegen Notation, was sind TPOs überhaupt, vorherige Arbeit von Alchouron et al, Darwiche und Pearl
-            \item Metadata: Wie bauen Booth und Meyer auf der vorherigen Arbeit auf, Erklärung des Ansatzes zur TPO revision
-            \item BM operators: Wie benutzen BM die vorher besprochenen Metadaten für belief revision, Definition von Eigenschaften ihrer Operatoren
-            \item Iteration: Ausblick, wenn wir tpos mit der neuen Struktur anpassen können müssen wir auch die neue Struktur anpassen, ansonsten kann man nicht mehrere neue Informationen einpflegen.
-Hier haben BM sehr viel mehr geschrieben als hier vorgestellt aber ein konkreter Operator wird hier vorgestellt.
+            \item Formaler Hintergrund: Festlegen Notation, was sind TPOs überhaupt
+            \item Dann: Wie bauen Booth und Meyer auf der vorherigen Arbeit auf um tpos zu ändern
+            \item BM operatoren: Wie benutzen BM die vorher besprochenen Metadaten, Definition von Eigenschaften ihrer Operatoren
+            \item Iteration: Ausblick auf mehr als einen Änderungsschritt + konkreter Operator
         \end{itemize}
@@
         \begin{itemize}
-            \item Beispiel Frage zur Motivation, wird unser Beispiel sein. Wir haben zwei Verdächtige und diverse Beweise und Indizien, wie bilden wir uns ein Bild über die Welt?
+            \item Beispiel Frage zur Motivation, wird unser Beispiel sein.
+Unser Agent ist ein Richter in einem Mordprozess, wir haben zwei Verdächtige und diverse Beweise und Indizien, wie bilden wir uns ein Bild über die Welt?
             \item Iterierte Information: Immer wieder neue Informationen nacheinander mit der wir unseren GLauben immer wieder anpassen müssen.
-            \item Unvollständige Information: Kein gesichertes Wissen sondern Glauben und Annahmen aus Zeugenaussagen/Indizien
-            \item Inkonsistente Information: Zeugen können lügen, Indizien falsch sein, Informationen können mit dem aktuellen Glauben inkonsistent sein
-            \item Keine reine richtig/falsch Frage.
-Soll neuer Information immer geglaubt werden?
-Wie sollen Konflikte gelöst werden?
-Wie kann man abbilden, dass der Richter mit Indizien für einen Sachverhalt immer mehr bereit ist an diesen Sachverhalt zu glauben?
+            \item Nicht perfekte Information: Kein gesichertes Wissen sondern Zeugenaussagen/Indizien, können falsch sein, können unserem aktuellem Weltbild widersprechen
+            \item Keine Frage mit richtig/falsch Antwort. Soll neuer Information immer geglaubt werden? Wie sollen Konflikte gelöst werden?
         \end{itemize}
@@
         \begin{itemize}
+            \item Einordnung des Papiers in einen Kontext
             \item Belief change, Glaubens änderung, Veränderung der Weltansicht mit neuen, unsicheren informationen
-            \item Agent kann mensch oder maschine sein, phylosophie oder KI
+            \item Agent kann mensch oder maschine sein, Philosophie oder KI
             \item Unterschiedliche Lösungsansätze, nichtmonotone logik bekannt aus lehrstuhl kursen (truth maintenance systems, default logic wie reiter), probabilistisches denken (auch in Lehrstuhl kursen),
             \item Belief revision: operator basiert. Operatoren die einen Agentenstatus in einen neuen überführen mit neuen infromationen: definieren und Eigenschaften diskutieren
-            \item One step vs iterated depending: Je nachdem ob man eine neue information betrachtet oder eine Reihe von neuen informationen
+            \item One step vs iterated: Je nachdem ob man eine neue information betrachtet oder eine Reihe von neuen informationen
             \item Booth and Meyer: iterated belief revision
@@
         \begin{itemize}
-            \item Konditionaler Glauben Ändern: Indizien für Sachverhalt = Sachverhalt nicht direkt glauben aber bei mehr Indizien immer mehr daran glauben/immer mehr bereit sein es zu akzeptieren.
-            \item Ziel des Papiers: Revisionsoperatoren besprechen für die änderung von konditionalen glauben
-            \item Wie? über die definition von postulaten die diese operatoren einschränken und damit eine familie von operatoren definieren über die wir reden können
-            \item postulate sind nicht zwingend, nur zur einschränkung damit wir über diese operatoren reden können
+            \item Forschungsfrage des papiers
+            \item Wie kann man konditionalen Glauben ändern mithilfe von Revisionsoperatoren
+            \item Definition von postulaten die alle möglichen operatoren einschränken und damit eine familie von operatoren definieren über die wir reden können
+            \item Konkreten beispieloperator definieren der diese Postulate erfüllt
         \end{itemize}

### 2021-03-10 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: more notes

@@
         \item Jetzt: Verstehen der Forschungsfrage, Einordnung des Papiers in einen Forschungskontext und Aufsetzen des begleitenden Beispiels ohne Formalisierung
+        \item TIME: ~2
+        \item TAKES: 5-6
     \end{itemize}
@@
         \item Jetzt: Postulate um Änderungen dieser Glaubensmengen/Annahmen mit neuen Informationen einzuschränken
+        \item TIME: ~7
+        \item TAKES: 10-11
     \end{itemize}
@@
         \item $Mod(p) = \modelsOf{p} = \{ 100, 101, 110, 111\}$, $100 \in \modelsOf{p}$
-        \item Lower case greek letters often used for propositional sentences $\alpha$
+        \item Lower case greek letters used for propositional sentences $\alpha$
     \end{itemize}
@@
         \begin{itemize}
-            \item Konsistentes Beispiel in der Präsentation, der Agent ist ein Richter in einem Mörderprozess vor Gericht, John und Marry sind verdächtige und das Opfer könnte ein alien sein
-            \item Beispiel inspiriert aus der Literatur
-            \item Aussagenlogik, Aussagenlogische Signatur mit Aussagenvariablen p, q, r
-            \item "Mögliche Welt" als aussagenlogische Interpretationen/Belegungen, damit 2 hoch 3 = 8 mögliche Alternativen hier
+            \item Der Agent ist ein Richter in einem Mordprozess vor Gericht, John und Marry sind verdächtige und das Opfer könnte ein alien sein
+            \item Beispiel inspiriert aus der Literatur, "übersetzt" in Syntax die evtl bekannt ist
+            \item Logische Sprache, Aussagenlogik, Aussagenlogische Signatur mit Aussagenvariablen p, q, r
+            \item "Mögliche Welt" als aussagenlogische Interpretationen/Belegungen, damit 8 Alternativen hier
             \item Kodierung der Welt als Tupel von Wahrheitswerten (0 = false, 1 = true)
+            \item Beispiele für 1-2 Welten durchgehen: 010 = Mary ist Mörderin, Opfer ist kein Alien, 111 = John und Mary sind die Mörder, haben ein Alien getötet
             \item models of syntax, modelle von p
-            \item Aussagenlogische formeln als griechische buchstaben
-            \item Beispiele für 1-2 Welten durchgehen: 010 = Mary ist Mörderin, Opfer ist kein Alien, 111 = John und Mary sind die Mörder, haben ein Alien getötet
+            \item Aussagenlogische formeln als kleine griechische buchstaben
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Belief Sets}
+    \begin{itemize}
+        \item Set of propositions the agent accepts as true at any point in time \cite{Ferme2011}
+        \item Deductively closed
+        \item Possible for example: $Cn(\{ p \vee q, \neg(p \wedge q), \neg r \})$
+    \end{itemize}
+
+    \note{
+        \begin{itemize}
+            \item Glaubensmengen als aktuell als wahr akzeptierte Sätze eines Agenten
+            \item deduktiv abgeschlossen, d.h. alle formeln und logische folgerungen aus ihnen
+            \item Betrachtungsgegenstand von AGM-Theorie \cite{Alchourron1985}, wie kann man sie ändern mit neuen informationen
+            \item Zusätzlich bei menschlichem Schließen: Für wie wahrscheinlich halte ich etwas, wann wäre ich bereit es zu akzeptieren? -> Konditionale annahmen/glauben
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Epistemic States}
+    \begin{itemize}
+        \item abstract entity $\mathbb{E}$ that contain all information an agent need for their reasoning \cite{Darwiche1997}
+        \item strategy for reasoning can be modeled as tpo $\leq_{\mathbb{E}}$ over worlds
+        \item belief sets $B(\mathbb{E})$ can be extracted from epistemic states
+              \begin{itemize}
+                  \item set of minimal worlds in which $\alpha$ is true: $min(\alpha, \leq_{\mathbb{E}})$, set of most plausible worlds:  $min(\top, \leq_{\mathbb{E}})$
+                  \item Set of most plausible worlds $min(\top, \leq_{\mathbb{E}})$
+                  \item All sentences true in those worlds: $Th(min(\top, \leq_{\mathbb{E}}))$
+              \end{itemize}
+    \end{itemize}
+
+    \note{
+        \begin{itemize}
+            \item  Strategie des Agenten wie er seinen Glauben ändert, damit auch die konditionalen annahmen.
+            \item Darwiche and Pearl argumentieren das Belief sets nicht ausreichend sind, schlagen epistemische staten vor, abstrakt und enthalten glaubensmenge und strategie.
+            \item Strategie kann in form einer tpo über die welten definiert werden
         \end{itemize}
@@
             \item Mathematisch ausgedrückt sind sie die Äquivalenzklassen zur Symmetrie (teilt die Welten in disjunkte Teilmengen ein)
-        \end{itemize}
-    }
-\end{frame}
-
-\begin{frame}{Belief Sets}
-    \begin{itemize}
-        \item Set of propositions the agent accepts as true at any point in time \cite{Ferme2011}
-        \item Deductively closed
-        \item Possible for example: $Cn(\{ p \vee q, \neg(p \wedge q), \neg r \})$
-    \end{itemize}
-    % TODO: Cn here good?
-
-    \note{
-        \begin{itemize}
-            \item Belief sets als aktuell als wahr akzeptierte Sätze eines Agenten
-            \item deduktiv abgeschlossen
-            \item Gegensatz zu konditionalen glauben: Sätze im Belief set werden als war angenommen.
-            \item Betrachtungsgegenstand von AGM-Theorie \cite{Alchourron1985} die Postulate definiert haben um Belief set revision einzuschränken, rationale revision, wir sprechen das allerdings später an weil wir die neu formulierten Postulates von \cite{Darwiche1997} nutzen
-        \end{itemize}
-    }
-\end{frame}
-
-\begin{frame}{Epistemic States}
-    \begin{itemize}
-        \item abstract entity $\mathbb{E}$ that contain all information an agent need for their reasoning \cite{Darwiche1997}
-        \item strategy for reasoning can be modeled as tpo $\leq_{\mathbb{E}}$ over worlds
-        \item belief sets $B(\mathbb{E})$ can be extracted from epistemic states
-              \begin{itemize}
-                  \item set of minimal worlds in which $\alpha$ is true: $min(\alpha, \leq_{\mathbb{E}})$, set of most plausible worlds:  $min(\top, \leq_{\mathbb{E}})$
-                  \item Set of most plausible worlds $min(\top, \leq_{\mathbb{E}})$
-                  \item All sentences true in those worlds: $Th(min(\top, \leq_{\mathbb{E}}))$
-              \end{itemize}
-    \end{itemize}
-    % TODO very complex, make shorter?
-    \note{
-        \begin{itemize}
-            \item Darwiche and Pearl argumentieren das Belief sets nicht ausreichend sind.
-            \item Die Postulate von AGM definieren nur wie sich belief sets ändern (prinzip of least change/geringste änderung) aber conditional beliefs können sich ändern wie sie wollen.
-            \item Epistemic states enthalten die Strategie des Agenten wie er seinen Glauben ändert, damit auch die conditional beliefs.
-            \item ("commonly used" does not mean has to be used, abstract) - BM nehmen es aber an in ihrem paper
         \end{itemize}
@@
             \tiny
+            \item AGM postulate für belief set änderung nach dem prinzip des minimal change, neu formuliert mit der epistemischen stati sicht
             \item $\mathbb{E}$ als epistemischer status, $B(\mathbb{E})$ belief set des status, $B(\mathbb{E}) + \alpha$ ist die expansion $B(\mathbb{E})$ mit $\alpha$ ($\alpha$ hinzufügen.
@@
         \begin{itemize}
-            \item Zusätzliche postulate von DP um conditional belief revision einzuschränken
+            \item Zusätzliche postulate von DP um die änderung von konditionalen annahmen einzuschränken
             \item Semantische version aka wie sich die Ordnung der Welten ändert mit v,w in W
-            \item CR1/2: Relative Ordnung der alpha/not alpha welten bleibt gleich bei alpha/not alpha revision
-            \item CR3 wenn eine alpha welt strikt bevorzugt wurde vor einer not alpha welt dann muss das auch nach einer revision mit alpha gelten
-            \item CR4 wie CR3 nur für "weak preference"
+            \item CR1/2: Relative Ordnung der welten die alpha modelle/nicht alpha modelle sind bleibt gleich bei revision mit alpha (minimal change)
+            \item CR3 wenn eine welt die ein alpha model ist strikt bevorzugt wurde vor einem nicht model dann muss das auch nach einer revision mit alpha gelten
+            \item CR4 wie CR3 nur für schwache ordnung
         \end{itemize}
@@
         \item Jetzt: Einführung einer intuitiven Visualisierung der neuen Struktur die wir im weiteren Verlauf nutzen
+        \item TIME: ~17
+        \item TAKES:
     \end{itemize}

### 2021-03-10 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: notes

@@
         \item Paper "How to Revise a Total Preorder" von booth and meyer
+        \item Das papier bespricht vieles, wir konzentrieren uns auf: operatoren die die weltanschauung eines agenten unter neuen informationen anpassen
         \item Folien sind nummeriert unten rechts, bei Fragen am besten Nummer aufschreiben
@@
         \item TIME: ~17
-        \item TAKES:
+        \item TAKES: 9-10
     \end{itemize}
@@
         \item Additional structure $W^{\pm} = \{x^{\epsilon} \mid x \in W \textrm{ and } \epsilon \in \{+, -\}\}$
+        \item Interval representing a world $(w^{+}, w^{-})$
         \item "A bad day surfing is better than a good day working" \cite{booth2006bad}
         \item Worlds are either supported by evidence or not $w \in \modelsOf{\alpha}$ / $w \in \modelsOf{\neg\alpha}$
-        \item Interval representing a world $(w^{+}, w^{-})$
-    \end{itemize}
-    \note{
-        \begin{itemize}
-            \item zusätzliche struktur um plausibilität von welten in W nach neuer information zu modelieren
+    \end{itemize}
+    \note{
+        \begin{itemize}
+            \item zusätzliche struktur W+- um unterschiedliche plausibilität von welten in W nach neuer information zu modelieren
             \item "A bad day surfing is better than a good day working" als idee das eine Welt sogar unter evidenz die sie nicht supported mehr plausibel bleiben kann, e.g.
@@
         \item Jetzt: Abstrakte tpo revision am Beispiel
+        \item TIME: ~26
+        \item TAKES: 19
     \end{itemize}
@@
         \item Jetzt: Wie die Revision von Annahmen funktioniert für mehr als einen Input
+        \item TIME: ~45
+        \item TAKES:
     \end{itemize}

### 2021-03-10 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: small fixes

@@
             \item Syntax: neue tpo als tpo subscript alpha, generiert mit superskript *
-            \item Damit operatorbasierte belief revision, konditionale glauben (strategie) in form der tpo und glaubensset weil man es aus der tpo extrahieren kann
             \item Prinzip einfach: Für jeden satz alpha und welt x, ASSOZIIERE x mit ihrer positive representation x+ in w+ wenn x ein model von alpha ist und auf ihre negative representation x- wenn sie kein model von alpha ist
             \item Die neue TPO ergibt sich dann aus der Ordnung auf den jeweiligen positiven/negativen representationen
+            \item Damit operatorbasierte belief revision, konditionale glauben (strategie) in form der tpo und glaubensset weil man es aus der tpo extrahieren kann
         \end{itemize}
@@
     \begin{itemize}
-        \item for $010, 110 \in W$, $010 \leq 110$ before, revise by $\alpha = p$
+        \item for $010, 110 \in W$, $010 < 110$ before, revise by $\alpha = p$
     \end{itemize}
@@
             \item BM vergleichen sie mit den AGM postulaten, AGM postulate für revision von belief sets, postulate 1-5 für revision von tpos
-            \item charakteristisch für "admissible revision operators" die eingaben nicht ignorieren, selbst wenn es nicht zu Änderungen am belief set führt (siehe 5)
+            \item (charakteristisch für "admissible revision operators" die eingaben nicht ignorieren, selbst wenn es nicht zu Änderungen am belief set führt (siehe 5))
             \item (im gegensatz zu e.g. natural revision von boutilier die Änderungen in conditional beliefs minimiert)

### 2021-03-11 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: timing data
feat: small changes and timing

@@
         \item Jetzt: Verstehen der Forschungsfrage, Einordnung des Papiers in einen Forschungskontext und Aufsetzen des begleitenden Beispiels ohne Formalisierung
-        \item TIME: ~2
         \item TAKES: 5-6
@@
         \item Conditional beliefs \cite{Darwiche1997}
-        \item Change of conditional beliefs \cite{Booth2011}
+        \item Strategy to change conditional beliefs \cite{Booth2011}
     \end{itemize}
@@
         \item Jetzt: Postulate um Änderungen dieser Glaubensmengen/Annahmen mit neuen Informationen einzuschränken
-        \item TIME: ~7
-        \item TAKES: 10-11
+        \item TAKES: 6-11
     \end{itemize}
@@
         \item $Mod(p) = \modelsOf{p} = \{ 100, 101, 110, 111\}$, $100 \in \modelsOf{p}$
-        \item Lower case greek letters used for propositional sentences $\alpha$
+        \item Lower case greek letters used for formulas $\alpha$
     \end{itemize}
@@
               \begin{itemize}
-                  \item set of minimal worlds in which $\alpha$ is true: $min(\alpha, \leq_{\mathbb{E}})$, set of most plausible worlds:  $min(\top, \leq_{\mathbb{E}})$
                   \item Set of most plausible worlds $min(\top, \leq_{\mathbb{E}})$
@@
             \item Darwiche and Pearl argumentieren das Belief sets nicht ausreichend sind, schlagen epistemische staten vor, abstrakt und enthalten glaubensmenge und strategie.
+            \item Belief sets können von epistemischen Staten extrahiert werden als formeln die in allen plausibelsten Welten wahr sind
+            \item Was sind plausibelste welten? tpo!
             \item Strategie kann in form einer tpo über die welten definiert werden
@@
 Wird "non-priotized revision" genannt
-            \item 3 und 4: "Inclusion" und "Vacuity": zusammen, wenn neues belief ist konsistent mit dem vorherigen belief set dann gibt es keinen grund beliefs zu entfernen.
+            \item 3 und 4: zusammen, wenn neues belief ist konsistent mit dem vorherigen belief set dann gibt es keinen grund beliefs zu entfernen.
 das neue belief set wird vorheriges belief set + alpha + was aus alpha und belief set folgt sein, minimal change wenn alpha konsistent mit belief set
@@
         \item Jetzt: Einführung einer intuitiven Visualisierung der neuen Struktur die wir im weiteren Verlauf nutzen
-        \item TIME: ~17
-        \item TAKES: 9-10
+        \item TAKES: 9-15
     \end{itemize}
@@
         \item Jetzt: Abstrakte tpo revision am Beispiel
-        \item TIME: ~26
-        \item TAKES: 19
+        \item TAKES: 11-19
     \end{itemize}
@@
             \item 3 und 4: die relative Ordnung für Welten die entweder beide Modelle für die Eingabe sind oder nicht muss gleich bleiben (schon gegeben in conditional belief revision postulates CR1/CR2 von Darwiche and pearl)
-            \item 5: wenn eine welt x mindestens so plausibel ist wie eine Welt y soll x nach einer Eingabe für die x ein model ist und y nicht strikt plausibler sein (ähnlich wie CR3/4 von DP aber strenger)
+            \item 5: eine welt x ist mindestens so plausibel ist wie eine Welt y.
+x soll nach einer Eingabe, für die x ein model ist und y nicht model ist, strikt plausibler sein (ähnlich wie CR3/4 von DP aber strenger)
             \item BM vergleichen sie mit den AGM postulaten, AGM postulate für revision von belief sets, postulate 1-5 für revision von tpos
@@
         \begin{itemize}
-            \item theorem 1 als definition der funktionen/revisionsoperatoren für eine tpo die BM diskutieren/vorschlagen
-            \item erinnern an faithful tpo, W+-, 1-7
+            \item theorem definiert die familie von operatoren die booth und meyer diskutieren
+            \item funktionen * die aus einer tpo und einer formel in L eine neue tpo erzeugen
+            \item generiert aus den vorgestellten strukturen wenn sie postulate erfüllt
         \end{itemize}
@@
         \begin{itemize}
+            \item (OPTIONAL oder sehr schnell)
             \item Es gibt postulate die erfordern, dass neuen Informationen immer geglaubt wird und sie in das belief set aufgenommen werden, e.g. \ref{E2} als $\alpha \in B(\mathbb{E}\ast\alpha)$
@@
         \item Jetzt: Ein möglicher konkreter Beispieloperator + Visualisierung
-        \item Jetzt: Wie die Revision von Annahmen funktioniert für mehr als einen Input
-        \item TIME: ~45
-        \item TAKES:
+        \item Jetzt: Wie die Revision von Annahmen funktioniert für mehr als einen Input, iterated tpo revision!
+        \item TAKES: 10-15
     \end{itemize}
@@
             \item damit neue tpo ablesbar, minimale welt 100, neues belief set "John ist der mörderer" wie vorher und intuitiv
-            \item was hat sich jetzt geändert? die konditionalen annahmen, was der agent bereit ist zu akzeptieren mit neuen beweisen
+            \item was hat sich jetzt geändert? die konditionalen annahmen, tpo revision was der agent bereit ist zu akzeptieren mit neuen beweisen
+            \item aber auch: die strategie für zukünftige tpo revision (W+- und faithful tpo)
         \end{itemize}
@@
             \item hier, revision mit alpha = r = "Das opfer war ein alien"
-            \item wie vorher besprochen, trotz der evidenz ist "das opfer ist ein alien" nicht teil der minimalen welten und damit nicht teil des belief sets (non priotized revision)
-            \item aber die konditionalen annahmen haben sich jetzt verändert, der abstand zwischen den alien welten und nicht alien welten ist weg
+            \item trotz der evidenz ist "das opfer ist ein alien" nicht teil der minimalen welten und damit nicht teil des belief sets (non priotized revision)
+            \item aber die strategie für konditionalen annahmen revision hat sich jetzt verändert, der abstand zwischen den alien welten und nicht alien welten ist weg
             \item 1. tpo revision, 1. neue tpo ablesbar

### 2021-03-11 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: notes

@@
         \begin{itemize}
-            \item Einordnung des Papiers in einen Kontext
+            \item Einordnung des Papiers in ein Forschungsgebiet
             \item Belief change, Glaubens änderung, Veränderung der Weltansicht mit neuen, unsicheren informationen
@@
 Daher nehmen sie E6 nicht an und nur E1-5, E7-8 als "DP-AGM"
-            \item 7 und 8: Wenn ein belief set nach revision mit alpha konsistent ist mit beta dann kann kann man das belief set von alpha und beta durch expansion mit beta erreichen (revision nicht nötig), wieder minimal change
+            \item 7 und 8: Wenn ein belief set nach revision mit alpha konsistent ist mit beta dann kann man das belief set von alpha und beta durch expansion mit beta erreichen (revision nicht nötig), wieder minimal change
         \end{itemize}
@@
         \item Interval representing a world $(w^{+}, w^{-})$
-        \item "A bad day surfing is better than a good day working" \cite{booth2006bad}
         \item Worlds are either supported by evidence or not $w \in \modelsOf{\alpha}$ / $w \in \modelsOf{\neg\alpha}$
@@
             \item zusätzliche struktur W+- um unterschiedliche plausibilität von welten in W nach neuer information zu modelieren
-            \item "A bad day surfing is better than a good day working" als idee das eine Welt sogar unter evidenz die sie nicht supported mehr plausibel bleiben kann, e.g.
-aliens tendenziell nicht so einfach zu glauben
+            \item idee: welten können sogar wenn sie von informationen unterstützt werden als nicht so plausibel wie andere welten angesehen werden.
+e.g.
+welten in denen es aliens gibt glaubt man eventuell nicht, selbst wenn man informationen erhält die für sie sprechen
         \end{itemize}

### 2021-03-12 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: final panic notes

@@
         \item Paper "How to Revise a Total Preorder" von booth and meyer
-        \item Das papier bespricht vieles, wir konzentrieren uns auf: operatoren die die weltanschauung eines agenten unter neuen informationen anpassen
+        \item Das papier bespricht vieles, wir konzentrieren uns auf: operatoren die die weltanschauung eines agenten unter neuen informationen anpassen, nur tpo revision an sich
         \item Folien sind nummeriert unten rechts, bei Fragen am besten Nummer aufschreiben
@@
         \begin{itemize}
+            \item Zentral informal: Funktion * die für einen Status und neue Informationen einen neuen Status ermitteln
             \item Einführung mit Motivation, Forschungskontext und Beispiel
             \item Formaler Hintergrund: Festlegen Notation, was sind TPOs überhaupt
-            \item Dann: Wie bauen Booth und Meyer auf der vorherigen Arbeit auf um tpos zu ändern
+            \item Benötigte neue Metadaten, Operator für tpo revision definieren, besprechen wie man diese neuen strukturen anpassen kann
+            \item Dann: Wie bauen Booth und Meyer auf der vorherigen Arbeit auf um tpos zu ändern, welche neuen metadaten/strukturen brauche sie dafür?
             \item BM operatoren: Wie benutzen BM die vorher besprochenen Metadaten, Definition von Eigenschaften ihrer Operatoren
-            \item Iteration: Ausblick auf mehr als einen Änderungsschritt + konkreter Operator
+            \item Iteration: Ausblick auf mehr als einen Änderungsschritt + konkreter Operator für die änderung der neuen struktur
         \end{itemize}
@@
     \begin{itemize}
-        \item "conditional belief" revision operators
+        \item conditional belief revision operators
         \item axiomatisation of a family of operators by defining properties
@@
             \item Forschungsfrage des papiers
+            \item "conditional belief revision  operators" = tpo revision operatoren
             \item Wie kann man konditionalen Glauben ändern mithilfe von Revisionsoperatoren
@@
 
-\begin{frame}{Epistemic States}
-    \begin{itemize}
-        \item abstract entity $\mathbb{E}$ that contain all information an agent need for their reasoning \cite{Darwiche1997}
-        \item strategy for reasoning can be modeled as tpo $\leq_{\mathbb{E}}$ over worlds
-        \item belief sets $B(\mathbb{E})$ can be extracted from epistemic states
-              \begin{itemize}
-                  \item Set of most plausible worlds $min(\top, \leq_{\mathbb{E}})$
-                  \item All sentences true in those worlds: $Th(min(\top, \leq_{\mathbb{E}}))$
-              \end{itemize}
-    \end{itemize}
-
-    \note{
-        \begin{itemize}
-            \item Strategie des Agenten wie er seinen Glauben ändert, damit auch die konditionalen annahmen.
-            \item Darwiche and Pearl argumentieren das Belief sets nicht ausreichend sind, schlagen epistemische staten vor, abstrakt und enthalten glaubensmenge und strategie.
-            \item Belief sets können von epistemischen Staten extrahiert werden als formeln die in allen plausibelsten Welten wahr sind
-            \item Was sind plausibelste welten? tpo!
-            \item Strategie kann in form einer tpo über die welten definiert werden
-        \end{itemize}
-    }
-\end{frame}
-
-\begin{frame}{Total preorders}
-    \begin{itemize}
-        \item Common tool to handle preference orderings over propositional worlds \cite{Booth2011}
-        \item binary relation $\leq$, total, reflexive, transitive
-        \item  $<$ strict, $\sim$ symmetric closure
-    \end{itemize}
-    \note{
-        \begin{itemize}
-            \item übliches werkzeug um präferenzen von möglichen welten zu modellieren
-            \item total (for all $x, y \in W$ either $x \leq y$ or $y \leq x$)
-            \item reflexive ($x \leq x$ for all $x \in W$)
-            \item transitive (if $x \leq y$ and $y \leq z$ then $x \leq z$)
-            \item  $<$ strict part of $\leq$
-            \item $\sim$ (tilde) symmetrische relation auf of $\leq$ (i.e. $x \sim y$ iff $x \leq y$ and $y \leq x$)
-        \end{itemize}
-    }
-\end{frame}
-
-\begin{frame}{Preorder example}
-    \begin{itemize}
-        \item Judge beliefs
-              \begin{itemize}
-                  \item Murderer probably acted alone but possible that they conspired
-                  \item Unlikely, but not impossible, for the victim to be an alien
-              \end{itemize}
-        \item $\leq$ over $W$: $010 \sim 100 < 000 \sim 110 < 011 \sim 101 < 001 \sim 111$
-    \end{itemize}
-    \note{
-        \begin{itemize}
-            \item Beispiel TPO anhand des richters der denkt einer der angeklagten ist wahrscheinlich der mörderer und hat alleine gehandelt. sehr unwahrscheinliche aber möglich, opfer ist ein alien.
-            \item ein Mörderer und kein Alien gleich plausibel, dann kein/beide, dann jeweils mit Alien
-        \end{itemize}
-    }
-\end{frame}
-
-\begin{frame}{Preorder visualisation}
-    \label{slide:vis-ranks}
-    \begin{itemize}
-        \item $[[x]]_{\sim} = \{y \mid y \sim x\}$
-        \item $[[x]] \leq [[y]]$ iff $x \leq y$
-    \end{itemize}
-
-    \begin{table}[H]
-        \centering
-        \begin{tabular}{llll}
-            $R_{1}$                                          & $R_{2}$                                         & $R_{3}$                                         & $R_{4}$ \\ \hline
-            \multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}$010$\\ $100$\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}$000$\\ $110$\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}$011$\\ $101$\end{tabular}} &
-            \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}$001$\\ $111$\end{tabular}}                                                                                                                \\ \hline
-        \end{tabular}
-        \caption{Visualizing a tpo as a linearly ordered set of ranks, as done in \cite{booth2006bad}}.
-        \label{tab:visualising-a-tpo-example}
-    \end{table}
-
-    \note{
-        \begin{itemize}
-            \item TPOs können visualisiert werden als geordnete Liste von Rängen auf denen die Welten sind
-            \item Die Ränge enthalten jeweils Welten mit gleicher Plausibilität
-            \item Mathematisch ausgedrückt sind sie die Äquivalenzklassen zur Symmetrie (teilt die Welten in disjunkte Teilmengen ein)
-        \end{itemize}
-    }
-\end{frame}
-
-\begin{frame}{Belief Set Revision Postulates\footnote{AGM postulates \cite{Alchourron1985}, reformulated for epistemic states by Darwiche and Pearl \cite{Darwiche1997}}}
+\begin{frame}{Belief Set Revision Postulates\footnote{AGM postulates \cite{Alchourron1985}}}
     \label{slide:e1-8}
-    \begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\mathbb{E}\!*\!\arabic*$)]
-        \item\label{E1} $\qquad B(\mathbb{E}\ast\alpha) = Cn(B(\mathbb{E}\ast\alpha))$
-        \item\label{E2} $\qquad \alpha \in B(\mathbb{E}\ast\alpha)$
-        \item\label{E3} $\qquad B(\mathbb{E}\ast\alpha)  \subseteq B(\mathbb{E})+\alpha$
-        \item\label{E4} $\qquad \textrm{If } \neg \alpha \notin B(\mathbb{E}) \textrm{ then } B(\mathbb{E}) + \alpha \subseteq B(\mathbb{E} \ast \alpha)$
-        \item\label{E5} $\qquad \textrm{If } \mathbb{E} = \mathbb{F} \textrm{ and } \alpha \equiv \beta \textrm{ then } B(\mathbb{E} \ast \alpha) = B(\mathbb{F} \ast \beta)$
-        \item\label{E6} $\qquad \bot \in B(\mathbb{E} \ast \alpha) \textrm{ iff } \models \neg \alpha$
-        \item\label{E7} $\qquad B(\mathbb{E} \ast (\alpha \wedge \beta)) \subseteq B(\mathbb{E} \ast \alpha) + \beta$
-        \item\label{E8} $\qquad \textrm{If } \neg \beta \notin B(\mathbb{E} \ast \alpha) \textrm{ then } B(\mathbb{E} \ast \alpha) + \beta \subseteq B(\mathbb{E} \ast (\alpha \wedge \beta))$
-    \end{enumerate}
+    \begin{itemize}
+        \item AGM theory for belief set revision
+        \item minimal change for belief set with new information
+        \item no restrictions on the changes in conditional beliefs
+    \end{itemize}
+    %\begin{enumerate}[wide=0pt, widest=99,leftmargin=\parindent,label = ($\mathbb{E}\!*\!\arabic*$)]
+    %    \item\label{E1} $\qquad B(\mathbb{E}\ast\alpha) = Cn(B(\mathbb{E}\ast\alpha))$
+    %    \item\label{E2} $\qquad \alpha \in B(\mathbb{E}\ast\alpha)$
+    %    \item\label{E3} $\qquad B(\mathbb{E}\ast\alpha)  \subseteq B(\mathbb{E})+\alpha$
+    %    \item\label{E4} $\qquad \textrm{If } \neg \alpha \notin B(\mathbb{E}) \textrm{ then } B(\mathbb{E}) + \alpha \subseteq B(\mathbb{E} \ast \alpha)$
+    %    \item\label{E5} $\qquad \textrm{If } \mathbb{E} = \mathbb{F} \textrm{ and } \alpha \equiv \beta \textrm{ then } B(\mathbb{E} \ast \alpha) = B(\mathbb{F} \ast \beta)$
+    %    \item\label{E6} $\qquad \bot \in B(\mathbb{E} \ast \alpha) \textrm{ iff } \models \neg \alpha$
+    %    \item\label{E7} $\qquad B(\mathbb{E} \ast (\alpha \wedge \beta)) \subseteq B(\mathbb{E} \ast \alpha) + \beta$
+    %    \item\label{E8} $\qquad \textrm{If } \neg \beta \notin B(\mathbb{E} \ast \alpha) \textrm{ then } B(\mathbb{E} \ast \alpha) + \beta \subseteq B(\mathbb{E} \ast (\alpha \wedge \beta))$
+    %\end{enumerate}
 
@@
 
+\begin{frame}{Epistemic States}
+    \begin{itemize}
+        \item abstract entity $\mathbb{E}$ that contain all information an agent need for their reasoning \cite{Darwiche1997}
+        \item strategy for reasoning can be modeled as tpo $\leq_{\mathbb{E}}$ over worlds
+        \item belief sets $B(\mathbb{E})$ can be extracted from epistemic states
+              \begin{itemize}
+                  \item Set of most plausible worlds $min(\top, \leq_{\mathbb{E}})$
+                  \item All sentences true in those worlds: $Th(min(\top, \leq_{\mathbb{E}}))$
+              \end{itemize}
+    \end{itemize}
+
+    \note{
+        \begin{itemize}
+            \item Strategie des Agenten wie er seinen Glauben ändert, damit auch die konditionalen annahmen.
+            \item Darwiche and Pearl argumentieren das Belief sets nicht ausreichend sind, schlagen epistemische staten vor, abstrakt und enthalten glaubensmenge und strategie.
+            \item Belief sets können von epistemischen Staten extrahiert werden als formeln die in allen plausibelsten Welten wahr sind
+            \item Was sind plausibelste welten? tpo!
+            \item Strategie kann in form einer tpo über die welten definiert werden
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Total preorders}
+    \begin{itemize}
+        \item Common tool to handle preference orderings over propositional worlds \cite{Booth2011}
+        \item binary relation $\leq$, total, reflexive, transitive
+        \item  $<$ strict, $\sim$ symmetric closure
+    \end{itemize}
+    \note{
+        \begin{itemize}
+            \item übliches werkzeug um präferenzen von möglichen welten zu modellieren
+            \item total (for all $x, y \in W$ either $x \leq y$ or $y \leq x$)
+            \item reflexive ($x \leq x$ for all $x \in W$)
+            \item transitive (if $x \leq y$ and $y \leq z$ then $x \leq z$)
+            \item  $<$ strict part of $\leq$
+            \item $\sim$ (tilde) symmetrische relation auf of $\leq$ (i.e. $x \sim y$ iff $x \leq y$ and $y \leq x$)
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Preorder example}
+    \begin{itemize}
+        \item Judge beliefs
+              \begin{itemize}
+                  \item Murderer probably acted alone but possible that they conspired
+                  \item Unlikely, but not impossible, for the victim to be an alien
+              \end{itemize}
+        \item $\leq$ over $W$: $010 \sim 100 < 000 \sim 110 < 011 \sim 101 < 001 \sim 111$
+    \end{itemize}
+    \note{
+        \begin{itemize}
+            \item Beispiel TPO anhand des richters der denkt einer der angeklagten ist wahrscheinlich der mörderer und hat alleine gehandelt. sehr unwahrscheinliche aber möglich, opfer ist ein alien.
+            \item ein Mörderer und kein Alien gleich plausibel, dann kein/beide, dann jeweils mit Alien
+        \end{itemize}
+    }
+\end{frame}
+
+\begin{frame}{Preorder visualisation}
+    \label{slide:vis-ranks}
+    \begin{itemize}
+        \item $[[x]]_{\sim} = \{y \mid y \sim x\}$
+        \item $[[x]] \leq [[y]]$ iff $x \leq y$
+    \end{itemize}
+
+    \begin{table}[H]
+        \centering
+        \begin{tabular}{llll}
+            $R_{1}$                                          & $R_{2}$                                         & $R_{3}$                                         & $R_{4}$ \\ \hline
+            \multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}$010$\\ $100$\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}$000$\\ $110$\end{tabular}} & \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}$011$\\ $101$\end{tabular}} &
+            \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}$001$\\ $111$\end{tabular}}                                                                                                                \\ \hline
+        \end{tabular}
+        \caption{Visualizing a tpo as a linearly ordered set of ranks, as done in \cite{booth2006bad}}.
+        \label{tab:visualising-a-tpo-example}
+    \end{table}
+
+    \note{
+        \begin{itemize}
+            \item TPOs können visualisiert werden als geordnete Liste von Rängen auf denen die Welten sind
+            \item Die Ränge enthalten jeweils Welten mit gleicher Plausibilität
+            \item Mathematisch ausgedrückt sind sie die Äquivalenzklassen zur Symmetrie (teilt die Welten in disjunkte Teilmengen ein)
+        \end{itemize}
+    }
+\end{frame}
+
 \begin{frame}{Conditional Belief Revision Postulates\footnote{by Darwiche and Pearl \cite{Darwiche1997}}}
@@
         \item Vorher: Neue Metadaten/Strukturen im epistemischen Zustand und Visualisierung
+        \item Uns interessieren funktionen * die für eine tpo und alle alpha aus L eine neue tpo generieren
         \item Jetzt: Nutzen dieser neuen Strukturen für tpo revision, Postulates für BM revision operatoren und Definition der Familie von BM revisons operatoren
@@
         \begin{itemize}
-            \item theorem definiert die familie von operatoren die booth und meyer diskutieren
+            \item theorem charakterisiert die familie von operatoren die booth und meyer diskutieren
             \item funktionen * die aus einer tpo und einer formel in L eine neue tpo erzeugen
-            \item generiert aus den vorgestellten strukturen wenn sie postulate erfüllt
+            \item erfüllt immer die postulate wenn sie aus den vorgegebenen strukturen generiert wird
+            \item für jeden revisionsoperator * für eine tpo kann man eine faithful tpo generieren die den gleichen operator erzeugt nach der definition hier
         \end{itemize}

### 2021-03-14 paper/1901_3230880_philip_heltweg.tex
fix: fixed missing negation in agm postulate
feat: removed erklaerung page

@@
 
-\begin{titlepage}
-\pagenumbering{gobble}
-  {\centering
-  \vskip 30 pt
-  \LARGE Synopsis of "How to Revise a Total Preorder" \cite{Booth2011} for seminar 1901 - "Representation and processing of uncertain knowledge with logic-based methods" \par
-  \vskip 1.5em
-  \large Philip Heltweg, matriculation number 3230880 \par
-  \vskip 1.5em}
-
-  Ich erkläre, dass ich die schriftliche Ausarbeitung zum Seminar selbstständig und ohne unzulässige Inanspruchnahme Dritter verfasst habe.
-Ich habe dabei nur die angegebenen Quellen und Hilfsmittel verwendet und die aus diesen wörtlich oder sinngemäß entnommenen Stellen als solche kenntlich gemacht.
-Die Versicherung selbstständiger Arbeit gilt auch für enthaltene Zeichnungen, Skizzen oder graphische Darstellungen.
-Die Ausarbeitung wurde bisher in gleicher oder ähnlicher Form weder derselben noch einer anderen Prüfungsbehörde vorgelegt und auch nicht veröffentlicht.
-Mit der Abgabe der elektronischen Fassung der endgültigen Version der Ausarbeitung nehme ich zur Kenntnis, dass diese mit Hilfe eines Plagiatserkennungsdienstes auf enthaltene Plagiate geprüft werden kann und ausschließlich für Prüfungszwecke gespeichert wird.
-\end{titlepage}
-\pagenumbering{arabic}
-
 \title{Of judges, aliens and total preorders}
@@
     \item\label{E3} $\qquad B(\mathbb{E}\ast\alpha)  \subseteq B(\mathbb{E})+\alpha$
-    \item\label{E4} $\qquad \textrm{If } \alpha \notin B(\mathbb{E}) \textrm{ then } B(\mathbb{E}) + \alpha \subseteq B(\mathbb{E} \ast \alpha)$
+    \item\label{E4} $\qquad \textrm{If } \neg \alpha \notin B(\mathbb{E}) \textrm{ then } B(\mathbb{E}) + \alpha \subseteq B(\mathbb{E} \ast \alpha)$
     \item\label{E5} $\qquad \textrm{If } \mathbb{E} = \mathbb{F} \textrm{ and } \alpha \equiv \beta \textrm{ then } B(\mathbb{E} \ast \alpha) = B(\mathbb{F} \ast \beta)$
@@
         \begin{array}{ll}
-                      x^{+} \textrm{ if } x \in \modelsOf{\alpha}\\
+            x^{+} \textrm{ if } x \in \modelsOf{\alpha} \\
             x^{-} \textrm{ if } x \in \modelsOf{\neg\alpha}
@@
     \begin{array}{ll}
-                      p(x^{\epsilon}) \textrm{ if } x \in \modelsOf{\alpha}\\
+        p(x^{\epsilon}) \textrm{ if } x \in \modelsOf{\alpha} \\
         p(x^{\epsilon}) + a \textrm{ if } x \in \modelsOf{\neg\alpha}
